### 2015-05-24 sk_model_v15.tex
w

\documentclass[twocolumn,superscriptaddress,prb,10pt]{revtex4-1}
%\usepackage{verbatim}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage[colorlinks,bookmarks=false,citecolor=blue,linkcolor=red,urlcolor=blue]{hyperref}
\usepackage{times}

%\usepackage[dvips]{graphics}

%%%%%%%%%%%%%   useful shortcuts %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def \h{\hbar}   %  \h won't be used for any greek letter
\def \refe{\eqref}
\def \trm{\textrm}
\def \f{\frac}
\def \hf{\tfrac{1}{2}}    \def \HF{\dfrac{1}{2}}
\def \u{\uparrow}
\def \d{\downarrow}

\def \ord{\mathcal{O}}
\newcommand{\ra}{\rightarrow}   \newcommand{\lra}{\longrightarrow}

\def\lba{\left(}    \def\rba{\right)}
\def\lbc{\left[}    \def\rbc{\right]}
\def\lbb{\left\{}    \def\rbb{\right\}}

\def\tr{\textrm{Tr}}
\def\refe{\eqref}

\newcommand{\bra}[1]{\langle\left.{#1}\right|}
\newcommand{\ket}[1]{\left|{#1}\right.\rangle}
\newcommand{\xpct}[1]{\langle{#1}\rangle}    % expectatn value

%\DeclareMathOperator{\tr}{tr}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\vp}{{\bf p}}  % usual vector quantities
\newcommand{\vq}{{\bf q}}  % double bracketing not required with \vec
\newcommand{\vk}{{\bf k}}  % but required with \bf

\renewcommand{\vr}{{\bf r}} 
\newcommand{\vx}{{\bf x}}

\newcommand{\hc}{\hat{c}}  \newcommand{\hcd}{\hat{c}^\dag} 
\newcommand{\hd}{\hat{d}}  \newcommand{\hdd}{\hat{d}^\dag}

\begin{document}

\title{The classical mutual information in mean-field spin glass models}

\author{Vincenzo Alba}
\affiliation{International School for Advanced Studies (SISSA),
Via Bonomea 265, 34136, Trieste, Italy, 
INFN, Sezione di Trieste}
\author{Stephen Inglis}
\affiliation{Department of Physics and Arnold Sommerfeld
Center for Theoretical Physics, Ludwig-Maximilians-Universit\"at
M\"unchen, D-80333 M\"unchen, Germany}
%\author{Lode Pollet}

\date{\today}

\begin{abstract}

We investigate the \emph{classical} R\'enyi entropy $S_n$ and the associated mutual 
information ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the 
paradigm model of mean-field spin glasses. We use both classical Monte Carlo simulations 
and analytical tools. First, we investigate the S-K model on the $n$-sheets booklet. This 
is obtained by gluing together $n$ independent copies of the model, and it is the 
main ingredient to construct entaglement-related quantities. We find that at low temperature 
the S-K model is in a glassy phase, whereas at high temperature it exhibits paramagnetic 
behavior. Interestingly, the critical temperature of the paramagnetic-glassy transition 
depends in a non-trivial way on the geometry of the booklet. At high-temperatures we provide 
the exact solution of the model exploiting the replica symmetry. This is the permutation 
symmetry among the fictitious replicas that are used in the replica trick to perform disorder 
averages. In the low-temperature glassy phase the replica symmetry has 
to be broken. Using a simple generalization of the celebrated Parisi solution, we provide 
approximated results for thermodynamic quantities and for $S_n$ and ${\mathcal I}_n$. 
Finally, we show that both $S_n$ and ${\mathcal I}_n$ exhibit a volume law in the whole phase 
diagram. Their densities $S_n/N$ and ${\mathcal I}_n/N$ are finite and smooth 
function of the temperature, in the thermodynamic limit. In contrast with local spin models, 
${\mathcal I}_n/N$ does not exhibit any crossing for different system sizes at the 
critical point.

\end{abstract}

% \pacs{73.43.Cd, 71.10.Pm  {\tt check!}}

\maketitle

%########################################################################
\section{Introduction}

Besides being ubiquitous in nature, disorder leads to several intriguing 
physical phenomena. Arguably, \emph{spin glasses} provide one of the most 
striking examples. While at any finite temperature disorder prevents the 
usual magnetic ordering, at low-enough temperatures these systems display a 
new and exotic type of ``order''. In the past decades an intense theoretical 
effort has been devoted to characterizing this spin glass order, the nature of 
the paramagnetic-glassy transition, and that of the associated order 
parameter~\cite{binder-1986,parisi-book,young-1998,nishimori-book,castellani-2005}.

All these issues have been thoroughly addressed in the Sherrington-Kirkpatrick 
(S-K) model~\cite{sherrington-1978,sherrington-1978-prl}, which is exactly 
solvable. The S-K model is a \emph{classical} Ising model on the fully-connected 
graph of $N$ sites, with quenched random interactions. Its hamiltonian reads  
%
\begin{equation}
{\mathcal H}=-\sum\limits_{1\le i<j\le N}J_{ij}S_i S_j-
h\sum\limits_{1\le i\le N}S_i.
\label{SK-intro}
\end{equation}
%
Here $S_i=\pm 1$ are classical Ising spins, $h$ is an external magnetic field, and 
$J_{ij}$ are uncorrelated (from site to site) random variables. The S-K model hosts 
a low-temperature glassy phase, which is separated from a high-temperature paramagnetic 
one by a second order phase transition. In contrast with the mean-field nature of 
Eq.~\eqref{SK-intro}, the solution of the S-K model has been a mathematical challenge. 
Although it was proposed as an ansatz by Parisi~\cite{parisi-1980} more than thirthy 
years ago, its rigourous proof was obtained only recently~\cite{talagrand-2006}. Moreover, 
the solution exhibits several intricate features, such as lack of self-averaging~\cite{pastur-1991}, 
ultrametricity~\cite{mezard-1984,rammal-1986}, and replica symmetry breaking~\cite{parisi-book,
castellani-2005}. The last refers to the breaking of the permutation symmetry among the 
fictitious replicas of the system, which in the standard replica trick~\cite{cardy-book} are 
used to perform disorder averages. Finally, although the applicability of the S-K 
model to describe realistic spin glasses is still highly debated~\cite{yucesoy-2012,
billoire-2012,yucesoy-2013}, we should mention that there are recent proposals on how to 
realize this model in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser 
systems~\cite{ghofraniha-2015}.

In the last decade entanglement-related quantities have emerged as valuable tools to 
understand the physics of complex systems~\cite{amico-2008,eisert-2009,calabrese-2009,
cc-rev}, both classical and quantum. For instance, at a conformally invariant critical 
point entanglement measures contain universal information about the underlying 
conformal field theory (CFT), such as the central charge~\cite{holzhey-1994,vidal-2003,
calabrese-2004,calabrese-2012}. For classical spin models a lot of attention has been 
focused on the \emph{classical} R\'enyi entropy~\cite{jaconis-2013,stephan-2014}. Given 
a bipartition of the system into two complementary subregions $A$ and $B$, the classical 
R\'enyi entropy $S_n(A)$ (with $n\in\mathbb{N}$) is defined as 
%
\begin{equation}
S_n(A)\equiv \frac{1}{1-n}\log\Big(\sum\limits_{i_A\in{\mathcal C}_A} p^n_{i_A}
\Big).i 
\label{renyi-intro}
\end{equation}
%
Here ${\mathcal C}_A$ denotes the set of all the possible spin configurations in part 
$A$, whereas $p_{i_A}$ is the probability of the configuration $i_A$. 
%Clearly, $p_{i_A}\equiv\sum_{j_b\in{\mathcal C}_B}p_{i_A,j_B}$, with $p_{i_A,j_B}$ 
%being the probability that the system is in the configuration $i_A\in{\mathcal C}_A$
%in part $A$, and $j_B\in{\mathcal C}_B$ in part $B$. For a spin model at inverse 
%temperature $\beta$, one has $p_{i_A,j_B}\equiv e^{-\beta E(i_A,j_B)}/Z(\beta)$, 
%where $E(i_A,j_B)$ is the energy of the system, and $Z(\beta)$ its partition function. 
Alternatively, $S_n(A)$ can be obtained from the partition function of the model on 
an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
precise definition). This consists of $n$ independent and identical replicas (the 
booklet ``sheets'') of the model. Notice that these \emph{physical} replicas are different 
from the \emph{fictitious} ones used to perform the disorder average. Each sheet is 
divided into two parts $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. 
The spins in part $A$ of different sheets are constrained to be equal. It is 
convenient to introduce the aspect ratio $0\le\omega\le1$ as  
%
\begin{equation}
\label{a-ratio}
\omega\equiv \frac{N_A}{N}.
\end{equation}
%
Clearly,  Eq.~\eqref{renyi-intro} can be extended to quantum systems~\cite{stephan-2009,
stephan-2010,stephan-2011,zaletel-2011,alcaraz-2013,stephan-2014-a} by interpreting 
$p_{i_A}$ as the probability of finding part $A$ in the \emph{quantum} configuration 
$i_A$. From $S_n(A)$, one defines the classical mutual information ${\mathcal I}_n(A,B)$ 
as 
%
\begin{equation}
{\mathcal I}_n(A,B)\equiv S_n(A)+S_n(B)-S_n(A\cup B). 
\end{equation}
%
For local models ${\mathcal I}_n$ obeys the area law~\cite{wolf-2008} ${\mathcal I}_n(A)
\propto\ell$, with $\ell$ being the length of the boundary between $A$ and $B$. Remarkably, 
for different $\ell$, the ratio ${\mathcal I}_n/\ell$ exhibits a crossing at a second 
order phase transition~\cite{jaconis-2013}, and it can be used as a diagnostic tool for 
critical behaviors. For conformally invariant critical models more universal information 
can be extracted from the subleading contributions, i.e., the corrections to the area 
law, of ${\mathcal I}_n$~\cite{stephan-2014}.

Recently, the study of the interplay between disorder and entanglement became a fruitful 
research area~\cite{refael-2009}. However, the behavior of entanglement-related quantities 
in glassy phases, and at glassy critical points, has not been explored yet. Here we investigate 
both the classical R\'enyi entropy $S_n(A)$ and the mutual information ${\mathcal I}_n$ 
in the S-K model, using classical Monte Carlo simulations and analytical tools. We often 
restrict ourselves to the case with $n=2$. As usual in disordered system, we 
focus on disorder-averaged quantities, considering $[S_n]$ and $[{\mathcal I}_n]$, 
with the brackets $[\cdot]$ denoting the average over different realizations of 
$J_{ij}$ in Eq.~\eqref{SK-intro}.

We start discussing the thermodynamic phase diagram of the S-K model on the $n$-sheets 
booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
We find that for any $\omega$ the S-K model exhibits a low-temperature glassy phase, which 
is divided by the standard paramagnetic one at high temperatures by a critical point. 
Surprisingly, the critical temperature exhibits a non-trivial dependence on $\omega$ 
that we are able to determine analytically. 
In the high-temperature region, for any fixed $\omega$, the permutational symmetry 
among the replicas, both the physical and the fictitious ones, is preserved. This 
allows us to provide an exact analytic expression for the free energy of the model 
and several derived quantities, such as the internal energy. We check our result 
against Monte Carlo simulations, finding perfect agreement. Oppositely, we provide 
both numerical and analytical evidence that in the low-temperature phase, for any 
$\omega$, the replica symmetry has to be broken. Specifically, we numerically observe 
that the replica-symmetric (RS) result for the internal energy  is systematically 
lower than the Monte Carlo data, as in the standard S-K model~\cite{sherrington-1978-prl,
sherrington-1978}. This discrepancy becomes larger upon lowering the temperature.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/cartoon}
\caption{ The booklet geometry considered in this work. (a) The single sheet 
 (``page'') of the booklet: The $N$ spins living on the sheet are divided into 
 two groups $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. Here 
 $\omega\equiv N_A/N$ is the booklet ratio. (b) The $n$ sheets are glued together 
 to form the booklet. The spins in part $B$ of the booklet pages are at inverse 
 temperature $\beta$. The spins in part $A$ are identified  (see Eq.~\eqref{book-constraint}). 
 As a consequence, the effective temperature in part $A$ is $n\beta$. 
 $Z(\omega,n,\beta)$ denotes the partition function of the S-K model on 
 the booklet. 
}
\label{cartoon}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Inspired by the Parisi scheme~\cite{parisi-1979}, we devise a systematic 
way of breaking the replica symmetry in successive steps. Precisely, our scheme  
breaks only the symmetry among the fictitious replicas, preserving that among the 
physical ones. Although this appears natural, we are not able to provide a rigourous 
proof that this is the correct symmetry breaking pattern. In particular, we cannot 
exclude that the symmetry among the physical replicas has to be broken. As a consequence, 
our scheme should be regarded as an approximation, and not as an exact solution. 
Finally, we should mention that we restrict ourselves to the one-level replica symmetry 
breaking ($1$-RSB). This, however, is a minor limitation because, in principle, it is 
possible to implement in our ansatz the full breaking of the replica symmetry 
($\infty$-RSB). Surprisingly, we numerically observe that the $1$-RSB approximation 
for the internal energy is in excellent agreement with the Monte Carlo data for  
$\beta\lesssim 3$, whereas the RS approximation fails already at $\beta\approx 1$. 
This suggests that the $1$-RSB ansatz captures correctly some aspects of the 
replica symmetry breaking.

This scenario, and, in particular, the effects of the replica symmetry breaking, are 
reflected in the behavior of $[S_2]$ and $[{\mathcal I}_2]$. First, since $[S_2]$ exhibits 
the volume law behavior $[S_2]\propto N$, we consider its density $[S_2]/N$. For finite-size 
systems, and for any $\omega$, we find that $[S_2]/N$ exhibits a maximum at infinite 
temperature, and it is a monotonically decreasing function of the temperature. More 
specifically, the Monte Carlo data suggest a vanishing behavior in the zero-temperature 
limit. Moreover, the finite-size corrections are neglegible at high temperatures, 
whereas they increase upon lowering the temperature. A standard finite-size scaling 
analysis shows that in the thermodynamic limit $[S_2]/N$ is finite and smooth as a 
function of $\beta$ and $\omega$, in the whole phase diagram. In the paramagnetic phase 
we are able to calculate the functional form of $[S_2]$, using the replica-symmetric 
approximation. This perfectly matches the Monte Carlo data. At low temperatures deviations 
from the replica-symmetric result are observed, reflecting the replica symmetry breaking. 
Remarkably, we observe that the one-step replica symmetry breaking ($1$-RSB) approximation 
$S_2^{1\textrm{-}RSB}/N$ is in full agreement with the Monte Carlo data for $\beta
\lesssim 3$, confirming what is observed for the internal energy.

Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This  
obeys a volume law for any $\beta$ and $\omega$, in sharp contrast with local spin models, 
where an area law is observed~\cite{wolf-2008}. The mutual information density $[{\mathcal I}_2]/N$ 
vanishes in both the infinite-temperature and the zero-temperature limits, for any $\omega$. 
Surprisingly, for different sizes ${\mathcal I}_2/N$ does not exhibit any crossing at the 
paramagnetic-glassy transition, in striking contrast with local spin models~\cite{jaconis-2013}. 
In the thermodynamic limit $[{\mathcal I}_2]/N$ is finite and smooth (as a function of $\beta$) 
in the whole phase diagram. Interestingly, for any $\omega$, ${\mathcal I}_2/N$ exhibits a 
maximum for $\beta\approx 1$. However, the position of this maximum is not simply related to 
paramagnetic-glassy transition. Finally, at high temperature $[{\mathcal I}_2]/N$ is fully 
described analytically within the replica symmetric approximation, whereas at low temperatures 
one has to include  the effects of the replica symmetry breaking. Similar to $[S_2]$, we observe 
that the $1$-RSB approximation for $[{\mathcal I})_2]/N$, is in good agreement with the Monte Carlo 
data for $\beta\approx 3$.

The Article is organized as follows. In section~\ref{booklet} we introduce the classical 
R\'enyi entropy and the mutual information, reviewing their representation in terms of 
the booklet partition functions. In section~\ref{the-model} we present the structure of 
the  the solution of the S-K model on the booklet. Specifically, we discuss the replica 
trick, which is used to perform disorder averages, and the saddle point approximation in 
the thermodynamic limit . Section~\ref{solution} is concerned with the replica-symmetric 
(RS) approximation. In subsection~\ref{para-section} we focus on the high-temperature 
region where this approximation becomes exact. In subsection~\ref{rs-section} we discuss 
the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} is devoted to   
presenting the one-step replica symmetry breaking ($1$-RSB) approximation. In 
section~\ref{mc-results} we check the validity of both the RS and the $1$-RSB approximations 
against Monte Carlo data. Section~\ref{Renyi-section} and~\ref{I2-section} present our results 
for the classical R\'enyi entropy and the mutual information, respectively. Finally, 
we conclude in section~\ref{conclusions}.

%########################################################################
\section{The booklet construction \& and the classical mutual information}
\label{booklet}

Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
the R\'enyi mutual information ${\mathcal I}_n(A,B,\beta)$ (with $n\in\mathbb{N}$) 
is defined as~\cite{jaconis-2013,stephan-2014} 
%
\begin{equation}
\label{MI}
{\mathcal I}_n(A,B,\beta)\equiv\frac{1}{1-n}\log\Big(
\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z(\beta)^nZ(n\beta)}
\Big).
\end{equation}
%
Here $Z(A,n,\beta)$ is the partition function of the model on the so-called 
$n$-sheet booklet, whereas $Z(\beta)$ and $Z(n\beta)$ are the partition functions 
on a the plane (a single sheet) at inverse temperatures $\beta$ and $n\beta$, 
respectively. The booklet geometry is illustrated in Figure~\ref{cartoon}. The 
sheet is divided into two parts $A$ and $B$ (cf. Figure~\ref{cartoon} (a)). 
Then $n$ copies of the system (``sheets'') are ``glued'' together to form the 
booklet. The spins in part $A$ of different sheets are identified (cf. 
Figure~\ref{cartoon} (b)). Notice that a similar construction~\cite{guerra-2002} 
plays an important role in the mathematical proof of the Parisi ansats. While spins 
in $B$ are at inverse temperature $\beta$, the ones in $A$ are at the effective 
temperature $n\beta$. The definition of $Z(B,n\beta)$ is obtained by exchanging 
$A$ and $B$. Alternatively, ${\mathcal I}_n$ can be rewritten as 
%
\begin{equation}
{\mathcal I}_n(A,B,\beta)=S_n(A)+S_n(B)-S_n(A\cup B),
\end{equation}
%
where $S_n(X)$ is the ``booklet'' classical R\'enyi entropy
%
\begin{equation}
\label{renyi}
S_n(X)\equiv \frac{1}{1-n}\log\left(\frac{Z(X,n,\beta)}{Z^n(\beta)}\right).
\end{equation}
%
Notice that $S_n(X)$ corresponds to $S_n(X)\equiv1/(n-1)\log(F(X,n,\beta))
-n\log(F(\beta))$, where $F(X,n,\beta)\equiv\log(Z(\beta))$ and $F(\beta)
\equiv\log(Z(X,n,\beta))$ are related (apart from a factor $\beta$) to the 
free energy of the model on the booklet and on the plane, respectively.
Since here we focus on the effects of the disorder, we consider 
the disorder-averaged mutual information $[{\mathcal I}_n]$ 
%
\begin{equation}
[{\mathcal I}_n(A,B,\beta)]=[S_n(A)]+[S_n(B)]-[S_n(A\cup B)],
\end{equation}
%
where the square brackets $[\cdot]$ denote the average over different disorder 
realizations (cf. section~\ref{the-model}). Notice that $[{\mathcal I}_n]$ is 
directly obtained from the so-called quenched averaged free energy $[F(X,n,\beta)]$, 
which is usually considered in disordered systems~\cite{cardy-book}.

For clean (i.e., without disorder) \emph{local} spin models ${\mathcal I}_n$ 
obeys the boundary law 
%
\begin{equation}
{\mathcal I}_n(A,B,\beta)=\alpha_n\ell+{\mathcal G}_n+\gamma_n,
\label{GMI}
\end{equation}
%
with $\ell$ the length of the boundary between $A$ and $B$, and 
$\alpha_n,\gamma_n$ two non-universal constants. Here ${\mathcal G}_n$ 
is the so-called geometric mutual information~\cite{stephan-2014}. 
Interestingly, for critical systems ${\mathcal G}_n$ depends only on the 
geometry of $A$ and $B$, and it is universal. In particular, for conformally 
invariant models ${\mathcal G}_n$ can be calculated using standard methods of 
conformal field theory (CFT), and it allows to numerically 
extract universal information about the CFT, such as the central 
charge~\cite{stephan-2014}.  Remarkably, there is numerical evidence that  
${\mathcal I}_n/\ell$ exhibits a crossing for different 
system sizes at a second order phase transition, implying that it 
can be used as a diagnostic tool to detect phase 
transitions~\cite{jaconis-2013}.

%########################################################################
\section{The Sherrington-Kirkpatrick (S-K) model on the booklet}
\label{the-model}

Here we introduce the Sherrington-Kirkpatrick (S-K) model on the booklet 
(see Fig.~\ref{cartoon}). In particular, in subsection~\ref{the-model-def}  
we define the model and its partition function. In subsection~\ref{replica-sec} 
we discuss the replicated booklet construction that is used to calculate the 
disorder-averaged free energy $[F(\omega,n,\beta)]$. 
In~\ref{saddle-point} we consider the thermodynamic limit, 
using the saddle point approximation. We also introduce the overlap tensor,  
which contains all the information about the thermodynamic behavior of the 
model. The analytical formula for the replicated partition function (Eq.~\eqref{Z-ac}) 
of the S-K the model, and the saddle point equations (Eqs.~\eqref{saddle-final}) 
for the overlap tensor are the main results of this section.

%########################################################################
\subsection{The model and its partition function}
\label{the-model-def}

The Sherrington-Kirkpatrick (S-K) model~\cite{sherrington-1978-prl,
sherrington-1978} on the $n$-sheets booklet (cf. Figure~\ref{cartoon}) is 
defined by the Hamiltonian
%
\begin{equation}
{\mathcal H}=-\sum\limits_{r=1}^n\left\{\sum\limits_{i<j}J_{ij}S^{(r)}_i 
S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\right\}.
\label{SK-ham}
\end{equation}
%
Here $S_i^{(r)}=\pm 1$ are classical Ising spins, $r\in[1,n]$ labels the 
different sheets (``pages'') of the booklet, $i\in[1,N]$ denotes the sites on 
each sheet, $J_{ij}$ is the interaction strength, and $h$ is an external 
magnetic field. Here we choose $h=0$. The total number of spins in the booklet 
is $nN$. The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
$N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
In each ``page''  all the sites are divided into two groups $A\equiv\{1,\dots, 
N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ 
sites, respectively. The spins living in part $A$ and different sheets 
are identified, i.e., $\forall i\in A$ one has  
%
\begin{equation}
S_i^{(r)}=S_{i}^{(r')}\quad\forall\, r,r'. 
\label{book-constraint}
\end{equation}
%
Since in each sheet all spins interact with each other, there is no notion of distance. 
between different spins. Thus, physical observables should depend on the booklet geometry 
only through the ratio $\omega\equiv N_A/N_B$.

In Eq.~\eqref{SK-ham} the couplings $J_{ij}\in\mathbb{R}$ are uncorrelated quenched 
random variables. $J_{ij}$ are the same in all the sheets of the booklet. Specifically, 
here we choose $J_{ij}$ distributed according to the (gaussian) distribution ($P(J_{ij})$)  
%
\begin{equation}
P(J_{ij})=
\left(\frac{N}{2\pi}\right)^{1/2}
\exp\Big\{-\frac{N}{2}
\Big(J_{ij}-\frac{J_0}{N}\Big)^2\Big\}.
\label{quenched-distr}
\end{equation}
%
The mean and the variance of $P(\{J_{ij}\})$ are given as $[J_{ij}]=J_0/N$ 
and $[(J_{ij}-[J_{ij}])^2]=J^2/N$, respectively. The square brackets $[\cdot]$ denote 
the average over different realinzations of $J_{ij}$.  Here we restrict ourselves to 
$J_0=0$ and $J=1$. The factors $N$ in Eq.~\eqref{quenched-distr} ensure a well-defined 
thermodynamic limit.

The partition function $Z(\omega,n,\beta,\{J\})$ of the S-K model on the booklet 
at inverse temperature $\beta\equiv 1/T$, and fixed disorder realization $\{J_{ij}\}$, 
reads 
%
\begin{multline}
Z(\omega,n,\beta,\{J\})\equiv\textrm{Tr}'\exp(-\beta{\mathcal H})=\\
\textrm{Tr}'\exp\Big\{\beta\sum\limits_{r}\Big(
\sum\limits_{i<j}S^{(r)}_i 
S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\Big)\Big\},
\label{book-pf}
\end{multline}
%
where $\textrm{Tr}'\equiv \sum_{\{S_i\}}$ denotes the sum over all possible 
spin configurations. The prime in $\textrm{Tr}'$ stresses that only spin configurations 
satisfying the booklet constraint in Eq.~\eqref{book-constraint} are considered. 
In the two limits $\omega\to 0$ and $\omega\to1$ one recovers the standard 
S-K model. In particular, for $\omega=0$, i.e., $n$ disconnected sheets, from 
Eq.~\eqref{book-pf} one has $Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with 
$Z(\beta,\{J\})$ the partition function of the S-K model on the plane. 
On the other hand, for $\omega=1$ it is $Z(1,n,\beta,\{J\})=Z(n\beta,\{J\})$, 
i.e., the partition function of the S-K model at inverse temperature $n\beta$. 
The quenched averaged free energy $[F(\omega,n,\beta)]$, is defined as 
%
\begin{equation}
\label{free-energy}
[F(\omega,n,\beta)]\equiv -\frac{1}{\beta}\int {\mathcal D}\{J\}
\log Z(\omega,n,\beta,\{J\}), 
\end{equation}
%
where $\int{\mathcal D}\{J\}\equiv\prod\nolimits_{i<j}\int_{-\infty}^{
+\infty}dJ_{ij}P(J_{ij})$. Notice that $[F(\omega,n,\beta)]$ is the 
main ingredient to construct the classical R\'enyi entropies and the 
mutual information (cf. Eq.~\eqref{MI} and Eq.~\eqref{renyi}).

At $\omega=0$ and $\omega=1$ the phase diagram of the S-K model in the 
thermodynamic limit is well established~\cite{nishimori-book}. In particular, 
at $\omega=0$ the model exhibits a standard paramagnetic phase in the high 
temperature region, whereas at low temperatures a glassy phase is present, 
with replica-symmetry breaking~\cite{nishimori-book}. The two phases are 
divided by a second order phase transition at $\beta=\beta_c=1$. The phase 
diagram for $\omega=1$ is the same, apart from the trivial redefinition
$\beta\to n\beta$. We anticipate here (see section~\ref{rs-section}) that 
a similar scenario holds for generic $\omega$. Specifically, the glassy 
phase at low temperatures along with the replica symmetry breaking mechanism 
survive for generic $0<\omega<1$, while at high temperature the model is 
paramagnetic. The critical point at $\beta=\beta_c(\omega)$, which marks the 
transition between the two phases, is a nontrivial function of the booklet 
ratio $\omega$.

%########################################################################
\subsection{The replicated booklet and the overlap tensor}
\label{replica-sec}

The disorder-averaged free energy $[F(\omega,n,\beta)]$ (cf. 
Eq.~\eqref{free-energy}) is obtained, using the standard replica 
trick~\cite{cardy-book}, as  
%
\begin{equation}
\label{replica-trick}
[F(\omega,n,\beta)]=\lim_{\alpha\to 0}\frac{[Z^\alpha(\omega,n,\beta)]-1}
{\alpha}. 
\end{equation}
%
Here $[Z^\alpha(\omega,n,\beta)]$ is the disorder-averaged partition 
function of $\alpha\in\mathbb{N}$ independent copies of the S-K model on the 
booklet. Precisely, $[Z^\alpha(\omega,n,\beta)]$ reads 
%
\begin{multline}
[Z^\alpha(\omega,n,\beta)]=\int{\mathcal D}\{J\}
\tr'\exp\sum\limits_{r,\gamma}
\Big\{\\
\beta\sum\limits_{i<j}J_{ij}S_i^{(r,\gamma)}S_j^{(r,\gamma)}
+\beta h\sum\limits_{i}S^{(r,\gamma)}_i\Big\},
\label{rep-Z}
\end{multline}
%
where the index $\gamma=1,2,\dots,\alpha$ labels the different fictitious 
replicas introduced in Eq.~\eqref{replica-trick}, whereas $r$ denote the 
physical replicas, as in Eq.~\eqref{book-pf}. Clearly, physical and fictitious 
replicas do not interact. Notice that $Z^{\alpha}(\omega,n,\beta)$ can be 
thought of as the partition function of the S-K model on a ``replicated'' 
booklet.

Using Eq.~\eqref{quenched-distr}, the disorder average in Eq.~\eqref{rep-Z} 
can be performed explicitly, to obtain 
%
\begin{multline}
[Z^\alpha(\omega,n,\beta)]=\tr'\exp\sum\limits_{r,\gamma}\Big\{\\
\frac{1}{N}
\sum\limits_{i<j}\Big(
\frac{\beta^2}{2}\sum\limits_{\gamma',r'}S^{(r,\gamma)}_iS^{(r,\gamma)}_j
S^{(r',\gamma')}_iS^{(r',\gamma')}_j\\
+\beta J_0 S_i^{(r,\gamma)}S_j^{(r,\gamma)}\Big)
+\beta h\sum\limits_{i}
S_i^{(r,\gamma)}\Big\}.
\label{dis-aver-Z}
\end{multline}
%
In contrast with Eq.~\eqref{rep-Z}, physical and unphysical replicas are 
now coupled by a four-spin term. It is convenient to introduce the auxiliary 
Hubbard-Stratonovich variables $q_{\gamma\gamma'}^{rr'}$ and $m_\gamma^r$, 
with $\gamma,\gamma'=1,\dots,\alpha$ and $r=1,\dots,n$. Following the spin 
glass literature~\cite{parisi-book}, we dub $q_{\gamma\gamma'}^{rr'}$ the 
overlap tensor. In the standard S-K model (i.e., for $n=1$) 
$q_{\gamma\gamma'}^{rr'}$ becomes a $\alpha\times\alpha$ 
matrix~\cite{sherrington-1978-prl}. Eq.~\eqref{dis-aver-Z} now 
yields  
%
\begin{multline}
\label{hs-Z}
[Z^\alpha(\omega,n,\beta)]=\exp\Big(\frac{\beta^2Nn\alpha}{4}\Big)
\int\prod_{\substack{\gamma\le\gamma'\\r,r'}}
dq^{rr'}_{\gamma\gamma'}
\int\prod_{\gamma,r}dm_\gamma^r\\
\tr'\exp
\Big\{-N {\mathcal K}(\{q,m\})
+\sum_i{\mathcal L}_i(\{q,m\})\Big\},
\end{multline}
%
where we neglected subleading contributions ${\mathcal O}(1/N)$ in 
the thermodynamic limit. Here ${\mathcal K}(\{q,m\})$ is spin-independent 
and reads 
%
\begin{multline}
{\mathcal K}(\{q,m\})\equiv 
\frac{\beta^2}{2}\Big(\sum\limits_{\gamma<\gamma'}\sum
\limits_{r,r'} (q_{\gamma\gamma'}^{rr'})^2
\\
+\sum\limits_{\gamma}\sum\limits_{r<r'}(q_{\gamma\gamma}^{
rr'})^2\Big)
+\frac{\beta}{2 J_0}\sum\limits_{\gamma r}(m_\gamma^r)^2. 
\label{Gamma}
\end{multline}
%
On the other hand ${\mathcal L}_i(\{q,m\})$ depends on the spin degrees of 
freedom, and it is given as   
%
\begin{multline}
{\mathcal L}_i(\{q,m\})
\equiv\beta^2\sum\limits_{\gamma<\gamma'}\sum\limits_{rr'}
q_{\gamma\gamma'}^{rr'}S_i^{(r,\gamma)}
S_i^{(r',\gamma')}+\\
\beta^2\sum_\gamma\sum\limits_{r<r'}
q_{\gamma\gamma}^{rr'}S^{(r,\gamma)}_i
S^{(r',\gamma)}_i
+\beta\sum\limits_{\gamma r}(m_\gamma^r+h)
S_i^{(r,\gamma)}.
\label{mf-action}
\end{multline}
%
Interestingly, ${\mathcal L}_i$ describes a system of $n\alpha$ spins living 
in the replica space with the long-range interaction $q_{\gamma\gamma'}^{rr'}$, 
and a magnetic field $m_\gamma^r+h$. Notice that, while the first term in 
Eq.~\eqref{mf-action} is off-diagonal in the space of the fictitious replicas, 
the second one is diagonal. The latter fully determines the behavior of the model 
in the paramagnetic phase at high temperatures (see section~\ref{para-section}).

Since in Eq.~\eqref{hs-Z} spins on  different sites are decoupled, one can 
perform the trace over the spins in parts $A$ and $B$ (see Fig.~\ref{cartoon}) 
independently, to obtain 
%
\begin{multline}
[Z^\alpha(\omega,n,\beta)]=
\int\prod_{\substack{\gamma\le\gamma'\\r,r'}}
dq^{rr'}_{\gamma\gamma'}
\int\prod_{\gamma,r}dm_\gamma^r
\exp\Big\{N\Big(\\
\frac{\beta^2n\alpha}{4}+\omega\log\tr_Ae^{{\mathcal L}}+
(1-\omega)\log\tr_Be^{{\mathcal L}}-{\mathcal K}\Big)\Big\}.
\label{z-final}
\end{multline}
%
Here to lighten the notation we drop the dependence on the coordinate $i$ 
and the arguments of ${\mathcal L}_i(\{q,m\})$ and ${\mathcal K}(\{q,m\})$. 
$\textrm{Tr}_{A}$ and $\textrm{Tr}_{B}$  denote the trace over the spin degrees 
of freedom living in parts $A$ and $B$ of the booklet.
The subscript in $\tr_A$ is to stress that spins living in different physical 
replicas (i.e., for $r\ne r'$ in Eq.~\eqref{mf-action}) are identified (due 
to the booklet constraint in Eq.~\eqref{book-constraint}), whereas they have 
to be treated as independent variables in performing $\tr_B$.  
Notice that in Eq.~\eqref{z-final} the trace acts over a system of $n\alpha$ 
spins, instead of $Nn\alpha$, as in Eq.~\eqref{hs-Z}.

%########################################################################
\subsection{The saddle point approximation}
\label{saddle-point}

In the thermodynamic limit, i.e., for $N,N_A\to\infty$, at fixed ratio 
$\omega\equiv N_A/N$, one can take the saddle point approximation in 
Eq.~\eqref{z-final}, which yields   
%
\begin{multline}
[Z^\alpha(\omega,n,\beta)]\approx
\exp\Big\{N\alpha\Big(\frac{\beta^2n}{4}-\frac{\mathcal K}{\alpha}\\
+\frac{\omega}{\alpha}\log\tr_A\exp({\mathcal L})+
\frac{1}{\alpha}(1-\omega)\log\tr_B\exp({\mathcal L})
\Big)\Big\}. 
\label{Z-ac}
\end{multline}
%
The overlap tensor $q_{\gamma\gamma'}^{rr'}$ and $m_\gamma^r$ are 
determined by solving the saddle point equations 
%
\begin{align}
\label{saddle}
& \frac{\partial}{\partial q_{\gamma\gamma'}^{rr'}}
\left(\omega\log\tr_A e^{{\mathcal L}}+(1-\omega)\log\tr_B 
e^{{\mathcal L}}\right)=q_{\gamma\gamma'}^{rr'}\\
\nonumber
& \frac{\partial}{\partial m_\gamma^r}\left(\omega\log\tr_A 
e^{{\mathcal L}}+(1-\omega)\log\tr_B e^{{\mathcal L}}\right)=
\frac{1}{J_0}m_\gamma^r.
\end{align}
%
It is enlightening to rewrite Eqs.~\eqref{saddle} as 
%
\begin{align}
\nonumber
& q_{\gamma\gamma'}^{rr'}=
\omega\langle S^{(r,\gamma)} S^{(r',\gamma')}\rangle_A+
(1-\omega)\langle S^{(r,\gamma)}S^{(r',\gamma')}
\rangle_B\\
& \frac{1}{J_0}m_\gamma^r=\omega\langle S^{(r,\gamma)}
\rangle_A+(1-\omega)\langle S^{(r,\gamma)}
\rangle_B
\label{saddle-final}
\end{align}
%
where $\langle {\mathcal O}\rangle_{A(B)}\equiv (Z_{A(B)})^{-1}
\tr_{A(B)}\{{\mathcal O}\exp({\mathcal L})\}$ with $Z_{A(B)}\equiv\tr_{A(B)}
\exp({\mathcal L})$. The first equation in Eqs.~\eqref{saddle-final} implies 
that $q_{\gamma\gamma}^{rr}=1$ $\forall\gamma,r$. For $\omega=0$ and $n=1$, 
one recovers the saddle point equations for the standard SK model~\cite{parisi-book,
nishimori-book}.

In order to calculate the free energy $[F(\omega,n,\beta)]$ one has to solve 
the saddle point equations~\eqref{saddle-final}, take the analytic continuation 
$\alpha\in\mathbb{R}$, and, finally, the limit $\alpha\to 0$.  
(cf. Eq.~\eqref{replica-trick}). Although it is possible to solve the 
Eqs.~\eqref{saddle-final} numerically for any fixed $r,\alpha\in\mathbb{N}$, 
taking the analytic continuation $\alpha\in\mathbb{R}$ is a formidable task, 
since the dependence of $Z^\alpha(\omega,n,\beta)$ on $\alpha$ is in general 
too complicated. The strategy to solve this problem is to choose a specific form of 
the overlap tensor $q_{\gamma\gamma'}^{rr'}$ in terms of ``few'' parameters, which 
allows to perform the analytic continuation and the limit $\alpha\to 0$ exactly.

For the standard S-K model (i.e., for $n=1$) the simplest parametrization is the 
replica-symmetric one (RS), which amounts to take $q^{11}_{\gamma\gamma'}=q$. 
This relies on the observation that the fictitious replicas appear symmetrically 
in Eq.~\eqref{rep-Z}. Although the RS ansatz gives the correct result at high 
temperature, it fails in the glassy phase at low temperatures, where the permutational 
invariance within the replicas has to be broken~\cite{almeida-1978}. A systematic 
scheme to break the replica symmetry, which allows to capture the the glassy behavior 
of the S-K model at low temperature, is the celebrated Paris ansatz~\cite{parisi-1979}. 
We anticipate (see section~\ref{rsb-1-section}) that a similar scheme has to be used to 
describe the glassy phase of the S-K model on the booklet.

%########################################################################
\section{The replica-symmetric (RS) ansatz}
\label{solution}

In this section we present the solution of the S-K model on the booklet, using 
the replica symmetric approximation. In subsection~\ref{para-section} we focus 
on the paramagnetic phase at high temperature, where this approximation is exact. 
In particular, we show that the behavior of the model is fully determined by the 
diagonal part of the overlap tensor $q_{\gamma\gamma'}^{rr'}$. The general structure 
of $q_{\gamma\gamma'}^{rr'}$ in the replica-symmetric (RS) ansatz  is discussed in 
subsection~\ref{rs-section}. This allows to determine the critical temperature of 
the paramagnetic-glassy transition. Similar to the standard S-K model, the RS ansatz 
is not correct in the low-temperature region.

%########################################################################
\subsection{The paramagnetic phase}
\label{para-section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.9\linewidth]{./draft_figs/RSB0_saddle_ht}
\caption{
 The S-K model on the $2$-sheets booklet with zero magnetic field in the 
 paramagnetic phase: the solution $q_0$ of the saddle point equation 
 Eq.~\eqref{saddle-high-t} plotted as a function of the ratio 
 $\omega$ and for $\beta=1/T=0,3/4,1,4/3$. At $\omega=1$ one has 
 $q_0=1,\forall\beta$. In the zero-temperature limit $\beta\to\infty$ 
 it is $q_0\to 1,\forall\omega$. The straight line is the infinite 
 temperature result. 
}
\label{RSB0_saddle_ht}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here we provide the exact analytical expression for the free energy 
$[F_{para}(\omega,n,\beta)]$  in the paramagnetic non-glassy phase of 
the S-K model on the booklet. We start discussing the infinite temperature 
limit (i.e., $\beta\to 0$).

Using Eq.~\eqref{mf-action} one obtains  $\tr_Ae^{{\mathcal L}}=
2^{\alpha}+{\mathcal O}(\beta^2)$ and $\tr_B e^{{\mathcal L}}=2^{n\alpha}+
{\mathcal O}(\beta^2)$, implying  
%
\begin{align}
& \langle S^{(r,\gamma)}S^{(r',\gamma')}\rangle_B=2^{n\alpha}
\delta_{\gamma,\gamma'}\delta_{r,r'}+{\mathcal O}(\beta^2)\\\nonumber
& \langle S^{(r,\gamma)}S^{(r',\gamma')}\rangle_A=2^{\alpha}
\delta_{\gamma,\gamma'}+{\mathcal O}(\beta^2).
\end{align}
%
After substituting in Eqs.~\eqref{saddle-final}, it is straightforward to 
obtain the infinite-temperature overlap tensor $q_{\gamma\gamma'}^{rr'}$ 
as 
%
\begin{equation}
q_{\gamma\gamma'}^{rr'}=(1-\omega)\delta_{\gamma,\gamma'}\delta_{r,r'}+
\omega\delta_{\gamma,\gamma'}.
\label{inf-t-q}
\end{equation}
%
Remarkably, $q_{\gamma\gamma'}^{rr'}$ becomes diagonal in both the 
indices $\gamma,\gamma'$ and $r,r'$, i.e.,  the physical and 
fictitious replica spaces. The analytic continuation $\alpha\to 0$ 
(cf. Eq.~\eqref{replica-trick}) can be performed explicitly, to obtain 
%
\begin{multline}
[F_{para}(\omega,n,\beta)]=N\Big\{(n-\omega(n-1))\log(2)\\
+\frac{\beta^2}{4}(\omega^2(n^2-n)+n)\Big\}+
{\mathcal O}(\beta^4).
\label{logZ-ht}
\end{multline}
% 
It is natural to expect that for arbitrary $\beta\le\beta_c$, with 
$\beta_c$ the critical temperature of the paramagnetic-glassy 
transition, the overlap tensor $q_{\gamma\gamma'}^{rr'}$ remains 
diagonal. This suggests the ansatz 
%
\begin{equation}
q_{\gamma\gamma'}^{rr'}=(1-q_0)\delta_{r,r'}\delta_{\gamma,\gamma'}+
q_0\delta_{\gamma,\gamma'}.
\label{high-t-q}
\end{equation}
%
with $q_0\in {\mathbb R}$ a parameter. The ansatz~\eqref{high-t-q} is formally 
obtained from Eq.~\eqref{inf-t-q} by replacing $\omega\to q_0$. Notice that 
one has $q_{\gamma\gamma}^{rr}=1$, in agreement with Eqs.~\eqref{saddle-final}. 
Using Eq.~\eqref{high-t-q}, one obtains ${\mathcal L}_{para}$ (cf. 
Eq.~\eqref{mf-action}) as   
%
\begin{equation}
\label{high-t-action}
{\mathcal L}_{para}=\beta^2\frac{q_0}{2}\Big\{\sum_\gamma\sum_{rr'}S^{(r,
\gamma)}S^{(r',\gamma)}-n\alpha\Big\}.
\end{equation}
%
After introducing the auxiliary Hubbard-Stratonovich variables $z_\lambda$ 
(with $\lambda=1,\dots,\alpha$), one can write 
%
\begin{multline}
\label{ht-saddle}
\textrm{Tr}_B\exp({\mathcal L}_{para})=\\\tr_B\int\prod_\lambda Dz_{\lambda}
\exp\Big(z_\lambda\beta\sqrt{q_0}\sum_r S^{(r,\lambda)}\Big),
\end{multline}
%
where $\int Dz f(z)\equiv(2\pi)^{-1/2}\int\exp(-z^2/2)f(z)$. Notice that 
due to the square root in Eq.~\eqref{ht-saddle}, one has the constraint 
$q_0>0$. Moreover, from Eq.~\eqref{high-t-action} 
one obtains $\textrm{Tr}_A\exp({\mathcal L})=2^{n\alpha}$. The trace 
$\textrm{Tr}_B$ in Eq.~\eqref{ht-saddle} can be performed explicitly. 
Using Eq.~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, one obtains 
the free energy $[F_{para}(\omega,n,\beta)]$ as  
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.9\linewidth]{./draft_figs/RSB0_saddle}
\caption{\label{RSB0-saddle}
 The S-K model on the $2$-sheets booklet with zero magnetic field. The 
 overlap tensor in the replica-symmetric (RS) approximation (see Eq.~\eqref{rs-ansatz}): 
 the solutions $q_0$ and $q_0'$ (shown as full and dotted lines, respectively) 
 of the saddle point equations Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} 
 plotted as a function of the ratio $\omega$, and inverse temperature 
 $\beta=1/T=1,3/2,2$. At $\omega=1$ one has that $q_0=1,\forall\beta$.
 In the limit $\beta\to\infty$ it is $q_0,q_0'\to 1,\forall\omega$.
}
\label{RSB0_saddle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{multline}
[F_{para}(\omega,n,\beta)]=N\Big\{
n\log(2)-\omega(n-1)\log(2)\\+
\beta^2\Big(\frac{n}{4}-\frac{q_0^2}{4}(n^2-n)
+\frac{\omega}{2}q_0n^2-q_0n\Big)\\
+(1-\omega)\log\int Dz\cosh^n(z\sqrt{q_0}\beta)
\Big\},
\label{ht-logZ}
\end{multline}
%
where $q_0$ is determined by solving the saddle point condition $\partial[F_{para}
(\omega,n,\beta)]/\partial q_0=0$. For the $2$-sheets booklet (i.e., $n=2$) this is  
given as   
%
\begin{equation}
q_0=\omega+(1-\omega)\tanh(\beta^2 q_0).
\label{saddle-high-t}
\end{equation}
%
Alternatively, Eq.~\eqref{saddle-high-t} can be obtained by substituting the 
ansatz~\eqref{high-t-q} in Eqs.~\eqref{saddle-final}.

Clearly, for two independent copies of the S-K model (i.e., $\omega=0$) 
Eq.~\eqref{saddle-high-t} gives $q_0=0$ for $\beta\le1$, whereas 
one obtains $q_0\ne0$ for $\beta>1$. On the other hand, for $\omega=1$ 
one has $q_0=1$ $\forall\beta$. For generic $0<\omega<1$ the solution of 
Eq.~\eqref{saddle-high-t} is shown in Figure~\ref{RSB0_saddle_ht}, plotting 
$q_0$ as a function of $\omega$, for $\beta=0,0.75,1,1.1$. For $\beta=0$ it 
is $q_0=\omega$ (straight line in the Figure). In the low-temperature limit 
one has $q_0\to 1$, for any $\omega$. In particular, it is straightforward 
to check that  $q_0\approx 1-2(1-\omega)\exp(-2\beta^2)$ for $\beta\to\infty$.

%##########################################################################
\subsection{The replica-symmetric (RS) approximation} 
\label{rs-section}

In the replica-symmetric (RS) approximation one writes the overlap tensor  
$q_{\gamma\gamma'}^{rr'}$ as
%
\begin{equation}
q_{\gamma\gamma'}^{rr'}=(1-q_0)\delta_{r,r'}\delta_{\gamma,\gamma'}+
q_0\delta_{\gamma,\gamma'}+(1-\delta_{\gamma,\gamma'})q'_0.
\label{rs-ansatz}
\end{equation}
%
The first two terms in Eq.~\eqref{rs-ansatz} are the same as in the paramagnetic 
phase (cf. Eq.~\eqref{high-t-q}). The last term sets $q_{\gamma\gamma'}^{rr'}=q'_0$ 
$\forall\gamma\ne\gamma'$ and $\forall r,r'$. Physically, Eq.~\eqref{rs-ansatz} 
means that we require the permutational symmetry in both the physical and fictitious 
replica space. We do not have any rigorous argument to justify the ansatz~\eqref{rs-ansatz}, 
besides its simplicity. However, we numerically observe that it captures quite accurately 
the behavior of the model, at least around the paramagnetic-glassy transition (see 
section~\ref{mc-results} for the Monte Carlo results).

Using Eq.~\eqref{rs-ansatz} and Eqs.~\eqref{replica-trick}\eqref{Z-ac} one obtains 
the replica-symmetric approximation for the free energy $[F_{RS}(\omega,n,\beta)]$ 
as 
%
\begin{multline}
[F_{RS}(\omega,n,\beta)]=\\\lim_{\alpha\to 0}\Big\{
N\Big[\frac{\beta^2}{4}n-\frac{\beta^2}{4}\Big(
(q_0^2-(q'_0)^2)n^2-q_0^2n\Big)\\
+\frac{1-\omega}{\alpha}\log\tr_B\exp({\mathcal L}_{RS})\\
+\frac{\omega}{\alpha}\log\tr_A \exp({\mathcal L}_{RS})
\Big]\Big\},
\label{rs-F}
\end{multline}
%
where ${\mathcal L}_{RS}$ is obtained by substituting Eq.~\eqref{rs-ansatz} 
in Eq.~\eqref{mf-action}, which yields 
%
\begin{multline}
\label{l-rs}
{\mathcal L}_{RS}=\frac{q_0'}{2}\beta^2
\sum\limits_{\gamma\gamma'}\sum_{rr'}
S^{(r,\gamma)}S^{(r',\gamma')}\\
+\frac{q_0-q_0'}{2}\beta^2\sum_\gamma\sum_{rr'}
S^{(r,\gamma)}S^{(r',\gamma')}-\frac{q_0}{2}\beta^2n\alpha.
\end{multline}
%
To calculate the last two terms in Eq.~\eqref{rs-F} one has to introduce 
two auxiliary Hubbard-Stratonovich variables $z,z'$, similar to the 
paramagnetic phase (cf. section~\ref{para-section}). Thus, after performing 
the trace over the spin variables, in the limit $\alpha\to0$, one obtains 
%
\begin{align}
\label{eq1}
 \log\tr_B\exp({\mathcal L}_{RS})=&
-\frac{q_0}{2}\beta^2 n\alpha+n\alpha\log(2)\\\nonumber
&+\alpha\int Dz
\log\int Dz'H_{RS}^n(z,z'),\\
\label{eq2}
 \log\tr_A\exp({\mathcal L}_{RS})=&
-\frac{q_0}{2}\beta^2 n\alpha+\alpha\log(2)\\\nonumber
&+\alpha\int Dz
\log\int Dz'H_{RS}(nz,nz'), 
\end{align}
%
where we define $H_{RS}(z,z')\equiv\cosh(\beta z\sqrt{q_0'}+\beta z'\sqrt{q_0-q_0'})$. 
Notice that because of the square roots in the definition of $H_{RS}(z,z')$, 
one has the constraint $0\le q_0'\le q_0\le 1$.

In Eq.~\eqref{eq1}\eqref{eq2} 
$q_0,q_0'$ have to satisfy the saddle point conditions $\partial[F_{RS}(\omega,n,\beta)]/
\partial q_0=\partial[F_{RS}(\omega,n,\beta)]/\partial q'_0=0$ 
(cf. Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} for the  precise form of the 
saddle point equations for $n=2$). 
The resulting $q_0$ and $q_0'$ are plotted in Figure~\ref{RSB0-saddle} (full 
and dotted lines, respectively) as function of $\omega$ and for several values of 
$\beta$. Clearly, for any $\beta$ one has $q_0=1$ in the limit $\omega\to 1$. Also, 
in the zero-temperature limit $\beta\to\infty$ one has that $q_0\to 1$ 
and $q_0'\to 1$, for any $\omega$. Moreover, a simple calculation yields  
%
\begin{align}
\label{low-t}
& q_0=1 -(1-\omega)\sqrt{\frac{2}{\pi}}\frac{1}{\beta}\exp\Big(-\frac{1}{\pi}-
\sqrt{\frac{2}{\pi}}\beta\Big)+\dots
\\\nonumber 
& q_0'=1-\frac{1}{\sqrt{2\pi}\beta}-\frac{1}{2\pi\beta^2}+{\mathcal O}(\beta^{-3}),
\end{align}
%
with the dots denoting exponentially suppressed terms. Interestingly, from 
Eq.~\eqref{low-t} one has that $q_0\to 1$ exponentially in the limit $\beta\to\infty$, 
as in the paramagnetic phase (cf. section~\ref{para-section}), whereas 
$q_0'-1\propto 1/\beta$, similar to the standard SK model~\cite{nishimori-book}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure}[t]
\includegraphics*[width=0.9\linewidth]{./draft_figs/betac}
\caption{
 The critical temperature $\beta_c\equiv 1/T_c$ for the S-K model on the $2$-sheets  
 booklet (see Fig.~\ref{cartoon}) with zero magnetic field: $\beta_c$ as a function 
 of the booklet ratio $\omega\equiv N_A/N$. Here $\beta_c$  is obtained from the 
 replica-symmetric (RS) approximation of the model. Notice that one has $\beta_c=1$ 
 and $\beta_c=1/2$ for $\omega=0$ and $\omega=1$, respectively. 
}
\label{beta_c}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Finally, using the replica-symmetric ansatz Eq.~\eqref{rs-ansatz} one can determine 
the critical temperature $\beta_c$ of the paramagnetic-glassy transition. 
Near the glassy transition one should expect $q'_0\to0$, whereas $q_0$ 
should remain finite ($q_0>0$ in the paramagnetic phase, see section~\ref{para-section}). 
By expanding $[F_{RS}(\omega,n,\beta)]$ (cf. Eq~\eqref{rs-F}) for small $q_0'$, and 
keeping only terms up to ${\mathcal O}((q_0')^2$, one obtains a standard Landau theory. 
Thus, $\beta_c$ is obtained imposing that the coefficient of the quadratic term $q_0'^2$ 
changes sign. This leads to the equation 
%
\begin{equation}
\exp(-4q_0\beta^2_c)+2\exp(-2q_0\beta^2_c)=\frac{1-4\beta^2_c}
{4\beta^2_c\omega-1},
\label{tc}
\end{equation}
%
where $q_0$ is obtained by solving the high-temperature saddle point 
equation~\eqref{saddle-high-t}. The resulting $\beta_c$ solution of Eq.~\eqref{tc} 
is shown in Fig.~\ref{beta_c} as a function of $\omega$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/U_w05}
\caption{
 The S-K model on the $2$-sheets booklet with zero magnetic field and 
 booklet ratio $\omega=1/2$ (see Fig.~\ref{cartoon}): The internal energy 
 per spin $U/N$ as a function of the inverse temperature $\beta$. The triangles, 
 squares, and rhombi, denote the Monte Carlo data for a booklet with 
 $N=32,64,128$ spins per sheet. The plus symbols are the extrapolations to the 
 thermodynamic limit $N\to\infty$, at fixed $\omega$. The dash-dotted line is the 
 analytical result $U_{RS}/N$ obtained using the replica-symmetric (RS) approximation. 
 The horizontal dotted line is the exact zero-temperature result $U/N\approx-1.52642$.
}
\label{U-MC}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%##########################################################################
\section{The one-step replica-symmetry-broken (1-RSB) approximation}
\label{rsb-1-section}

In this section we go beyond the replicas-ymmetric approximation, including some 
of the effects of the replica symmetry breaking. More specifically, 
here we discuss the one-step replica symmetry breaking (1-RSB) approximation for the 
S-K model on the booklet. The overlap tensor $q_{\gamma\gamma'}^{rr'}$ now reads  
%
\begin{equation}
\label{q-rsb1}
q_{\gamma\gamma'}^{rr'}=(1-q_0)\delta_{\gamma,\gamma'}\delta_{r,r'} +
q_0\delta_{\gamma,\gamma'}+(1-\delta_{\gamma,\gamma'})q', 
\end{equation}
%
which is formally equivalent to the RS ansatz in Eq.~\eqref{rs-ansatz}, apart from 
the trivial redefinition $q_0'\to q'$. However, in contrast with Eq.~\eqref{rs-ansatz}, 
where $q_0'\in\mathbb{R}$ is a number, here $q'$ is a matrix. Inspired by the Parisi 
scheme for the standard S-K model~\cite{parisi-1979}, we choose 
%
\begin{displaymath}
q'=\left\{
\begin{array}{cc}
q_1' & \textrm{if}\, \lfloor\gamma/m_1\rfloor=\lfloor\gamma'/m_1\rfloor\\\\
q_0' & \textrm{otherwise}\\
\end{array}
\right.
\label{q-rsb1a}
\end{displaymath}
%
where now $q_0',q_1'\in{\mathbb R}$, $m_1\in{\mathbb N}$, and $\lfloor\cdot\rfloor$ 
denotes the floor function. The off-diagonal elements of $q'$ do not depend on 
$r,r'$, meaning that, although the permutational symmetry between the 
fictitious replicas is broken, the symmetry among the physical ones is preserved. 
Notice that the choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block 
diagonal structure for $q'$:  the elements in the $m_1\times m_1$ diagonal 
blocks are set to $q_1'$, whereas all the off-diagonal elements are set to 
$q_0'$. As for the replica-symmetric ansatz in Eq.~\eqref{rs-ansatz}, we do 
not have any rigorous argument to justify Eq.~\eqref{q-rsb1a} (see 
section~\eqref{mc-results}, for numerical results).

The effective interaction ${\mathcal L}_{1\textrm{-}RSB}$ (cf. Eq.~\eqref{mf-action}) 
in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in Eq.~\eqref{mf-action}. 
This yields  
%
\begin{multline}
{\mathcal L}_{1\textrm{-}RSB}/\beta^2=-\frac{q_0}{2}n\alpha
-\frac{q_1'-q_0}{2}\sum\limits_{\sigma=1}^{\alpha/m_1}
\sum\limits_{\gamma\in B_\sigma}\Big(\sum_r S^{(r,\gamma)}\Big)^2\\
+\frac{q_0'}{2}\Big(\sum\limits_{\gamma,r}
S^{(r,\gamma)}\Big)^2-
\frac{q_0'-q_1'}{2}\sum\limits_{\sigma=1}^{\alpha/m_1}
\Big(\sum\limits_{\gamma\in B_\sigma,r}S^{(r,\gamma)}\Big)^2,
\label{blocks}
\end{multline}
%
where we defined $B_\sigma\equiv[\sigma m_1,(\sigma+1)m_1)$ with $\sigma\in\mathbb{N}$. 
It is convenient t to introduce the Hubbard-Stratonovich variables $z,z_\sigma,z_{\sigma,\gamma}$ 
(one for each term in Eq.~\eqref{blocks}). One then obtains 
%
\begin{multline}
\log\tr'\exp({\mathcal L}_{1\textrm{-}RSB})=
-\frac{q_0}{2}\beta^2 n\alpha\\
+\log\tr'\int Dz\prod_\sigma\int Dz_\sigma\prod\limits_{\gamma\in B_\sigma}
\int Dz_{\sigma,\gamma}\prod_r\exp\Big\{\beta\Big[\\\nonumber
z\sqrt{q'_0}S^{(r,\gamma)}
+z_{\sigma,\gamma}\sqrt{q_0-q_1'} S^{(r,\gamma)}+
z_{\sigma}\sqrt{q_1'-q_0'}S^{(r,\gamma)}\Big]\Big\}
\end{multline}
%
The trace over the spin variables can now be performed explicitly. Finally, 
one obtains the 1-RSB approximation for the free energy 
$[F_{1\textrm{-}RSB}(\omega,n,\beta)]$ as 
%
\begin{widetext}
\begin{multline}
[F_{1\textrm{-}RSB}(\omega,n\beta)]/N=
(\omega+(1-\omega)n)\log(2)+
\frac{n}{4}\beta^2\Big(1+nq_0'^2
-n(m_1-1)(q_1'^2-q_0'^2)-
(n-1)q_0^2-2q_0\Big)\\
+\int Dz\left\{\frac{\omega}{m_1}\log\int Dz'\Big\{\int Dz''
H_{1\textrm{-}RSB}^n(z,z',z'')\Big\}^{m_1}
+\frac{1-\omega}{m_1}
\log\int Dz'\Big\{\int Dz''
H_{1\textrm{-}RSB}(nz,nz',nz'')\Big\}^{m_1}
\right\}, 
\label{RSB-1-logZ}
\end{multline}
\end{widetext}
%
where we defined $H_{1\textrm{-}RSB}(z,z',z'')$ as 
%
\begin{multline}
H_{1\textrm{-}RSB}(z,z',z'')\equiv\cosh(z\beta\sqrt{q'_0}\\+
z''\beta\sqrt{q_0-q'_1} +z'\beta\sqrt{q_1'-q_0'})
\label{H1}
\end{multline}
%
Similar to the replica-symmetric situation (see section~\ref{rs-section}), 
from Eq.~\eqref{H1} one has the constraint $0\le q_0'\le q_1'\le q_0\le 1$.
The parameters $q_0,q_0',q_1',m_1$ are obtained by solving the saddle 
point equations Eqs.~\eqref{RSB-1-saddle-a}\eqref{RSB-1-saddle-b}\eqref{RSB-1-saddle-c}
\eqref{RSB-1-saddle-d}. One should remark that, although $m_1\in\mathbb{N}$ in 
Eq.~\eqref{q-rsb1a}, one obtains $m_1\in\mathbb{R}$ from the saddle point equations. 
Finally, the RS result $F_{RS}(\omega,n,\beta)$ is recovered from Eq.~\eqref{RSB-1-logZ} 
in the limit $q_1'\to q_0'$, while the paramagnetic solution corresponds to 
$q_1'\to q_0'\to 0$.

%##########################################################################
\section{Monte Carlo results: The internal energy}
\label{mc-results}

In this section we numerically confirm the results of section~\ref{solution}. 
To this purpose, we discuss Monte Carlo (MC) data for the S-K model on the 
$2$-sheets booklet with zero external magnetic field. We focus on the 
internal energy $U(\omega,n,\beta)$ 
%
\begin{equation}
\label{U-def}
U(\omega,n,\beta)\equiv-\frac{\partial}{\partial\beta}
[\log(Z(\omega,n,\beta))]. 
\end{equation}
%  
Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
$\beta$, for the booklet with $\omega=1/2$ (see Fig.~\ref{cartoon}). The cicles, squares, 
and triangles are the MC results for different sizes (i.e., number of spins per sheet) 
$N=32,64,128$. The vertical dotted line is the critical temperature $\beta_c\approx 0.603$ of 
the paramagnetic-glassy transition (cf. Fig.~\ref{beta_c}). Clearly, in the high-temperature 
region for $\beta<\beta_c$ finite size effects are small, and already for $N=64$ the MC data 
are indistinguishable from the result in the thermodynamic limit. Oppositely, stronger 
scaling corrections are  visible in the low-temperature phase at $\beta>\beta_c$. 
The plus symbols in Fig.~\ref{U-MC} are the numerical extrapolations in the 
thermodynamic limit $N\to\infty$. These are obtained by fitting the finite size MC data 
to the ansatz $U(\omega,\beta)/N=u_{\infty}(\omega,\beta)+c/N^{\phi}$, where 
$u_{\infty}$ is energy density in the thermodynamic limit, $c$ a fitting parameter, and 
$\phi$ the exponent of the scaling corrections. In our fits we fix $\phi=2/3$, which 
is the exponent governing the finite-size corrections of $U/N$ in 
the standard S-K model~\cite{billoire-2007,aspelmeier-2008}.

The dash-dotted line is the analytical result $U_{RS}$ obtained using the 
replica-symmetric (RS) approximation (see section~\ref{rs-section}). 
Using Eq~\eqref{U-def} and Eq.~\eqref{rs-F}, $U_{RS}$  is obtained as   
%
\begin{equation}
U_{RS}=-N\beta(1+q_0^2-2q_0'^2). 
\label{U}
\end{equation}
% 
Here $q_0,q_0'$ are solutions of the saddle point equations Eqs.~\eqref{RS-saddle-1}
\eqref{RS-saddle-2}. Notice that $U_{RS}$ depends on $\omega$ only through $q_0,q_0'$. 
From Fig.~\ref{U-MC} one has that, while $U_{RS}$ is in perfec agreeement with the numerics 
for $\beta\approx\beta_c$, deviations appear in the low-temperature region. Moreover, these 
deviations increase upon lowering the temperature, and already at $\beta\gtrsim 1$, $U_{RS}$ 
is incompatible with the data. This is has to be attributed to the replica symmetry breaking 
happening in the glassy phase.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/U_extrapolated}
\caption{
 The S-K model on the 2-sheets booklet and zero magnetic field: 
 The internal energy per spin $U/N$ in the thermodynamic limit. 
 The symbols are the Monte Carlo data extrapolated to the thermodynamic 
 limit $N\to\infty$, at fixed booklet ratio $\omega$ (see Fig.~\ref{cartoon}).  
 $U/N$ is plotted as a function of inverse temperature $\beta$ and for 
 $\omega=0,1/4,1/2,3/4,1$. The lines are the analytical results $U_{RS}$ 
 obtained using the replica-symmetric (RS) approximation. The stars denote 
 the value of $U_c/N$ at the paramagnetic-glassy transition. 
}
\label{U-RS}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/U_extrapolated_v1}
\caption{
 The S-K model on the 2-sheets booklet with zero magnetic field: 
 The internal energy per spin $U/N$ in the thermodynamic limit plotted 
 as a function of inverse temperature $\beta$. The plus symbols are the same 
 Monte Carlo data as in Figure~\ref{U-RS}. The lines denote $U/N$ 
 in the replica-symmetric (RS) approximation (same as in Fig.~\ref{U-RS}). 
 The circles are the results  in the one-step replica symmetry breaking 
 (1-RSB) approximation.
}
\label{U-RSB-1}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Finally, since in the limit $\beta\to\infty$ all the physical replicas are in the same state, 
one should expect that $u_\infty(\omega,\beta)\to n u_\infty(0,\beta)$ (horizonthal line in 
Fig.~\ref{U-MC}), with $u_{\infty}(0,\beta)\to-0.76321...$~\cite{parisi-1979,parisi-1983} the 
zero-temperature internal energy density of the S-K model on a single sheet. Surprisingly, 
this behavior is already observed in the MC data at $\beta\approx 3$, whereas it is not 
captured correctly by the RS approximation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/Renyi_MC_v2}
\caption{ The classical Renyi entropy per spin $S_2(\omega)/N$  in the 
 S-K model on the $2$-sheets booklet with zero magnetic: $S_2(\omega)/N$ as a 
 function of the inverse temperature $\beta$. The different panels 
 correspond to different booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). 
 The triangles, squares and rhombi denote the Monte Carlo results for 
 booklets with $N=32,64,128$ spins per sheet. The plus symbols are the numerical 
 extrapolations to the thermodynamic limit. The dash-dotted lines are the  
 analytical results $U_{RS}/N$ using the replica-symmetry (RS) approximation. 
 The circles are the analytical results $U_{1\textrm{-}RSB}$ obtained 
 using the one-step replica symmetry breaking (1-RSB) ansatz.
}
\label{Renyi-MC}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The behavior of $U/N$ for $\omega\ne1/2$ is investigated in Fig.~\ref{U-RS},
plotting $U/N$ as a function of $\beta$ for $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
are the MC data extrapolated in the thermodynamic, at fixed $\omega$. Similar to Fig.~\ref{U-RS}, 
the extrapolations are done assuming $U/N(\omega,n,\beta)=u_{\infty}(\omega,n,\beta)+
c/N^{\phi}$, with $\phi=2/3$ irrespective of $\omega$. The stars in Fig.~\ref{U-RS} are 
the critical values $U_c/N$ at the paramagnetic-glassy transition. Specifically, here  
$\beta_c$ is obtained by numerically solving Eq.~\eqref{tc}. The lines in Fig.~\ref{U-RS} 
denote the replica-symmetric result $U_{RS}$ (cf. Eq.~\eqref{U}).

For generic $n$ and $\omega$, in the limit $\beta\to 0$, Eq.~\eqref{U-def} 
and Eq.~\eqref{logZ-ht} give  
%
\begin{equation}
U_{RS}(\omega,n,\beta)= -N\frac{\beta}{2}(\omega^2(n^2-n)+n)+{\mathcal O}(\beta^2), 
\label{ht-U}
\end{equation}
%
i.e., a linear behavior of $U/N$ as a function of $\beta$. For $\omega=0$ and $\omega=1$ 
this behavior is exact up to the critical point at $\beta=\beta_c$, meaning that the higher 
orders ${\mathcal O}(\beta^2)$ in Eq.~\eqref{ht-U} are zero. This is only an approximation at 
intermediate $0<\omega<1$. Clearly, Fig.~\ref{U-RS} confirms that at $\beta<\beta_c$ both 
Eq.~\eqref{U} and Eq.~\eqref{ht-U} are in excellent agreement with the numerical results. 
However, one should observe that $U_{RS}$ is not correct in the low-temperature at 
$\beta>\beta_c$, where the replica symmetry breaking has to be taken into account.

The effects of the replica symmetry breaking are more carefully discussed in 
Fig.~\ref{U-RSB-1}, plotting $U/N$ versus $1\le\beta\le 2$. The plus symbols and the lines 
are the same as in Fig.~\ref{U-RS}.  The full circles denote the internal energy per spin 
$U_{1\textrm{-}RSB}/N$ as obtained using the $1$-step replica symmetry breaking (1-RSB) 
approximation (see section~\ref{rsb-1-section}). Specifically, from Eq.~\eqref{RSB-1-logZ} 
and Eq.~\eqref{U-def}, for $n=2$ a straightforward calculation gives 
%
\begin{equation}
U_{1\textrm{-}RSB}=-N\beta(1+q_0^2+2q_1'^2(m_1-1)-2q_0'^2m_1), 
\label{U'}
\end{equation}
%
where $q_0,q_0',q_1',m_1\in\mathbb{R}$ are solutions of the saddle point 
equations \eqref{RSB-1-saddle-a}-\eqref{RSB-1-saddle-d}. Clearly, from Eq.~\eqref{U'} 
one has $U_{1\textrm{-}RSB}\to U_{RS}$ for $q_1'\to q_0'$, as expected. 
Moreover, since for $\beta\approx\beta_c$ it is $q_1'\approx q_0'\approx0$, one has  
that $U_{RSB}\approx U_{RS}$, i.e. the effects of the replica symmetry breaking are 
negligible near the critical point. 
On the other hand, in the replica symmetry broken phase at low temperature, 
where the RS approximation $U_{RS}$ fails (see Fig.~\ref{U-RS}), $U_{1\textrm{-}RSB}$ 
is in good agreement with the Monte Carlo data, at least up to $\beta\approx 2$.  
This allows us to conclude that, although the ansatz in Eq.~\eqref{q-rsb1} 
might not be correct in the limit $\beta\to\infty$, it captures some of the effects 
of the replica symmetry breaking.

%##########################################################################
\section{The classical R\'enyi entropies}
\label{Renyi-section}

We now turn to discuss the behavior of the classical R\'enyi entropies (cf. 
Eq.~\eqref{renyi}) in the S-K model. Here we restrict ourselves to the second R\'enyi 
entropy $S_2$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
there is no boundary between the two parts $A$ and $B$ of the system (see Fig.~\ref{cartoon}), 
implying that $S_2$ exhibits the volume law $S_2\propto N$, rather than the area law. 
Therefore it is natural to consider the entropy per spin $S_2/N$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
\begin{figure*}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/I2_MC_v1}
\caption{The classical mutual information per spin ${\mathcal I}_2/N$ 
 in the S-K model on the $2$-sheets booklet with zero magnetic field: 
 ${\mathcal I}_2/N$ versus the inverse temperature $\beta$. The 
 different panels correspond to different booklet ratios $\omega=1/2,1/4,1/8$ 
 (see Fig.~\ref{cartoon}). The same scale is used on both axes in all 
 panels. The symbols are the Monte Carlo data 
 for systems with $N=32,64,128$ spins per sheet. The dash-dotted line is 
 the analytical result in the replica-symmetric (RS) approximation.  
}
\label{I2-MC}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The Monte Carlo data for $S_2/N$  are shown in Fig.~\ref{Renyi-MC} plotted versus the 
inverse temperature $0.25\le\beta\le 2.5$. The different panels correspond to the  
booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the empty 
circles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per per 
sheet. Clearly, finite size effects are present, which increase upon lowering 
the temperature, as expected. In order to obtain $S_2/N$ in the thermodynamic limit 
we fit the data to the ansatz $S_2(\omega)=s_2(\omega)+c'(\omega)/N^{\phi'}$, where 
$s_2(\omega)$ is the entropy per spin in the limit $N\to\infty$, $c'$ a constant, and 
$\phi'$ the exponent of the scaling corrections. The plus symbols in Fig.~\ref{Renyi-MC} 
are the results of the fits. We should mention that the fits give $\phi'\approx 2/3$, 
which is the exponent of the scaling corrections of the free energy in the standard 
S-K model. This is not surprising, since $S_2(\omega)$ is obtained as the difference 
$S_2(\omega)\equiv [F(0,2,\beta)-F(\omega,2,\beta)]$ (cf. Eq.~\eqref{renyi}). 
Clearly, in the thermodynamic limit $S_2(\omega)/N$ is finite for any $\beta$, 
confirming the expected volume law $S_2\propto N$ behavior. Moreover, $S_2/N$ 
exhibits a maximum in the infinite-temperature limit $\beta\to0$. The height of this 
maximum  is a decreasing function of $\omega$ (compare the panels (a)(b)(c) in 
Fig.~\ref{Renyi-MC}). Finally, for any fixed $\omega$, $S_2(\omega)$ decreases 
smoothly upon lowering the temperature. In particular, the Monte Carlo data suggest 
a vanishing behavior in the zero-temperature limit $\beta\to\infty$.

The dash-dotted line in Fig.~\ref{Renyi-MC} denotes the analytical result $S_2^{RS}$ 
obtained using the replica-symmetric (RS) approximation (see section~\ref{rs-section}).
More precisely, $S_2^{RS}/N$ is obtained from Eq.~\eqref{renyi} and the expression for 
the replica symmetric free energy $[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). Notice that in the 
high-temperature limit $\beta\to0$, where the RS approximation is exact, 
Eq.~\eqref{renyi} and Eq.~\eqref{ht-logZ} give 
%
\begin{equation}
S^{RS}_2(\omega)=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^2).
\end{equation}
%
From Fig~\ref{Renyi-MC} one has that the extrapolated MC data are in quantitative 
agreement with $S_2^{RS}/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
observed at lower temperatures (not shown in the Figure). 
These are reflecting the symmetry breaking. A better approximation for $S_2(\omega)/N$ 
at low temperatures is obtained by including the effects of the replica symmetry breaking. 
The full circles in Fig.~\ref{Renyi-MC} are the analytical results $S_2^{1\textrm{-}RSB}$
obtained using the one step replica symmetry breaking (1-RSB) ansatz 
(see section~\ref{rsb-1-section}). $S_2^{1\textrm{-}RSB}$ is formally obtained 
using Eq.~\eqref{renyi} and the free energy $[F_{1\textrm{-}RSB}]$ (cf. 
Eq.~\eqref{RSB-1-logZ}). Remarkably,  $S_2^{1\textrm{-}RSB}$ is in excellent 
agreement with the Monte Carlo extrapolations for $\beta\lesssim 2$, where the RS 
approximation fails.

%##########################################################################
\section{The classical R\'enyi mutual information}
\label{I2-section}

Here we focus on the behavior of the Renyi mutual information ${\mathcal I}_2$ in 
the S-K model. Similar to $S_2(\omega)$, the mutual information obeys the volume 
law ${\mathcal I}_2(\omega)\propto N$. This is in contrast with local models, 
where ${\mathcal I}_n(\omega)$ exhibits an area law. Here we consider the 
mutual information per spin ${\mathcal I}_2(\omega)/N$.

Figure~\ref{I2-MC} ${\mathcal I}_2/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,1/8$ 
(panels from left to right in the Figure). Notice that by definition (cf. Eq.~\eqref{MI}) 
${\mathcal I}_n(\omega)={\mathcal I}_n(1-\omega)$. Circles, squares, and rhombi in 
Fig.~\ref{I2-MC} are Monte Carlo data for $N=32,64,128$. 
In the high-temperature region ${\mathcal I}_2$ exhibits a clear vanishing 
behavior, for any $0<\omega<1$. Moreover, finite size effects are ``small''. 
Using Eq.~\eqref{logZ-ht} it is straightforward to derive the high-temperature 
behavior of ${\mathcal I}_n(\omega)$ as  
%
\begin{equation}
{\mathcal I}_n(\omega)=\frac{N\beta^2}{2}\omega(1-\omega)n+{\mathcal O}
(\beta^4).
\end{equation}
%
At lower temperatures ${\mathcal I}_2/N$ increases monotonically up to $\beta\approx 1$, 
where it exhibits a maximum. Interestingly, the largest value of ${\mathcal I}_2/N$ 
(${\mathcal I}_2/N\approx 0.09$ for $\omega=1/2$) is quite small, as it is observed in 
local spin models~\cite{jaconis-2013}. The height of the maximum decreases as a function of 
$\omega$. Its position is not simply related to the paramagnetic-glassy transition at $\beta=1$ 
of the standard S-K model. This is not surprising because ${\mathcal I}_n(\omega)$ is constructed 
by combining the partition functions of the S-K model on the booklets with ratios $\omega$, 
$1-\omega$, $\omega=0$, and $\omega=1$ (cf. Eq.~\eqref{MI}), and the critical temperature of 
the paramagnetic-glassy transition is a non trivial function of $\omega$ (see Fig.~\ref{beta_c}). 
As a consequence, the geometric mutual information ${\mathcal G}_n$ (cf.~\eqref{GMI}) 
is not well defined for the S-K model. 
Furthermore, the curves for ${\mathcal I}_2/N$ calculated at different sizes do not exhibit any 
crossing at $\beta=1$, in sharp contrast with local models~\cite{jaconis-2013}, for which it has 
been shown that ${\mathcal I}_n(\omega)/N$ exhibits a crossing at a second order phase transition. 
For $\beta\gtrsim 1$, ${\mathcal I}_2$ decreases monotonically, for any $N$. 
The dash-dotted line in Fig.~\ref{I2-MC} denotes the analytical result obtained using the replica 
symmetric (RS) approximation (see section~\ref{rs-section}). Formally this is obtained using 
Eq~\eqref{MI} and Eq.~\eqref{rs-F}. This is in perfect agreement with the 
MC data in the whole paramagnetic phase.

Interestingly, at low temperatures ${\mathcal I}_2/N$ exhibits strong finite-size corrections, and 
significant deviations from the RS result. 
In order to extract the thermodynamic behavior of ${\mathcal I}_2/N$ we fit the MC data to 
%
\begin{equation}
\frac{{\mathcal I}_2}{N}=a+\frac{b}{N^\gamma}
\end{equation}
%
where we fix $\gamma=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}. 
The circles, squares, and triangles denote ${\mathcal I}_2/N$ in the thermodynamic limit 
$N\to\infty$ for $\omega=1/2,1/4,1/8$. 
Interestingly, we numerically checked that in the zero-temperature limit the data 
support the vanishing behavior as ${\mathcal I}_2/N\propto \beta^{-2}$. This reflects 
the vanishing of the classical R\'enyi entropy $S_2$ at zero temperature (see Fig.~\ref{Renyi-MC}).
The dash-dotted lines are the RS results (same as 
in Fig.~\ref{I2-MC}). Remarkably, the RS approximation is in good agreement with 
the extrapolations, at least within the error bars, up to $\beta\lesssim 1.5$, whereas 
deviations occur at lower temperatures (not shown in the figure). For $\omega=1/8$, 
the numerical results exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
These deviations have to be attributed to the physics of the replica symmetry breaking. 
The full rhombi in Fig.~\ref{I2-extrapolated} are the analytical results for ${\mathcal I}_2/N$ 
including some of the effects of the replica symmetry breaking. More precisely, 
${\mathcal I}_2^{1\textrm{-}RSB}$ is obtained using Eq.~\eqref{MI} and the one-step replica 
symmetry breaking (1-RSB) approximation for the free energy of the S-K model on the 
booklet (cf. Eq.~\eqref{RSB-1-logZ}). The agreement between ${\mathcal I}_2^{1\textrm{-}RSB}$ 
is perfect, at least up to $\beta\lesssim 2$. Notice that at lower temperatures 
one should expect deviations from ${\mathcal I}_2^{1\textrm{-}RSB}$, similar to what it 
is observed in the standard S-K model. In particular, one should implement the fully 
breaking of the replica symmetry ($\infty$-RSB).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics*[width=0.93\linewidth]{./draft_figs/I2_extrapolated}
\caption{ The classical mutual information per spin ${\mathcal I}_2/N$ 
 in the SK model on the $2$-sheets booklet with zero magnetic field: 
 ${\mathcal I}_2$ plotted versus $\beta$. The symbols denote the 
 Monte Carlo results extrapolated to the thermodynamic limit for 
 booklet ratios $\omega=1/2,1/4,1/8$ (circles, squares, triangles). 
 The dash-dotted lines are the analytical results in the 
 replica-symmetric (RS) appproximation. The full symbols (rhombi) 
 are the results in the first-step replica-symmetry-breaking (1-RSB) 
 approximation.
}
\label{I2-extrapolated}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%##########################################################################
\section{Summary and Conclusions}
\label{conclusions}

We investigated the \emph{classical} R\'enyi entropy $S_n$ and the mutual information 
${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the paradigm model 
for mean-field spin glasses. As usual in disordered systems, we focused on the quenched 
averages $[S_n]$ and $[{\mathcal I}_n]$, with the brackets $[\cdot]$ denoting the average 
over different disorder realizations. Here $S_n$ and ${\mathcal I}_n$ were obtained 
from suitable combinations of the partition functions of the S-K model on the 
so-called $n$-sheets booklet (cf.~\ref{cartoon}). This is obtained by ``gluing'' together 
$n$ independent replicas (``sheets'') of the model. One each replica the spins are 
divided into two groups $A$ and $B$, containing $N_A$ and $N_B$ spins respectively. The 
spins in part $A$ of the different sheets are identified. Due to the mean-field nature of 
the model, the R\'enyi entropies and other physical quantities depend on the bipartition 
only through the aspect ratio $\omega\equiv N_A/N$. Although many of our analytic results 
are for generic $n$, we often restricted ourselves to the $2$-sheets booklet, i.e., the 
second R\'enyi entropy $S_2$ and ${\mathcal I}_2$.

We investigated the phase diagram of the S-K model on the $2$-sheets booklet as a function 
of $\omega$ and the inverse temperature $\beta$, in the situation without external 
magnetic field ($h=0$ in Eq.~\eqref{SK-intro}). For any $\omega$, in the 
thermodynamic limit the S-K model exhibit glassy phase for low-enough tempereatures, 
whereas at high temperature the model is paramagnetic. The two phases are divided 
by a second order phase transition, as in the standard, i.e., on the plane, S-K model. 
Interestingly, we found that the critical temperature depends in a non-trivial 
way on $\omega$. Moreover, we fully characterized the high-temperature phase 
using the replica-symmetric (RS) approximation, which is a simple generalization 
of the replica-symmetric solution of the S-K model model on the plane. Specifically, 
we provided the exact formula for the disorder-averaged free energy $[F_{para}(\omega,n,
\beta)]$ of the S-K model on the booklet (cf. Eq.~\eqref{ht-logZ}). The analytic results 
for $S_2$ and ${\mathcal I}_2$ follow straightforwardly using Eq.~\eqref{renyi} and 
Eq.~\eqref{MI}. In the low-temperature glassy phase the replica symmetry has to be 
broken, similar to the standard S-K model. In order to take into account the 
replica symmetry breaking we device a simple generalization of the the Parisi 
ansatz~\cite{parisi-1980}, which allows to break the replica symmetry in successive 
steps. After restricting ourselves to the one-step replica symmetry breaking, we 
provide the exact formula for the disorder-averaged free energy $F_{1\textrm{-}RSB}
(\omega,n,\beta)$ (cf. Eq.~\eqref{RSB-1-logZ}), and, correspondingly, $S_2^{1\textrm{RSB}}$, 
${\mathcal I}_2^{1\textrm{-}RSB}$. As a preliminary check, we compared the analytical 
results for the internal energy $U_{RS}$ and $U_{1\textrm{-}RSB}$ with Monte Carlo data. 
In the high-temperature region, where the replica symmetry is not broken, these are 
in perfect agreement with $U_{RS}$. Oppositely, in the glassy phase, where the replica 
symmetry breaking occurs, the Monte Carlo data exhibit deviations from the analytical 
results already at $\beta\approx 1$. However, we numerically observed that the one-step 
replica-symmetry-broken approximation $U_{1\textrm{-}RSB}$ matches the Monte Carlo 
data up to $\beta\approx 3$.

Finally, we discussed the behavior of $S_2$ and ${\mathcal I}_2$. Due to the mean-field 
nature of the S-K model we observed that both quantities obey a volume law $S_2\propto N$, 
${\mathcal I}_2\propto N$. Thus we considered the densities $S_2/N$ and ${\mathcal I}_2/N$, 
focusing on the thermodynamic limit $N\to\infty$, at fixed $\omega$. 
At high temperature the Monte Carlo data for $S_2/N$ are in excellent agreement with the 
replica-symmetric result $S_2^{RS}$. Interestingly, we observed that $S_2/N$ exhibits a 
maximum at infinite temperature, and it is a \emph{smooth} monotonically descreasing 
function of the temperature. This behavior does not depend on the booklet aspect ratio 
$\omega$.  Moreover, while in the high-temperature region $S_2$ is fully described by 
the replica symmetric ansatz $S_2^{RS}$, in the glassy phase it exhibits signatures of 
the replica symmetry breaking. The one-step replica symmetry breaking approximation 
$S_2^{1\textrm{-}RSB}$ is in full agreement with the Monte Carlo data for $\beta\approx 3$, 
reflecting the behavior of the internal energy. Finally, we numerically observed that the 
mutual information per spin ${\mathcal I}_2/N$ does not show any crossing for different 
system sizes $N$, in contrast with local models, where it exhibits a crossing at 
the critical point. In the thermodynamic limit ${\mathcal I}_2/N$ is vanishing both 
at $\beta=0$, and $\beta=\infty$, whereas it has a mximum at intermediate temperatures. 
The position of this maximum is not  simply related to the paramagnetic glassy transition 
of the S-K model.

Finally, our work opens several interesting research directions. First, it would be 
interesting to extend our results taking into account the full breaking of the replica 
symmetry. This would allow to reach a conclusion on the correctness of the replica symmetry 
breaking scheme that we used. Moreover, it would be interesting to go beyond the saddle 
point approximation, including finite-size correztions. An interesting question would be 
to investigate hwo the paramagnetic-glassy transition is associated with the subleading 
corrections to the observed volume law in the classical R\'enyi entropies. Also, it 
would be interesting to investigate the behavior of entanglement-related quantities in 
disordered quantum spin systems that exhibit replica symmetry breaking~\cite{read-1995, 
andreanov-2012}. Finally, it would be enlightening to understand the interplay between 
the physical and the fictitious replicas at the level of the entropy. Notice that,  
using the analytical results provided in the paper, it is possible to perform the 
analytic continuation $n\to 1$ to obtain the von Neumann classical mutual information. 
It would be interesting to check wheather this differs significantly from the 
R\'enyi mutual information.

\section{Acknowledgements}
We would like to thank Pasquale Calabrese for useful discussions. V.A.  acknowledge 
financial support by the ERC under Starting Grant 279391 EDEQS.

\appendix

%##########################################################################
\section{The saddle point equations} 
\label{saddle-equations}

In this section we provide the analytical expression for the saddle point equations 
\eqref{saddle-final}, which determine the overlap tensor $q_{\gamma\gamma'}^{rr'}$ 
(see section~\ref{replica-trick}) in the thermodynamic limit, and the behavior of the 
S-K model on the booklet. We restrict ourselves to the situation with zero magnetic 
field and to the $2$-sheets booklet (see Fig.~\ref{cartoon}). It is straightforward 
to generalize the calculation to the case with non zero magnetic field and to the 
$n$-sheets booklet. Here we provide the saddle point equations obtained in both the 
replica-symmmetric (RS) approximation (see section~\ref{rs-section}), and the 
one-step replica symmetry breaking ($1$-RSB) approximation (see 
section~\ref{rsb-1-section}).

%####################################
\subsection{The replica symmetric (RS) approximation}

In the replica-symmetric approximation $q_{\gamma\gamma'}^{rr'}$ depends on the two 
parameters $q_0,q_0'\in\mathbb{R}$ (cf. Eq.~\eqref{rs-ansatz}). The saddle point 
equations are easily derived using the RS approximation for the free energy $[F_{RS}
(\omega,n,\beta)]$ (cf. Eq.~\eqref{rs-F}) of the S-K model on the booklet as 
$\nabla_{\mathbf{q}}[F_{RS}(\omega,2,\beta)]=0$, where $\mathbf{q}\equiv(q_0,q_0')$, 
and $\nabla_{\mathbf{q}}\equiv\partial/\partial\mathbf{q}$. A straightforward 
calculation gives the system of equations  
%
\begin{equation}
\label{RS-saddle-1}
\frac{1-q_0}{1-\omega}=2\int dz G_0(z)(1+\exp(2\beta^2(q_0-q_0'))\cosh(2z))^{-1},
\end{equation}
%
and
%
\begin{multline}
\label{RS-saddle-2}
2\beta^2\frac{1-q_0'}{1-\omega}=
\int dz G_0(z)\Big\{\frac{\omega}{1-\omega}\Delta_0(z)
\log\cosh(2z)\\
+\Delta_0(z)\log(1+\exp(2\beta^2(q_0-q_0'))\cosh(2z))\\
+2\beta^2(1+\exp(2\beta^2(q_0-q_0'))\cosh(2z))^{-1}
\Big\}
\end{multline}
%
where we defined $\Delta_0(z)$ as 
%
\begin{equation}
\Delta_0(z)\equiv\frac{z^2}{2\beta^2q_0'^2}-\frac{1}{2q_0'},
\end{equation}
%
and the so-called heat kernel $G_0(z)$ as 
%
\begin{equation}
G_0(z)\equiv\frac{1}{\sqrt{2\pi \beta^2 q_0'}}\exp\Big(-\frac{z^2}
{2\beta^2 q_0'}\Big).
\end{equation}
%
Notice that it is trivial to check that $\int dz G_0(z)\Delta_0(z)=0$.

%##########################################################################
\subsection{The one-step replica symmetry breaking ($1$-RSB) approximation}

In the one-step replica symmetry breaking scenario (see section~\ref{rsb-1-section}) 
the overlap depends on the four parameters $q_0,q_0',q_1',m_1\in\mathbb{R}$. The 
saddle point equations are now given as $\nabla_{\mathbf{p}}[F_{1\textrm{-}RSB}]=0$, 
where now $\mathbf{p}\equiv(q_0,q_0',q_1',m_1)$, and $[F_{1\textrm{-}RSB}]$ is 
the disorder-averaged free energy given in Eq.~\eqref{RSB-1-logZ}.
It is useful to define the modified heat kernel $G_1(z)$ as 
%
\begin{equation}
G_1(z)\equiv\frac{1}{\sqrt{2\pi \beta^2 (q_1'-q_0')}}\exp\Big(-\frac{z^2}
{2\beta^2 (q_1'-q_0')}\Big), 
\end{equation}
%
and 
%
\begin{align}
& \Delta_1(z)\equiv \frac{z^2}{\beta^2(q_1'-q_0')^2}-\frac{1}{q_1'-q_0'}\\\nonumber
& \Gamma(z)\equiv \Big\{\int dz'G_1(z')\cosh^{m_1}(2z+2z')\Big\}^{-1}\\\nonumber
& \Gamma'(z)\equiv \Big\{\int dz'G_1(z')\Big(1+\cosh(2z+2z')\Big)^{m_1}\Big\}^{-1}\\\nonumber
& \Theta(z,z')\equiv 1+\exp(2\beta^2(q_0-q_1'))\cosh(2z+2z'). 
\end{align}
%
Finally, a straightforward calculation yields the saddle point equations for 
$q_0,q_0',q_1',m_1$ as 
%
\begin{widetext}
\begin{multline}
0=(1+q_0-2\omega)\exp(-2\beta^2(q_0-q_1'))
-2(1-\omega)\int dzdz'G_{0}(z)
\Gamma'(z)G_{1}
(z')\cosh(2z+2z')\Theta^{m_1-1}(z,z')
\label{RSB-1-saddle-a}
\end{multline}
%
\begin{multline}
0=4\beta^2m_1q_0'+\frac{\omega}{m_1}\int dz G_{0}(z)
\Delta_0(z)\log\int dz'G_{1}(z')
\cosh^{m_1}(2z +2z')\\
+\frac{1-\omega}{m_1}\int dzG_{0}(z)
\Delta(z)\log\int dz'G_{1}(z')\Theta^{m_1}(z,z')
-\frac{\omega}{m_1}\int dzdz'G_{0}(z)\Gamma(z)
G_{1}(z')\Delta_1(z')\cosh^{m_1}(2z+2z')\\
-\frac{1-\omega}{m_1}
\int dzdz'G_{0}(z)\Gamma'(z)G_{1}(z')\Delta_1(z')\Theta^{m_1}(z,z')
\label{RSB-1-saddle-b}
\end{multline}
%
\begin{multline}
0=-4\beta^2(m_1-1)q_1'-4\beta^2\omega+\frac{\omega}{m_1}
\int dzdz'G_{0}(z)\Gamma(z)G_{1}(z')\Delta_1(z')
\cosh^{m_1}(2z+2z')\\+
\frac{1-\omega}{m_1}\int dzdz'G_{0}(z)
\Gamma'(z)
G_{1}(z')\Big\{\Delta_1(z')\Theta^{m_1}(z,z')
-4\beta^2m_1\exp(2\beta^2(q_0-q_1'))\cosh(2z+2z')
\Theta^{m_1-1}(z,z')
\Big\}
\label{RSB-1-saddle-c}
\end{multline}
%
\begin{multline}
0=-\beta^2(q_1'^2-q_0'^2)+\frac{\omega}{m_1}
\int dzdz'G_{0}(z)\Gamma(z)G_{1}(z')\cosh^{m_1}(2z+2z')
\log\cosh(2z+2z')\\+
\frac{1-\omega}{m_1}\int dzdz' G_{0}(z)\Gamma'(z)
G_{1}(z')\Theta^{m_1}(z,z')\log(\Theta(z,z'))
-\frac{1-\omega}{m_1^2}\int dz G_{0}(z)\log\int dz' 
G_{1}(z')\Theta^{m_1}(z,z')\\
-\frac{\omega}{m_1^2}\int dzG_{0}(z)\log
\int dz'G_{1}(z')\cosh^{m_1}(2z+2z').
\label{RSB-1-saddle-d}
\end{multline}
\end{widetext}
%

%##########################################################################
\begin{thebibliography}{99}

\bibitem{amico-2008}
L. Amico, R. Fazio, A. Osterloh, and V. Vedral, Entanglement in Many-Body 
Systems, Rev. Mod. Phys. {\bf 80}, 517 (2008).

\bibitem{eisert-2009}
J. Eisert, M. Cramer, and M. B. Plenio, Area laws for the entanglement 
entropy - a review, Rev. Mod. Phys. {\bf 82}, 277 (2009).

\bibitem{calabrese-2009}
P.~Calabrese, J.~Cardy, and B. Doyon Eds., Special issue: Entanglement 
entropy in extended systems, J.\ Phys.\ A {\bf 42}, 50 (2009).

\bibitem{cc-rev}
P.~Calabrese and J.~Cardy, Entanglement entropy and conformal field theory, 
J.\ Phys.\ A {\bf 42} 504005 (2009).

\bibitem{holzhey-1994} C. Holzhey, F. Larsen, and F. Wilczek,
Geometric and Renormalized Entropy in Conformal Field Theory,
Nucl. Phys. B {\bf 424}, 443 (1994).

\bibitem{vidal-2003}
G.~Vidal, J.~I.~Latorre, E.~Rico, and A.~Kitaev,
Entanglement in quantum critical phenomena, Phys.\ Rev.\ Lett.\ 
{\bf 90}, 227902 (2003). J.~I.~Latorre, E.~Rico, and G.~Vidal,
Ground state entanglement in quantum spin chains, Quant.\ Inf.\ 
and\ Comp.\ {\bf 4}, 048 (2004).

\bibitem{calabrese-2004}
P.~Calabrese and J.~Cardy, Entanglement entropy and quantum field theory,
J.\ Stat.\ Mech.\ (2004) P06002. 
P.~Calabrese and J.~Cardy, Entanglement entropy and quantum field theory: 
a non-technical introduction, Int. J.\ Quant.\ Inf.\ {\bf 4}, 429 (2006).

\bibitem{binder-1986}
K.~Binder and A.~P.~Young, Rev.\ Mod.\ Phys.\ {\bf 58}, 801 (1986).

\bibitem{young-1998}
A.~P.~Young, \emph{Spin Glasses and Random Fields} (Singapore: World Scientific).

\bibitem{wilms-2011}
J.~Wilms, M.~Troyer, and F.~Verstraete, J.\ Stat.\ Mech.\ (2011) P10011.

\bibitem{wilms-2012}
J.~Wilms, J.~Vidal, F.~Verstraete,and S.~Dusuel, J.\ Stat.\ Mech.\ (2012)P01023.

\bibitem{parisi-book}
M.~Mezard, G.~Parisi, and M.~Virasoro, \emph{Spin Glass theory and beyond}, World Scientific, Singapore (1987).

\bibitem{fisher-1986}
D.~S.~Fisher and D.~A.~Huse, Phys.\ Rev.\ Lett.\ {\bf 56} 1601 (1986).

\bibitem{huse-1987}
D.~S.~Fisher and D.~A.Huse, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L997 (1987).

\bibitem{huse-1987-a}
D.~A.~Huse and D.~S.~Fisher, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L1005 (1987).

\bibitem{fisher-1988}
D.~S.~Fisher and D.~A.Huse, Phys.\ Rev. B {\bf 38}, 386 (1988).

\bibitem{newman-1996}
C.~Newman and D.~L.~Stein, Phys.\ Rev.\ Lett.\ {\bf 76}, 515 (1996).

\bibitem{krzakala-2000}
F.~Krzakala and O.~C.~Martin, Phys.\ Rev.\ Lett.\ {\bf 85}, 3013 (2000).

\bibitem{palassini-2000}
M.~Palassini and A.~P.~Young, Phys.\ Rev.\ Lett.\  {\bf 85}, 3017 (2000).

\bibitem{sherrington-1978-prl}
D.~Sherrington and S.~Kirkpatrick, Phys.\ Rev.\ Lett.\ {\bf 35}, 
1972 (1978).
\bibitem{sherrington-1978}
D.~Sherrington and S.~Kirkpatrick, Phys.\ Rev.\ B {\bf 17}, 4385 
(1978).

\bibitem{parisi-1980}
G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1101 (1980).

\bibitem{parisi-1980-a}
G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1887 (1980).

\bibitem{parisi-1980-b}
G.~Parisi, J.\ Phys.\ A\ {\bf 13}, L115 (1980).

\bibitem{parisi-1979}
G.~Parisi, Phys.\ Rev.\ Lett.\ {\bf 43}, 1754 (1979).

\bibitem{parisi-1983}
G.~Parisi, Phys.\ Rev.\ Lett\ {\bf 50}, 1946 (1983).

\bibitem{mezard-1984}
M.~Mezard, G.~Parisi, N.~Sourlas, G.~Toulouse, and M.~Virasoro, 
Phys.\ Rev.\ Lett.\ {\bf 52}, 1156 (1984).

\bibitem{nishimori-book}
H.~Nishimori, ``Statistical Physics of Spin Glasses and Information Processing'', 
Clarendon Press, Oxford (2001).

\bibitem{stephan-2014}
J.-M.~St\'ephan, S.~Inglis, P.~Fendley, and R.~G.~Melko, 
Phys.\ Rev.\ Lett.\ {\bf 112}, 127204 (2014).

\bibitem{jaconis-2013}
J.~Iaconis, S.~Inglis, A.~B.~Kallin, and R.~G.~Melko, 
Phys.\ Rev.\ B {\bf 87}, 195134 (2013).

\bibitem{yucesoy-2012}
B.~Yucesoy, H.~G.~Katzgraber, and J.~Machta, Phys.\ Rev.\ Lett. {\bf 109}, 
177204 (2012).

\bibitem{yucesoy-2013}
B.~Yucesoy, H.~G.~Katzgraber, and J.~Machta, Phys.\ Rev.\ Lett.\ {\bf 110}, 
219702 (2013)

\bibitem{billoire-2012}
A.~Billoire, L.~A.~Fernandez, A.~Maiorano, E.~Marinari, 
V.~Martin-Mayor, G.~Parisi, F.~Ricci-Tersenghi, J.~J.~Ruiz-Lorenzo, 
and D.~Yllanes, Phys.\ Rev.\ Lett.\ {\bf 110}, 219701 (2013).

\bibitem{morrison-2008}
S.~Morrison, A.~Kantian, A.~J.~Daley, H.~G.~Katzgraber, M.~Lewenstein, 
H.~P.~B\"uchler, and P.~Zoller, New\ J.\ Phys.\ {\bf 10}, 
073032 (2008).

\bibitem{ghofraniha-2015}
N.~Ghofraniha, I.~Viola, F.~Di~Maria, G.~Barbarella, G.~Gigli, L.~Leuzzi, 
and C.~Conti, Nature\ Comm.\ {\bf 6}, 6058 (2015).

\bibitem{rotondo-2015}
P.~Rotondo, E.~Tesio, and S.~Caracciolo, Phys.\ Rev.\ B {\bf 91}, 
014415 (2015).

%\bibitem{bouchaud-2003}
%J.-P.~Bouchaud, F.~Krzakala, and O.~C.~Martin, Phys.\ Rev.\ B {\bf 68}, 
%224404 (2003).

%\bibitem{boettcher-2005}
%S.~Boettcher: Eur.\ Phys.\ J.\ {\bf B46}, 501 (2005).

%\bibitem{katzgraber-2003}
%H.~G.~Katzgraber and I.~A.~Campbell, 
%Phys.\ Rev.\ B {\bf 68}, 180402R (2003).

\bibitem{aspelmeier-2008}
T.~Aspelmeier, A.~Billoire, E.~Marinari, and M.~A.~Moore, 
J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 41} 324008 (2008).

\bibitem{billoire-2007}
A.~Billoire, in \emph{Rugged Free Energy Landscape}, Springer Lecture 
Notes in Physics, edited by W. Janke (Springer, Berlin-Heidelberg 
2007.

\bibitem{read-1995}
N.~Read, S.~Sachdev, and J.~Ye, Phys.\ Rev.\ B {\bf 52}, 384 (1995).

\bibitem{andreanov-2012}
A.~Andreanov and M.~M\"uller, Phys.\ Rev.\ Lett.\ {\bf 109}, 177201 (2012).

\bibitem{cardy-book}
J.~Cardy, \emph{Scaling and Renormalization in Statistical Physics} 
(Cambridge Lecture Notes in Physics).

\bibitem{almeida-1978}
J.~R.~L.~de Almeida and D.~J.~Thouless, J.\ Phys.\ A {\bf 11}, 983 (1978).

\bibitem{stephan-2009}
J-M~St\'ephan, S.~Furukawa, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 80}, 
184421 (2009)

\bibitem{stephan-2010}
J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 82}, 125455 
(2010);

\bibitem{stephan-2011}
J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 84}, 
195128 (2011).

\bibitem{zaletel-2011}
M.~P.~Zaletel, J.~H.~Bardarson, and J.~E.~Moore, Phys.\ Rev.\ Lett.\ {\bf 107}, 
020402 (2011).

\bibitem{alcaraz-2013}
F.~C.~Alcaraz and M.~A.~Rajabpour, Phys.\ Rev.\ Lett.\ {\bf 111}, 017201 (2013).

\bibitem{talagrand-2006}
M.~Talagrand, Ann.\ of\ Math.\ {\bf 163}, 221 (2006).

\bibitem{guerra-2002}
F.~Guerra and F.~L.~Toninelli, Commun.\ Math.\ Phys.\ {\bf 230}, 71 (2002).

\bibitem{rammal-1986}
R.~Rammal, G.~Toulouse, and M.~A.~Virasoro, Rev.\ Mod.\ Phys.\ {\bf 58}, 765 
(1986).

\bibitem{calabrese-2012}
P.~Calabrese, J.~Cardy, and E.~Tonni, Phys.\ Rev.\ Lett.\ {\bf 109}, 
130502 (2012).

\bibitem{stephan-2014-a}
J.-M.~St\'ephan, Phys.\ Rev.\ B {\bf 90}, 045424 (2014).

\bibitem{castellani-2005}
T.~Castellani and A.~Cavagna, J.\ Stat.\ Mech.\ (2005) P05012.

\bibitem{wolf-2008}
M.~M.~Wolf, F.~Verstraete, M.~B.~Hastings, and J.~I.~Cirac, Phys.\ Rev.\ Lett.\ 
{\bf 100}, 070502 (2008).

\bibitem{refael-2009}
G.~Refael and J.~E.~Moore J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 42} 504010 (2009).

\bibitem{pastur-1991}
L.~A.~Pastur and M.~V.~Shcherbina, J.\ Stat.\ Phys.\ {\bf 62}, 1 (1991).

\end{thebibliography}

\end{document}

### 2015-05-24 compile.sh

@@ -1,0 +1,3 @@
+#latex sk_model_v15.tex
+#dvipdf sk_model_v15.dvi
+pdflatex sk_model_v15.tex

### 2015-05-26 sk_model_v15.tex
initial version
Stephen's first edits -- need to change Fig.1 and add MC methods section

@@
 M\"unchen, D-80333 M\"unchen, Germany}
-%\author{Lode Pollet}
+\author{Lode Pollet}
+\affiliation{Department of Physics and Arnold Sommerfeld
+    Center for Theoretical Physics, Ludwig-Maximilians-Universit\"at
+M\"unchen, D-80333 M\"unchen, Germany}
 
@@
 information ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the 
-paradigm model of mean-field spin glasses. We use both classical Monte Carlo simulations 
-and analytical tools. First, we investigate the S-K model on the $n$-sheets booklet. This 
-is obtained by gluing together $n$ independent copies of the model, and it is the 
-main ingredient to construct entaglement-related quantities. We find that at low temperature 
+paradigm model of mean-field spin glasses. 
+Using both classical Monte Carlo simulation and analytical tools we investigate the S-K model 
+on a booklet of $n$-sheets.
+This is obtained by gluing together $n$ independent copies of the model, and it is the 
+main ingredient to construct the R\'enyi entaglement-related quantities. We find that at low temperature 
 the S-K model is in a glassy phase, whereas at high temperature it exhibits paramagnetic 
@@
 averages. In the low-temperature glassy phase the replica symmetry has 
-to be broken. Using a simple generalization of the celebrated Parisi solution, we provide 
+to be broken. Using a generalization of the celebrated Parisi solution, we provide 
 approximated results for thermodynamic quantities and for $S_n$ and ${\mathcal I}_n$. 
@@
 Besides being ubiquitous in nature, disorder leads to several intriguing 
-physical phenomena. Arguably, \emph{spin glasses} provide one of the most 
-striking examples. While at any finite temperature disorder prevents the 
+physical phenomena. 
+Arguably, \emph{spin glasses} represent one of the most prototypical examples
+of disorder.
+While at any finite temperature disorder prevents the 
 usual magnetic ordering, at low-enough temperatures these systems display a 
@@
 S_n(A)\equiv \frac{1}{1-n}\log\Big(\sum\limits_{i_A\in{\mathcal C}_A} p^n_{i_A}
-\Big).i 
+\Big)
 \label{renyi-intro}
@@
 in the S-K model, using classical Monte Carlo simulations and analytical tools. We often 
-restrict ourselves to the case with $n=2$. As usual in disordered system, we 
+restrict ourselves to the case with $n=2$, as this is where numerical simulation is most
+efficient . As usual in disordered system, we 
 focus on disorder-averaged quantities, considering $[S_n]$ and $[{\mathcal I}_n]$, 
@@
  As a consequence, the effective temperature in part $A$ is $n\beta$. 
- $Z(\omega,n,\beta)$ denotes the partition function of the S-K model on 
+ $Z(A,n,\beta)$ denotes the partition function of the S-K model on 
  the booklet. 
@@
 
-This scenario, and, in particular, the effects of the replica symmetry breaking, are 
+In this scenario the effects of the replica symmetry breaking are 
 reflected in the behavior of $[S_2]$ and $[{\mathcal I}_2]$. First, since $[S_2]$ exhibits 
@@
 that the $1$-RSB approximation for $[{\mathcal I})_2]/N$, is in good agreement with the Monte Carlo 
-data for $\beta\approx 3$.
+data for $\beta \lesssim 3$.
 
@@
 Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
-the R\'enyi mutual information ${\mathcal I}_n(A,B,\beta)$ (with $n\in\mathbb{N}$) 
+the R\'enyi mutual information ${\mathcal I}_n(A,B,\beta)$ (with $n\in\mathbb{N}$
+and $A \cup B$ is the entire system)) 
 is defined as~\cite{jaconis-2013,stephan-2014} 
@@
 in $B$ are at inverse temperature $\beta$, the ones in $A$ are at the effective 
-temperature $n\beta$. The definition of $Z(B,n\beta)$ is obtained by exchanging 
+temperature $n\beta$. The definition of $Z(B,n,\beta)$ is obtained by exchanging 
 $A$ and $B$. Alternatively, ${\mathcal I}_n$ can be rewritten as 
@@
 Notice that $S_n(X)$ corresponds to $S_n(X)\equiv1/(n-1)\log(F(X,n,\beta))
--n\log(F(\beta))$, where $F(X,n,\beta)\equiv\log(Z(\beta))$ and $F(\beta)
-\equiv\log(Z(X,n,\beta))$ are related (apart from a factor $\beta$) to the 
+-n\log(F(\beta))$, where $F(X,n,\beta)\equiv\log(Z(X,n\beta))$ and $F(\beta)
+\equiv\log(Z(\beta))$ are related (apart from a factor $\beta$) to the 
 free energy of the model on the booklet and on the plane, respectively.
@@
 %
-Since in each sheet all spins interact with each other, there is no notion of distance. 
+Since in each sheet all spins interact with each other, there is no notion of distance 
 between different spins. Thus, physical observables should depend on the booklet geometry 
-only through the ratio $\omega\equiv N_A/N_B$.
+only through the ratio $\omega\equiv N_A/N$.
 
@@
 {\mathcal L}_i(\{q,m\})
-\equiv\beta^2\sum\limits_{\gamma<\gamma'}\sum\limits_{rr'}
+\equiv\beta^2\sum\limits_{\gamma<\gamma'}\sum\limits_{r,r'}
 q_{\gamma\gamma'}^{rr'}S_i^{(r,\gamma)}
@@
 of $q_{\gamma\gamma'}^{rr'}$ in the replica-symmetric (RS) ansatz  is discussed in 
-subsection~\ref{rs-section}. This allows to determine the critical temperature of 
+subsection~\ref{rs-section}. This allows us to determine the critical temperature of 
 the paramagnetic-glassy transition. Similar to the standard S-K model, the RS ansatz 
@@
 By expanding $[F_{RS}(\omega,n,\beta)]$ (cf. Eq~\eqref{rs-F}) for small $q_0'$, and 
-keeping only terms up to ${\mathcal O}((q_0')^2$, one obtains a standard Landau theory. 
+keeping only terms up to ${\mathcal O}((q_0')^2)$, one obtains a standard Landau theory. 
 Thus, $\beta_c$ is obtained imposing that the coefficient of the quadratic term $q_0'^2$ 
@@
 entropy $S_2$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
-there is no boundary between the two parts $A$ and $B$ of the system (see Fig.~\ref{cartoon}), 
-implying that $S_2$ exhibits the volume law $S_2\propto N$, rather than the area law. 
+there is no well defined boundary between the two parts $A$ and $B$ of the system (unlike Fig.~\ref{cartoon} for local models).
+The fully connected nature of the model suggests that $S_2$ should be volume law $S_2 \propto N$ for all temperature.
 Therefore it is natural to consider the entropy per spin $S_2/N$.
@@
 law ${\mathcal I}_2(\omega)\propto N$. This is in contrast with local models, 
-where ${\mathcal I}_n(\omega)$ exhibits an area law. Here we consider the 
-mutual information per spin ${\mathcal I}_2(\omega)/N$.
+where ${\mathcal I}_n(\omega)$ is constructed to exhibit an area law at all temperatures.
+Again, the fully connected nature of the S-K model means that common expectations from local models
+do not apply.  Here we consider the mutual information per spin ${\mathcal I}_2(\omega)/N$.
 
@@
 crossing at $\beta=1$, in sharp contrast with local models~\cite{jaconis-2013}, for which it has 
-been shown that ${\mathcal I}_n(\omega)/N$ exhibits a crossing at a second order phase transition. 
+been shown that ${\mathcal I}_n(\omega)/\ell$ exhibits a crossing at a second order phase transition. 
 For $\beta\gtrsim 1$, ${\mathcal I}_2$ decreases monotonically, for any $N$. 
@@
 where we fix $\gamma=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}. 
-The circles, squares, and triangles denote ${\mathcal I}_2/N$ in the thermodynamic limit 
+The circles, squares, and triangles denote ${\mathcal I}_2/N$ extrapolated from Monte Carlo to the thermodynamic limit 
 $N\to\infty$ for $\omega=1/2,1/4,1/8$. 
@@
 so-called $n$-sheets booklet (cf.~\ref{cartoon}). This is obtained by ``gluing'' together 
-$n$ independent replicas (``sheets'') of the model. One each replica the spins are 
+$n$ independent replicas (``sheets'') of the model. On each replica the spins are 
 divided into two groups $A$ and $B$, containing $N_A$ and $N_B$ spins respectively. The 
@@
 whereas at high temperature the model is paramagnetic. The two phases are divided 
-by a second order phase transition, as in the standard, i.e., on the plane, S-K model. 
+by a second order phase transition, as in the standard S-K model. 
 Interestingly, we found that the critical temperature depends in a non-trivial 
@@
 point approximation, including finite-size correztions. An interesting question would be 
-to investigate hwo the paramagnetic-glassy transition is associated with the subleading 
+to investigate how the paramagnetic-glassy transition is associated with the subleading 
 corrections to the observed volume law in the classical R\'enyi entropies. Also, it 
@@
 financial support by the ERC under Starting Grant 279391 EDEQS. 
+[Stephen's grant under Lode?]
 

### 2015-06-01 sk_model_v15.tex
latest

@@
 paradigm model of mean-field spin glasses. 
-Using both classical Monte Carlo simulation and analytical tools we investigate the S-K model 
-on a booklet of $n$-sheets.
+Using both classical Monte Carlo simulation and analytical tools we investigate the 
+S-K model on a booklet of $n$-sheets.
 This is obtained by gluing together $n$ independent copies of the model, and it is the 
-main ingredient to construct the R\'enyi entaglement-related quantities. We find that at low temperature 
-the S-K model is in a glassy phase, whereas at high temperature it exhibits paramagnetic 
-behavior. Interestingly, the critical temperature of the paramagnetic-glassy transition 
-depends in a non-trivial way on the geometry of the booklet. At high-temperatures we provide 
-the exact solution of the model exploiting the replica symmetry. This is the permutation 
-symmetry among the fictitious replicas that are used in the replica trick to perform disorder 
-averages. In the low-temperature glassy phase the replica symmetry has 
-to be broken. Using a generalization of the celebrated Parisi solution, we provide 
-approximated results for thermodynamic quantities and for $S_n$ and ${\mathcal I}_n$. 
-Finally, we show that both $S_n$ and ${\mathcal I}_n$ exhibit a volume law in the whole phase 
-diagram. Their densities $S_n/N$ and ${\mathcal I}_n/N$ are finite and smooth 
-function of the temperature, in the thermodynamic limit. In contrast with local spin models, 
-${\mathcal I}_n/N$ does not exhibit any crossing for different system sizes at the 
-critical point.
+main ingredient to construct the R\'enyi entaglement-related quantities. We find that at 
+low temperature the S-K model is in a glassy phase, whereas at high temperature it exhibits 
+paramagnetic behavior. Interestingly, the temperature of the paramagnetic-glassy 
+transition depends in a non-trivial way on the geometry of the booklet. At high-temperatures 
+we provide the exact solution of the model exploiting the replica symmetry. This is the 
+permutation symmetry among the fictitious replicas that are used in the replica trick to 
+perform disorder averages. In the glassy phase the replica symmetry has to be broken. 
+Using a generalization of the celebrated Parisi solution, we provide approximated results 
+for $S_n$ and ${\mathcal I}_n$, and for standard thermodynamic quantities. Both $S_n$ 
+and ${\mathcal I}_n$ exhibit a volume law in the whole phase diagram. We characterize 
+analytically and numerically the behavior of the corresponding densities $S_n/N$ and 
+${\mathcal I}_n/N$, in the thermodynamic limit. Remarkably, at the critical point 
+${\mathcal I}_n/N$ does not exhibit any crossing for different system sizes, in 
+contrast with local spin models.
 
@@
 Arguably, \emph{spin glasses} represent one of the most prototypical examples
-of disorder.
+of exotic behavior induced by disorder.
 While at any finite temperature disorder prevents the 
 usual magnetic ordering, at low-enough temperatures these systems display a 
-new and exotic type of ``order''. In the past decades an intense theoretical 
+new type of ``order''. In the past decades an intense theoretical 
 effort has been devoted to characterizing this spin glass order, the nature of 
@@
 a low-temperature glassy phase, which is separated from a high-temperature paramagnetic 
-one by a second order phase transition. In contrast with the mean-field nature of 
-Eq.~\eqref{SK-intro}, the solution of the S-K model has been a mathematical challenge. 
+one by a second order phase transition. In contrast with its mean-field nature, the 
+solution of the S-K model has been a mathematical challenge. 
 Although it was proposed as an ansatz by Parisi~\cite{parisi-1980} more than thirthy 
@@
 $A$, whereas $p_{i_A}$ is the probability of the configuration $i_A$. 
-%Clearly, $p_{i_A}\equiv\sum_{j_b\in{\mathcal C}_B}p_{i_A,j_B}$, with $p_{i_A,j_B}$ 
-%being the probability that the system is in the configuration $i_A\in{\mathcal C}_A$
-%in part $A$, and $j_B\in{\mathcal C}_B$ in part $B$. For a spin model at inverse 
-%temperature $\beta$, one has $p_{i_A,j_B}\equiv e^{-\beta E(i_A,j_B)}/Z(\beta)$, 
-%where $E(i_A,j_B)$ is the energy of the system, and $Z(\beta)$ its partition function. 
 Alternatively, $S_n(A)$ can be obtained from the partition function of the model on 
@@
 %
-Clearly,  Eq.~\eqref{renyi-intro} can be extended to quantum systems~\cite{stephan-2009,
-stephan-2010,stephan-2011,zaletel-2011,alcaraz-2013,stephan-2014-a} by interpreting 
-$p_{i_A}$ as the probability of finding part $A$ in the \emph{quantum} configuration 
-$i_A$. From $S_n(A)$, one defines the classical mutual information ${\mathcal I}_n(A,B)$ 
+Eq.~\eqref{renyi-intro} can be used for quantum systems by interpreting $p_{i_A}$ as 
+the probability of finding part $A$ in the \emph{quantum} configuration $i_A$. In particular, 
+for $n=1$ it defines the subsystem Shannon entropy~\cite{alcaraz-2013,stephan-2014-a}. 
+From $S_n(A)$, one defines the classical mutual information ${\mathcal I}_n(A,B)$ 
 as 
@@
 For local models ${\mathcal I}_n$ obeys the area law~\cite{wolf-2008} ${\mathcal I}_n(A)
-\propto\ell$, with $\ell$ being the length of the boundary between $A$ and $B$. Remarkably, 
+\propto\ell$, with $\ell$ the length of the boundary between $A$ and $B$. Remarkably, 
 for different $\ell$, the ratio ${\mathcal I}_n/\ell$ exhibits a crossing at a second 
-order phase transition~\cite{jaconis-2013}, and it can be used as a diagnostic tool for 
-critical behaviors. For conformally invariant critical models more universal information 
-can be extracted from the subleading contributions, i.e., the corrections to the area 
-law, of ${\mathcal I}_n$~\cite{stephan-2014}.
+order phase transition~\cite{jaconis-2013}, implying that it can be used as a diagnostic 
+tool for critical behaviors. For conformally invariant critical models more universal 
+information can be extracted from the area-law corrections of ${\mathcal I}_n$~\cite{stephan-2014}.
 
@@
 research area~\cite{refael-2009}. However, the behavior of entanglement-related quantities 
-in glassy phases, and at glassy critical points, has not been explored yet. Here we investigate 
+in glassy phases, and at glassy critical points, has not been explored yet (see 
+Ref.~\onlinecite{castelnovo-2010} for some interesting results). Here we investigate 
 both the classical R\'enyi entropy $S_n(A)$ and the mutual information ${\mathcal I}_n$ 
 in the S-K model, using classical Monte Carlo simulations and analytical tools. We often 
-restrict ourselves to the case with $n=2$, as this is where numerical simulation is most
-efficient . As usual in disordered system, we 
-focus on disorder-averaged quantities, considering $[S_n]$ and $[{\mathcal I}_n]$, 
-with the brackets $[\cdot]$ denoting the average over different realizations of 
-$J_{ij}$ in Eq.~\eqref{SK-intro}.
+restrict ourselves to the case with $n=2$, as this is where numerical simulations are 
+most efficient. As usual in disordered system, we focus on disorder-averaged quantities, 
+considering $[S_n]$ and $[{\mathcal I}_n]$, with the brackets $[\cdot]$ denoting the 
+average over different realizations of $J_{ij}$ (cf. Eq.~\eqref{SK-intro}).
 
@@
 booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
-We find that for any $\omega$ the S-K model exhibits a low-temperature glassy phase, which 
-is divided by the standard paramagnetic one at high temperatures by a critical point. 
+We show that for any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, 
+which is divided by the standard paramagnetic one at high temperatures by a critical point. 
 Surprisingly, the critical temperature exhibits a non-trivial dependence on $\omega$ 
 that we are able to determine analytically. 
-In the high-temperature region, for any fixed $\omega$, the permutational symmetry 
-among the replicas, both the physical and the fictitious ones, is preserved. This 
-allows us to provide an exact analytic expression for the free energy of the model 
-and several derived quantities, such as the internal energy. We check our result 
-against Monte Carlo simulations, finding perfect agreement. Oppositely, we provide 
-both numerical and analytical evidence that in the low-temperature phase, for any 
-$\omega$, the replica symmetry has to be broken. Specifically, we numerically observe 
-that the replica-symmetric (RS) result for the internal energy  is systematically 
-lower than the Monte Carlo data, as in the standard S-K model~\cite{sherrington-1978-prl,
-sherrington-1978}. This discrepancy becomes larger upon lowering the temperature.
+In the high-temperature region the permutational symmetry among the replicas, both the 
+physical and the fictitious ones, is preserved. This allows us to provide an exact analytic 
+expression for the free energy of the model and several derived quantities, such as the internal 
+energy. We compare our results with Monte Carlo simulations, finding perfect agreement. 
+Oppositely, we provide evidence that in the low-temperature phase the replica symmetry is  
+broken. Precisely, we numerically observe that the replica-symmetric (RS) result for the 
+internal energy  is systematically lower than the Monte Carlo data, as in the standard 
+S-K model~\cite{sherrington-1978-prl,sherrington-1978}. This discrepancy becomes larger 
+upon lowering the temperature.
 
@@
 
-Inspired by the Parisi scheme~\cite{parisi-1979}, we devise a systematic 
-way of breaking the replica symmetry in successive steps. Precisely, our scheme  
-breaks only the symmetry among the fictitious replicas, preserving that among the 
-physical ones. Although this appears natural, we are not able to provide a rigourous 
-proof that this is the correct symmetry breaking pattern. In particular, we cannot 
-exclude that the symmetry among the physical replicas has to be broken. As a consequence, 
-our scheme should be regarded as an approximation, and not as an exact solution. 
-Finally, we should mention that we restrict ourselves to the one-level replica symmetry 
-breaking ($1$-RSB). This, however, is a minor limitation because, in principle, it is 
-possible to implement in our ansatz the full breaking of the replica symmetry 
-($\infty$-RSB). Surprisingly, we numerically observe that the $1$-RSB approximation 
-for the internal energy is in excellent agreement with the Monte Carlo data for  
-$\beta\lesssim 3$, whereas the RS approximation fails already at $\beta\approx 1$. 
-This suggests that the $1$-RSB ansatz captures correctly some aspects of the 
-replica symmetry breaking.
-
-In this scenario the effects of the replica symmetry breaking are 
-reflected in the behavior of $[S_2]$ and $[{\mathcal I}_2]$. First, since $[S_2]$ exhibits 
-the volume law behavior $[S_2]\propto N$, we consider its density $[S_2]/N$. For finite-size 
-systems, and for any $\omega$, we find that $[S_2]/N$ exhibits a maximum at infinite 
-temperature, and it is a monotonically decreasing function of the temperature. More 
-specifically, the Monte Carlo data suggest a vanishing behavior in the zero-temperature 
-limit. Moreover, the finite-size corrections are neglegible at high temperatures, 
-whereas they increase upon lowering the temperature. A standard finite-size scaling 
-analysis shows that in the thermodynamic limit $[S_2]/N$ is finite and smooth as a 
-function of $\beta$ and $\omega$, in the whole phase diagram. In the paramagnetic phase 
-we are able to calculate the functional form of $[S_2]$, using the replica-symmetric 
-approximation. This perfectly matches the Monte Carlo data. At low temperatures deviations 
-from the replica-symmetric result are observed, reflecting the replica symmetry breaking. 
-Remarkably, we observe that the one-step replica symmetry breaking ($1$-RSB) approximation 
-$S_2^{1\textrm{-}RSB}/N$ is in full agreement with the Monte Carlo data for $\beta
-\lesssim 3$, confirming what is observed for the internal energy.
-
-Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This  
-obeys a volume law for any $\beta$ and $\omega$, in sharp contrast with local spin models, 
-where an area law is observed~\cite{wolf-2008}. The mutual information density $[{\mathcal I}_2]/N$ 
-vanishes in both the infinite-temperature and the zero-temperature limits, for any $\omega$. 
-Surprisingly, for different sizes ${\mathcal I}_2/N$ does not exhibit any crossing at the 
-paramagnetic-glassy transition, in striking contrast with local spin models~\cite{jaconis-2013}. 
-In the thermodynamic limit $[{\mathcal I}_2]/N$ is finite and smooth (as a function of $\beta$) 
-in the whole phase diagram. Interestingly, for any $\omega$, ${\mathcal I}_2/N$ exhibits a 
-maximum for $\beta\approx 1$. However, the position of this maximum is not simply related to 
-paramagnetic-glassy transition. Finally, at high temperature $[{\mathcal I}_2]/N$ is fully 
-described analytically within the replica symmetric approximation, whereas at low temperatures 
-one has to include  the effects of the replica symmetry breaking. Similar to $[S_2]$, we observe 
-that the $1$-RSB approximation for $[{\mathcal I})_2]/N$, is in good agreement with the Monte Carlo 
-data for $\beta \lesssim 3$.
+Inspired by the Parisi scheme~\cite{parisi-1979}, we devise a systematic way of breaking 
+the replica symmetry in successive steps. In our scheme we break only the symmetry among 
+the fictitious replicas, preserving that among the physical ones. Although this appears 
+natural, we are not able to provide a rigourous proof that this is the correct symmetry 
+breaking pattern. In particular, we cannot exclude that the symmetry among the physical 
+replicas has to be broken. As a consequence, our scheme should be regarded as an 
+approximation, and not as an exact solution. Finally, we restrict ourselves to the 
+one-level replica symmetry breaking ($1$-RSB), although, in principle, it is possible 
+to treat within our scheme the full breaking of the replica symmetry ($\infty$-RSB). 
+Surprisingly, we observe that the $1$-RSB approximation for the internal energy is in 
+excellent agreement with the Monte Carlo data for  $\beta\lesssim 3$, whereas the RS 
+approximation fails already at $\beta\approx 1$. This suggests that the $1$-RSB ansatz 
+captures correctly some aspects of the replica symmetry breaking.
+
+Clear signatures of the replica symmetry breaking are observed in the behavior of $[S_2]$. 
+First, since $[S_2]$ exhibits the volume law behavior $[S_2]\propto N$, 
+we consider its density $[S_2]/N$. For finite-size systems, and for any $\omega$, $[S_2]/N$ 
+exhibits a maximum at infinite temperature, and it is a decreasing function of the temperature, 
+as expected. Finite-size corrections are neglegible at high temperatures, whereas they increase 
+upon lowering the temperature. In the paramagnetic phase we are able to determine the functional 
+form of $[S_2]/N$ in the thermodynamic limit, using the replica-symmetric approximation. This 
+perfectly matches the Monte Carlo data. At low temperatures deviations from the RS result are 
+observed, reflecting the replica symmetry breaking. Remarkably, we observe that the one-step 
+replica symmetry breaking ($1$-RSB) result $S_2^{1\textrm{-}RSB}/N$ is in full agreement with 
+the Monte Carlo data for $\beta\lesssim 3$, confirming what is observed for the internal 
+energy.
+
+Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This obeys a volume 
+law for any $\beta$ and $\omega$, in contrast with local spin models, where an area law is 
+observed~\cite{wolf-2008}. The corresponding density $[{\mathcal I}_2]/N$ vanishes in 
+both the infinite-temperature and the zero-temperature limits. Surprisingly, ${\mathcal I}_2/N$ 
+does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition.
+This is in striking contrast with local spin models~\cite{jaconis-2013}. Interestingly, for 
+any $\omega$, ${\mathcal I}_2/N$ exhibits a maximum for $\beta\approx 1$. However, the 
+position of this maximum is not simply related to the paramagnetic-glassy transition. Finally, 
+at high temperature $[{\mathcal I}_2]/N$ is fully described analytically by the RS result 
+$[{\mathcal I}_2]^{RS}/N$, whereas at low temperatures one has to include the effects of the 
+replica symmetry breaking. Similar to $[S_2]$, we observe that the $1$-RSB approximation 
+$[{\mathcal I}^{1\textrm{-}RSB}_2]/N$, is in good agreement with the Monte Carlo data 
+for $\beta\lesssim 3$.
 
@@
 trick, which is used to perform disorder averages, and the saddle point approximation in 
-the thermodynamic limit . Section~\ref{solution} is concerned with the replica-symmetric 
-(RS) approximation. In subsection~\ref{para-section} we focus on the high-temperature 
-region where this approximation becomes exact. In subsection~\ref{rs-section} we discuss 
+the thermodynamic limit . Section~\ref{solution} is concerned with the RS approximation. 
+In subsection~\ref{para-section} we focus on the high-temperature 
+region, where this approximation becomes exact. In subsection~\ref{rs-section} we discuss 
 the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} is devoted to   
-presenting the one-step replica symmetry breaking ($1$-RSB) approximation. In 
-section~\ref{mc-results} we check the validity of both the RS and the $1$-RSB approximations 
-against Monte Carlo data. Section~\ref{Renyi-section} and~\ref{I2-section} present our results 
-for the classical R\'enyi entropy and the mutual information, respectively. Finally, 
-we conclude in section~\ref{conclusions}.
+the $1$-RSB approximation. In section~\ref{mc-results} we check the validity of both 
+the RS and the $1$-RSB results comparing with Monte Carlo simulations for the internal energy. 
+Section~\ref{Renyi-section} and~\ref{I2-section} discuss the classical R\'enyi entropy and the 
+mutual information, respectively. Finally, we conclude in section~\ref{conclusions}.
 
@@
 
+%Clearly, $p_{i_A}\equiv\sum_{j_b\in{\mathcal C}_B}p_{i_A,j_B}$, with $p_{i_A,j_B}$ 
+%being the probability that the system is in the configuration $i_A\in{\mathcal C}_A$
+%in part $A$, and $j_B\in{\mathcal C}_B$ in part $B$. For a spin model at inverse 
+%temperature $\beta$, one has $p_{i_A,j_B}\equiv e^{-\beta E(i_A,j_B)}/Z(\beta)$, 
+%where $E(i_A,j_B)$ is the energy of the system, and $Z(\beta)$ its partition function.
+
 Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
-the R\'enyi mutual information ${\mathcal I}_n(A,B,\beta)$ (with $n\in\mathbb{N}$
-and $A \cup B$ is the entire system)) 
-is defined as~\cite{jaconis-2013,stephan-2014} 
+the R\'enyi classical entropy $S_n(A)$ is defined as~\cite{jaconis-2013,stephan-2014} 
+%
+\begin{equation}
+\label{renyi}
+S_n(A)\equiv \frac{1}{1-n}\log\left(\frac{Z(A,n,\beta)}{Z^n(\beta)}\right).
+\end{equation}
+%
+Here $Z(A,n,\beta)$ is the partition function of the model on the $n$-sheet booklet, 
+whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures $\beta$. 
+The booklet geometry is illustrated in Figure~\ref{cartoon}. 
+Each sheet is divided into two parts $A$ and $B$ (cf. Figure~\ref{cartoon} (a)). Then $n$ copies 
+of the system are ``glued'' together to form the booklet. The spins in part $A$ of the different 
+sheets are identified (cf. Figure~\ref{cartoon} (b)). While spins in parts $B$ of the booklet 
+are at inverse temperature $\beta$, the ones in $A$ are at the effective temperature $n\beta$. 
+A similar geometric construction~\cite{guerra-2002} plays an important role in the mathematical 
+proof of the Parisi ansatz.
+
+Notice that one has $S_n(A)\equiv1/(n-1)\log(F(A,n,\beta))-n\log(F(\beta))$, where $F(A,n,\beta)
+\equiv\log(Z(A,n\beta))$ and $F(\beta)\equiv\log(Z(\beta))$ are related (apart from a factor 
+$\beta$) to the free energy of the model on the booklet and on the plane, respectively.
+The mutual information ${\mathcal I}_n(A,B,\beta)$ is defined~\cite{jaconis-2013,stephan-2014} 
 %
@@
 {\mathcal I}_n(A,B,\beta)\equiv\frac{1}{1-n}\log\Big(
-\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z(\beta)^nZ(n\beta)}
-\Big).
-\end{equation}
-%
-Here $Z(A,n,\beta)$ is the partition function of the model on the so-called 
-$n$-sheet booklet, whereas $Z(\beta)$ and $Z(n\beta)$ are the partition functions 
-on a the plane (a single sheet) at inverse temperatures $\beta$ and $n\beta$, 
-respectively. The booklet geometry is illustrated in Figure~\ref{cartoon}. The 
-sheet is divided into two parts $A$ and $B$ (cf. Figure~\ref{cartoon} (a)). 
-Then $n$ copies of the system (``sheets'') are ``glued'' together to form the 
-booklet. The spins in part $A$ of different sheets are identified (cf. 
-Figure~\ref{cartoon} (b)). Notice that a similar construction~\cite{guerra-2002} 
-plays an important role in the mathematical proof of the Parisi ansats. While spins 
-in $B$ are at inverse temperature $\beta$, the ones in $A$ are at the effective 
-temperature $n\beta$. The definition of $Z(B,n,\beta)$ is obtained by exchanging 
-$A$ and $B$. Alternatively, ${\mathcal I}_n$ can be rewritten as 
-%
-\begin{equation}
-{\mathcal I}_n(A,B,\beta)=S_n(A)+S_n(B)-S_n(A\cup B),
-\end{equation}
-%
-where $S_n(X)$ is the ``booklet'' classical R\'enyi entropy
-%
-\begin{equation}
-\label{renyi}
-S_n(X)\equiv \frac{1}{1-n}\log\left(\frac{Z(X,n,\beta)}{Z^n(\beta)}\right).
-\end{equation}
-%
-Notice that $S_n(X)$ corresponds to $S_n(X)\equiv1/(n-1)\log(F(X,n,\beta))
--n\log(F(\beta))$, where $F(X,n,\beta)\equiv\log(Z(X,n\beta))$ and $F(\beta)
-\equiv\log(Z(\beta))$ are related (apart from a factor $\beta$) to the 
-free energy of the model on the booklet and on the plane, respectively.
-Since here we focus on the effects of the disorder, we consider 
-the disorder-averaged mutual information $[{\mathcal I}_n]$ 
-%
-\begin{equation}
-[{\mathcal I}_n(A,B,\beta)]=[S_n(A)]+[S_n(B)]-[S_n(A\cup B)],
-\end{equation}
-%
-where the square brackets $[\cdot]$ denote the average over different disorder 
-realizations (cf. section~\ref{the-model}). Notice that $[{\mathcal I}_n]$ is 
-directly obtained from the so-called quenched averaged free energy $[F(X,n,\beta)]$, 
-which is usually considered in disordered systems~\cite{cardy-book}.
+\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z^n(\beta)Z(n\beta)}
+\Big),
+\end{equation}
+%
+where $Z(B,n,\beta)$ is obtained from $Z(A,n,\beta)$ by replacing $A$ with $B$. 
+Notice that the disorder-averaged mutual information $[{\mathcal I}_n]$ and the R\'enyi 
+entropy $[S_n]$ are directly related to the so-called quenched-averaged free energy 
+$[F(A,n,\beta)]$, which is the main quantity of interest in disordered systems~\cite{cardy-book}.
 
@@
 extract universal information about the CFT, such as the central 
-charge~\cite{stephan-2014}.  Remarkably, there is numerical evidence that  
-${\mathcal I}_n/\ell$ exhibits a crossing for different 
-system sizes at a second order phase transition, implying that it 
-can be used as a diagnostic tool to detect phase 
-transitions~\cite{jaconis-2013}.
+charge~\cite{stephan-2014}.
 
@@
 Here we introduce the Sherrington-Kirkpatrick (S-K) model on the booklet 
-(see Fig.~\ref{cartoon}). In particular, in subsection~\ref{the-model-def}  
-we define the model and its partition function. In subsection~\ref{replica-sec} 
+(see Fig.~\ref{cartoon}). In subsection~\ref{the-model-def}  we define the 
+model and its partition function. In subsection~\ref{replica-sec} 
 we discuss the replicated booklet construction that is used to calculate the 
@@
 which contains all the information about the thermodynamic behavior of the 
-model. The analytical formula for the replicated partition function (Eq.~\eqref{Z-ac}) 
-of the S-K the model, and the saddle point equations (Eqs.~\eqref{saddle-final}) 
-for the overlap tensor are the main results of this section.
+model. The analytical formula for the replicated partition function (Eq.~\eqref{Z-ac}), 
+and the saddle point equations (Eqs.~\eqref{saddle-final}) for the overlap tensor 
+are the main results of this section.
 
@@
 The Sherrington-Kirkpatrick (S-K) model~\cite{sherrington-1978-prl,
-sherrington-1978} on the $n$-sheets booklet (cf. Figure~\ref{cartoon}) is 
+sherrington-1978} on the $n$-sheets booklet (cf. Fig.~\ref{cartoon}) is 
 defined by the Hamiltonian
@@
 $N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
-In each ``page''  all the sites are divided into two groups $A\equiv\{1,\dots, 
-N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ 
-sites, respectively. The spins living in part $A$ and different sheets 
+In each ``page'' of the booklet all the sites are divided into two groups $A\equiv
+\{1,\dots, N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv 
+N-N_A$ sites, respectively. The spins living in part $A$ and different sheets 
 are identified, i.e., $\forall i\in A$ one has  
@@
 between different spins. Thus, physical observables should depend on the booklet geometry 
-only through the ratio $\omega\equiv N_A/N$.
-
-In Eq.~\eqref{SK-ham} the couplings $J_{ij}\in\mathbb{R}$ are uncorrelated quenched 
-random variables. $J_{ij}$ are the same in all the sheets of the booklet. Specifically, 
-here we choose $J_{ij}$ distributed according to the (gaussian) distribution ($P(J_{ij})$)  
+only through the ratio $\omega$ (cf. Eq.~\eqref{a-ratio}).
+
+In Eq.~\eqref{SK-ham} the couplings $J_{ij}\in\mathbb{R}$ are uncorrelated (from site to site) 
+quenched random variables. $J_{ij}$ are the same in all the sheets of the booklet. Specifically, 
+here we choose $J_{ij}$ distributed according to a gaussian distribution   
 %
@@
 satisfying the booklet constraint in Eq.~\eqref{book-constraint} are considered. 
-In the two limits $\omega\to 0$ and $\omega\to1$ one recovers the standard 
-S-K model. In particular, for $\omega=0$, i.e., $n$ disconnected sheets, from 
-Eq.~\eqref{book-pf} one has $Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with 
-$Z(\beta,\{J\})$ the partition function of the S-K model on the plane. 
-On the other hand, for $\omega=1$ it is $Z(1,n,\beta,\{J\})=Z(n\beta,\{J\})$, 
-i.e., the partition function of the S-K model at inverse temperature $n\beta$. 
-The quenched averaged free energy $[F(\omega,n,\beta)]$, is defined as 
+In the two limits $\omega=0$ and $\omega=1$ one recovers the standard 
+S-K model. In particular, for $\omega=0$, i.e., $n$ disconnected sheets, one has 
+$Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with $Z(\beta,\{J\})$ the partition function 
+of the S-K model on the plane. On the other hand, for $\omega=1$ it is $Z(1,n,\beta,
+\{J\})=Z(n\beta,\{J\})$, i.e., the partition function of the S-K model at inverse 
+temperature $n\beta$. The quenched averaged free energy $[F(\omega,n,\beta)]$, is defined 
+as 
 %
@@
 where $\int{\mathcal D}\{J\}\equiv\prod\nolimits_{i<j}\int_{-\infty}^{
-+\infty}dJ_{ij}P(J_{ij})$. Notice that $[F(\omega,n,\beta)]$ is the 
-main ingredient to construct the classical R\'enyi entropies and the 
-mutual information (cf. Eq.~\eqref{MI} and Eq.~\eqref{renyi}).
++\infty}dJ_{ij}P(J_{ij})$. 
+%Notice that $[F(\omega,n,\beta)]$ is the 
+%main ingredient to construct the classical R\'enyi entropies and the 
+%mutual information (cf. Eq.~\eqref{MI} and Eq.~\eqref{renyi}).
 
@@
 a similar scenario holds for generic $\omega$. Specifically, the glassy 
-phase at low temperatures along with the replica symmetry breaking mechanism 
-survive for generic $0<\omega<1$, while at high temperature the model is 
-paramagnetic. The critical point at $\beta=\beta_c(\omega)$, which marks the 
-transition between the two phases, is a nontrivial function of the booklet 
-ratio $\omega$.
+replica-symmetry-broken phase at low temperatures survives for generic 
+$0<\omega<1$, while at high temperature the model is paramagnetic. The 
+critical point at $\beta=\beta_c(\omega)$, which marks the transition 
+between the two phases, is a nontrivial function of the booklet ratio 
+$\omega$.
 
@@
 In contrast with Eq.~\eqref{rep-Z}, physical and unphysical replicas are 
-now coupled by a four-spin term. It is convenient to introduce the auxiliary 
-Hubbard-Stratonovich variables $q_{\gamma\gamma'}^{rr'}$ and $m_\gamma^r$, 
-with $\gamma,\gamma'=1,\dots,\alpha$ and $r=1,\dots,n$. Following the spin 
-glass literature~\cite{parisi-book}, we dub $q_{\gamma\gamma'}^{rr'}$ the 
-overlap tensor. In the standard S-K model (i.e., for $n=1$) 
+now coupled by a four-spin interaction. It is convenient to introduce the  
+Hubbard-Stratonovich variables $q_{\gamma\gamma'}^{rr'}$ and $m_\gamma^r$. 
+Following the spin glass literature~\cite{parisi-book}, we dub $q_{\gamma
+\gamma'}^{rr'}$ the overlap tensor. In the standard S-K model (i.e., for $n=1$) 
 $q_{\gamma\gamma'}^{rr'}$ becomes a $\alpha\times\alpha$ 
@@
 Eq.~\eqref{mf-action} is off-diagonal in the space of the fictitious replicas, 
-the second one is diagonal. The latter fully determines the behavior of the model 
-in the paramagnetic phase at high temperatures (see section~\ref{para-section}).
+the second one is diagonal. We anticipate here that the latter fully determines the 
+behavior of the model in the paramagnetic phase (see section~\ref{para-section}).
 
@@
 of freedom living in parts $A$ and $B$ of the booklet.
-The subscript in $\tr_A$ is to stress that spins living in different physical 
+The subscript $A$ in $\tr_A$ is to stress that spins living in different physical 
 replicas (i.e., for $r\ne r'$ in Eq.~\eqref{mf-action}) are identified (due 
@@
 e^{{\mathcal L}}\right)=q_{\gamma\gamma'}^{rr'}\\
-\nonumber
+%\nonumber
+\label{saddle-a}
 & \frac{\partial}{\partial m_\gamma^r}\left(\omega\log\tr_A 
@@
 %
-It is enlightening to rewrite Eqs.~\eqref{saddle} as 
+It is enlightening to rewrite Eqs.~\eqref{saddle}~\eqref{saddle-a} as 
 %
 \begin{align}
-\nonumber
+\label{saddle-final}
 & q_{\gamma\gamma'}^{rr'}=
@@
 \rangle_B
-\label{saddle-final}
+\label{saddle-final-a}
 \end{align}
@@
 \tr_{A(B)}\{{\mathcal O}\exp({\mathcal L})\}$ with $Z_{A(B)}\equiv\tr_{A(B)}
-\exp({\mathcal L})$. The first equation in Eqs.~\eqref{saddle-final} implies 
+\exp({\mathcal L})$. Notice that Eq.~\eqref{saddle-final} implies 
 that $q_{\gamma\gamma}^{rr}=1$ $\forall\gamma,r$. For $\omega=0$ and $n=1$, 
@@
 In order to calculate the free energy $[F(\omega,n,\beta)]$ one has to solve 
-the saddle point equations~\eqref{saddle-final}, take the analytic continuation 
+Eqs.~\eqref{saddle-final}~\eqref{saddle-final-a}, take the analytic continuation 
 $\alpha\in\mathbb{R}$, and, finally, the limit $\alpha\to 0$.  
-(cf. Eq.~\eqref{replica-trick}). Although it is possible to solve the 
-Eqs.~\eqref{saddle-final} numerically for any fixed $r,\alpha\in\mathbb{N}$, 
-taking the analytic continuation $\alpha\in\mathbb{R}$ is a formidable task, 
-since the dependence of $Z^\alpha(\omega,n,\beta)$ on $\alpha$ is in general 
-too complicated. The strategy to solve this problem is to choose a specific form of 
-the overlap tensor $q_{\gamma\gamma'}^{rr'}$ in terms of ``few'' parameters, which 
-allows to perform the analytic continuation and the limit $\alpha\to 0$ exactly.
+(cf. Eq.~\eqref{replica-trick}). Although it is possible to solve 
+Eqs.~\eqref{saddle-final}~\eqref{saddle-final-a} numerically for any fixed $r,
+\alpha\in\mathbb{N}$, taking the analytic continuation $\alpha\in\mathbb{R}$ is a 
+formidable task, since the dependence of $Z^\alpha(\omega,n,\beta)$ on $\alpha$ is in 
+general too complicated. The strategy is usually to choose a specific 
+form of the overlap tensor $q_{\gamma\gamma'}^{rr'}$ in terms of ``few'' 
+parameters, which allows to perform the analytic continuation and the limit 
+$\alpha\to 0$ exactly.
 
 For the standard S-K model (i.e., for $n=1$) the simplest parametrization is the 
-replica-symmetric one (RS), which amounts to take $q^{11}_{\gamma\gamma'}=q$. 
-This relies on the observation that the fictitious replicas appear symmetrically 
-in Eq.~\eqref{rep-Z}. Although the RS ansatz gives the correct result at high 
-temperature, it fails in the glassy phase at low temperatures, where the permutational 
-invariance within the replicas has to be broken~\cite{almeida-1978}. A systematic 
-scheme to break the replica symmetry, which allows to capture the the glassy behavior 
-of the S-K model at low temperature, is the celebrated Paris ansatz~\cite{parisi-1979}. 
+replica-symmetric one (RS), which amounts to taking $q^{11}_{\gamma\gamma'}=q$. 
+This relies on the observation that fictitious replicas appear symmetrically 
+in Eq.~\eqref{rep-Z}. Although the RS ansatz is correct at high temperatures, it 
+fails in the glassy phase at low temperatures, where the permutational invariance 
+within the replicas has to be broken~\cite{almeida-1978}. Parisi's ansatz~\cite{parisi-1979}
+provides a systematic scheme to break the replica symmetry in successive steps, and it  
+allows to capture the the glassy behavior of the S-K model at low temperature. 
 We anticipate (see section~\ref{rsb-1-section}) that a similar scheme has to be used to 
@@
 In this section we present the solution of the S-K model on the booklet, using 
-the replica symmetric approximation. In subsection~\ref{para-section} we focus 
-on the paramagnetic phase at high temperature, where this approximation is exact. 
-In particular, we show that the behavior of the model is fully determined by the 
-diagonal part of the overlap tensor $q_{\gamma\gamma'}^{rr'}$. The general structure 
-of $q_{\gamma\gamma'}^{rr'}$ in the replica-symmetric (RS) ansatz  is discussed in 
-subsection~\ref{rs-section}. This allows us to determine the critical temperature of 
-the paramagnetic-glassy transition. Similar to the standard S-K model, the RS ansatz 
-is not correct in the low-temperature region.
+the replica symmetric (RS) approximation. In subsection~\ref{para-section} we focus 
+on the high temperature phase, where this approximation is exact, and the 
+behavior of the model is fully determined by the diagonal part of the overlap 
+tensor $q_{\gamma\gamma'}^{rr'}$. The full structure of $q_{\gamma\gamma'}^{rr'}$ 
+in the RS ansatz  is discussed in subsection~\ref{rs-section}. This allows us to 
+determine the critical temperature of the paramagnetic-glassy transition.
 
@@
 
-Here we provide the exact analytical expression for the free energy 
-$[F_{para}(\omega,n,\beta)]$  in the paramagnetic non-glassy phase of 
+Here we provide the exact analytical expression for the disorder-averaged free 
+energy $[F_{para}(\omega,n,\beta)]$  in the paramagnetic non-glassy phase of 
 the S-K model on the booklet. We start discussing the infinite temperature 
-limit (i.e., $\beta\to 0$).
-
-Using Eq.~\eqref{mf-action} one obtains  $\tr_Ae^{{\mathcal L}}=
-2^{\alpha}+{\mathcal O}(\beta^2)$ and $\tr_B e^{{\mathcal L}}=2^{n\alpha}+
-{\mathcal O}(\beta^2)$, implying  
+limit (i.e., $\beta\to 0$), restricting ourselves to zero magnetic field.
+
+Using Eq.~\eqref{mf-action}, a standard high-temperature expansion yields 
+$\tr_Ae^{{\mathcal L}}=2^{\alpha}+{\mathcal O}(\beta^2)$ and $\tr_B e^{{
+\mathcal L}}=2^{n\alpha}+{\mathcal O}(\beta^2)$, implying  
 %
@@
 & \langle S^{(r,\gamma)}S^{(r',\gamma')}\rangle_B=2^{n\alpha}
-\delta_{\gamma,\gamma'}\delta_{r,r'}+{\mathcal O}(\beta^2)\\\nonumber
+\delta_{\gamma,\gamma'}\delta_{r,r'}+{\mathcal O}(\beta^2)\\
 & \langle S^{(r,\gamma)}S^{(r',\gamma')}\rangle_A=2^{\alpha}
@@
 %
-After substituting in Eqs.~\eqref{saddle-final}, it is straightforward to 
+After substituting in Eq.~\eqref{saddle-final}, it is straightforward to 
 obtain the infinite-temperature overlap tensor $q_{\gamma\gamma'}^{rr'}$ 
@@
 indices $\gamma,\gamma'$ and $r,r'$, i.e.,  the physical and 
-fictitious replica spaces. The analytic continuation $\alpha\to 0$ 
-(cf. Eq.~\eqref{replica-trick}) can be performed explicitly, to obtain 
+fictitious replica spaces. Using Eq~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, 
+after performing the analytic continuation $\alpha\to 0$, one obtains  
 %
@@
 Alternatively, Eq.~\eqref{saddle-high-t} can be obtained by substituting the 
-ansatz~\eqref{high-t-q} in Eqs.~\eqref{saddle-final}.
-
-Clearly, for two independent copies of the S-K model (i.e., $\omega=0$) 
+ansatz~\eqref{high-t-q} in Eqs.~\eqref{saddle-final}~\eqref{saddle-final-a}.
+
+Clearly, for two independent copies of the S-K model, i.e., $\omega=0$,  
 Eq.~\eqref{saddle-high-t} gives $q_0=0$ for $\beta\le1$, whereas 
-one obtains $q_0\ne0$ for $\beta>1$. On the other hand, for $\omega=1$ 
-one has $q_0=1$ $\forall\beta$. For generic $0<\omega<1$ the solution of 
-Eq.~\eqref{saddle-high-t} is shown in Figure~\ref{RSB0_saddle_ht}, plotting 
-$q_0$ as a function of $\omega$, for $\beta=0,0.75,1,1.1$. For $\beta=0$ it 
+one has $q_0\ne0$ for $\beta>1$. On the other hand, for $\omega=1$ 
+one has $q_0=1$ $\forall\beta$. For intermediate $0<\omega<1$ $q_0$ 
+is plotted as a function of $\omega$ in Fig.~\ref{RSB0_saddle}. For $\beta=0$ it 
 is $q_0=\omega$ (straight line in the Figure). In the low-temperature limit 
@@
 phase (cf. Eq.~\eqref{high-t-q}). The last term sets $q_{\gamma\gamma'}^{rr'}=q'_0$ 
-$\forall\gamma\ne\gamma'$ and $\forall r,r'$. Physically, Eq.~\eqref{rs-ansatz} 
-means that we require the permutational symmetry in both the physical and fictitious 
-replica space. We do not have any rigorous argument to justify the ansatz~\eqref{rs-ansatz}, 
-besides its simplicity. However, we numerically observe that it captures quite accurately 
-the behavior of the model, at least around the paramagnetic-glassy transition (see 
-section~\ref{mc-results} for the Monte Carlo results).
+$\forall\gamma\ne\gamma'$ and $\forall r,r'$. Clearly, $q_{\gamma\gamma'}^{rr'}$ is 
+symmetric in both the physical and fictitious replica spaces. We do not have any 
+rigorous argument to justify the ansatz~\eqref{rs-ansatz}, besides its simplicity. 
+However, we numerically observe that it captures quite accurately the behavior of 
+the model, at least around the paramagnetic-glassy transition (see section~\ref{mc-results} 
+for the comparision with Monte Carlo data).
 
@@
 
-In Eq.~\eqref{eq1}\eqref{eq2} 
-$q_0,q_0'$ have to satisfy the saddle point conditions $\partial[F_{RS}(\omega,n,\beta)]/
-\partial q_0=\partial[F_{RS}(\omega,n,\beta)]/\partial q'_0=0$ 
-(cf. Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} for the  precise form of the 
-saddle point equations for $n=2$). 
+In Eq.~\eqref{eq1}\eqref{eq2} $q_0,q_0'$ satisfy the saddle point conditions 
+$\partial[F_{RS}(\omega,n,\beta)]/\partial q_0=\partial[F_{RS}(\omega,n,\beta)]/
+\partial q'_0=0$ (cf. Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} for the precise 
+form of the saddle point equations for $n=2$). 
 The resulting $q_0$ and $q_0'$ are plotted in Figure~\ref{RSB0-saddle} (full 
@@
 \sqrt{\frac{2}{\pi}}\beta\Big)+\dots
-\\\nonumber 
+\\ 
 & q_0'=1-\frac{1}{\sqrt{2\pi}\beta}-\frac{1}{2\pi\beta^2}+{\mathcal O}(\beta^{-3}),
@@
 
+%##########################################################################
+\subsection{The paramagnetic-glassy transition}
+
 Finally, using the replica-symmetric ansatz Eq.~\eqref{rs-ansatz} one can determine 
@@
 Near the glassy transition one should expect $q'_0\to0$, whereas $q_0$ 
-should remain finite ($q_0>0$ in the paramagnetic phase, see section~\ref{para-section}). 
-By expanding $[F_{RS}(\omega,n,\beta)]$ (cf. Eq~\eqref{rs-F}) for small $q_0'$, and 
-keeping only terms up to ${\mathcal O}((q_0')^2)$, one obtains a standard Landau theory. 
-Thus, $\beta_c$ is obtained imposing that the coefficient of the quadratic term $q_0'^2$ 
-changes sign. This leads to the equation 
+should remain finite (see section~\ref{para-section}). By expanding $[F_{RS}(\omega,n,\beta)]$ 
+(cf. Eq~\eqref{rs-F}) for small $q_0'$, and keeping only terms up to ${\mathcal O}((q_0')^2)$, 
+one obtains a standard Landau theory. Thus, $\beta_c$ is obtained imposing that the 
+coefficient of the quadratic term $q_0'^2$ changes sign. This leads to the equation 
 %
@@
 %
-where $q_0$ is obtained by solving the high-temperature saddle point 
-equation~\eqref{saddle-high-t}. The resulting $\beta_c$ solution of Eq.~\eqref{tc} 
-is shown in Fig.~\ref{beta_c} as a function of $\omega$.
+where $q_0$ is obtained by solving the high-temperature saddle point equation~\eqref{saddle-high-t}. 
+The resulting $\beta_c$ is plotted in Fig.~\ref{beta_c} as a function of $\omega$.
 
@@
 %##########################################################################
-\section{The one-step replica-symmetry-broken (1-RSB) approximation}
+\section{The one-step replica-symmetry-broking (1-RSB) approximation}
 \label{rsb-1-section}
@@
 %
-\begin{displaymath}
+\begin{equation}
 q'=\left\{
@@
 \label{q-rsb1a}
-\end{displaymath}
+\end{equation}
 %
@@
 fictitious replicas is broken, the symmetry among the physical ones is preserved. 
-Notice that the choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block 
-diagonal structure for $q'$:  the elements in the $m_1\times m_1$ diagonal 
-blocks are set to $q_1'$, whereas all the off-diagonal elements are set to 
-$q_0'$. As for the replica-symmetric ansatz in Eq.~\eqref{rs-ansatz}, we do 
-not have any rigorous argument to justify Eq.~\eqref{q-rsb1a} (see 
-section~\eqref{mc-results}, for numerical results).
+The choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block-diagonal structure for 
+$q'$: the matrix elements of the $m_1\times m_1$ diagonal blocks of $q'$ are set to 
+$q_1'$, whereas all the off-diagonal elements are set to $q_0'$. As for the replica-symmetric 
+ansatz in Eq.~\eqref{rs-ansatz}, we do not have any rigorous argument to justify 
+Eq.~\eqref{q-rsb1a} (see section~\eqref{mc-results}, however, for numerical results).
 
@@
 where we defined $B_\sigma\equiv[\sigma m_1,(\sigma+1)m_1)$ with $\sigma\in\mathbb{N}$. 
-It is convenient t to introduce the Hubbard-Stratonovich variables $z,z_\sigma,z_{\sigma,\gamma}$ 
+It is convenient to introduce the Hubbard-Stratonovich variables $z,z_\sigma,z_{\sigma,\gamma}$ 
 (one for each term in Eq.~\eqref{blocks}). One then obtains 
@@
 \begin{multline}
+\label{step}
 \log\tr'\exp({\mathcal L}_{1\textrm{-}RSB})=
@@
 +\log\tr'\int Dz\prod_\sigma\int Dz_\sigma\prod\limits_{\gamma\in B_\sigma}
-\int Dz_{\sigma,\gamma}\prod_r\exp\Big\{\beta\Big[\\\nonumber
-z\sqrt{q'_0}S^{(r,\gamma)}
-+z_{\sigma,\gamma}\sqrt{q_0-q_1'} S^{(r,\gamma)}+
-z_{\sigma}\sqrt{q_1'-q_0'}S^{(r,\gamma)}\Big]\Big\}
-\end{multline}
-%
-The trace over the spin variables can now be performed explicitly. Finally, 
-one obtains the 1-RSB approximation for the free energy 
+\int Dz_{\sigma,\gamma}\prod_r\exp\Big\{\\
+\beta\Big(z\sqrt{q'_0}+z_{\sigma,\gamma}\sqrt{q_0-q_1'}+
+z_{\sigma}\sqrt{q_1'-q_0'}\Big)S^{(r,\gamma)}\Big\}.
+\end{multline}
+%
+The trace over the spin variables can now be performed explicitly in Eq.~\eqref{step}. 
+Finally, one obtains the 1-RSB approximation for the free energy 
 $[F_{1\textrm{-}RSB}(\omega,n,\beta)]$ as 
@@
 point equations Eqs.~\eqref{RSB-1-saddle-a}\eqref{RSB-1-saddle-b}\eqref{RSB-1-saddle-c}
-\eqref{RSB-1-saddle-d}. One should remark that, although $m_1\in\mathbb{N}$ in 
-Eq.~\eqref{q-rsb1a}, one obtains $m_1\in\mathbb{R}$ from the saddle point equations. 
-Finally, the RS result $F_{RS}(\omega,n,\beta)$ is recovered from Eq.~\eqref{RSB-1-logZ} 
-in the limit $q_1'\to q_0'$, while the paramagnetic solution corresponds to 
-$q_1'\to q_0'\to 0$.
+\eqref{RSB-1-saddle-d}. One should remark that, although formally $m_1\in\mathbb{N}$, 
+one obtains $m_1\in\mathbb{R}$ from the saddle point equations. 
+Finally, the RS result $F_{RS}(\omega,n,\beta)$ (cf. Eq.~\eqref{rs-F}) is recovered 
+from Eq.~\eqref{RSB-1-logZ} in the limit $q_1'=q_0'$, while the result in the 
+paramagnetic phase (cf. Eq.~\eqref{ht-logZ}) corresponds to $q_1'=q_0'=0$.
 
@@
 In this section we numerically confirm the results of section~\ref{solution}. 
-To this purpose, we discuss Monte Carlo (MC) data for the S-K model on the 
-$2$-sheets booklet with zero external magnetic field. We focus on the 
-internal energy $U(\omega,n,\beta)$ 
+We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
+with zero external magnetic field. We focus on the internal energy $U(\omega,n,
+\beta)$ 
 %
@@
 Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
-$\beta$, for the booklet with $\omega=1/2$ (see Fig.~\ref{cartoon}). The cicles, squares, 
-and triangles are the MC results for different sizes (i.e., number of spins per sheet) 
-$N=32,64,128$. The vertical dotted line is the critical temperature $\beta_c\approx 0.603$ of 
-the paramagnetic-glassy transition (cf. Fig.~\ref{beta_c}). Clearly, in the high-temperature 
-region for $\beta<\beta_c$ finite size effects are small, and already for $N=64$ the MC data 
-are indistinguishable from the result in the thermodynamic limit. Oppositely, stronger 
-scaling corrections are  visible in the low-temperature phase at $\beta>\beta_c$. 
+$\beta$, for $\omega=1/2$ (see Fig.~\ref{cartoon}). The cicles, squares, and triangles 
+are the MC results for different sizes, i.e., number of spins per sheet, $N=32,64,128$. 
+The vertical dotted line is the critical temperature $\beta_c\approx 0.603$ of 
+the paramagnetic-glassy transition (cf. Fig.~\ref{beta_c}). In the high-temperature 
+region finite size effects are small, and already for $N=64$ the MC data are indistinguishable 
+from the thermodynamic limit. Oppositely, stronger scaling corrections are  visible in 
+the low-temperature phase at $\beta>\beta_c$. 
 The plus symbols in Fig.~\ref{U-MC} are the numerical extrapolations in the 
-thermodynamic limit $N\to\infty$. These are obtained by fitting the finite size MC data 
-to the ansatz $U(\omega,\beta)/N=u_{\infty}(\omega,\beta)+c/N^{\phi}$, where 
+thermodynamic limit. These are obtained by fitting the finite size MC data 
+to the ansatz $U/N=u_{\infty}(\omega,\beta)+c/N^{\phi}$, where 
 $u_{\infty}$ is energy density in the thermodynamic limit, $c$ a fitting parameter, and 
@@
 
-The dash-dotted line is the analytical result $U_{RS}$ obtained using the 
-replica-symmetric (RS) approximation (see section~\ref{rs-section}). 
-Using Eq~\eqref{U-def} and Eq.~\eqref{rs-F}, $U_{RS}$  is obtained as   
+The dash-dotted line in Fig.~\ref{U-MC} is the analytical result $U_{RS}$ obtained using 
+the replica-symmetric (RS) approximation (see section~\ref{rs-section}). 
+Using Eq.~\eqref{rs-F} and Eq~\eqref{U-def}, $U_{RS}$  is obtained as   
 %
@@
 \eqref{RS-saddle-2}. Notice that $U_{RS}$ depends on $\omega$ only through $q_0,q_0'$. 
-From Fig.~\ref{U-MC} one has that, while $U_{RS}$ is in perfec agreeement with the numerics 
+From Fig.~\ref{U-MC} one has that, while $U_{RS}$ is in perfect agreement with the numerics 
 for $\beta\approx\beta_c$, deviations appear in the low-temperature region. Moreover, these 
@@
 Fig.~\ref{U-MC}), with $u_{\infty}(0,\beta)\to-0.76321...$~\cite{parisi-1979,parisi-1983} the 
-zero-temperature internal energy density of the S-K model on a single sheet. Surprisingly, 
+zero-temperature density of internal energy for the S-K model on the plane. Surprisingly, 
 this behavior is already observed in the MC data at $\beta\approx 3$, whereas it is not 
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/Renyi_MC_v2}
-\caption{ The classical Renyi entropy per spin $S_2(\omega)/N$  in the 
- S-K model on the $2$-sheets booklet with zero magnetic: $S_2(\omega)/N$ as a 
+\caption{ The classical disorder-averaged Renyi entropy per spin $[S_2(\omega)]/N$  
+ in the S-K model on the $2$-sheets booklet with zero magnetic: $[S_2(\omega)]/N$ as a 
  function of the inverse temperature $\beta$. The different panels 
- correspond to different booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). 
+ correspond to different booklet aspect ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). 
  The triangles, squares and rhombi denote the Monte Carlo results for 
@@
  extrapolations to the thermodynamic limit. The dash-dotted lines are the  
- analytical results $U_{RS}/N$ using the replica-symmetry (RS) approximation. 
- The circles are the analytical results $U_{1\textrm{-}RSB}$ obtained 
+ analytical results in the replica-symmetry (RS) approximation. 
+ The circles are the analytical results obtained 
  using the one-step replica symmetry breaking (1-RSB) ansatz.
@@
 
-The behavior of $U/N$ for $\omega\ne1/2$ is investigated in Fig.~\ref{U-RS},
+The behavior of $U/N$ is similar for $\omega\ne1/2$, and it is investigated in Fig.~\ref{U-RS},
 plotting $U/N$ as a function of $\beta$ for $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
@@
 $\beta_c$ is obtained by numerically solving Eq.~\eqref{tc}. The lines in Fig.~\ref{U-RS} 
-denote the replica-symmetric result $U_{RS}$ (cf. Eq.~\eqref{U}).
-
-For generic $n$ and $\omega$, in the limit $\beta\to 0$, Eq.~\eqref{U-def} 
-and Eq.~\eqref{logZ-ht} give  
-%
-\begin{equation}
-U_{RS}(\omega,n,\beta)= -N\frac{\beta}{2}(\omega^2(n^2-n)+n)+{\mathcal O}(\beta^2), 
+denote $U_{RS}$ (cf. Eq.~\eqref{U}). 
+At high temperature, and for generic $n$ and $\omega$, Eq.~\eqref{logZ-ht} and Eq.~\eqref{U-def} 
+give  
+%
+\begin{equation}
+U_{RS}= -N\frac{\beta}{2}(\omega^2(n^2-n)+n)+{\mathcal O}(\beta^2), 
 \label{ht-U}
@@
 i.e., a linear behavior of $U/N$ as a function of $\beta$. For $\omega=0$ and $\omega=1$ 
-this behavior is exact up to the critical point at $\beta=\beta_c$, meaning that the higher 
-orders ${\mathcal O}(\beta^2)$ in Eq.~\eqref{ht-U} are zero. This is only an approximation at 
-intermediate $0<\omega<1$. Clearly, Fig.~\ref{U-RS} confirms that at $\beta<\beta_c$ both 
-Eq.~\eqref{U} and Eq.~\eqref{ht-U} are in excellent agreement with the numerical results. 
-However, one should observe that $U_{RS}$ is not correct in the low-temperature at 
-$\beta>\beta_c$, where the replica symmetry breaking has to be taken into account.
-
-The effects of the replica symmetry breaking are more carefully discussed in 
-Fig.~\ref{U-RSB-1}, plotting $U/N$ versus $1\le\beta\le 2$. The plus symbols and the lines 
-are the same as in Fig.~\ref{U-RS}.  The full circles denote the internal energy per spin 
+this behavior is exact up to $\beta=\beta_c$, meaning that the higher orders ${\mathcal O}(\beta^2)$ 
+in Eq.~\eqref{ht-U} are zero. This is only an approximation at intermediate $0<\omega<1$. 
+Both Eq.~\eqref{U} and Eq.~\eqref{ht-U} are clearly confirmed in Fig.~\ref{U-RS}.
+
+However, Eq.~\eqref{ht-U} is not correct for $\beta>\beta_c$, where the replica symmetry breaking 
+has to be taken into account. The effects of the replica symmetry breaking are more carefully 
+discussed in Fig.~\ref{U-RSB-1}, plotting $U/N$ versus $1\le\beta\le 2$. The plus symbols and the 
+lines are the same as in Fig.~\ref{U-RS}. The circles denote the internal energy per spin 
 $U_{1\textrm{-}RSB}/N$ as obtained using the $1$-step replica symmetry breaking (1-RSB) 
@@
 where $q_0,q_0',q_1',m_1\in\mathbb{R}$ are solutions of the saddle point 
-equations \eqref{RSB-1-saddle-a}-\eqref{RSB-1-saddle-d}. Clearly, from Eq.~\eqref{U'} 
-one has $U_{1\textrm{-}RSB}\to U_{RS}$ for $q_1'\to q_0'$, as expected. 
-Moreover, since for $\beta\approx\beta_c$ it is $q_1'\approx q_0'\approx0$, one has  
+equations \eqref{RSB-1-saddle-a}-\eqref{RSB-1-saddle-d}. Clearly, Eq.~\eqref{U'} 
+implies $U_{1\textrm{-}RSB}\to U_{RS}$ for $q_1'\to q_0'$, as expected. 
+Moreover, for $\beta\approx\beta_c$ one has $q_1'\approx q_0'\approx0$, implying   
 that $U_{RSB}\approx U_{RS}$, i.e. the effects of the replica symmetry breaking are 
-negligible near the critical point. 
-On the other hand, in the replica symmetry broken phase at low temperature, 
-where the RS approximation $U_{RS}$ fails (see Fig.~\ref{U-RS}), $U_{1\textrm{-}RSB}$ 
+negligible near the critical point. Interestingly, at low temperatures, where the 
+RS approximation $U_{RS}$ fails (see Fig.~\ref{U-RS}), $U_{1\textrm{-}RSB}$ 
 is in good agreement with the Monte Carlo data, at least up to $\beta\approx 2$.  
-This allows us to conclude that, although the ansatz in Eq.~\eqref{q-rsb1} 
-might not be correct in the limit $\beta\to\infty$, it captures some of the effects 
+This allows us to conclude that, although the 1-RSB ansatz (cf. Eq.~\eqref{q-rsb1}) 
+is not correct for $\beta\to\infty$, it captures some of the effects 
 of the replica symmetry breaking.
@@
 
-We now turn to discuss the behavior of the classical R\'enyi entropies (cf. 
-Eq.~\eqref{renyi}) in the S-K model. Here we restrict ourselves to the second R\'enyi 
-entropy $S_2$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
-there is no well defined boundary between the two parts $A$ and $B$ of the system (unlike Fig.~\ref{cartoon} for local models).
-The fully connected nature of the model suggests that $S_2$ should be volume law $S_2 \propto N$ for all temperature.
-Therefore it is natural to consider the entropy per spin $S_2/N$.
+We now turn to discuss the behavior of the disorder-averaged classical R\'enyi entropies 
+(cf. Eq.~\eqref{renyi}) in the S-K model. Here we restrict ourselves to the second R\'enyi 
+entropy $[S_2]$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
+there is no well defined boundary between the two parts $A$ and $B$ of the system 
+(unlike Fig.~\ref{cartoon} for local models). The fully connected nature of the S-K model 
+suggests the volume-law behavir $[S_2]\propto N$ for all temperature.
+Therefore it is natural to consider the entropy per spin $[S_2]/N$.
 
@@
 
-The Monte Carlo data for $S_2/N$  are shown in Fig.~\ref{Renyi-MC} plotted versus the 
+The Monte Carlo data for $[S_2]/N$  are shown in Fig.~\ref{Renyi-MC} plotted versus the 
 inverse temperature $0.25\le\beta\le 2.5$. The different panels correspond to the  
 booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the empty 
-circles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per per 
-sheet. Clearly, finite size effects are present, which increase upon lowering 
-the temperature, as expected. In order to obtain $S_2/N$ in the thermodynamic limit 
-we fit the data to the ansatz $S_2(\omega)=s_2(\omega)+c'(\omega)/N^{\phi'}$, where 
-$s_2(\omega)$ is the entropy per spin in the limit $N\to\infty$, $c'$ a constant, and 
+triangles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per per sheet. 
+Clearly, finite size effects are present, which increase upon lowering 
+the temperature, as expected. In order to obtain $[S_2]/N$ in the thermodynamic limit 
+we fit the data to the ansatz $[S_2]=s_2(\omega)+c'(\omega)/N^{\phi'}$, where 
+$s_2(\omega)$ is the entropy per spin in the thermodynamic limit, $c'$ a constant, and 
 $\phi'$ the exponent of the scaling corrections. The plus symbols in Fig.~\ref{Renyi-MC} 
@@
 which is the exponent of the scaling corrections of the free energy in the standard 
-S-K model. This is not surprising, since $S_2(\omega)$ is obtained as the difference 
-$S_2(\omega)\equiv [F(0,2,\beta)-F(\omega,2,\beta)]$ (cf. Eq.~\eqref{renyi}). 
-Clearly, in the thermodynamic limit $S_2(\omega)/N$ is finite for any $\beta$, 
-confirming the expected volume law $S_2\propto N$ behavior. Moreover, $S_2/N$ 
+S-K model. This is not surprising, since $[S_2]$ is obtained as the difference 
+$[S_2]\equiv [F(0,2,\beta)-F(\omega,2,\beta)]$ (cf. Eq.~\eqref{renyi}). 
+Clearly, in the thermodynamic limit $[S_2]/N$ is finite for any $\beta$, 
+confirming the expected volume law behavior. Moreover, $[S_2]/N$ 
 exhibits a maximum in the infinite-temperature limit $\beta\to0$. The height of this 
 maximum  is a decreasing function of $\omega$ (compare the panels (a)(b)(c) in 
-Fig.~\ref{Renyi-MC}). Finally, for any fixed $\omega$, $S_2(\omega)$ decreases 
-smoothly upon lowering the temperature. In particular, the Monte Carlo data suggest 
-a vanishing behavior in the zero-temperature limit $\beta\to\infty$.
-
-The dash-dotted line in Fig.~\ref{Renyi-MC} denotes the analytical result $S_2^{RS}$ 
-obtained using the replica-symmetric (RS) approximation (see section~\ref{rs-section}).
-More precisely, $S_2^{RS}/N$ is obtained from Eq.~\eqref{renyi} and the expression for 
-the replica symmetric free energy $[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). Notice that in the 
+Fig.~\ref{Renyi-MC}).
+
+The dash-dotted line in Fig.~\ref{Renyi-MC} denotes the analytical result $[S_2^{RS}]$ 
+obtained using the RS approximation (see section~\ref{rs-section}). More precisely, 
+$[S_2^{RS}]/N$ is obtained from Eq.~\eqref{renyi} and the expression for the free energy 
+$[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). Notice that in the 
 high-temperature limit $\beta\to0$, where the RS approximation is exact, 
@@
 \begin{equation}
-S^{RS}_2(\omega)=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^2).
+[S^{RS}_2]=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^3).
 \end{equation}
@@
 From Fig~\ref{Renyi-MC} one has that the extrapolated MC data are in quantitative 
-agreement with $S_2^{RS}/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
-observed at lower temperatures (not shown in the Figure). 
-These are reflecting the symmetry breaking. A better approximation for $S_2(\omega)/N$ 
-at low temperatures is obtained by including the effects of the replica symmetry breaking. 
-The full circles in Fig.~\ref{Renyi-MC} are the analytical results $S_2^{1\textrm{-}RSB}$
-obtained using the one step replica symmetry breaking (1-RSB) ansatz 
-(see section~\ref{rsb-1-section}). $S_2^{1\textrm{-}RSB}$ is formally obtained 
+agreement with $[S_2^{RS}]/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
+observed at lower temperatures (not shown in the Figure). These reflect the symmetry 
+breaking. A better approximation for $[S_2]/N$ at low temperatures is obtained by 
+including the effects of the replica symmetry breaking. The circles in Fig.~\ref{Renyi-MC} 
+denote the one-step replica symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$
+(see section~\ref{rsb-1-section}). Here $[S_2^{1\textrm{-}RSB}]/N$ is formally obtained 
 using Eq.~\eqref{renyi} and the free energy $[F_{1\textrm{-}RSB}]$ (cf. 
-Eq.~\eqref{RSB-1-logZ}). Remarkably,  $S_2^{1\textrm{-}RSB}$ is in excellent 
-agreement with the Monte Carlo extrapolations for $\beta\lesssim 2$, where the RS 
-approximation fails.
+Eq.~\eqref{RSB-1-logZ}). Remarkably, $[S_2^{1\textrm{-}RSB}]/N$ is in excellent 
+agreement with the Monte Carlo extrapolations for $\beta\lesssim 2$.
 
@@
 
-Here we focus on the behavior of the Renyi mutual information ${\mathcal I}_2$ in 
-the S-K model. Similar to $S_2(\omega)$, the mutual information obeys the volume 
-law ${\mathcal I}_2(\omega)\propto N$. This is in contrast with local models, 
-where ${\mathcal I}_n(\omega)$ is constructed to exhibit an area law at all temperatures.
-Again, the fully connected nature of the S-K model means that common expectations from local models
-do not apply.  Here we consider the mutual information per spin ${\mathcal I}_2(\omega)/N$.
+Here we focus on the behavior of the Renyi mutual information $[{\mathcal I}_2]$ in 
+the S-K model. Similar to $[S_2]$, the mutual information obeys the volume 
+law $[{\mathcal I}_2]\propto N$. This is in contrast with local models, where 
+$[{\mathcal I}_n]$ by construction exhibits an area law at all temperatures.
+However, due to the fully connected nature of the S-K model common expectations 
+from local models do not apply.  Here we consider the mutual information per spin 
+$[{\mathcal I}_2]/N$.
 
@@
 
+\bibitem{castelnovo-2010}
+C.~Castelnovo, C.~Chamon, and D.~Sherrington, Phys.\ Rev.\ B {\bf 81}, 184303 (2010).
+
 \end{thebibliography}

### 2015-06-09 algorithm.tex
revised

\documentclass{article}                         
\usepackage{amssymb,amsmath,bm,color}

\begin{document}

\section{Numerical methods}

There are a few approaches to calculate the log of the ratio of the partition function numerically.
Numerical integration of the energy as a function of temperature\cite{jaconis-2013} can be used, but requires highly accurate information over a large range of temperature for both the normal and modified partition function.

We can also directly calculate the ratio of partition functions where $A$ changes only slightly, and build up the full quantity by taking the product of many such measurements.
This method is usually referred to as the ratio trick, and in finite dimensional systems there are efficient ways to calculate this ratio\cite{stephan-2014}.
In an infinite dimensional system the only efficient way to use this method is to increase $A$ more slowly than typical.
For this study, $A$ is increased by only 4 sites at a time.

First, if we want to sample from $A=0$ (two disconnected systems) to $A=N$ (two fully connected systems), let us use the ratio trick to write
\begin{align}
\frac{Z(A,n,\beta)}{\bigl[ Z(\beta) \bigr]^n} = \prod_{i=0}^{N/4-1} \frac{Z(A_i,n,\beta)}{Z(A_{i+1},n,\beta)}
\end{align}
where we define the set of $A_i$ such that
\begin{align}
A_i = 4i,\quad i \in [0,N/4] .
\end{align}
Second, we can write the ratio of partition functions as
\begin{align}
\frac{Z(A_i,n,\beta)}{Z(A_{j},n,\beta)} = \frac{T_{j\rightarrow i}}{T_{i\rightarrow j}}
\end{align}
where $T_{i\rightarrow j}$  is the probability one could transition to a valid state with $A_j$ given that one is currently in a valid state with $A_i$.
Since the region $A$ is realized as a hard constraint on the spin configurations in the two copies if $A_j < A_i$ this probability is one.
When $A_j > A_i$ a naive method would simply count the fraction of cases where the spin configurations match on the two copies where one wants to increase $A$, and this fraction would correspond to the transition probability.

Building on that approach we use the following method:
\begin{enumerate}
\item Do a full sweep of the system to generate an importance sampled state.
\item For the four spins spin that $A_j$ has that are not in $A_i$, calculate 
\begin{align}
W_a = \sum_i e^{-\beta E_i}
\end{align}
where $i$ runs over all $2^8$ configurations of the four spins in two replicas.
\item Calculate the quantity
\begin{align}
W_b = \sum_j e^{-\beta E_j}
\end{align}
where $j$ runs over all $2^4$ configurations where the four spins in the two replicas match.
\item Using these two quantities, we can now express the transition probability as
\begin{align}
T_{i \rightarrow j} = \Bigl< \frac{W_b}{W_a} \Bigr>
\end{align}
\end{enumerate}

This method is much faster than simply counting matching configurations as it allows us to integrate over all possible configurations of the spins we are adding, treating the remaining spins in the system as a bath that is updated by the regular Monte Carlo updates with importance sampling.
The scaling of this measurement is exponential with the number of spins added to $A$ per step, and is why we have restricted it to four spins per step in this study.
We also gain some speed by calculating the weights in each replica seperately, and then recombining the results in a smart way, meaning that we only have to explicitly loop over $2 \cdot 2^4 = 32$ configurations.

We calculate this quantity for every disorder and then take the disorder average of the R\'enyi entropy of each disorder.
When calculating the mutual information
\begin{align}
I_{n}(A) = S_{n}(A) + S^*_{n}(N-A) - S_{n}(N)
\end{align}
we do this calculating for each specific realization of disorder, and then take the disorder average of this final quantity.
The star in $S^*$ denotes the fact that even though $A$ denotes the size of the region that is connected, due to disorder one must be careful which specific spins are in the region.
$S^*$ is defined in such a way that the connected spins in $S_{n}(A)$ and those in $S^*_{n}(N-A)$ contain every spin in the system exactly once.

%For each disorder and each $\omega_i$ we create a simulation, and measure
%\begin{align}
%\frac{Z(\omega_i,\alpha,\beta)}{Z(\omega_{i+1},\alpha,\beta)} = \\
%\frac{Z(\omega_i,\alpha,\beta)}{Z(\omega_{i-1},\alpha,\beta)}
%\end{align}

%Due to the infinite dimensional nature of the Sherrington-Kirkpatrick model, the calculation the R\'enyi mutual information is unable to exploit efficient methods that are available for finite dimensional systems [ref: JMS/Inglis].

\end{document}

### 2015-06-09 sk_model_v15.tex
revised

@@
 paradigm model of mean-field spin glasses. 
-Using both classical Monte Carlo simulation and analytical tools we investigate the 
+Using both classical Monte Carlo simulations and analytical tools we investigate the 
 S-K model on a booklet of $n$-sheets.
@@
 and ${\mathcal I}_n$ exhibit a volume law in the whole phase diagram. We characterize 
-analytically and numerically the behavior of the corresponding densities $S_n/N$ and 
-${\mathcal I}_n/N$, in the thermodynamic limit. Remarkably, at the critical point 
-${\mathcal I}_n/N$ does not exhibit any crossing for different system sizes, in 
-contrast with local spin models.
+analytically the behavior of the corresponding densities $S_n/N$ and ${\mathcal I}_n/N$, 
+in the thermodynamic limit. Remarkably, at the critical point ${\mathcal I}_n/N$ does not 
+exhibit any crossing for different system sizes, in contrast with local spin models.
 
@@
 
-All these issues have been thoroughly addressed in the Sherrington-Kirkpatrick 
+All these issues can be thoroughly addressed in the Sherrington-Kirkpatrick 
 (S-K) model~\cite{sherrington-1978,sherrington-1978-prl}, which is exactly 
@@
 a low-temperature glassy phase, which is separated from a high-temperature paramagnetic 
-one by a second order phase transition. In contrast with its mean-field nature, the 
-solution of the S-K model has been a mathematical challenge. 
-Although it was proposed as an ansatz by Parisi~\cite{parisi-1980} more than thirthy 
-years ago, its rigourous proof was obtained only recently~\cite{talagrand-2006}. Moreover, 
-the solution exhibits several intricate features, such as lack of self-averaging~\cite{pastur-1991}, 
-ultrametricity~\cite{mezard-1984,rammal-1986}, and replica symmetry breaking~\cite{parisi-book,
-castellani-2005}. The last refers to the breaking of the permutation symmetry among the 
-fictitious replicas of the system, which in the standard replica trick~\cite{cardy-book} are 
-used to perform disorder averages. Finally, although the applicability of the S-K 
+one by a second order phase transition. Despite its mean-field nature, the solution 
+of the S-K model has been a mathematical challenge. Although it was proposed as an 
+ansatz by Parisi~\cite{parisi-1980} more than thirthy years ago, its rigourous proof 
+was obtained only recently~\cite{talagrand-2006}. Moreover, the solution exhibits several 
+intricate features, such as lack of self-averaging~\cite{pastur-1991}, ultrametricity~\cite{
+mezard-1984,rammal-1986}, and replica symmetry breaking~\cite{parisi-book,castellani-2005}. 
+The last refers to the breaking of the permutation symmetry among the fictitious replicas 
+of the system, which are introduced to perform disorder averages (\emph{replica 
+trick}~\cite{cardy-book}). Finally, although the applicability of the S-K 
 model to describe realistic spin glasses is still highly debated~\cite{yucesoy-2012,
-billoire-2012,yucesoy-2013}, we should mention that there are recent proposals on how to 
-realize this model in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser 
-systems~\cite{ghofraniha-2015}.
+billoire-2012,yucesoy-2013}, there are recent proposals on how to realize this model 
+in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser systems~\cite{
+ghofraniha-2015}.
 
@@
 The spins in part $A$ of different sheets are constrained to be equal. It is 
-convenient to introduce the aspect ratio $0\le\omega\le1$ as  
+convenient to introduce the booklet aspect ratio $0\le\omega\le1$ as  
 %
@@
 Oppositely, we provide evidence that in the low-temperature phase the replica symmetry is  
-broken. Precisely, we numerically observe that the replica-symmetric (RS) result for the 
+broken. For instance, we numerically observe that the replica-symmetric (RS) result for the 
 internal energy is systematically lower than the Monte Carlo data, as in the standard 
@@
 replicas has to be broken. As a consequence, our scheme should be regarded as an 
-approximation, and not as an exact solution. Finally, we restrict ourselves to the 
-one-level replica symmetry breaking ($1$-RSB), although, in principle, it is possible 
-to treat within our scheme the full breaking of the replica symmetry ($\infty$-RSB). 
-Surprisingly, we observe that the $1$-RSB approximation for the internal energy is in 
+approximation, and not as an exact solution. We restrict ourselves to the 
+one-level replica symmetry breaking ($1$-RSB). 
+Surprisingly, we observe that the $1$-RSB result for the internal energy is in 
 excellent agreement with the Monte Carlo data for  $\beta\lesssim 3$, whereas the RS 
@@
 observed~\cite{wolf-2008}. The corresponding density $[{\mathcal I}_2]/N$ vanishes in 
-both the infinite-temperature and the zero-temperature limits. Surprisingly, ${\mathcal I}_2/N$ 
+both the infinite-temperature and the zero-temperature limits. Surprisingly, $[{\mathcal I}_2]/N$ 
 does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition.
@@
 position of this maximum is not simply related to the paramagnetic-glassy transition. Finally, 
-at high temperature $[{\mathcal I}_2]/N$ is fully described analytically by the RS result 
+at high temperature $[{\mathcal I}_2]/N$ is described analytically by the RS result 
 $[{\mathcal I}_2]^{RS}/N$, whereas at low temperatures one has to include the effects of the 
@@
 the booklet partition functions. In section~\ref{the-model} we present the structure of 
-the  the solution of the S-K model on the booklet. Specifically, we discuss the replica 
+the solution of the S-K model on the booklet. Specifically, we discuss the replica 
 trick, which is used to perform disorder averages, and the saddle point approximation in 
-the thermodynamic limit . Section~\ref{solution} is concerned with the RS approximation. 
-In subsection~\ref{para-section} we focus on the high-temperature 
-region, where this approximation becomes exact. In subsection~\ref{rs-section} we discuss 
-the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} is devoted to   
-the $1$-RSB approximation. In section~\ref{mc-results} we check the validity of both 
-the RS and the $1$-RSB results comparing with Monte Carlo simulations for the internal energy. 
-Section~\ref{Renyi-section} and~\ref{I2-section} discuss the classical R\'enyi entropy and the 
-mutual information, respectively. Finally, we conclude in section~\ref{conclusions}.
+the thermodynamic limit. Section~\ref{solution} is concerned with the RS approximation. 
+Precisely, in subsection~\ref{para-section} we focus on the high-temperature 
+region, where this pproximation becomes exact. In subsection~\ref{rs-section} we discuss 
+the structure of the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} 
+is devoted to   the $1$-RSB approximation. In section~\ref{mc-results} we check the validity 
+of both the RS and the $1$-RSB results comparing with Monte Carlo simulations for the 
+internal energy. Section~\ref{Renyi-section} and~\ref{I2-section} discuss the classical R\'enyi 
+entropy and the mutual information, respectively. Finally, we conclude in section~\ref{conclusions}.
 
 %########################################################################
-\section{The booklet construction \& and the classical mutual information}
+\section{The booklet construction \& and the classical R\'enyi entropy}
 \label{booklet}
 
-%Clearly, $p_{i_A}\equiv\sum_{j_b\in{\mathcal C}_B}p_{i_A,j_B}$, with $p_{i_A,j_B}$ 
-%being the probability that the system is in the configuration $i_A\in{\mathcal C}_A$
-%in part $A$, and $j_B\in{\mathcal C}_B$ in part $B$. For a spin model at inverse 
-%temperature $\beta$, one has $p_{i_A,j_B}\equiv e^{-\beta E(i_A,j_B)}/Z(\beta)$, 
-%where $E(i_A,j_B)$ is the energy of the system, and $Z(\beta)$ its partition function.
-
 Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
-the R\'enyi classical entropy $S_n(A)$ is defined as~\cite{jaconis-2013,stephan-2014} 
+the classical R\'enyi entropy $S_n(A)$ is defined as~\cite{jaconis-2013,stephan-2014} 
 %
@@
 are at inverse temperature $\beta$, the ones in $A$ are at the effective temperature $n\beta$. 
-A similar geometric construction~\cite{guerra-2002} plays an important role in the mathematical 
-proof of the Parisi ansatz.
-
-Notice that one has $S_n(A)\equiv1/(n-1)\log(F(A,n,\beta))-n\log(F(\beta))$, where $F(A,n,\beta)
+Notice that a similar geometric construction~\cite{guerra-2002} plays an important role in the 
+mathematical proof of the Parisi ansatz.
+
+Clearly, one has $S_n(A)\equiv1/(n-1)\log(F(A,n,\beta))-n\log(F(\beta))$, where $F(A,n,\beta)
 \equiv\log(Z(A,n\beta))$ and $F(\beta)\equiv\log(Z(\beta))$ are related (apart from a factor 
@@
 The mutual information ${\mathcal I}_n(A,B,\beta)$ is defined~\cite{jaconis-2013,stephan-2014} 
+as 
 %
@@
 
-Here we introduce the Sherrington-Kirkpatrick (S-K) model on the booklet 
-(see Fig.~\ref{cartoon}). In subsection~\ref{the-model-def}  we define the 
+Here we introduce the Sherrington-Kirkpatrick (S-K) model on the booklet. 
+In subsection~\ref{the-model-def}  we define the 
 model and its partition function. In subsection~\ref{replica-sec} 
@@
 disorder-averaged free energy $[F(\omega,n,\beta)]$. 
-In~\ref{saddle-point} we consider the thermodynamic limit, 
+In section~\ref{saddle-point} we consider the thermodynamic limit, 
 using the saddle point approximation. We also introduce the overlap tensor,  
@@
 model. The analytical formula for the replicated partition function (Eq.~\eqref{Z-ac}), 
-and the saddle point equations (Eqs.~\eqref{saddle-final}) for the overlap tensor 
-are the main results of this section.
+and the saddle point equations (Eqs.~\eqref{saddle-final}\eqref{saddle-final-a}) 
+for the overlap tensor are the main results of this section.
 
@@
 $N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
-In each ``page'' of the booklet all the sites are divided into two groups $A\equiv
-\{1,\dots, N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv 
-N-N_A$ sites, respectively. The spins living in part $A$ and different sheets 
-are identified, i.e., $\forall i\in A$ one has  
+In each ``sheet'' of the booklet all the sites are divided into two groups $A\equiv\{1,
+\dots, N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ 
+sites, respectively. The spins living in part $A$ and different sheets are identified, 
+i.e., $\forall i\in A$ one has  
 %
@@
 quenched random variables. $J_{ij}$ are the same in all the sheets of the booklet. Specifically, 
-here we choose $J_{ij}$ distributed according to a gaussian distribution   
+here $J_{ij}$ are drawn from the gaussian distribution   
 %
@@
 The partition function $Z(\omega,n,\beta,\{J\})$ of the S-K model on the booklet 
-at inverse temperature $\beta\equiv 1/T$, and fixed disorder realization $\{J_{ij}\}$, 
-reads 
+at inverse temperature $\beta\equiv 1/T$, and for fixed disorder realization 
+$\{J_{ij}\}$, reads 
 %
@@
 spin configurations. The prime in $\textrm{Tr}'$ stresses that only spin configurations 
-satisfying the booklet constraint in Eq.~\eqref{book-constraint} are considered. 
-In the two limits $\omega=0$ and $\omega=1$ one recovers the standard 
-S-K model. In particular, for $\omega=0$, i.e., $n$ disconnected sheets, one has 
-$Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with $Z(\beta,\{J\})$ the partition function 
-of the S-K model on the plane. On the other hand, for $\omega=1$ it is $Z(1,n,\beta,
-\{J\})=Z(n\beta,\{J\})$, i.e., the partition function of the S-K model at inverse 
-temperature $n\beta$. The quenched averaged free energy $[F(\omega,n,\beta)]$, is defined 
-as 
+satisfying the constraint in Eq.~\eqref{book-constraint} are considered. In the two limits 
+$\omega=0$ and $\omega=1$ one recovers the standard S-K model. In particular, for $\omega=0$, 
+i.e., $n$ disconnected sheets, one has $Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with 
+$Z(\beta,\{J\})$ the partition function of the S-K model on the plane. On the other hand, 
+for $\omega=1$ it is $Z(1,n,\beta,\{J\})=Z(n\beta,\{J\})$, i.e., the partition function 
+of the S-K model at inverse temperature $n\beta$. The quenched averaged free energy 
+$[F(\omega,n,\beta)]$, is defined as 
 %
@@
 +\infty}dJ_{ij}P(J_{ij})$.
-%Notice that $[F(\omega,n,\beta)]$ is the 
-%main ingredient to construct the classical R\'enyi entropies and the 
-%mutual information (cf. Eq.~\eqref{MI} and Eq.~\eqref{renyi}).
 
@@
 between the two phases, is a nontrivial function of the booklet ratio 
-$\omega$.
+$\omega$ (see section~\ref{tc-section}).
 
@@
 the thermodynamic limit. Here ${\mathcal K}(\{q,m\})$ is spin-independent 
-and reads 
+and it reads 
 %
@@
 to be treated as independent variables in performing $\tr_B$.
-Notice that in Eq.~\eqref{z-final} the trace acts over a system of $n\alpha$ 
-spins, instead of $Nn\alpha$, as in Eq.~\eqref{hs-Z}.
 
@@
 replica-symmetric one (RS), which amounts to taking $q^{11}_{\gamma\gamma'}=q$. 
-This relies on the observation that fictitious replicas appear symmetrically 
+This relies on the observation that the fictitious replicas appear symmetrically 
 in Eq.~\eqref{rep-Z}. Although the RS ansatz is correct at high temperatures, it 
 fails in the glassy phase at low temperatures, where the permutational invariance 
-within the replicas has to be broken~\cite{almeida-1978}. Parisi's ansatz~\cite{parisi-1979}
-provides a systematic scheme to break the replica symmetry in successive steps, and it  
-allows to capture the the glassy behavior of the S-K model at low temperature. 
-We anticipate (see section~\ref{rsb-1-section}) that a similar scheme has to be used to 
-describe the glassy phase of the S-K model on the booklet.
+within the replicas has to be broken~\cite{almeida-1978}. the celebrated Parisi 
+ansatz~\cite{parisi-1979} provides a systematic scheme to break the replica 
+symmetry in successive steps, and it allows to capture the the glassy behavior of 
+the S-K model at low temperature. We anticipate (see section~\ref{rsb-1-section} for 
+the details) that a similar scheme has to be used to describe the glassy phase of 
+the S-K model on the booklet.
 
@@
 behavior of the model is fully determined by the diagonal part of the overlap 
-tensor $q_{\gamma\gamma'}^{rr'}$. The full structure of $q_{\gamma\gamma'}^{rr'}$ 
-in the RS ansatz  is discussed in subsection~\ref{rs-section}. This allows us to 
-determine the critical temperature of the paramagnetic-glassy transition.
+tensor $q_{\gamma\gamma'}^{rr'}$ (see section~\ref{replica-sec} for its 
+definition). The generic structure of $q_{\gamma\gamma'}^{rr'}$ 
+within the RS ansatz  is discussed in subsection~\ref{rs-section}. This allows us 
+to determine the critical temperature of the paramagnetic-glassy transition.
 
@@
 Here we provide the exact analytical expression for the disorder-averaged free 
-energy $[F_{para}(\omega,n,\beta)]$  in the paramagnetic non-glassy phase of 
-the S-K model on the booklet. We start discussing the infinite temperature 
-limit (i.e., $\beta\to 0$), restricting ourselves to zero magnetic field.
-
+energy $[F_{para}(\omega,n,\beta)]$  in the paramagnetic non-glassy phase. 
+We start discussing the infinite temperature limit (i.e., $\beta\to 0$), 
+restricting ourselves to zero magnetic field. 
 Using Eq.~\eqref{mf-action}, a standard high-temperature expansion yields 
@@
 %
-After substituting in Eq.~\eqref{saddle-final}, it is straightforward to 
-obtain the infinite-temperature overlap tensor $q_{\gamma\gamma'}^{rr'}$ 
-as 
+Using Eq.~\eqref{saddle-final}, it is straightforward to obtain the 
+infinite-temperature overlap tensor $q_{\gamma\gamma'}^{rr'}$ as 
 %
@@
 Remarkably, $q_{\gamma\gamma'}^{rr'}$ becomes diagonal in both the 
-indices $\gamma,\gamma'$ and $r,r'$, i.e.,  the physical and 
-fictitious replica spaces. Using Eq~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, 
+indices $\gamma,\gamma'$ and $r,r'$, i.e., the physical and fictitious 
+replica spaces. Using Eq~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, 
 after performing the analytic continuation $\alpha\to 0$, one obtains  
@@
 %
-After introducing the auxiliary Hubbard-Stratonovich variables $z_\lambda$ 
-(with $\lambda=1,\dots,\alpha$), one can write 
+After introducing the Hubbard-Stratonovich variables $z_\lambda$ (with 
+$\lambda=1,\dots,\alpha$), one can write 
 %
@@
 one has $q_0\ne0$ for $\beta>1$. On the other hand, for $\omega=1$ 
-one has $q_0=1$ $\forall\beta$. For intermediate $0<\omega<1$ $q_0$ 
+one has $q_0=1$ $\forall\beta$. For intermediate $0<\omega<1$, $q_0$ 
 is plotted as a function of $\omega$ in Fig.~\ref{RSB0_saddle}. For $\beta=0$ it 
@@
 %
-where we define $H_{RS}(z,z')\equiv\cosh(\beta z\sqrt{q_0'}+\beta z'\sqrt{q_0-q_0'})$. 
+where $H_{RS}(z,z')\equiv\cosh(\beta z\sqrt{q_0'}+\beta z'\sqrt{q_0-q_0'})$. 
 Notice that because of the square roots in the definition of $H_{RS}(z,z')$, 
@@
 
-In Eq.~\eqref{eq1}\eqref{eq2} $q_0,q_0'$ satisfy the saddle point conditions 
+In Eqs.~\eqref{eq1}\eqref{eq2} $q_0,q_0'$ satisfy the saddle point conditions 
 $\partial[F_{RS}(\omega,n,\beta)]/\partial q_0=\partial[F_{RS}(\omega,n,\beta)]/
-\partial q'_0=0$ (cf. Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} for the precise 
-form of the saddle point equations for $n=2$). 
-The resulting $q_0$ and $q_0'$ are plotted in Figure~\ref{RSB0-saddle} (full 
-and dotted lines, respectively) as function of $\omega$ and for several values of 
-$\beta$. Clearly, for any $\beta$ one has $q_0=1$ in the limit $\omega\to 1$. Also, 
-in the zero-temperature limit $\beta\to\infty$ one has that $q_0\to 1$ 
-and $q_0'\to 1$, for any $\omega$. Moreover, a simple calculation yields  
+\partial q'_0=0$ (cf. Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} for their 
+form for $n=2$). The resulting $q_0$ and $q_0'$ are plotted in Fig.~\ref{RSB0-saddle} 
+(full and dotted lines, respectively) as function of $\omega$ and for several 
+values of $\beta$. Clearly, for any $\beta$ one has $q_0=1$ in the limit 
+$\omega\to 1$. Also, in the zero-temperature limit $\beta\to\infty$ one has 
+that $q_0\to 1$ and $q_0'\to 1$, for any $\omega$. Moreover, a simple calculation 
+yields  
 %
@@
 %
-with the dots denoting exponentially suppressed terms. Interestingly, from 
-Eq.~\eqref{low-t} one has that $q_0\to 1$ exponentially in the limit $\beta\to\infty$, 
+with the dots denoting exponentially suppressed terms in the limit $\beta\to\infty$. 
+Interestingly, from Eq.~\eqref{low-t} one has that $q_0\to 1$ exponentially in the limit $\beta\to\infty$, 
 as in the paramagnetic phase (cf. section~\ref{para-section}), whereas 
@@
 \subsection{The paramagnetic-glassy transition}
-
-Finally, using the replica-symmetric ansatz Eq.~\eqref{rs-ansatz} one can determine 
+\label{tc-section}
+
+Using the replica-symmetric ansatz Eq.~\eqref{rs-ansatz} one can determine 
 the critical temperature $\beta_c$ of the paramagnetic-glassy transition. 
@@
 (cf. Eq~\eqref{rs-F}) for small $q_0'$, and keeping only terms up to ${\mathcal O}((q_0')^2)$, 
-one obtains a standard Landau theory. Thus, $\beta_c$ is obtained imposing that the 
+one obtains a standard Landau theory. Thus, $\beta_c$ is obtained by imposing that the 
 coefficient of the quadratic term $q_0'^2$ changes sign. This leads to the equation 
@@
 %##########################################################################
-\section{The one-step replica-symmetry-broking (1-RSB) approximation}
+\section{The one-step replica-symmetry-breaking (1-RSB) approximation}
 \label{rsb-1-section}
 
-In this section we go beyond the replicas-ymmetric approximation, including some 
+In this section we go beyond the replica-ymmetric approximation, including some 
 of the effects of the replica symmetry breaking. More specifically, 
-here we discuss the one-step replica symmetry breaking (1-RSB) approximation for the 
-S-K model on the booklet. The overlap tensor $q_{\gamma\gamma'}^{rr'}$ now reads  
+here we discuss the one-step replica symmetry breaking (1-RSB) approximation. 
+The overlap tensor $q_{\gamma\gamma'}^{rr'}$ now reads  
 %
@@
 %
-where now $q_0',q_1'\in{\mathbb R}$, $m_1\in{\mathbb N}$, and $\lfloor\cdot\rfloor$ 
-denotes the floor function. The off-diagonal elements of $q'$ do not depend on 
-$r,r'$, meaning that, although the permutational symmetry between the 
-fictitious replicas is broken, the symmetry among the physical ones is preserved. 
-The choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block-diagonal structure for 
-$q'$: the matrix elements of the $m_1\times m_1$ diagonal blocks of $q'$ are set to 
-$q_1'$, whereas all the off-diagonal elements are set to $q_0'$. As for the replica-symmetric 
-ansatz in Eq.~\eqref{rs-ansatz}, we do not have any rigorous argument to justify 
-Eq.~\eqref{q-rsb1a} (see section~\eqref{mc-results}, however, for numerical results).
+where $q_0',q_1'\in{\mathbb R}$, $m_1\in{\mathbb N}$, and $\lfloor\cdot\rfloor$ 
+denotes the floor function. Notice that the off-diagonal elements of $q'$ (i.e., for 
+$\gamma\ne\gamma'$) do not depend on $r,r'$, meaning that, although the permutational 
+symmetry between the fictitious replicas is broken, the symmetry among the physical ones 
+is preserved. The choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block-diagonal 
+structure for $q'$: the matrix elements of the $m_1\times m_1$ diagonal blocks of $q'$ 
+are set to $q_1'$, whereas all the off-diagonal elements are set to $q_0'$. As for the 
+replica-symmetric ansatz in Eq.~\eqref{rs-ansatz}, we do not have any rigorous argument 
+to justify Eq.~\eqref{q-rsb1a} (see section~\eqref{mc-results}, however, for numerical 
+results).
 
 The effective interaction ${\mathcal L}_{1\textrm{-}RSB}$ (cf. Eq.~\eqref{mf-action}) 
-in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in Eq.~\eqref{mf-action}. 
-This yields  
+in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in 
+Eq.~\eqref{mf-action}. This yields  
 %
@@
 %
-The trace over the spin variables can now be performed explicitly in Eq.~\eqref{step}. 
+The trace over the spin variables in Eq.~\eqref{step} can be now performed explicitly. 
 Finally, one obtains the 1-RSB approximation for the free energy 
@@
 H_{1\textrm{-}RSB}(z,z',z'')\equiv\cosh(z\beta\sqrt{q'_0}\\+
-z''\beta\sqrt{q_0-q'_1} +z'\beta\sqrt{q_1'-q_0'})
+z''\beta\sqrt{q_0-q'_1} +z'\beta\sqrt{q_1'-q_0'}).
 \label{H1}
@@
 The parameters $q_0,q_0',q_1',m_1$ are obtained by solving the saddle 
-point equations Eqs.~\eqref{RSB-1-saddle-a}\eqref{RSB-1-saddle-b}\eqref{RSB-1-saddle-c}
-\eqref{RSB-1-saddle-d}. One should remark that, although formally $m_1\in\mathbb{N}$, 
-one obtains $m_1\in\mathbb{R}$ from the saddle point equations. 
-Finally, the RS result $F_{RS}(\omega,n,\beta)$ (cf. Eq.~\eqref{rs-F}) is recovered 
-from Eq.~\eqref{RSB-1-logZ} in the limit $q_1'=q_0'$, while the result in the 
-paramagnetic phase (cf. Eq.~\eqref{ht-logZ}) corresponds to $q_1'=q_0'=0$.
+point equations~\eqref{RSB-1-saddle-a}\eqref{RSB-1-saddle-b}\eqref{RSB-1-saddle-c}
+\eqref{RSB-1-saddle-d}. One should remark that, although formally $m_1$ is an 
+integer, one obtains $m_1\in\mathbb{R}$ from the saddle point equations. 
+Clearly, the replica-symmetric result $[F_{RS}(\omega,n,\beta)]$ (cf. 
+Eq.~\eqref{rs-F}) is recovered from Eq.~\eqref{RSB-1-logZ} in the limit 
+$q_1'=q_0'$, while the free energy in the paramagnetic phase $[F_{para}(\omega,n,
+\beta)]$ (cf. Eq.~\eqref{ht-logZ}) corresponds to $q_1'=q_0'=0$.
 
@@
 Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
-$\beta$, for $\omega=1/2$ (see Fig.~\ref{cartoon}). The cicles, squares, and triangles 
+$\beta$, for $\omega=1/2$ (see Fig.~\ref{cartoon}). The circles, squares, and triangles 
 are the MC results for different sizes, i.e., number of spins per sheet, $N=32,64,128$. 
@@
 (unlike Fig.~\ref{cartoon} for local models). The fully connected nature of the S-K model 
-suggests the volume-law behavir $[S_2]\propto N$ for all temperature.
+suggests the volume-law behavior $[S_2]\propto N$ for all temperature.
 Therefore it is natural to consider the entropy per spin $[S_2]/N$.
@@
 $[S_2]\equiv [F(0,2,\beta)-F(\omega,2,\beta)]$ (cf. Eq.~\eqref{renyi}). 
-Clearly, in the thermodynamic limit $[S_2]/N$ is finite for any $\beta$, 
-confirming the expected volume law behavior. Moreover, $[S_2]/N$ 
+Clearly, from Fig.~\ref{I2-MC} one has that in the thermodynamic limit $[S_2]/N$ is 
+finite for any $\beta$, confirming the expected volume law behavior. Moreover, $[S_2]/N$ 
 exhibits a maximum in the infinite-temperature limit $\beta\to0$. The height of this 
@@
 denote the one-step replica symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$
-(see section~\ref{rsb-1-section}). Here $[S_2^{1\textrm{-}RSB}]/N$ is formally obtained 
-using Eq.~\eqref{renyi} and the free energy $[F_{1\textrm{-}RSB}]$ (cf. 
-Eq.~\eqref{RSB-1-logZ}). Remarkably, $[S_2^{1\textrm{-}RSB}]/N$ is in excellent 
-agreement with the Monte Carlo extrapolations for $\beta\lesssim 2$.
+(see section~\ref{rsb-1-section}). This is formally obtained using Eq.~\eqref{renyi} 
+and the free energy $[F_{1\textrm{-}RSB}]$ (cf. Eq.~\eqref{RSB-1-logZ}). Remarkably, 
+$[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the Monte Carlo extrapolations 
+for $\beta\lesssim 2$.
 
@@
 $[{\mathcal I}_n]$ by construction exhibits an area law at all temperatures.
-However, due to the fully connected nature of the S-K model common expectations 
-from local models do not apply.  Here we consider the mutual information per spin 
+Here we consider the mutual information per spin 
 $[{\mathcal I}_2]/N$.
 
-Figure~\ref{I2-MC} ${\mathcal I}_2/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,1/8$ 
+Figure~\ref{I2-MC} plots $[{\mathcal I}_2]/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,1/8$ 
 (panels from left to right in the Figure). Notice that by definition (cf. Eq.~\eqref{MI}) 
-${\mathcal I}_n(\omega)={\mathcal I}_n(1-\omega)$. Circles, squares, and rhombi in 
-Fig.~\ref{I2-MC} are Monte Carlo data for $N=32,64,128$. 
-In the high-temperature region ${\mathcal I}_2$ exhibits a clear vanishing 
-behavior, for any $0<\omega<1$. Moreover, finite size effects are ``small''. 
-Using Eq.~\eqref{logZ-ht} it is straightforward to derive the high-temperature 
-behavior of ${\mathcal I}_n(\omega)$ as  
-%
-\begin{equation}
-{\mathcal I}_n(\omega)=\frac{N\beta^2}{2}\omega(1-\omega)n+{\mathcal O}
+$[{\mathcal I}_n(\omega)]=[{\mathcal I}_n(1-\omega)]$. Circles, squares, and rhombi 
+are Monte Carlo data for $N=32,64,128$. In the high-temperature region $[{\mathcal I}_2]$ 
+exhibits a vanishing behavior. Moreover, finite size effects are 
+``small''. Using Eq.~\eqref{logZ-ht} it is straightforward to derive the high-temperature 
+behavior of $[{\mathcal I}_n]$ as  
+%
+\begin{equation}
+[{\mathcal I}_n]=\frac{N\beta^2}{2}\omega(1-\omega)n+{\mathcal O}
 (\beta^4).
@@
 %
-At lower temperatures ${\mathcal I}_2/N$ increases monotonically up to $\beta\approx 1$, 
-where it exhibits a maximum. Interestingly, the largest value of ${\mathcal I}_2/N$ 
-(${\mathcal I}_2/N\approx 0.09$ for $\omega=1/2$) is quite small, as it is observed in 
-local spin models~\cite{jaconis-2013}. The height of the maximum decreases as a function of 
-$\omega$. Its position is not simply related to the paramagnetic-glassy transition at $\beta=1$ 
-of the standard S-K model. This is not surprising because ${\mathcal I}_n(\omega)$ is constructed 
-by combining the partition functions of the S-K model on the booklets with ratios $\omega$, 
-$1-\omega$, $\omega=0$, and $\omega=1$ (cf. Eq.~\eqref{MI}), and the critical temperature of 
-the paramagnetic-glassy transition is a non trivial function of $\omega$ (see Fig.~\ref{beta_c}). 
-As a consequence, the geometric mutual information ${\mathcal G}_n$ (cf.~\eqref{GMI}) 
-is not well defined for the S-K model. 
-Furthermore, the curves for ${\mathcal I}_2/N$ calculated at different sizes do not exhibit any 
-crossing at $\beta=1$, in sharp contrast with local models~\cite{jaconis-2013}, for which it has 
-been shown that ${\mathcal I}_n(\omega)/\ell$ exhibits a crossing at a second order phase transition. 
-For $\beta\gtrsim 1$, ${\mathcal I}_2$ decreases monotonically, for any $N$. 
+Moreover, $[{\mathcal I}_2]/N$ increases upon lowering the temperature, up to $\beta\approx 1$, 
+where it exhibits a maximum. The height of this  
+maximum decreases as a function of $\omega$. Its position is not simply related to the 
+paramagnetic-glassy transition in the standard S-K model. This is not surprising 
+as $[{\mathcal I}_n]$ is constructed by combining the partition functions of the S-K model 
+on the booklets with aspect ratios $\omega$, $1-\omega$, $\omega=0$, and $\omega=1$ (cf. Eq.~\eqref{MI}), 
+and the critical temperature of the paramagnetic-glassy transition is a non trivial 
+function of $\omega$ (see Fig.~\ref{beta_c}). 
+Furthermore, the curves for $[{\mathcal I}_2]/N$ for different system sizes do not exhibit any 
+crossing. This is in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ 
+exhibits a crossing at a second order phase transition. 
 The dash-dotted line in Fig.~\ref{I2-MC} denotes the analytical result obtained using the replica 
 symmetric (RS) approximation (see section~\ref{rs-section}). Formally this is obtained using 
-Eq~\eqref{MI} and Eq.~\eqref{rs-F}. This is in perfect agreement with the 
-MC data in the whole paramagnetic phase.
-
-Interestingly, at low temperatures ${\mathcal I}_2/N$ exhibits strong finite-size corrections, and 
-significant deviations from the RS result. 
-In order to extract the thermodynamic behavior of ${\mathcal I}_2/N$ we fit the MC data to 
-%
-\begin{equation}
-\frac{{\mathcal I}_2}{N}=a+\frac{b}{N^\gamma}
-\end{equation}
-%
-where we fix $\gamma=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}. 
-The circles, squares, and triangles denote ${\mathcal I}_2/N$ extrapolated from Monte Carlo to the thermodynamic limit 
-$N\to\infty$ for $\omega=1/2,1/4,1/8$. 
-Interestingly, we numerically checked that in the zero-temperature limit the data 
-support the vanishing behavior as ${\mathcal I}_2/N\propto \beta^{-2}$. This reflects 
-the vanishing of the classical R\'enyi entropy $S_2$ at zero temperature (see Fig.~\ref{Renyi-MC}).
-The dash-dotted lines are the RS results (same as 
-in Fig.~\ref{I2-MC}). Remarkably, the RS approximation is in good agreement with 
-the extrapolations, at least within the error bars, up to $\beta\lesssim 1.5$, whereas 
-deviations occur at lower temperatures (not shown in the figure). For $\omega=1/8$, 
-the numerical results exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
+Eq~\eqref{MI} and Eq.~\eqref{rs-F}, and it is in perfect agreement with the MC data in the whole 
+paramagnetic phase.
+
+Interestingly, at low temperatures $[{\mathcal I}_2]/N$ exhibits strong finite-size corrections, 
+and significant deviations from the RS result. In order to extract the thermodynamic behavior of 
+$[{\mathcal I}_2]/N$ we fit the MC data to 
+%
+\begin{equation}
+\frac{[{\mathcal I}_2]}{N}=a+\frac{b}{N^{\phi''}},
+\end{equation}
+%
+where we fix $\phi''=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated} 
+(circles, squares, and triangles). Remarkably, the RS approximation (dash-dotted lines) is 
+in good agreement with the extrapolations up to $\beta\lesssim 1.5$, whereas deviations 
+occur at lower temperatures (not shown in the figure). 
+For $\omega=1/8$, the numerical results exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
 These deviations have to be attributed to the physics of the replica symmetry breaking. 
-The full rhombi in Fig.~\ref{I2-extrapolated} are the analytical results for ${\mathcal I}_2/N$ 
-including some of the effects of the replica symmetry breaking. More precisely, 
-${\mathcal I}_2^{1\textrm{-}RSB}$ is obtained using Eq.~\eqref{MI} and the one-step replica 
+The full rhombi in Fig.~\ref{I2-extrapolated} denote the result $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ 
+obtained in the one-step replica symmetry breaking approximation. More precisely, 
+$[{\mathcal I}_2^{1\textrm{-}RSB}]$ is obtained using Eq.~\eqref{MI} and the one-step replica 
 symmetry breaking (1-RSB) approximation for the free energy of the S-K model on the 
-booklet (cf. Eq.~\eqref{RSB-1-logZ}). The agreement between ${\mathcal I}_2^{1\textrm{-}RSB}$ 
-is perfect, at least up to $\beta\lesssim 2$. Notice that at lower temperatures 
-one should expect deviations from ${\mathcal I}_2^{1\textrm{-}RSB}$, similar to what it 
-is observed in the standard S-K model. In particular, one should implement the fully 
-breaking of the replica symmetry ($\infty$-RSB).
+booklet (cf. Eq.~\eqref{RSB-1-logZ}). The agreement between $[{\mathcal I}_2^{1\textrm{-}RSB}]$ 
+and the Monte Carlo data is perfect, at least up to $\beta\lesssim 2$.
 
@@
 ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the paradigm model 
-for mean-field spin glasses. As usual in disordered systems, we focused on the quenched 
+of mean-field spin glasses. We focused on the quenched 
 averages $[S_n]$ and $[{\mathcal I}_n]$, with the brackets $[\cdot]$ denoting the average 
-over different disorder realizations. Here $S_n$ and ${\mathcal I}_n$ were obtained 
-from suitable combinations of the partition functions of the S-K model on the 
-so-called $n$-sheets booklet (cf.~\ref{cartoon}). This is obtained by ``gluing'' together 
+over different disorder realizations. Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ 
+were obtained from suitable combinations of the partition functions of the S-K model on the 
+$n$-sheets booklet (cf. Fig.~\ref{cartoon}). This is constructed by ``gluing'' together 
 $n$ independent replicas (``sheets'') of the model. On each replica the spins are 
@@
 spins in part $A$ of the different sheets are identified. Due to the mean-field nature of 
-the model, the R\'enyi entropies and other physical quantities depend on the bipartition 
-only through the aspect ratio $\omega\equiv N_A/N$. Although many of our analytic results 
-are for generic $n$, we often restricted ourselves to the $2$-sheets booklet, i.e., the 
-second R\'enyi entropy $S_2$ and ${\mathcal I}_2$.
-
-We investigated the phase diagram of the S-K model on the $2$-sheets booklet as a function 
-of $\omega$ and the inverse temperature $\beta$, in the situation without external 
-magnetic field ($h=0$ in Eq.~\eqref{SK-intro}). For any $\omega$, in the 
-thermodynamic limit the S-K model exhibit glassy phase for low-enough tempereatures, 
-whereas at high temperature the model is paramagnetic. The two phases are divided 
-by a second order phase transition, as in the standard S-K model. 
-Interestingly, we found that the critical temperature depends in a non-trivial 
-way on $\omega$. Moreover, we fully characterized the high-temperature phase 
-using the replica-symmetric (RS) approximation, which is a simple generalization 
-of the replica-symmetric solution of the S-K model model on the plane. Specifically, 
-we provided the exact formula for the disorder-averaged free energy $[F_{para}(\omega,n,
-\beta)]$ of the S-K model on the booklet (cf. Eq.~\eqref{ht-logZ}). The analytic results 
-for $S_2$ and ${\mathcal I}_2$ follow straightforwardly using Eq.~\eqref{renyi} and 
-Eq.~\eqref{MI}. In the low-temperature glassy phase the replica symmetry has to be 
-broken, similar to the standard S-K model. In order to take into account the 
-replica symmetry breaking we device a simple generalization of the the Parisi 
-ansatz~\cite{parisi-1980}, which allows to break the replica symmetry in successive 
-steps. After restricting ourselves to the one-step replica symmetry breaking, we 
-provide the exact formula for the disorder-averaged free energy $F_{1\textrm{-}RSB}
-(\omega,n,\beta)$ (cf. Eq.~\eqref{RSB-1-logZ}), and, correspondingly, $S_2^{1\textrm{RSB}}$, 
-${\mathcal I}_2^{1\textrm{-}RSB}$. As a preliminary check, we compared the analytical 
-results for the internal energy $U_{RS}$ and $U_{1\textrm{-}RSB}$ with Monte Carlo data. 
-In the high-temperature region, where the replica symmetry is not broken, these are 
-in perfect agreement with $U_{RS}$. Oppositely, in the glassy phase, where the replica 
-symmetry breaking occurs, the Monte Carlo data exhibit deviations from the analytical 
-results already at $\beta\approx 1$. However, we numerically observed that the one-step 
-replica-symmetry-broken approximation $U_{1\textrm{-}RSB}$ matches the Monte Carlo 
-data up to $\beta\approx 3$.
-
-Finally, we discussed the behavior of $S_2$ and ${\mathcal I}_2$. Due to the mean-field 
-nature of the S-K model we observed that both quantities obey a volume law $S_2\propto N$, 
-${\mathcal I}_2\propto N$. Thus we considered the densities $S_2/N$ and ${\mathcal I}_2/N$, 
-focusing on the thermodynamic limit $N\to\infty$, at fixed $\omega$. 
-At high temperature the Monte Carlo data for $S_2/N$ are in excellent agreement with the 
-replica-symmetric result $S_2^{RS}$. Interestingly, we observed that $S_2/N$ exhibits a 
-maximum at infinite temperature, and it is a \emph{smooth} monotonically descreasing 
-function of the temperature. This behavior does not depend on the booklet aspect ratio 
-$\omega$.  Moreover, while in the high-temperature region $S_2$ is fully described by 
-the replica symmetric ansatz $S_2^{RS}$, in the glassy phase it exhibits signatures of 
-the replica symmetry breaking. The one-step replica symmetry breaking approximation 
-$S_2^{1\textrm{-}RSB}$ is in full agreement with the Monte Carlo data for $\beta\approx 3$, 
-reflecting the behavior of the internal energy. Finally, we numerically observed that the 
-mutual information per spin ${\mathcal I}_2/N$ does not show any crossing for different 
-system sizes $N$, in contrast with local models, where it exhibits a crossing at 
-the critical point. In the thermodynamic limit ${\mathcal I}_2/N$ is vanishing both 
-at $\beta=0$, and $\beta=\infty$, whereas it has a mximum at intermediate temperatures. 
-The position of this maximum is not  simply related to the paramagnetic glassy transition 
-of the S-K model.
-
-Finally, our work opens several interesting research directions. First, it would be 
-interesting to extend our results taking into account the full breaking of the replica 
-symmetry. This would allow to reach a conclusion on the correctness of the replica symmetry 
-breaking scheme that we used. Moreover, it would be interesting to go beyond the saddle 
-point approximation, including finite-size correztions. An interesting question would be 
-to investigate how the paramagnetic-glassy transition is associated with the subleading 
-corrections to the observed volume law in the classical R\'enyi entropies. Also, it 
-would be interesting to investigate the behavior of entanglement-related quantities in 
-disordered quantum spin systems that exhibit replica symmetry breaking~\cite{read-1995, 
-andreanov-2012}. Finally, it would be enlightening to understand the interplay between 
-the physical and the fictitious replicas at the level of the entropy. Notice that,  
-using the analytical results provided in the paper, it is possible to perform the 
-analytic continuation $n\to 1$ to obtain the von Neumann classical mutual information. 
-It would be interesting to check wheather this differs significantly from the 
-R\'enyi mutual information.
+the model, physical quantities depend on the bipartition only through the aspect ratio 
+$\omega\equiv N_A/N$.
+
+We first investigated the phase diagram of the S-K model on the $2$-sheets booklet as a 
+function of $\omega$ and the inverse temperature $\beta$. We considered the situation 
+without external magnetic field ($h=0$ in Eq.~\eqref{SK-intro}). For any $\omega$, in the 
+thermodynamic limit, the model exhibits a glassy phase for low enough temperatures and 
+a standard paramagnetic one at high temperature. The two phases are divided 
+by a phase transition, as in the S-K model on the plane. Interestingly, the critical 
+temperature exhibits a non-trivial dependence on $\omega$ that we determined analytically. 
+We fully characterized the high-temperature phase of the model using the replica-symmetric 
+(RS) approximation. Specifically, we provided the exact analytical expression for the 
+disorder-averaged free energy $[F_{para}(\omega,n,\beta)]$  (cf. Eq.~\eqref{ht-logZ}) in 
+the thermodynamic limit. On the other hand, in the glassy phase the replica symmetry has 
+to be broken, similar to the standard S-K model. To take into account the effects of the 
+replica symmetry breaking we used a generalization of the the Parisi 
+ansatz~\cite{parisi-1980}, i.e., breaking the replica symmetry in successive 
+steps. We restricted ourselves to the one-step replica symmetry breaking ($1$-RSB),   
+providing the exact expression for the disorder-averaged free energy $F_{1\textrm{-}RSB}
+(\omega,n,\beta)$ (cf. Eq.~\eqref{RSB-1-logZ}).
+
+Finally, we compared our analytical results with Monte Carlo simulations, focusing on the 
+internal energy per spin $U(\omega,n,\beta)/N$. In the high-temperature region, where the 
+replica symmetry is not broken, we observed perfect agreement with the replica-symmetric 
+result $U_{RS}/N$, for any $\omega$. In the glassy phase at low temperature, we found 
+significant deviations from $U_{RS}$ already at $\beta\approx 1$. On the other hand,  
+the one-step replica-symmetry-broken approximation $U_{1\textrm{-}RSB}/N$ matched the 
+Monte Carlo data for $\beta\lesssim 3$.
+
+Finally, we discussed the behavior of $[S_2]$ and $[{\mathcal I}_2]$. Due to the mean-field 
+nature of the S-K model we observed the volume laws $[S_2]\propto N$ and 
+$[{\mathcal I}_2]\propto N$, for any $\beta$. We considered the corresponding densities 
+$[S_2]/N$ and $[{\mathcal I}_2]/N$. Using the replica-symmetric (RS) and the one-step 
+replica symmetry breaking ($1$-RSB) approximations we provided analytical results for 
+both $[S_2]/N$ and $[{\mathcal I}_2]/N$. We observed that at high temperature the 
+RS result fully agrees with the Monte Carlo simulations, whereas deviatios occur in the 
+glassy phase, signalling the replica symmetry breaking. Similar to the internal energy, 
+we found that the $1$-RSB approximation fully matches the Monte Carlo data for $\beta\approx 3$.
+Interestingly, we numerically observed that at the critical point ${\mathcal I}_2/N$ 
+does not show any crossing for different system sizes, in contrast with local 
+models~\cite{jaconis-2013}.
+
+Our work opens several research directions. First, it would be interesting to extend our 
+results taking into account the full breaking of the replica symmetry, i.e., going beyond 
+the one-step replica symmetry breaking approximation. This would allow to reach a conclusion 
+on the correctness of the replica symmetry breaking scheme that we used. Moreover, it 
+would be interesting to discuss the finite size-corrections to the saddle 
+point approximation. An interesting direction would be to investigate wheather the 
+glassy behavior is reflected in the volume-law corrections to the classical R\'enyi 
+entropies. Also, it would be interesting to extend our results to {\it quantum} spin 
+systems exhibiting glassy behavior and replica symmetry breaking~\cite{read-1995,
+andreanov-2012}.
 
@@
 In this section we provide the analytical expression for the saddle point equations 
-\eqref{saddle-final}, which determine the overlap tensor $q_{\gamma\gamma'}^{rr'}$ 
-(see section~\ref{replica-trick}) in the thermodynamic limit, and the behavior of the 
-S-K model on the booklet. We restrict ourselves to the situation with zero magnetic 
-field and to the $2$-sheets booklet (see Fig.~\ref{cartoon}). It is straightforward 
-to generalize the calculation to the case with non zero magnetic field and to the 
-$n$-sheets booklet. Here we provide the saddle point equations obtained in both the 
-replica-symmmetric (RS) approximation (see section~\ref{rs-section}), and the 
-one-step replica symmetry breaking ($1$-RSB) approximation (see 
+\eqref{saddle-final}\eqref{saddle-final-a}, which determine the overlap tensor 
+$q_{\gamma\gamma'}^{rr'}$ (see section~\ref{replica-sec}). We restrict ourselves 
+zero magnetic field and to the $2$-sheets booklet (see Fig.~\ref{cartoon}). It is 
+straightforward to generalize the calculation to the case with non zero magnetic 
+field and to the $n$-sheets booklet. Specifically, here we provide the saddle point 
+equations obtained in both the replica-symmmetric (RS) (see section~\ref{rs-section}), 
+and the one-step replica symmetry breaking ($1$-RSB) approximation (see 
 section~\ref{rsb-1-section}).
@@
 %####################################
-\subsection{The replica symmetric (RS) approximation}
+\subsection{The replica-symmetric (RS) approximation}
 
@@
 parameters $q_0,q_0'\in\mathbb{R}$ (cf. Eq.~\eqref{rs-ansatz}). The saddle point 
-equations are easily derived using the RS approximation for the free energy $[F_{RS}
-(\omega,n,\beta)]$ (cf. Eq.~\eqref{rs-F}) of the S-K model on the booklet as 
-$\nabla_{\mathbf{q}}[F_{RS}(\omega,2,\beta)]=0$, where $\mathbf{q}\equiv(q_0,q_0')$, 
-and $\nabla_{\mathbf{q}}\equiv\partial/\partial\mathbf{q}$. A straightforward 
-calculation gives the system of equations  
+equations are easily derived from the RS approximation for the free energy $[F_{RS}
+(\omega,n,\beta)]$ (cf. Eq.~\eqref{rs-F}) as $\nabla_{\mathbf{q}}[F_{RS}(\omega,2,
+\beta)]=0$, where $\mathbf{q}\equiv(q_0,q_0')$, and $\nabla_{\mathbf{q}}\equiv
+\partial/\partial\mathbf{q}$. A straightforward calculation gives the two equations 
 %
@@
 +2\beta^2(1+\exp(2\beta^2(q_0-q_0'))\cosh(2z))^{-1}
-\Big\}
+\Big\},
 \end{multline}
@@
 %
-Notice that it is trivial to check that $\int dz G_0(z)\Delta_0(z)=0$.
+Notice that $\int dz G_0(z)\Delta_0(z)=0$.
 
@@
 
-In the one-step replica symmetry breaking scenario (see section~\ref{rsb-1-section}) 
-the overlap depends on the four parameters $q_0,q_0',q_1',m_1\in\mathbb{R}$. The 
-saddle point equations are now given as $\nabla_{\mathbf{p}}[F_{1\textrm{-}RSB}]=0$, 
-where now $\mathbf{p}\equiv(q_0,q_0',q_1',m_1)$, and $[F_{1\textrm{-}RSB}]$ is 
+In the one-step replica symmetry breaking approximation (see section~\ref{rsb-1-section}) 
+$q_{\gamma\gamma'}^{rr'}$ depends on the four parameters $q_0,q_0',q_1',m_1\in\mathbb{R}$. 
+The saddle point equations are given as $\nabla_{\mathbf{p}}[F_{1\textrm{-}RSB}]=0$, 
+where $\mathbf{p}\equiv(q_0,q_0',q_1',m_1)$, and $[F_{1\textrm{-}RSB}]$ is 
 the disorder-averaged free energy given in Eq.~\eqref{RSB-1-logZ}.
@@
 %
-Finally, a straightforward calculation yields the saddle point equations for 
-$q_0,q_0',q_1',m_1$ as 
+Finally, the saddle point equations for $q_0,q_0',q_1',m_1$ are obtained as 
 %

### 2015-06-10 sk_model_v15.tex
revised-1

@@
 
-In this section we numerically confirm the results of section~\ref{solution}. 
+In this section we numerically confirm the analytical results of section~\ref{solution}. 
 We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
@@
 Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
-$\beta$, for $\omega=1/2$ (see Fig.~\ref{cartoon}). The circles, squares, and triangles 
+$\beta$, for $\omega=1/2$. The circles, squares, and triangles 
 are the MC results for different sizes, i.e., number of spins per sheet, $N=32,64,128$. 
-The vertical dotted line is the critical temperature $\beta_c\approx 0.603$ of 
+The vertical dotted line is the critical temperature $\beta_c\approx 0.6$ of 
 the paramagnetic-glassy transition (cf. Fig.~\ref{beta_c}). In the high-temperature 
@@
 \eqref{RS-saddle-2}. Notice that $U_{RS}$ depends on $\omega$ only through $q_0,q_0'$. 
-From Fig.~\ref{U-MC} one has that, while $U_{RS}$ is in perfect agreement with the numerics 
-for $\beta\approx\beta_c$, deviations appear in the low-temperature region. Moreover, these 
-deviations increase upon lowering the temperature, and already at $\beta\gtrsim 1$, $U_{RS}$ 
-is incompatible with the data. This is has to be attributed to the replica symmetry breaking 
-happening in the glassy phase.
+From Fig.~\ref{U-MC} one has that, while $U_{RS}$ is in perfect agreement with the 
+numerics for $\beta\approx\beta_c$, deviations appear in the low-temperature region. 
+Notice that already at $\beta\gtrsim 1$, $U_{RS}$ is incompatible with the data. 
+Moreover, these deviations increase upon lowering the temperature. This has to be 
+attributed to the replica symmetry breaking happening in the glassy phase. 
+Finally, since in the limit $\beta\to\infty$ all the physical replicas are in the same state, 
+one should expect that $u_\infty(\omega,\beta)\to n \tilde u_\infty$ (horizonthal line in 
+Fig.~\ref{U-MC}), with $\tilde u_{\infty}=-0.76321...$~\cite{parisi-1979,parisi-1983} the 
+zero-temperature internal energy density of the S-K model on the plane. Surprisingly, 
+this behavior is already observed in the MC data at $\beta\approx 3$, whereas it is not 
+captured correctly by the RS approximation.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Finally, since in the limit $\beta\to\infty$ all the physical replicas are in the same state, 
-one should expect that $u_\infty(\omega,\beta)\to n u_\infty(0,\beta)$ (horizonthal line in 
-Fig.~\ref{U-MC}), with $u_{\infty}(0,\beta)\to-0.76321...$~\cite{parisi-1979,parisi-1983} the 
-zero-temperature density of internal energy for the S-K model on the plane. Surprisingly, 
-this behavior is already observed in the MC data at $\beta\approx 3$, whereas it is not 
-captured correctly by the RS approximation.
 
@@
 
-The behavior of $U/N$ is similar for $\omega\ne1/2$, and it is investigated in Fig.~\ref{U-RS},
-plotting $U/N$ as a function of $\beta$ for $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
-are the MC data extrapolated in the thermodynamic, at fixed $\omega$. Similar to Fig.~\ref{U-RS}, 
+The behavior of $U/N$ for $\omega\ne1/2$ is investigated in Fig.~\ref{U-RS},
+plotting $U/N$ as a function of $\beta$ and $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
+are the MC data extrapolated to the thermodynamic, at fixed $\omega$. Similar to Fig.~\ref{U-RS}, 
 the extrapolations are done assuming $U/N(\omega,n,\beta)=u_{\infty}(\omega,n,\beta)+
@@
 i.e., a linear behavior of $U/N$ as a function of $\beta$. For $\omega=0$ and $\omega=1$ 
-this behavior is exact up to $\beta=\beta_c$, meaning that the higher orders ${\mathcal O}(\beta^2)$ 
-in Eq.~\eqref{ht-U} are zero. This is only an approximation at intermediate $0<\omega<1$. 
-Both Eq.~\eqref{U} and Eq.~\eqref{ht-U} are clearly confirmed in Fig.~\ref{U-RS}.
-
-However, Eq.~\eqref{ht-U} is not correct for $\beta>\beta_c$, where the replica symmetry breaking 
+this behavior is exact up to the critical point at $\beta=\beta_c$, meaning that the higher 
+orders ${\mathcal O}(\beta^2)$ in Eq.~\eqref{ht-U} are zero. This is only an approximation 
+at intermediate $0<\omega<1$. Both the behaviors in Eq.~\eqref{U} and Eq.~\eqref{ht-U} are 
+clearly confirmed in Fig.~\ref{U-RS}.
+
+However, the RS result is not correct for $\beta>\beta_c$, where the replica symmetry breaking 
 has to be taken into account. The effects of the replica symmetry breaking are more carefully 
-discussed in Fig.~\ref{U-RSB-1}, plotting $U/N$ versus $1\le\beta\le 2$. The plus symbols and the 
-lines are the same as in Fig.~\ref{U-RS}. The circles denote the internal energy per spin 
-$U_{1\textrm{-}RSB}/N$ as obtained using the $1$-step replica symmetry breaking (1-RSB) 
-approximation (see section~\ref{rsb-1-section}). Specifically, from Eq.~\eqref{RSB-1-logZ} 
-and Eq.~\eqref{U-def}, for $n=2$ a straightforward calculation gives 
+discussed in Fig.~\ref{U-RSB-1}, focusing on the low temperature phase at $1\le\beta\le 2$. 
+The plus symbols and the lines are the same as in Fig.~\ref{U-RS}. The circles denote the 
+internal energy per spin $U_{1\textrm{-}RSB}/N$ as obtained using the $1$-step replica 
+symmetry breaking (1-RSB) approximation (see section~\ref{rsb-1-section}). Specifically, 
+from Eq.~\eqref{RSB-1-logZ} and Eq.~\eqref{U-def}, for $n=2$ a straightforward calculation 
+gives 
 %
@@
 Moreover, for $\beta\approx\beta_c$ one has $q_1'\approx q_0'\approx0$, implying   
-that $U_{RSB}\approx U_{RS}$, i.e. the effects of the replica symmetry breaking are 
-negligible near the critical point. Interestingly, at low temperatures, where the 
-RS approximation $U_{RS}$ fails (see Fig.~\ref{U-RS}), $U_{1\textrm{-}RSB}$ 
+that $U_{1\textrm{-}RSB}\approx U_{RS}$, i.e. the effects of the replica symmetry 
+breaking are negligible near the critical point. Interestingly, at low temperatures, where the 
+RS approximation fails (see Fig.~\ref{U-RS}), $U_{1\textrm{-}RSB}$ 
 is in good agreement with the Monte Carlo data, at least up to $\beta\approx 2$.  
@@
 We now turn to discuss the behavior of the disorder-averaged classical R\'enyi entropies 
-(cf. Eq.~\eqref{renyi}) in the S-K model. Here we restrict ourselves to the second R\'enyi 
+(cf. Eq.~\eqref{renyi}). Here we restrict ourselves to the second R\'enyi 
 entropy $[S_2]$. Due to the mean-field nature of the S-K model (cf. Eq.~\eqref{SK-ham}), 
 there is no well defined boundary between the two parts $A$ and $B$ of the system 
-(unlike Fig.~\ref{cartoon} for local models). The fully connected nature of the S-K model 
-suggests the volume-law behavior $[S_2]\propto N$ for all temperature.
-Therefore it is natural to consider the entropy per spin $[S_2]/N$.
+(unlike in local spin models). This suggests the volume-law behavior $[S_2]\propto N$ 
+for all temperatures. Thus, it is natural to consider the entropy per spin 
+$[S_2]/N$.
 
@@
 inverse temperature $0.25\le\beta\le 2.5$. The different panels correspond to the  
-booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the empty 
-triangles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per per sheet. 
+booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the 
+triangles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per sheet. 
 Clearly, finite size effects are present, which increase upon lowering 
@@
 $s_2(\omega)$ is the entropy per spin in the thermodynamic limit, $c'$ a constant, and 
-$\phi'$ the exponent of the scaling corrections. The plus symbols in Fig.~\ref{Renyi-MC} 
+$\phi'$ the exponent of the finite-size corrections. The plus symbols in Fig.~\ref{Renyi-MC} 
 are the results of the fits. We should mention that the fits give $\phi'\approx 2/3$, 
@@
 $[S_2]\equiv [F(0,2,\beta)-F(\omega,2,\beta)]$ (cf. Eq.~\eqref{renyi}). 
-Clearly, from Fig.~\ref{I2-MC} one has that in the thermodynamic limit $[S_2]/N$ is 
+Clearly, from Fig.~\ref{Renyi-MC} one has that in the thermodynamic limit $[S_2]/N$ is 
 finite for any $\beta$, confirming the expected volume law behavior. Moreover, $[S_2]/N$ 
@@
 
-The dash-dotted line in Fig.~\ref{Renyi-MC} denotes the analytical result $[S_2^{RS}]$ 
-obtained using the RS approximation (see section~\ref{rs-section}). More precisely, 
-$[S_2^{RS}]/N$ is obtained from Eq.~\eqref{renyi} and the expression for the free energy 
-$[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). Notice that in the 
-high-temperature limit $\beta\to0$, where the RS approximation is exact, 
+The dash-dotted line denotes the analytical result $[S_2^{RS}]$ obtained within the RS 
+approximation (see section~\ref{rs-section}). More precisely, $[S_2^{RS}]/N$ is obtained 
+from Eq.~\eqref{renyi} and the expression for the free energy $[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). 
+Notice that in the high-temperature limit $\beta\to0$, where the RS approximation is exact, 
 Eq.~\eqref{renyi} and Eq.~\eqref{ht-logZ} give 
@@
 agreement with $[S_2^{RS}]/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
-observed at lower temperatures (not shown in the Figure). These reflect the symmetry 
-breaking. A better approximation for $[S_2]/N$ at low temperatures is obtained by 
-including the effects of the replica symmetry breaking. The circles in Fig.~\ref{Renyi-MC} 
-denote the one-step replica symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$
-(see section~\ref{rsb-1-section}). This is formally obtained using Eq.~\eqref{renyi} 
-and the free energy $[F_{1\textrm{-}RSB}]$ (cf. Eq.~\eqref{RSB-1-logZ}). Remarkably, 
+observed at lower temperatures (not shown in the Figure). A better approximation for 
+$[S_2]/N$ at low temperatures is obtained by including the effects of the replica 
+symmetry breaking. The circles in Fig.~\ref{Renyi-MC} denote the one-step replica 
+symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$ (see section~\ref{rsb-1-section}), 
+which is obtained from Eq.~\eqref{renyi}  Eq.~\eqref{RSB-1-logZ}. Remarkably, 
 $[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the Monte Carlo extrapolations 
@@
 
-Here we focus on the behavior of the Renyi mutual information $[{\mathcal I}_2]$ in 
-the S-K model. Similar to $[S_2]$, the mutual information obeys the volume 
-law $[{\mathcal I}_2]\propto N$. This is in contrast with local models, where 
-$[{\mathcal I}_n]$ by construction exhibits an area law at all temperatures.
-Here we consider the mutual information per spin 
-$[{\mathcal I}_2]/N$.
+Here we focus on the behavior of the Renyi mutual information $[{\mathcal I}_2]$. 
+Similar to $[S_2]$, the mutual information exhibits the volume law $[{\mathcal I}_2]
+\propto N$. This is in contrast with local models, where $[{\mathcal I}_n]$ by 
+construction one finds an area law at all temperatures. Here we consider the 
+mutual information per spin $[{\mathcal I}_2]/N$.
 

### 2015-06-11 sk_model_v15.tex
revised-3

@@
 paradigm model of mean-field spin glasses. 
-Using both classical Monte Carlo simulations and analytical tools we investigate the 
-S-K model on a booklet of $n$-sheets.
+First, using classical Monte Carlo simulations and analytical tools we investigate the 
+S-K model on the $n$-sheets booklet.
 This is obtained by gluing together $n$ independent copies of the model, and it is the 
@@
 paramagnetic behavior. Interestingly, the temperature of the paramagnetic-glassy 
-transition depends in a non-trivial way on the geometry of the booklet. At high-temperatures 
+transition depends non-trivially on the geometry of the booklet. At high-temperatures 
 we provide the exact solution of the model exploiting the replica symmetry. This is the 
@@
 The last refers to the breaking of the permutation symmetry among the fictitious replicas 
-of the system, which are introduced to perform disorder averages (\emph{replica 
+of the model, which are introduced to perform disorder averages (\emph{replica 
 trick}~\cite{cardy-book}). Finally, although the applicability of the S-K 
 model to describe realistic spin glasses is still highly debated~\cite{yucesoy-2012,
-billoire-2012,yucesoy-2013}, there are recent proposals on how to realize this model 
+billoire-2012,yucesoy-2013}, there are recent proposals on how to realize it  
 in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser systems~\cite{
@@
 
-In the last decade entanglement-related quantities have emerged as valuable tools to 
+In the last decade entanglement-related quantities emerged as valuable tools to 
 understand the physics of complex systems~\cite{amico-2008,eisert-2009,calabrese-2009,
@@
 an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
-precise definition). This consists of $n$ independent and identical replicas (the 
-booklet ``sheets'') of the model. Notice that these \emph{physical} replicas are different 
+definition). This consists of $n$ independent and identical replicas (the 
+booklet ``sheets'') of the model. These \emph{physical} replicas are different 
 from the \emph{fictitious} ones used to perform the disorder average. Each sheet is 
@@
 %
-Eq.~\eqref{renyi-intro} can be used for quantum systems by interpreting $p_{i_A}$ as 
+Eq.~\eqref{renyi-intro} can also be used for quantum systems by interpreting $p_{i_A}$ as 
 the probability of finding part $A$ in the \emph{quantum} configuration $i_A$. In particular, 
-for $n=1$ it defines the subsystem Shannon entropy~\cite{alcaraz-2013,stephan-2014-a}. 
-From $S_n(A)$, one defines the classical mutual information ${\mathcal I}_n(A,B)$ 
-as 
+for $n=1$ Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
+stephan-2014-a}. From $S_n(A)$, one defines the classical mutual information 
+${\mathcal I}_n(A,B)$ as 
 %
@@
 whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures $\beta$. 
-The booklet geometry is illustrated in Figure~\ref{cartoon}. 
-Each sheet is divided into two parts $A$ and $B$ (cf. Figure~\ref{cartoon} (a)). Then $n$ copies 
+The booklet geometry is illustrated in Fig.~\ref{cartoon}. 
+Each sheet is divided into two parts $A$ and $B$ (cf. Fig.~\ref{cartoon} (a)). Then $n$ copies 
 of the system are ``glued'' together to form the booklet. The spins in part $A$ of the different 
-sheets are identified (cf. Figure~\ref{cartoon} (b)). While spins in parts $B$ of the booklet 
+sheets are identified (cf. Fig.~\ref{cartoon} (b)). While spins in parts $B$ of the booklet 
 are at inverse temperature $\beta$, the ones in $A$ are at the effective temperature $n\beta$. 
@@
  The S-K model on the $2$-sheets booklet with zero magnetic field in the 
- paramagnetic phase: the solution $q_0$ of the saddle point equation 
- Eq.~\eqref{saddle-high-t} plotted as a function of the ratio 
- $\omega$ and for $\beta=1/T=0,3/4,1,4/3$. At $\omega=1$ one has 
- $q_0=1,\forall\beta$. In the zero-temperature limit $\beta\to\infty$ 
- it is $q_0\to 1,\forall\omega$. The straight line is the infinite 
+ paramagnetic phase: the solution $q_0$ of the saddle point 
+ equation~\eqref{saddle-high-t} plotted as a function of the booklet aspect 
+ ratio $\omega$ and several values of the inverse temperature $\beta=1/T$. 
+ At $\omega=1$ one has $q_0=1,\forall\beta$. In the zero-temperature limit 
+ one has $q_0\to 1,\forall\omega$. The straight line is the infinite 
  temperature result. 
@@
  the solutions $q_0$ and $q_0'$ (shown as full and dotted lines, respectively) 
- of the saddle point equations Eqs.~\eqref{RS-saddle-1}\eqref{RS-saddle-2} 
- plotted as a function of the ratio $\omega$, and inverse temperature 
- $\beta=1/T=1,3/2,2$. At $\omega=1$ one has that $q_0=1,\forall\beta$.
- In the limit $\beta\to\infty$ it is $q_0,q_0'\to 1,\forall\omega$.
+ of the saddle point equations~\eqref{RS-saddle-1}\eqref{RS-saddle-2} 
+ plotted as a function of the booklet aspect ratio $\omega$, and inverse 
+ temperature $\beta=1/T=1,3/2,2$. At $\omega=1$ one has that $q_0=1,
+ \forall\beta$. In the limit $\beta\to\infty$ it is $q_0,q_0'\to 1,\forall
+ \omega$.
 }
@@
 \caption{
- The critical temperature $\beta_c\equiv 1/T_c$ for the S-K model on the $2$-sheets  
- booklet (see Fig.~\ref{cartoon}) with zero magnetic field: $\beta_c$ as a function 
- of the booklet ratio $\omega\equiv N_A/N$. Here $\beta_c$  is obtained from the 
- replica-symmetric (RS) approximation of the model. Notice that one has $\beta_c=1$ 
- and $\beta_c=1/2$ for $\omega=0$ and $\omega=1$, respectively. 
+ The critical temperature $\beta_c\equiv 1/T_c$ of the paramagnetic-glassy 
+ transition for the S-K model on the $2$-sheets booklet (see Fig.~\ref{cartoon}) 
+ with zero magnetic field: $\beta_c$ as a function of the booklet ratio $\omega
+ \equiv N_A/N$. Here $\beta_c$  is obtained from the replica-symmetric (RS) 
+ approximation. Notice that $\beta_c=1$ and $\beta_c=1/2$ for $\omega=0$ and 
+ $\omega=1$, respectively. 
 }
@@
  as a function of inverse temperature $\beta$. The plus symbols are the same 
- Monte Carlo data as in Figure~\ref{U-RS}. The lines denote $U/N$ 
+ Monte Carlo data as in Fig.~\ref{U-RS}. The lines denote $U/N$ 
  in the replica-symmetric (RS) approximation (same as in Fig.~\ref{U-RS}). 
@@
 \caption{ The classical disorder-averaged Renyi entropy per spin $[S_2(\omega)]/N$  
- in the S-K model on the $2$-sheets booklet with zero magnetic: $[S_2(\omega)]/N$ as a 
- function of the inverse temperature $\beta$. The different panels 
+ in the S-K model on the $2$-sheets booklet with zero magnetic field: 
+ $[S_2(\omega)]/N$ as a function of the inverse temperature $\beta$. The different panels 
  correspond to different booklet aspect ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). 
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/I2_MC_v1}
-\caption{The classical mutual information per spin ${\mathcal I}_2/N$ 
+\caption{The classical disorder-averaged mutual information per spin $[{\mathcal I}_2]/N$ 
  in the S-K model on the $2$-sheets booklet with zero magnetic field: 
- ${\mathcal I}_2/N$ versus the inverse temperature $\beta$. The 
+ $[{\mathcal I}_2]/N$ versus the inverse temperature $\beta$. The 
  different panels correspond to different booklet ratios $\omega=1/2,1/4,1/8$ 
@@
 The Monte Carlo data for $[S_2]/N$  are shown in Fig.~\ref{Renyi-MC} plotted versus the 
-inverse temperature $0.25\le\beta\le 2.5$. The different panels correspond to the  
-booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the 
+inverse temperature $0.25\le\beta\le 2.5$. Some details on the Monte Carlo method used 
+to calculate $[S_2]$ are provided in Appendix~\ref{mc-method}. The different panels 
+correspond to the booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the 
 triangles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per sheet. 
@@
 the temperature, as expected. In order to obtain $[S_2]/N$ in the thermodynamic limit 
-we fit the data to the ansatz $[S_2]=s_2(\omega)+c'(\omega)/N^{\phi'}$, where 
+we fit the data to the ansatz $[S_2]/N=s_2(\omega)+c'(\omega)/N^{\phi'}$, where 
 $s_2(\omega)$ is the entropy per spin in the thermodynamic limit, $c'$ a constant, and 
@@
 Similar to $[S_2]$, the mutual information exhibits the volume law $[{\mathcal I}_2]
-\propto N$. This is in contrast with local models, where $[{\mathcal I}_n]$ by 
-construction one finds an area law at all temperatures. Here we consider the 
+\propto N$. This is in contrast with local models, where $[{\mathcal I}_n]$ for any 
+$n$ by construction obeys an area law at all temperatures. Here we consider the 
 mutual information per spin $[{\mathcal I}_2]/N$.
 
-Figure~\ref{I2-MC} plots $[{\mathcal I}_2]/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,1/8$ 
-(panels from left to right in the Figure). Notice that by definition (cf. Eq.~\eqref{MI}) 
-$[{\mathcal I}_n(\omega)]=[{\mathcal I}_n(1-\omega)]$. Circles, squares, and rhombi 
+Figure~\ref{I2-MC} plots $[{\mathcal I}_2]/N$ versus $0\le\beta\le 2.5$ and $\omega=1/2,1/4,
+1/8$ (panels from left to right in the Figure). Notice that by definition (cf. Eq.~\eqref{MI}) 
+$[{\mathcal I}_n(\omega)]=[{\mathcal I}_n(1-\omega)]$. Circles, squares, and triangles  
 are Monte Carlo data for $N=32,64,128$. In the high-temperature region $[{\mathcal I}_2]$ 
-exhibits a vanishing behavior. Moreover, finite size effects are 
-``small''. Using Eq.~\eqref{logZ-ht} it is straightforward to derive the high-temperature 
-behavior of $[{\mathcal I}_n]$ as  
+exhibits a vanishing behavior. Finite size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
+it is straightforward to derive the high-temperature behavior of $[{\mathcal I}_n]$ as  
 %
@@
 Moreover, $[{\mathcal I}_2]/N$ increases upon lowering the temperature, up to $\beta\approx 1$, 
-where it exhibits a maximum. The height of this  
-maximum decreases as a function of $\omega$. Its position is not simply related to the 
-paramagnetic-glassy transition in the standard S-K model. This is not surprising 
-as $[{\mathcal I}_n]$ is constructed by combining the partition functions of the S-K model 
-on the booklets with aspect ratios $\omega$, $1-\omega$, $\omega=0$, and $\omega=1$ (cf. Eq.~\eqref{MI}), 
-and the critical temperature of the paramagnetic-glassy transition is a non trivial 
-function of $\omega$ (see Fig.~\ref{beta_c}). 
-Furthermore, the curves for $[{\mathcal I}_2]/N$ for different system sizes do not exhibit any 
-crossing. This is in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ 
-exhibits a crossing at a second order phase transition. 
-The dash-dotted line in Fig.~\ref{I2-MC} denotes the analytical result obtained using the replica 
-symmetric (RS) approximation (see section~\ref{rs-section}). Formally this is obtained using 
-Eq~\eqref{MI} and Eq.~\eqref{rs-F}, and it is in perfect agreement with the MC data in the whole 
-paramagnetic phase.
+where it exhibits a maximum. The height of this maximum decreases as a function of $\omega$. 
+Its position is not simply related to the paramagnetic-glassy transition in the standard S-K 
+model. This is not surprising as $[{\mathcal I}_n]$ is constructed by combining the partition 
+functions on booklets with different aspect ratios $\omega$, $1-\omega$, $\omega=0$, and 
+$\omega=1$ (cf. Eq.~\eqref{MI}), and the critical temperature of the paramagnetic-glassy 
+transition is a non trivial function of $\omega$ (see Fig.~\ref{beta_c}). Furthermore, the 
+data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. This is 
+in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ exhibits a 
+crossing at a second order phase transition. The dash-dotted line in Fig.~\ref{I2-MC} is the 
+analytical result obtained using the replica symmetric (RS) approximation (see 
+section~\ref{rs-section}). Formally, this is obtained using Eq~\eqref{MI} and Eq.~\eqref{rs-F}, 
+and it is in perfect agreement with the MC data in the whole paramagnetic phase.
 
@@
 These deviations have to be attributed to the physics of the replica symmetry breaking. 
-The full rhombi in Fig.~\ref{I2-extrapolated} denote the result $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ 
-obtained in the one-step replica symmetry breaking approximation. More precisely, 
-$[{\mathcal I}_2^{1\textrm{-}RSB}]$ is obtained using Eq.~\eqref{MI} and the one-step replica 
-symmetry breaking (1-RSB) approximation for the free energy of the S-K model on the 
-booklet (cf. Eq.~\eqref{RSB-1-logZ}). The agreement between $[{\mathcal I}_2^{1\textrm{-}RSB}]$ 
-and the Monte Carlo data is perfect, at least up to $\beta\lesssim 2$.
+The full rhombi in Fig.~\ref{I2-extrapolated} denote the one-step replica symmetry breaking result 
+$[{\mathcal I}_2^{1\textrm{-}RSB}]$, which is obtained using Eq.~\eqref{MI} and Eq.~\eqref{RSB-1-logZ}). 
+The agreement between $[{\mathcal I}_2^{1\textrm{-}RSB}]$ and the Monte Carlo data is perfect 
+up to $\beta\lesssim 2$.
+
+%##########################################################################
+\section{Summary and Conclusions}
+\label{conclusions}
+
+We investigated the \emph{classical} R\'enyi entropy $S_n$ and the mutual information 
+${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the paradigm model 
+of mean-field spin glasses. We focused on the quenched 
+averages $[S_n]$ and $[{\mathcal I}_n]$, with the brackets $[\cdot]$ denoting the average 
+over different disorder realizations. Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ 
+were obtained from suitable combinations of the partition functions of the S-K model on the 
+$n$-sheets booklet (cf. Fig.~\ref{cartoon}). This is constructed by ``gluing'' together 
+$n$ independent replicas (``sheets'') of the model. On each replica the spins are 
+divided into two groups $A$ and $B$, containing $N_A$ and $N_B$ spins respectively. The 
+spins in part $A$ of the different sheets are identified. Due to the mean-field nature of 
+the model, physical quantities depend on the bipartition only through the aspect ratio 
+$\omega\equiv N_A/N$.
 
@@
 
-%##########################################################################
-\section{Summary and Conclusions}
-\label{conclusions}
-
-We investigated the \emph{classical} R\'enyi entropy $S_n$ and the mutual information 
-${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the paradigm model 
-of mean-field spin glasses. We focused on the quenched 
-averages $[S_n]$ and $[{\mathcal I}_n]$, with the brackets $[\cdot]$ denoting the average 
-over different disorder realizations. Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ 
-were obtained from suitable combinations of the partition functions of the S-K model on the 
-$n$-sheets booklet (cf. Fig.~\ref{cartoon}). This is constructed by ``gluing'' together 
-$n$ independent replicas (``sheets'') of the model. On each replica the spins are 
-divided into two groups $A$ and $B$, containing $N_A$ and $N_B$ spins respectively. The 
-spins in part $A$ of the different sheets are identified. Due to the mean-field nature of 
-the model, physical quantities depend on the bipartition only through the aspect ratio 
-$\omega\equiv N_A/N$.
-
 We first investigated the phase diagram of the S-K model on the $2$-sheets booklet as a 
@@
 disorder-averaged free energy $[F_{para}(\omega,n,\beta)]$  (cf. Eq.~\eqref{ht-logZ}) in 
-the thermodynamic limit. On the other hand, in the glassy phase the replica symmetry has 
-to be broken, similar to the standard S-K model. To take into account the effects of the 
-replica symmetry breaking we used a generalization of the the Parisi 
+the thermodynamic limit. On the other hand, we observed that in the glassy phase the 
+replica symmetry has to be broken, similar to the standard S-K model. To take into account 
+the effects of the replica symmetry breaking we used a generalization of the the Parisi 
 ansatz~\cite{parisi-1980}, i.e., breaking the replica symmetry in successive 
@@
 nature of the S-K model we observed the volume laws $[S_2]\propto N$ and 
-$[{\mathcal I}_2]\propto N$, for any $\beta$. We considered the corresponding densities 
+$[{\mathcal I}_2]\propto N$, for any $\beta$. We considered the densities 
 $[S_2]/N$ and $[{\mathcal I}_2]/N$. Using the replica-symmetric (RS) and the one-step 
@@
 glassy behavior is reflected in the volume-law corrections to the classical R\'enyi 
-entropies. Also, it would be interesting to extend our results to {\it quantum} spin 
+entropies. Finally, it would be interesting to extend our results to {\it quantum} spin 
 systems exhibiting glassy behavior and replica symmetry breaking~\cite{read-1995,
@@
 %##########################################################################
+
+\section{Monte Carlo method to calculate the classical R\'enyi entropies}
+\label{mc-method}
+
+Here we describe the Monte Carlo method that we used to calculate the R\'enyi entropies 
+$S_n$ and the mutual information ${\mathcal I}_n$. The method exploits the representation 
+of $S_n$ as ratio of partition functions as 
+%
+\begin{equation}
+\label{renyi-app}
+S_n(A)\equiv \frac{1}{1-n}\log\left(\frac{Z(A,n,\beta)}{Z^n(\beta)}\right),
+\end{equation}
+%
+where $Z(A,n,\beta)$ and $Z(\beta)$ are the partition functions of the model on the booklet and 
+on the plane, respectively (see Fig.~\ref{cartoon} and section~\ref{booklet} for the definitions).  
+There are a only few approaches to numerically calculate the the ratio of partition functions in 
+Eq.~\eqref{renyi-app}. For instance, a brute force numerical integration of the internal energy as 
+a function of temperature\cite{jaconis-2013} can be used to calculate $Z(A,n,\beta)$ and $Z(\beta)$. 
+However, this requires high accuracy over a large range of temperature.
+
+Here we directly calculate the ratio of partition functions in Eq.~\eqref{renyi-app} using the 
+so-called \emph{ratio trick}. In the ratio trick one splits the subsystem $A$ as $A=\sum_{i}A_i$, 
+where $A_i$ is a sequence of subsystems such that $A_i\subset A_{i+1}$. 
+Then one writes 
+%
+\begin{align}
+\label{ratio-trick}
+\frac{Z(A,n,\beta)}{ Z^n(\beta)} = \prod_{i=0}^{N/4-1} \frac{Z(A_i,n,\beta)}{Z(A_{i+1},n,\beta)}
+\end{align}
+%
+where for simplicity we specialized to intervals $A_i$ such that
+%
+\begin{align}
+\label{sub-choice}
+A_i = 4i,\quad i \in [0,N/4] .
+\end{align}
+%
+Crucially, if the length of $A_i$ increases mildly with $i$, each term in the product 
+in the left hand side of~\eqref{ratio-trick} can be sampled efficiently in Monte 
+Carlo~\cite{stephan-2014}. Notice that a similar method has also been used in 
+Ref.~\onlinecite{alba-2010,alba-2011,alba-2013}. More specifically, one can write
+%
+\begin{align}
+\frac{Z(A_i,n,\beta)}{Z(A_{j},n,\beta)} = \frac{T_{j\rightarrow i}}{T_{i\rightarrow j}}
+\end{align}
+%
+where $T_{i\rightarrow j}$  is the (Monte Carlo) transition probability from a spin 
+configuration living on the booklet with $A=A_i$ to a spin configuration living on the 
+booklet with $A=A_j$. Notice that spins in region $A$ of different sheets are identified 
+(cf. Eq.~\eqref{book-constraint}). Clearly, if $j<i$ one has $T_{i\rightarrow j}=1$.
+When $j>i$ a naive method to determine $T_{i\rightarrow j}$ would be to simply count the 
+fraction of times (during the Monte Carlo update) that a spin configuration living on 
+the booklet with $A=A_i$ is also a valid spin configuration on the booklet with $A=A_j$.
+In the following we provide a more efficient scheme to calculate $T_{i\rightarrow j}$.
+
+To summarize, our approach for calculating the ratio of partition functions in 
+Eq.~\eqref{ratio-trick} consists of four steps:
+\begin{enumerate}
+\item Do a full Monte Carlo sweep of the system on the booklet with $A=A_i$ 
+to generate an importance sampled spin configuration. This can be done with any 
+update scheme, such as standard Metropolis or cluster updates
+\item For the the spins living in $A_{i+1}-A_i$ calculate 
+%
+\begin{align}
+W_a = \sum_i e^{-\beta E_i}.
+\end{align}
+%
+Here (cf. Eq.~\eqref{sub-choice}) $i$ runs over all the $n2^4$ configurations of the 
+four spins in $A_{i+1}-A_i$, and $E_i$ is the energy associated with configuration $i$. 
+\item Calculate the quantity
+\begin{align}
+W_b = \sum_j e^{-\beta E_j}
+\end{align}
+where $j$ runs over all the $2^4$ configurations with the four spins living in $A_{i+1}-
+A_i$ and different sheets are identified.
+\item Calculate the transition probability $T_{i\rightarrow i+1}$ as
+%
+\begin{align}
+T_{i \rightarrow i+1} = \Bigl< \frac{W_b}{W_a} \Bigr>.
+\end{align}
+%
+\end{enumerate}
+
+This method is much faster than simply counting configurations as it allows 
+us to integrate over all possible configurations of the spins in $A_{i+1}-A_i$, 
+treating the remaining ones as a bath that is updated by the regular Monte Carlo update. 
+The computational cost of this procedure grows exponentially with the number of spins 
+in $A_{i+1}-A_i$. 
+%We also gain some speed by calculating the weights in each replica seperately, 
+%and then recombining the results in a smart way, meaning that we only have to explicitly 
+%loop over $2 \cdot 2^4 = 32$ configurations.
+
+In our Monte Carlo simulations we calculate $Z(A_i,n,\beta)/Z(A_{i+1},n,\beta)$ 
+for every disorder realization and $S_n(A)$ using Eq.~\eqref{renyi-app}. 
+Finally, we average over the disorder to obtain $[S_n(A)]$.
+%When calculating the mutual information
+%\begin{align}
+%I_{n}(A) = S_{n}(A) + S^*_{n}(N-A) - S_{n}(N)
+%\end{align}
+%we do this calculating for each specific realization of disorder, and then take the disorder average of this final quantity.
+%The star in $S^*$ denotes the fact that even though $A$ denotes the size of the region that is connected, due to disorder one must be careful which specific spins are in the region.
+%$S^*$ is defined in such a way that the connected spins in $S_{n}(A)$ and those in $S^*_{n}(N-A)$ contain every spin in the system exactly once.
+
+%For each disorder and each $\omega_i$ we create a simulation, and measure
+%\begin{align}
+%\frac{Z(\omega_i,\alpha,\beta)}{Z(\omega_{i+1},\alpha,\beta)} = \\
+%\frac{Z(\omega_i,\alpha,\beta)}{Z(\omega_{i-1},\alpha,\beta)}
+%\end{align}
+
+%Due to the infinite dimensional nature of the Sherrington-Kirkpatrick model, the calculation the R\'enyi mutual information is unable to exploit efficient methods that are available for finite dimensional systems [ref: JMS/Inglis].
+
+%where $A$ changes only slightly, and build up the full quantity by taking the product of many such measurements.
+%This method is usually referred to as the ratio trick, and in finite dimensional systems there are efficient ways to calculate this ratio\cite{stephan-2014}.
+%In an infinite dimensional system the only efficient way to use this method is to increase $A$ more slowly than typical.
+%For this study, $A$ is increased by only 4 sites at a time.
+
+%First, if we want to sample from $A=0$ (two disconnected systems) to $A=N$ (two fully connected systems), let us use the ratio trick to write
+
 \begin{thebibliography}{99}
+\bibitem{binder-1986}
+K.~Binder and A.~P.~Young, Rev.\ Mod.\ Phys.\ {\bf 58}, 801 (1986).
+
+\bibitem{parisi-book}
+M.~Mezard, G.~Parisi, and M.~Virasoro, \emph{Spin Glass theory and beyond}, World Scientific, Singapore (1987).
+
+\bibitem{young-1998}
+A.~P.~Young, \emph{Spin Glasses and Random Fields} (Singapore: World Scientific).
+
+\bibitem{nishimori-book}
+H.~Nishimori, ``Statistical Physics of Spin Glasses and Information Processing'', 
+Clarendon Press, Oxford (2001).
+
+\bibitem{castellani-2005}
+T.~Castellani and A.~Cavagna, J.\ Stat.\ Mech.\ (2005) P05012.
+
+\bibitem{sherrington-1978}
+D.~Sherrington and S.~Kirkpatrick, Phys.\ Rev.\ B {\bf 17}, 4385 
+(1978).
+
+\bibitem{sherrington-1978-prl}
+D.~Sherrington and S.~Kirkpatrick, Phys.\ Rev.\ Lett.\ {\bf 35}, 
+1972 (1978).
+
+\bibitem{parisi-1980}
+G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1101 (1980).
+
+\bibitem{talagrand-2006}
+M.~Talagrand, Ann.\ of\ Math.\ {\bf 163}, 221 (2006).
+
+\bibitem{pastur-1991}
+L.~A.~Pastur and M.~V.~Shcherbina, J.\ Stat.\ Phys.\ {\bf 62}, 1 (1991).
+
+\bibitem{mezard-1984}
+M.~Mezard, G.~Parisi, N.~Sourlas, G.~Toulouse, and M.~Virasoro, 
+Phys.\ Rev.\ Lett.\ {\bf 52}, 1156 (1984).
+
+\bibitem{rammal-1986}
+R.~Rammal, G.~Toulouse, and M.~A.~Virasoro, Rev.\ Mod.\ Phys.\ {\bf 58}, 765 
+(1986).
+
+\bibitem{cardy-book}
+J.~Cardy, \emph{Scaling and Renormalization in Statistical Physics} 
+(Cambridge Lecture Notes in Physics).
+
+\bibitem{yucesoy-2012}
+B.~Yucesoy, H.~G.~Katzgraber, and J.~Machta, Phys.\ Rev.\ Lett. {\bf 109}, 
+177204 (2012).
+
+\bibitem{billoire-2012}
+A.~Billoire, L.~A.~Fernandez, A.~Maiorano, E.~Marinari, 
+V.~Martin-Mayor, G.~Parisi, F.~Ricci-Tersenghi, J.~J.~Ruiz-Lorenzo, 
+and D.~Yllanes, Phys.\ Rev.\ Lett.\ {\bf 110}, 219701 (2013).
+
+\bibitem{yucesoy-2013}
+B.~Yucesoy, H.~G.~Katzgraber, and J.~Machta, Phys.\ Rev.\ Lett.\ {\bf 110}, 
+219702 (2013)
+
+\bibitem{morrison-2008}
+S.~Morrison, A.~Kantian, A.~J.~Daley, H.~G.~Katzgraber, M.~Lewenstein, 
+H.~P.~B\"uchler, and P.~Zoller, New\ J.\ Phys.\ {\bf 10}, 
+073032 (2008).
+
+\bibitem{rotondo-2015}
+P.~Rotondo, E.~Tesio, and S.~Caracciolo, Phys.\ Rev.\ B {\bf 91}, 
+014415 (2015).
+
+\bibitem{ghofraniha-2015}
+N.~Ghofraniha, I.~Viola, F.~Di~Maria, G.~Barbarella, G.~Gigli, L.~Leuzzi, 
+and C.~Conti, Nature\ Comm.\ {\bf 6}, 6058 (2015).
 
@@
 
-\bibitem{binder-1986}
-K.~Binder and A.~P.~Young, Rev.\ Mod.\ Phys.\ {\bf 58}, 801 (1986).
-
-\bibitem{young-1998}
-A.~P.~Young, \emph{Spin Glasses and Random Fields} (Singapore: World Scientific).
-
-\bibitem{wilms-2011}
-J.~Wilms, M.~Troyer, and F.~Verstraete, J.\ Stat.\ Mech.\ (2011) P10011.
-
-\bibitem{wilms-2012}
-J.~Wilms, J.~Vidal, F.~Verstraete,and S.~Dusuel, J.\ Stat.\ Mech.\ (2012)P01023.
-
-\bibitem{parisi-book}
-M.~Mezard, G.~Parisi, and M.~Virasoro, \emph{Spin Glass theory and beyond}, World Scientific, Singapore (1987).
-
-\bibitem{fisher-1986}
-D.~S.~Fisher and D.~A.~Huse, Phys.\ Rev.\ Lett.\ {\bf 56} 1601 (1986).
-
-\bibitem{huse-1987}
-D.~S.~Fisher and D.~A.Huse, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L997 (1987).
-
-\bibitem{huse-1987-a}
-D.~A.~Huse and D.~S.~Fisher, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L1005 (1987).
-
-\bibitem{fisher-1988}
-D.~S.~Fisher and D.~A.Huse, Phys.\ Rev. B {\bf 38}, 386 (1988).
-
-\bibitem{newman-1996}
-C.~Newman and D.~L.~Stein, Phys.\ Rev.\ Lett.\ {\bf 76}, 515 (1996).
-
-\bibitem{krzakala-2000}
-F.~Krzakala and O.~C.~Martin, Phys.\ Rev.\ Lett.\ {\bf 85}, 3013 (2000).
-
-\bibitem{palassini-2000}
-M.~Palassini and A.~P.~Young, Phys.\ Rev.\ Lett.\  {\bf 85}, 3017 (2000).
-
-\bibitem{sherrington-1978-prl}
-D.~Sherrington and S.~Kirkpatrick, Phys.\ Rev.\ Lett.\ {\bf 35}, 
-1972 (1978).
-\bibitem{sherrington-1978}
-D.~Sherrington and S.~Kirkpatrick, Phys.\ Rev.\ B {\bf 17}, 4385 
-(1978).
-
-\bibitem{parisi-1980}
-G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1101 (1980).
-
-\bibitem{parisi-1980-a}
-G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1887 (1980).
-
-\bibitem{parisi-1980-b}
-G.~Parisi, J.\ Phys.\ A\ {\bf 13}, L115 (1980).
-
-\bibitem{parisi-1979}
-G.~Parisi, Phys.\ Rev.\ Lett.\ {\bf 43}, 1754 (1979).
-
-\bibitem{parisi-1983}
-G.~Parisi, Phys.\ Rev.\ Lett\ {\bf 50}, 1946 (1983).
-
-\bibitem{mezard-1984}
-M.~Mezard, G.~Parisi, N.~Sourlas, G.~Toulouse, and M.~Virasoro, 
-Phys.\ Rev.\ Lett.\ {\bf 52}, 1156 (1984).
-
-\bibitem{nishimori-book}
-H.~Nishimori, ``Statistical Physics of Spin Glasses and Information Processing'', 
-Clarendon Press, Oxford (2001).
+\bibitem{calabrese-2012}
+P.~Calabrese, J.~Cardy, and E.~Tonni, Phys.\ Rev.\ Lett.\ {\bf 109}, 
+130502 (2012).
+
+\bibitem{jaconis-2013}
+J.~Iaconis, S.~Inglis, A.~B.~Kallin, and R.~G.~Melko, 
+Phys.\ Rev.\ B {\bf 87}, 195134 (2013).
 
@@
 
-\bibitem{jaconis-2013}
-J.~Iaconis, S.~Inglis, A.~B.~Kallin, and R.~G.~Melko, 
-Phys.\ Rev.\ B {\bf 87}, 195134 (2013).
-
-\bibitem{yucesoy-2012}
-B.~Yucesoy, H.~G.~Katzgraber, and J.~Machta, Phys.\ Rev.\ Lett. {\bf 109}, 
-177204 (2012).
-
-\bibitem{yucesoy-2013}
-B.~Yucesoy, H.~G.~Katzgraber, and J.~Machta, Phys.\ Rev.\ Lett.\ {\bf 110}, 
-219702 (2013)
-
-\bibitem{billoire-2012}
-A.~Billoire, L.~A.~Fernandez, A.~Maiorano, E.~Marinari, 
-V.~Martin-Mayor, G.~Parisi, F.~Ricci-Tersenghi, J.~J.~Ruiz-Lorenzo, 
-and D.~Yllanes, Phys.\ Rev.\ Lett.\ {\bf 110}, 219701 (2013).
-
-\bibitem{morrison-2008}
-S.~Morrison, A.~Kantian, A.~J.~Daley, H.~G.~Katzgraber, M.~Lewenstein, 
-H.~P.~B\"uchler, and P.~Zoller, New\ J.\ Phys.\ {\bf 10}, 
-073032 (2008).
-
-\bibitem{ghofraniha-2015}
-N.~Ghofraniha, I.~Viola, F.~Di~Maria, G.~Barbarella, G.~Gigli, L.~Leuzzi, 
-and C.~Conti, Nature\ Comm.\ {\bf 6}, 6058 (2015).
-
-\bibitem{rotondo-2015}
-P.~Rotondo, E.~Tesio, and S.~Caracciolo, Phys.\ Rev.\ B {\bf 91}, 
-014415 (2015).
-
-%\bibitem{bouchaud-2003}
-%J.-P.~Bouchaud, F.~Krzakala, and O.~C.~Martin, Phys.\ Rev.\ B {\bf 68}, 
-%224404 (2003).
-
-%\bibitem{boettcher-2005}
-%S.~Boettcher: Eur.\ Phys.\ J.\ {\bf B46}, 501 (2005).
-
-%\bibitem{katzgraber-2003}
-%H.~G.~Katzgraber and I.~A.~Campbell, 
-%Phys.\ Rev.\ B {\bf 68}, 180402R (2003).
-
-\bibitem{aspelmeier-2008}
-T.~Aspelmeier, A.~Billoire, E.~Marinari, and M.~A.~Moore, 
-J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 41} 324008 (2008).
+\bibitem{alcaraz-2013}
+F.~C.~Alcaraz and M.~A.~Rajabpour, Phys.\ Rev.\ Lett.\ {\bf 111}, 017201 (2013).
+
+\bibitem{stephan-2014-a}
+J.-M.~St\'ephan, Phys.\ Rev.\ B {\bf 90}, 045424 (2014).
+
+\bibitem{wolf-2008}
+M.~M.~Wolf, F.~Verstraete, M.~B.~Hastings, and J.~I.~Cirac, Phys.\ Rev.\ Lett.\ 
+{\bf 100}, 070502 (2008).
+
+\bibitem{refael-2009}
+G.~Refael and J.~E.~Moore J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 42} 504010 (2009).
+
+\bibitem{castelnovo-2010}
+C.~Castelnovo, C.~Chamon, and D.~Sherrington, Phys.\ Rev.\ B {\bf 81}, 184303 (2010).
+
+\bibitem{parisi-1979}
+G.~Parisi, Phys.\ Rev.\ Lett.\ {\bf 43}, 1754 (1979).
+
+\bibitem{guerra-2002}
+F.~Guerra and F.~L.~Toninelli, Commun.\ Math.\ Phys.\ {\bf 230}, 71 (2002).
+
+\bibitem{almeida-1978}
+J.~R.~L.~de Almeida and D.~J.~Thouless, J.\ Phys.\ A {\bf 11}, 983 (1978).
 
@@
 
+\bibitem{aspelmeier-2008}
+T.~Aspelmeier, A.~Billoire, E.~Marinari, and M.~A.~Moore, 
+J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 41} 324008 (2008).
+
+\bibitem{parisi-1983}
+G.~Parisi, Phys.\ Rev.\ Lett\ {\bf 50}, 1946 (1983).
+
 \bibitem{read-1995}
@@
 
-\bibitem{cardy-book}
-J.~Cardy, \emph{Scaling and Renormalization in Statistical Physics} 
-(Cambridge Lecture Notes in Physics).
-
-\bibitem{almeida-1978}
-J.~R.~L.~de Almeida and D.~J.~Thouless, J.\ Phys.\ A {\bf 11}, 983 (1978).
-
-\bibitem{stephan-2009}
-J-M~St\'ephan, S.~Furukawa, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 80}, 
-184421 (2009)
-
-\bibitem{stephan-2010}
-J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 82}, 125455 
-(2010);
-
-\bibitem{stephan-2011}
-J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 84}, 
-195128 (2011).
-
-\bibitem{zaletel-2011}
-M.~P.~Zaletel, J.~H.~Bardarson, and J.~E.~Moore, Phys.\ Rev.\ Lett.\ {\bf 107}, 
-020402 (2011).
-
-\bibitem{alcaraz-2013}
-F.~C.~Alcaraz and M.~A.~Rajabpour, Phys.\ Rev.\ Lett.\ {\bf 111}, 017201 (2013).
-
-\bibitem{talagrand-2006}
-M.~Talagrand, Ann.\ of\ Math.\ {\bf 163}, 221 (2006).
-
-\bibitem{guerra-2002}
-F.~Guerra and F.~L.~Toninelli, Commun.\ Math.\ Phys.\ {\bf 230}, 71 (2002).
-
-\bibitem{rammal-1986}
-R.~Rammal, G.~Toulouse, and M.~A.~Virasoro, Rev.\ Mod.\ Phys.\ {\bf 58}, 765 
-(1986).
-
-\bibitem{calabrese-2012}
-P.~Calabrese, J.~Cardy, and E.~Tonni, Phys.\ Rev.\ Lett.\ {\bf 109}, 
-130502 (2012).
-
-\bibitem{stephan-2014-a}
-J.-M.~St\'ephan, Phys.\ Rev.\ B {\bf 90}, 045424 (2014).
-
-\bibitem{castellani-2005}
-T.~Castellani and A.~Cavagna, J.\ Stat.\ Mech.\ (2005) P05012.
-
-\bibitem{wolf-2008}
-M.~M.~Wolf, F.~Verstraete, M.~B.~Hastings, and J.~I.~Cirac, Phys.\ Rev.\ Lett.\ 
-{\bf 100}, 070502 (2008).
-
-\bibitem{refael-2009}
-G.~Refael and J.~E.~Moore J.\ Phys.\ A:\ Math.\ Theor.\ {\bf 42} 504010 (2009).
-
-\bibitem{pastur-1991}
-L.~A.~Pastur and M.~V.~Shcherbina, J.\ Stat.\ Phys.\ {\bf 62}, 1 (1991).
-
-\bibitem{castelnovo-2010}
-C.~Castelnovo, C.~Chamon, and D.~Sherrington, Phys.\ Rev.\ B {\bf 81}, 184303 (2010).
+\bibitem{alba-2010}
+V.~Alba, L.~Tagliacozzo, and P.~Calabrese, Phys.\ Rev.\ B {\bf 81}, 060411(R) (2010).
+
+\bibitem{alba-2011}
+V.~Alba, L.~Tagliacozzo, and P.~Calabrese, J.\ Stat.\ Mech.\ (2011) P06012.
+
+\bibitem{alba-2013}
+V.~Alba, J.\ Stat.\ Mech.\ (2013) P05013.
+
+%\bibitem{bouchaud-2003}
+
+%J.-P.~Bouchaud, F.~Krzakala, and O.~C.~Martin, Phys.\ Rev.\ B {\bf 68},
+
+%224404 (2003).
+
+%\bibitem{boettcher-2005}
+
+%S.~Boettcher: Eur.\ Phys.\ J.\ {\bf B46}, 501 (2005).
+
+%\bibitem{katzgraber-2003}
+
+%H.~G.~Katzgraber and I.~A.~Campbell,
+
+%Phys.\ Rev.\ B {\bf 68}, 180402R (2003).
 
@@
 
+%Unused bibitems
+
+%\bibitem{newman-1996}
+%C.~Newman and D.~L.~Stein, Phys.\ Rev.\ Lett.\ {\bf 76}, 515 (1996).
+%\bibitem{wilms-2012}
+%J.~Wilms, J.~Vidal, F.~Verstraete,and S.~Dusuel, J.\ Stat.\ Mech.\ (2012)P01023. 
+%
+%\bibitem{parisi-1980-a}
+%G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1887 (1980). 
+%\bibitem{huse-1987}
+%D.~S.~Fisher and D.~A.Huse, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L997 (1987).
+%\bibitem{wilms-2011}
+%J.~Wilms, M.~Troyer, and F.~Verstraete, J.\ Stat.\ Mech.\ (2011) P10011.
+%\bibitem{zaletel-2011}
+%M.~P.~Zaletel, J.~H.~Bardarson, and J.~E.~Moore, Phys.\ Rev.\ Lett.\ {\bf 107}, 
+%020402 (2011).
+%\bibitem{huse-1987-a}
+%D.~A.~Huse and D.~S.~Fisher, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L1005 (1987).
+%\bibitem{fisher-1988}
+%D.~S.~Fisher and D.~A.Huse, Phys.\ Rev. B {\bf 38}, 386 (1988).
+%\bibitem{parisi-1980-b}
+%G.~Parisi, J.\ Phys.\ A\ {\bf 13}, L115 (1980). 
+%\bibitem{fisher-1986}
+%D.~S.~Fisher and D.~A.~Huse, Phys.\ Rev.\ Lett.\ {\bf 56} 1601 (1986).
+%\bibitem{palassini-2000}
+%M.~Palassini and A.~P.~Young, Phys.\ Rev.\ Lett.\  {\bf 85}, 3017 (2000).
+%\bibitem{stephan-2010}
+%J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 82}, 125455 
+%(2010); 
+%\bibitem{stephan-2011}
+%J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 84}, 
+%195128 (2011).
+%\bibitem{stephan-2009}
+%J-M~St\'ephan, S.~Furukawa, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 80}, 
+%184421 (2009)
+%\bibitem{krzakala-2000}
+%F.~Krzakala and O.~C.~Martin, Phys.\ Rev.\ Lett.\ {\bf 85}, 3013 (2000).
 \end{document}

### 2015-06-12 sk_model_v15.tex
revised-3

@@
 paradigm model of mean-field spin glasses. 
-First, using classical Monte Carlo simulations and analytical tools we investigate the 
+Using classical Monte Carlo simulations and analytical tools we first investigate the 
 S-K model on the $n$-sheets booklet.
@@
 we provide the exact solution of the model exploiting the replica symmetry. This is the 
-permutation symmetry among the fictitious replicas that are used in the replica trick to 
-perform disorder averages. In the glassy phase the replica symmetry has to be broken. 
-Using a generalization of the celebrated Parisi solution, we provide approximated results 
-for $S_n$ and ${\mathcal I}_n$, and for standard thermodynamic quantities. Both $S_n$ 
-and ${\mathcal I}_n$ exhibit a volume law in the whole phase diagram. We characterize 
-analytically the behavior of the corresponding densities $S_n/N$ and ${\mathcal I}_n/N$, 
-in the thermodynamic limit. Remarkably, at the critical point ${\mathcal I}_n/N$ does not 
-exhibit any crossing for different system sizes, in contrast with local spin models.
+permutation symmetry among the fictitious replicas that are used to 
+perform disorder averages (via the replica trick). In the glassy phase the replica symmetry 
+has to be broken. Using a generalization of the celebrated Parisi solution, we provide 
+analytical results for $S_n$ and ${\mathcal I}_n$, and for standard thermodynamic quantities. 
+Both $S_n$ and ${\mathcal I}_n$ exhibit a volume law in the whole phase diagram. We fully 
+characterize the behavior of the corresponding densities $S_n/N$ and ${\mathcal I}_n/N$, 
+in the thermodynamic limit. Remarkably, at the critical point the mutual information does 
+not exhibit any crossing for different system sizes, in contrast with local spin models.
 
@@
 The last refers to the breaking of the permutation symmetry among the fictitious replicas 
-of the model, which are introduced to perform disorder averages (\emph{replica 
-trick}~\cite{cardy-book}). Finally, although the applicability of the S-K 
+of the model, which are introduced to perform disorder averages (via the so-called 
+\emph{replica trick}~\cite{cardy-book}). Finally, although the applicability of the S-K 
 model to describe realistic spin glasses is still highly debated~\cite{yucesoy-2012,
@@
 
-Recently, the study of the interplay between disorder and entanglement became a fruitful 
-research area~\cite{refael-2009}. However, the behavior of entanglement-related quantities 
-in glassy phases, and at glassy critical points, has not been explored yet (see 
+Although recently the study of the interplay between disorder and entanglement became a fruitful 
+research area~\cite{refael-2009}, the behavior of entanglement-related quantities 
+in glassy phases, and at glassy critical points, has not been explored yet (see, however,  
 Ref.~\onlinecite{castelnovo-2010} for some interesting results). Here we investigate 
@@
 We show that for any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, 
-which is divided by the standard paramagnetic one at high temperatures by a critical point. 
-Surprisingly, the critical temperature exhibits a non-trivial dependence on $\omega$ 
+which is divided by the standard paramagnetic one at high temperatures by a phase transition. 
+Surprisingly, the critical temperature exhibits a non trivial dependence on $\omega$ 
 that we are able to determine analytically. 
-In the high-temperature region the permutational symmetry among the replicas, both the 
+In the high-temperature region the permutation symmetry among the replicas, both the 
 physical and the fictitious ones, is preserved. This allows us to provide an exact analytic 
@@
 observed, reflecting the replica symmetry breaking. Remarkably, we observe that the one-step 
-replica symmetry breaking ($1$-RSB) result $S_2^{1\textrm{-}RSB}/N$ is in full agreement with 
+replica symmetry breaking ($1$-RSB) result $[S_2^{1\textrm{-}RSB}]/N$ is in full agreement with 
 the Monte Carlo data for $\beta\lesssim 3$, confirming what is observed for the internal 
@@
 Precisely, in subsection~\ref{para-section} we focus on the high-temperature 
-region, where this pproximation becomes exact. In subsection~\ref{rs-section} we discuss 
+region, where this approximation becomes exact. In subsection~\ref{rs-section} we discuss 
 the structure of the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} 
@@
 of both the RS and the $1$-RSB results comparing with Monte Carlo simulations for the 
-internal energy. Section~\ref{Renyi-section} and~\ref{I2-section} discuss the classical R\'enyi 
+internal energy. Section~\ref{Renyi-section} and section~\ref{I2-section} discuss the classical R\'enyi 
 entropy and the mutual information, respectively. Finally, we conclude in section~\ref{conclusions}.
@@
 Here $Z(A,n,\beta)$ is the partition function of the model on the $n$-sheet booklet, 
-whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures $\beta$. 
-The booklet geometry is illustrated in Fig.~\ref{cartoon}. 
-Each sheet is divided into two parts $A$ and $B$ (cf. Fig.~\ref{cartoon} (a)). Then $n$ copies 
-of the system are ``glued'' together to form the booklet. The spins in part $A$ of the different 
+whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures 
+$\beta$. The booklet geometry is illustrated in Fig.~\ref{cartoon}, and consists of 
+$n$ identical copies (``sheets'') of the system. Each sheet is divided into two 
+parts $A$ and $B$ (cf. Fig.~\ref{cartoon} (a)). The spins in part $A$ of the different 
 sheets are identified (cf. Fig.~\ref{cartoon} (b)). While spins in parts $B$ of the booklet 
@@
 and $[(J_{ij}-[J_{ij}])^2]=J^2/N$, respectively. The square brackets $[\cdot]$ denote 
-the average over different realinzations of $J_{ij}$.  Here we restrict ourselves to 
+the average over different realizations of $J_{ij}$.  Here we restrict ourselves to 
 $J_0=0$ and $J=1$. The factors $N$ in Eq.~\eqref{quenched-distr} ensure a well-defined 
@@
 in Eq.~\eqref{rep-Z}. Although the RS ansatz is correct at high temperatures, it 
-fails in the glassy phase at low temperatures, where the permutational invariance 
-within the replicas has to be broken~\cite{almeida-1978}. the celebrated Parisi 
+fails in the glassy phase at low temperatures, where the permutation invariance 
+within the replicas has to be broken~\cite{almeida-1978}. The celebrated Parisi 
 ansatz~\cite{parisi-1979} provides a systematic scheme to break the replica 
@@
 indices $\gamma,\gamma'$ and $r,r'$, i.e., the physical and fictitious 
-replica spaces. Using Eq~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, 
+replica spaces. Using Eq.~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, 
 after performing the analytic continuation $\alpha\to 0$, one obtains  
@@
 one has $q_0=1$ $\forall\beta$. For intermediate $0<\omega<1$, $q_0$ 
-is plotted as a function of $\omega$ in Fig.~\ref{RSB0_saddle}. For $\beta=0$ it 
+is plotted as a function of $\omega$ in Fig.~\ref{RSB0_saddle_ht}. For $\beta=0$ it 
 is $q_0=\omega$ (straight line in the Figure). In the low-temperature limit 
@@
 the model, at least around the paramagnetic-glassy transition (see section~\ref{mc-results} 
-for the comparision with Monte Carlo data).
+for the comparison with Monte Carlo data).
 
@@
 denotes the floor function. Notice that the off-diagonal elements of $q'$ (i.e., for 
-$\gamma\ne\gamma'$) do not depend on $r,r'$, meaning that, although the permutational 
+$\gamma\ne\gamma'$) do not depend on $r,r'$, meaning that, although the permutation 
 symmetry between the fictitious replicas is broken, the symmetry among the physical ones 
@@
 The behavior of $U/N$ for $\omega\ne1/2$ is investigated in Fig.~\ref{U-RS},
-plotting $U/N$ as a function of $\beta$ and $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
+plotting $U/N$ as a function of $\beta$ and for $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
 are the MC data extrapolated to the thermodynamic, at fixed $\omega$. Similar to Fig.~\ref{U-RS}, 
@@
 c/N^{\phi}$, with $\phi=2/3$ irrespective of $\omega$. The stars in Fig.~\ref{U-RS} are 
-the critical values $U_c/N$ at the paramagnetic-glassy transition. Specifically, here  
-$\beta_c$ is obtained by numerically solving Eq.~\eqref{tc}. The lines in Fig.~\ref{U-RS} 
+the critical values $U_c/N$ at the paramagnetic-glassy transition. The lines in Fig.~\ref{U-RS} 
 denote $U_{RS}$ (cf. Eq.~\eqref{U}). 
-At high temperature, and for generic $n$ and $\omega$, Eq.~\eqref{logZ-ht} and Eq.~\eqref{U-def} 
+Notice that at high temperature, and for generic $n$ and $\omega$, Eq.~\eqref{logZ-ht} and Eq.~\eqref{U-def} 
 give  
@@
 However, the RS result is not correct for $\beta>\beta_c$, where the replica symmetry breaking 
-has to be taken into account. The effects of the replica symmetry breaking are more carefully 
+has to be taken into account. This is  more carefully 
 discussed in Fig.~\ref{U-RSB-1}, focusing on the low temperature phase at $1\le\beta\le 2$. 
@@
 symmetry breaking result $[S_2^{1\textrm{-}RSB}]/N$ (see section~\ref{rsb-1-section}), 
-which is obtained from Eq.~\eqref{renyi}  Eq.~\eqref{RSB-1-logZ}. Remarkably, 
+which is obtained from Eq.~\eqref{renyi}  and Eq.~\eqref{RSB-1-logZ}. Remarkably, 
 $[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the Monte Carlo extrapolations 
@@
 are Monte Carlo data for $N=32,64,128$. In the high-temperature region $[{\mathcal I}_2]$ 
-exhibits a vanishing behavior. Finite size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
+exhibits a vanishing behavior. Moreover, finite size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
 it is straightforward to derive the high-temperature behavior of $[{\mathcal I}_n]$ as  
@@
 %
-Moreover, $[{\mathcal I}_2]/N$ increases upon lowering the temperature, up to $\beta\approx 1$, 
-where it exhibits a maximum. The height of this maximum decreases as a function of $\omega$. 
-Its position is not simply related to the paramagnetic-glassy transition in the standard S-K 
-model. This is not surprising as $[{\mathcal I}_n]$ is constructed by combining the partition 
-functions on booklets with different aspect ratios $\omega$, $1-\omega$, $\omega=0$, and 
-$\omega=1$ (cf. Eq.~\eqref{MI}), and the critical temperature of the paramagnetic-glassy 
-transition is a non trivial function of $\omega$ (see Fig.~\ref{beta_c}). Furthermore, the 
+Interestingly, $[{\mathcal I}_2]/N$ increases upon lowering the temperature 
+up to $\beta\approx 1$, where it exhibits a maximum. The height of this maximum 
+decreases as a function of $\omega$. We numerically observe that its position 
+is not simply related to the paramagnetic-glassy transition. 
+%This is not surprising as $[{\mathcal I}_n]$ is constructed by combining the partition 
+%functions on booklets with different aspect ratios $\omega$, $1-\omega$, $\omega=0$, and 
+%$\omega=1$ (cf. Eq.~\eqref{MI}), and the critical temperature of the paramagnetic-glassy 
+%transition is a non trivial function of $\omega$ (see Fig.~\ref{beta_c}). 
+Furthermore, the 
 data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. This is 
@@
 %
-where we fix $\phi''=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated} 
-(circles, squares, and triangles). Remarkably, the RS approximation (dash-dotted lines) is 
+where we fix $\phi''=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}.  
+Different symbols now correspond to different aspect ratios $\omega$. Remarkably, the RS 
+approximation (dash-dotted lines) is 
 in good agreement with the extrapolations up to $\beta\lesssim 1.5$, whereas deviations 
@@
 both $[S_2]/N$ and $[{\mathcal I}_2]/N$. We observed that at high temperature the 
-RS result fully agrees with the Monte Carlo simulations, whereas deviatios occur in the 
+RS result fully agrees with the Monte Carlo simulations, whereas deviations occur in the 
 glassy phase, signalling the replica symmetry breaking. Similar to the internal energy, 
@@
 results taking into account the full breaking of the replica symmetry, i.e., going beyond 
-the one-step replica symmetry breaking approximation. This would allow to reach a conclusion 
+the one-step replica symmetry breaking approximation. This would allow us to reach a conclusion 
 on the correctness of the replica symmetry breaking scheme that we used. Moreover, it 
@@
 $q_{\gamma\gamma'}^{rr'}$ (see section~\ref{replica-sec}). We restrict ourselves 
-zero magnetic field and to the $2$-sheets booklet (see Fig.~\ref{cartoon}). It is 
+to zero magnetic field and to the $2$-sheets booklet (see Fig.~\ref{cartoon}). It is 
 straightforward to generalize the calculation to the case with non zero magnetic 
@@
 on the plane, respectively (see Fig.~\ref{cartoon} and section~\ref{booklet} for the definitions).  
-There are a only few approaches to numerically calculate the the ratio of partition functions in 
+There are only few approaches to numerically calculate the the ratio of partition functions in 
 Eq.~\eqref{renyi-app}. For instance, a brute force numerical integration of the internal energy as 
@@
 \label{ratio-trick}
-\frac{Z(A,n,\beta)}{ Z^n(\beta)} = \prod_{i=0}^{N/4-1} \frac{Z(A_i,n,\beta)}{Z(A_{i+1},n,\beta)}
+\frac{Z(A,n,\beta)}{ Z^n(\beta)} = \prod_{i=0}^{N/4-1} \frac{Z(A_i,n,\beta)}{Z(A_{i+1},n,\beta)},
 \end{align}
@@
 Crucially, if the length of $A_i$ increases mildly with $i$, each term in the product 
-in the left hand side of~\eqref{ratio-trick} can be sampled efficiently in Monte 
-Carlo~\cite{stephan-2014}. Notice that a similar method has also been used in 
+in the left hand side of Eq.~\eqref{ratio-trick} can be sampled efficiently in Monte 
+Carlo~\cite{stephan-2014}. Notice that the same trick has also been used in 
 Ref.~\onlinecite{alba-2010,alba-2011,alba-2013}. More specifically, one can write
@@
 \end{align}
-%
 \end{enumerate}
-
+%
 This method is much faster than simply counting configurations as it allows 
@@
 %loop over $2 \cdot 2^4 = 32$ configurations.
-
 In our Monte Carlo simulations we calculate $Z(A_i,n,\beta)/Z(A_{i+1},n,\beta)$ 

### 2015-06-12 sk_model_v15.tex
revised-5

@@
 This is obtained by gluing together $n$ independent copies of the model, and it is the 
-main ingredient to construct the R\'enyi entaglement-related quantities. We find that at 
+main ingredient to construct the R\'enyi entanglement-related quantities. We find that at 
 low temperature the S-K model is in a glassy phase, whereas at high temperature it exhibits 
@@
 of the S-K model has been a mathematical challenge. Although it was proposed as an 
-ansatz by Parisi~\cite{parisi-1980} more than thirthy years ago, its rigourous proof 
+ansatz by Parisi~\cite{parisi-1980} more than thirty years ago, its rigorous proof 
 was obtained only recently~\cite{talagrand-2006}. Moreover, the solution exhibits several 
@@
 the fictitious replicas, preserving that among the physical ones. Although this appears 
-natural, we are not able to provide a rigourous proof that this is the correct symmetry 
+natural, we are not able to provide a rigorous proof that this is the correct symmetry 
 breaking pattern. In particular, we cannot exclude that the symmetry among the physical 
@@
 exhibits a maximum at infinite temperature, and it is a decreasing function of the temperature, 
-as expected. Finite-size corrections are neglegible at high temperatures, whereas they increase 
+as expected. Finite-size corrections are negligible at high temperatures, whereas they increase 
 upon lowering the temperature. In the paramagnetic phase we are able to determine the functional 
@@
 ansatz~\cite{parisi-1979} provides a systematic scheme to break the replica 
-symmetry in successive steps, and it allows to capture the the glassy behavior of 
+symmetry in successive steps, and it allows to capture the glassy behavior of 
 the S-K model at low temperature. We anticipate (see section~\ref{rsb-1-section} for 
@@
 
-In this section we go beyond the replica-ymmetric approximation, including some 
+In this section we go beyond the replica-symmetric approximation, including some 
 of the effects of the replica symmetry breaking. More specifically, 
@@
 Finally, since in the limit $\beta\to\infty$ all the physical replicas are in the same state, 
-one should expect that $u_\infty(\omega,\beta)\to n \tilde u_\infty$ (horizonthal line in 
+one should expect that $u_\infty(\omega,\beta)\to n \tilde u_\infty$ (horizontal line in 
 Fig.~\ref{U-MC}), with $\tilde u_{\infty}=-0.76321...$~\cite{parisi-1979,parisi-1983} the 
@@
 
-Here we focus on the behavior of the Renyi mutual information $[{\mathcal I}_2]$. 
+Here we focus on the behavior of the R\'enyi mutual information $[{\mathcal I}_2]$. 
 Similar to $[S_2]$, the mutual information exhibits the volume law $[{\mathcal I}_2]
@@
  The dash-dotted lines are the analytical results in the 
- replica-symmetric (RS) appproximation. The full symbols (rhombi) 
+ replica-symmetric (RS) approximation. The full symbols (rhombi) 
  are the results in the first-step replica-symmetry-breaking (1-RSB) 
@@
 replica symmetry has to be broken, similar to the standard S-K model. To take into account 
-the effects of the replica symmetry breaking we used a generalization of the the Parisi 
+the effects of the replica symmetry breaking we used a generalization of the Parisi 
 ansatz~\cite{parisi-1980}, i.e., breaking the replica symmetry in successive 
@@
 would be interesting to discuss the finite size-corrections to the saddle 
-point approximation. An interesting direction would be to investigate wheather the 
+point approximation. An interesting direction would be to investigate whether the 
 glassy behavior is reflected in the volume-law corrections to the classical R\'enyi 
@@
 field and to the $n$-sheets booklet. Specifically, here we provide the saddle point 
-equations obtained in both the replica-symmmetric (RS) (see section~\ref{rs-section}), 
+equations obtained in both the replica-symmetric (RS) (see section~\ref{rs-section}), 
 and the one-step replica symmetry breaking ($1$-RSB) approximation (see 
@@
 on the plane, respectively (see Fig.~\ref{cartoon} and section~\ref{booklet} for the definitions).  
-There are only few approaches to numerically calculate the the ratio of partition functions in 
+There are only few approaches to numerically calculate the ratio of partition functions in 
 Eq.~\eqref{renyi-app}. For instance, a brute force numerical integration of the internal energy as 
@@
 update scheme, such as standard Metropolis or cluster updates
-\item For the the spins living in $A_{i+1}-A_i$ calculate 
+\item For the spins living in $A_{i+1}-A_i$ calculate 
 %

### 2015-06-12 sk_model_v15.tex
revised-6

@@
  booklets with $N=32,64,128$ spins per sheet. The plus symbols are the numerical 
- extrapolations to the thermodynamic limit. The dash-dotted lines are the  
+ extrapolations to the thermodynamic limit. The inset in panel (a) shows 
+ $[S_2]/N$ at fixed $\beta=2$, plotted versus $N^{-2/3}$.The dotted line is 
+ a linear fit. In all the panels  the dash-dotted lines are the  
  analytical results in the replica-symmetry (RS) approximation. 
@@
 decreases as a function of $\omega$. We numerically observe that its position 
-is not simply related to the paramagnetic-glassy transition. 
-%This is not surprising as $[{\mathcal I}_n]$ is constructed by combining the partition 
-%functions on booklets with different aspect ratios $\omega$, $1-\omega$, $\omega=0$, and 
-%$\omega=1$ (cf. Eq.~\eqref{MI}), and the critical temperature of the paramagnetic-glassy 
-%transition is a non trivial function of $\omega$ (see Fig.~\ref{beta_c}). 
-Furthermore, the 
+is not simply related to the paramagnetic-glassy transition. Furthermore, the 
 data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. This is 
@@
 in $A_{i+1}-A_i$. 
-%We also gain some speed by calculating the weights in each replica seperately, 
-%and then recombining the results in a smart way, meaning that we only have to explicitly 
-%loop over $2 \cdot 2^4 = 32$ configurations.
 In our Monte Carlo simulations we calculate $Z(A_i,n,\beta)/Z(A_{i+1},n,\beta)$ 
@@
 Finally, we average over the disorder to obtain $[S_n(A)]$.
-%When calculating the mutual information
-%\begin{align}
-%I_{n}(A) = S_{n}(A) + S^*_{n}(N-A) - S_{n}(N)
-%\end{align}
-%we do this calculating for each specific realization of disorder, and then take the disorder average of this final quantity.
-%The star in $S^*$ denotes the fact that even though $A$ denotes the size of the region that is connected, due to disorder one must be careful which specific spins are in the region.
-%$S^*$ is defined in such a way that the connected spins in $S_{n}(A)$ and those in $S^*_{n}(N-A)$ contain every spin in the system exactly once.
-
-%For each disorder and each $\omega_i$ we create a simulation, and measure
-%\begin{align}
-%\frac{Z(\omega_i,\alpha,\beta)}{Z(\omega_{i+1},\alpha,\beta)} = \\
-%\frac{Z(\omega_i,\alpha,\beta)}{Z(\omega_{i-1},\alpha,\beta)}
-%\end{align}
-
-%Due to the infinite dimensional nature of the Sherrington-Kirkpatrick model, the calculation the R\'enyi mutual information is unable to exploit efficient methods that are available for finite dimensional systems [ref: JMS/Inglis].
-
-%where $A$ changes only slightly, and build up the full quantity by taking the product of many such measurements.
-%This method is usually referred to as the ratio trick, and in finite dimensional systems there are efficient ways to calculate this ratio\cite{stephan-2014}.
-%In an infinite dimensional system the only efficient way to use this method is to increase $A$ more slowly than typical.
-%For this study, $A$ is increased by only 4 sites at a time.
-
-%First, if we want to sample from $A=0$ (two disconnected systems) to $A=N$ (two fully connected systems), let us use the ratio trick to write
 
@@
 V.~Alba, J.\ Stat.\ Mech.\ (2013) P05013.
-
-%\bibitem{bouchaud-2003}
-
-%J.-P.~Bouchaud, F.~Krzakala, and O.~C.~Martin, Phys.\ Rev.\ B {\bf 68},
-
-%224404 (2003).
-
-%\bibitem{boettcher-2005}
-
-%S.~Boettcher: Eur.\ Phys.\ J.\ {\bf B46}, 501 (2005).
 

### 2015-06-13 sk_model_v15.tex
revised-8

@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/Renyi_MC_v2}
-\caption{ The classical disorder-averaged Renyi entropy per spin $[S_2(\omega)]/N$  
+\caption{ The classical disorder-averaged R\'enyi entropy per spin $[S_2(\omega)]/N$  
  in the S-K model on the $2$-sheets booklet with zero magnetic field: 

### 2015-06-16 sk_model_v15.tex
revised-9

@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/I2_extrapolated}
-\caption{ The classical mutual information per spin ${\mathcal I}_2/N$ 
+\caption{ The classical mutual information per spin $[{\mathcal I}_2]/N$ 
  in the SK model on the $2$-sheets booklet with zero magnetic field: 
- ${\mathcal I}_2$ plotted versus $\beta$. The symbols denote the 
+ $[{\mathcal I}_2]/N$ plotted versus $\beta$. The symbols denote the 
  Monte Carlo results extrapolated to the thermodynamic limit for 

### 2015-06-16 sk_model_v15.tex
revised-10

@@
 %
-From Fig~\ref{Renyi-MC} one has that the extrapolated MC data are in quantitative 
+From Fig.~\ref{Renyi-MC} one has that the extrapolated MC data are in quantitative 
 agreement with $[S_2^{RS}]/N$ for $\beta\lesssim 1.5$, whereas strong deviations are 
@@
 which is obtained from Eq.~\eqref{renyi}  and Eq.~\eqref{RSB-1-logZ}. Remarkably, 
-$[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the Monte Carlo extrapolations 
-for $\beta\lesssim 2$.
+$[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the extrapolated Monte Carlo 
+data for $\beta\lesssim 2$.
 
@@
 \bibitem{nishimori-book}
-H.~Nishimori, ``Statistical Physics of Spin Glasses and Information Processing'', 
+H.~Nishimori, \emph{Statistical Physics of Spin Glasses and Information Processing}, 
 Clarendon Press, Oxford (2001).
@@
 \bibitem{amico-2008}
-L. Amico, R. Fazio, A. Osterloh, and V. Vedral, Entanglement in Many-Body 
-Systems, Rev. Mod. Phys. {\bf 80}, 517 (2008).
+L. Amico, R. Fazio, A. Osterloh, and V. Vedral, Rev.\ Mod.\ Phys.\ {\bf 80}, 517 (2008).
 
 \bibitem{eisert-2009}
-J. Eisert, M. Cramer, and M. B. Plenio, Area laws for the entanglement 
-entropy - a review, Rev. Mod. Phys. {\bf 82}, 277 (2009).
+J. Eisert, M. Cramer, and M. B. Plenio, Rev.\ Mod.\ Phys.\ {\bf 82}, 277 (2009).
 
@@
 \bibitem{cc-rev}
-P.~Calabrese and J.~Cardy, Entanglement entropy and conformal field theory, 
-J.\ Phys.\ A {\bf 42} 504005 (2009).
+P.~Calabrese and J.~Cardy, J.\ Phys.\ A {\bf 42} 504005 (2009).
 
 \bibitem{holzhey-1994} C. Holzhey, F. Larsen, and F. Wilczek,
-Geometric and Renormalized Entropy in Conformal Field Theory,
 Nucl. Phys. B {\bf 424}, 443 (1994).
@@
 \bibitem{vidal-2003}
-G.~Vidal, J.~I.~Latorre, E.~Rico, and A.~Kitaev,
-Entanglement in quantum critical phenomena, Phys.\ Rev.\ Lett.\ 
-{\bf 90}, 227902 (2003). J.~I.~Latorre, E.~Rico, and G.~Vidal,
-Ground state entanglement in quantum spin chains, Quant.\ Inf.\ 
+G.~Vidal, J.~I.~Latorre, E.~Rico, and A.~Kitaev, Phys.\ Rev.\ Lett.\ 
+{\bf 90}, 227902 (2003). J.~I.~Latorre, E.~Rico, and G.~Vidal, Quant.\ Inf.\ 
 and\ Comp.\ {\bf 4}, 048 (2004).
@@
 \bibitem{calabrese-2004}
-P.~Calabrese and J.~Cardy, Entanglement entropy and quantum field theory,
-J.\ Stat.\ Mech.\ (2004) P06002. 
-P.~Calabrese and J.~Cardy, Entanglement entropy and quantum field theory: 
-a non-technical introduction, Int. J.\ Quant.\ Inf.\ {\bf 4}, 429 (2006).
+P.~Calabrese and J.~Cardy, J.\ Stat.\ Mech.\ (2004) P06002. 
+P.~Calabrese and J.~Cardy, Int. J.\ Quant.\ Inf.\ {\bf 4}, 429 (2006).
 

### 2015-06-23 sk_model_v16.tex
revised-23/06/2015

--- 2015-06-16 sk_model_v15.tex
@@
 %##########################################################################
-
 \section{Monte Carlo method to calculate the classical R\'enyi entropies}
@@
 Finally, we average over the disorder to obtain $[S_n(A)]$.
+
+%##########################################################################
+\section{The critical temperature}
+\label{binder}
+
+In this section we numerically determine the critical temperature $T_c$ of the 
+paramagnetic-glassy transition in the S-K model on the booklet. We restrict 
+ourselveses the $2$-sheets booklet with fixed aspect ratio (cf. Eq.~\eqref{a-ratio}) 
+$\omega=1/4$.
+
+Given two identical, i.e., with the same disorder realization, and independent 
+copies of the booklet, the overlap order parameter $q_i$ is defined as 
+%
+\begin{equation}
+q\equiv\frac{1}{2N}\sum\limits_{i}\langle S_i^{(r,1)}S_i^{(r,2)}\rangle,
+\end{equation}
+%
+where $S_i^{(r,1)}$ and $S_i^{(r,2)}$ are the spins living on the two copies 
+of the booklet and $r=1,2$ labels the booklet sheets in each copy. The 
+angular brackets $\langle\cdot\rangle$ denote the thermal average at 
+fixed disorder realization. 
+The overlap Binder cumulant $U_4$, which is defined as 
+%
+\begin{equation}
+U_4\equiv \frac{1}{2}\left(3-\frac{[\langle q^4\rangle]}{[\langle q^2\rangle]^2}
+\right)
+\end{equation}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\includegraphics*[width=0.87\linewidth]{./draft_figs/Binder}
+\caption{ 
+}
+\label{binder-fig}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2015-06-23 sk_model_v15.tex
23/06/2015

@@
 This is obtained by gluing together $n$ independent copies of the model, and it is the 
-main ingredient to construct the R\'enyi entanglement-related quantities. We find that at 
-low temperature the S-K model is in a glassy phase, whereas at high temperature it exhibits 
-paramagnetic behavior. Interestingly, the temperature of the paramagnetic-glassy 
-transition depends non-trivially on the geometry of the booklet. At high-temperatures 
-we provide the exact solution of the model exploiting the replica symmetry. This is the 
-permutation symmetry among the fictitious replicas that are used to 
-perform disorder averages (via the replica trick). In the glassy phase the replica symmetry 
-has to be broken. Using a generalization of the celebrated Parisi solution, we provide 
-analytical results for $S_n$ and ${\mathcal I}_n$, and for standard thermodynamic quantities. 
-Both $S_n$ and ${\mathcal I}_n$ exhibit a volume law in the whole phase diagram. We fully 
-characterize the behavior of the corresponding densities $S_n/N$ and ${\mathcal I}_n/N$, 
-in the thermodynamic limit. Remarkably, at the critical point the mutual information does 
-not exhibit any crossing for different system sizes, in contrast with local spin models.
+main ingredient to construct the R\'enyi entanglement-related quantities. We find a 
+glassy phase at low temperature, whereas at high temperature the model exhibits 
+paramagnetic behavior. The temperature of the paramagnetic-glassy transition depends 
+non-trivially on the geometry of the booklet. At high-temperatures we provide the exact 
+solution of the model exploiting the replica symmetry. This is the permutation symmetry 
+among the fictitious replicas that are used to perform disorder averages (via the replica 
+trick). In the glassy phase the replica symmetry has to be broken. Using a generalization 
+of the Parisi solution, we provide analytical results for $S_n$ and ${\mathcal I}_n$, 
+and for standard thermodynamic quantities. Both $S_n$ and ${\mathcal I}_n$ exhibit a 
+volume law in the whole phase diagram. We fully characterize the behavior of the 
+corresponding densities $S_n/N$ and ${\mathcal I}_n/N$, in the thermodynamic limit. 
+Interestingly, at the critical point the mutual information does not exhibit any 
+crossing for different system sizes, in contrast with local spin models.
 
@@
 of exotic behavior induced by disorder.
-While at any finite temperature disorder prevents the 
+While at any finite temperature disorder can prevent the 
 usual magnetic ordering, at low-enough temperatures these systems display a 
@@
 %
-Eq.~\eqref{renyi-intro} can also be used for quantum systems by interpreting $p_{i_A}$ as 
-the probability of finding part $A$ in the \emph{quantum} configuration $i_A$. In particular, 
-for $n=1$ Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
+Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by interpreting $p_{i_A}$ as 
+the probability of finding part $A$ in the \emph{quantum} configuration $i_A$. For $n=1$ 
+Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
 stephan-2014-a}. From $S_n(A)$, one defines the classical mutual information 
@@
 booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
-We show that for any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, 
-which is divided by the standard paramagnetic one at high temperatures by a phase transition. 
-Surprisingly, the critical temperature exhibits a non trivial dependence on $\omega$ 
-that we are able to determine analytically. 
-In the high-temperature region the permutation symmetry among the replicas, both the 
-physical and the fictitious ones, is preserved. This allows us to provide an exact analytic 
-expression for the free energy of the model and several derived quantities, such as the internal 
-energy. We compare our results with Monte Carlo simulations, finding perfect agreement. 
-Oppositely, we provide evidence that in the low-temperature phase the replica symmetry is  
-broken. For instance, we numerically observe that the replica-symmetric (RS) result for the 
-internal energy is systematically lower than the Monte Carlo data, as in the standard 
-S-K model~\cite{sherrington-1978-prl,sherrington-1978}. This discrepancy becomes larger 
-upon lowering the temperature.
+For any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, which is divided 
+by the standard paramagnetic one at high temperatures by a phase transition. The critical 
+temperature exhibits a non trivial dependence on $\omega$ that we are able to determine 
+analytically. In the high-temperature region the permutation symmetry among the replicas, 
+both the physical and the fictitious ones, is preserved. This allows us to provide an exact 
+analytic expression for the free energy of the model and several derived quantities, such as 
+the internal energy. We compare our results with Monte Carlo simulations, finding perfect 
+agreement. Oppositely, in the low-temperature phase the replica symmetry is broken. For 
+instance, we numerically observe that the replica-symmetric (RS) result for the internal 
+energy is systematically lower than the Monte Carlo data, as in the standard S-K 
+model~\cite{sherrington-1978-prl,sherrington-1978}. This discrepancy becomes larger upon 
+lowering the temperature.
 
@@
 natural, we are not able to provide a rigorous proof that this is the correct symmetry 
-breaking pattern. In particular, we cannot exclude that the symmetry among the physical 
-replicas has to be broken. As a consequence, our scheme should be regarded as an 
-approximation, and not as an exact solution. We restrict ourselves to the 
-one-level replica symmetry breaking ($1$-RSB). 
-Surprisingly, we observe that the $1$-RSB result for the internal energy is in 
-excellent agreement with the Monte Carlo data for  $\beta\lesssim 3$, whereas the RS 
-approximation fails already at $\beta\approx 1$. This suggests that the $1$-RSB ansatz 
+breaking pattern. As a consequence, our scheme should be regarded as an approximation, 
+and not as an exact solution. Moreover, we restrict ourselves to the one-level replica 
+symmetry breaking ($1$-RSB). Surprisingly, the $1$-RSB result for the internal energy 
+is in excellent agreement with the Monte Carlo data for  $\beta\lesssim 3$, whereas the 
+RS approximation fails already at $\beta\approx 1$. This suggests that the $1$-RSB ansatz 
 captures correctly some aspects of the replica symmetry breaking.
@@
 perfectly matches the Monte Carlo data. At low temperatures deviations from the RS result are 
-observed, reflecting the replica symmetry breaking. Remarkably, we observe that the one-step 
-replica symmetry breaking ($1$-RSB) result $[S_2^{1\textrm{-}RSB}]/N$ is in full agreement with 
-the Monte Carlo data for $\beta\lesssim 3$, confirming what is observed for the internal 
-energy.
+present, reflecting the replica symmetry breaking. Remarkably, the one-step replica symmetry 
+breaking ($1$-RSB) result $[S_2^{1\textrm{-}RSB}]/N$ is in full agreement with the Monte Carlo 
+data for $\beta\lesssim 3$, confirming what is observed for the internal energy.
 
@@
 both the infinite-temperature and the zero-temperature limits. Surprisingly, $[{\mathcal I}_2]/N$ 
-does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition.
-This is in striking contrast with local spin models~\cite{jaconis-2013}. Interestingly, for 
-any $\omega$, ${\mathcal I}_2/N$ exhibits a maximum for $\beta\approx 1$. However, the 
-position of this maximum is not simply related to the paramagnetic-glassy transition. Finally, 
-at high temperature $[{\mathcal I}_2]/N$ is described analytically by the RS result 
-$[{\mathcal I}_2]^{RS}/N$, whereas at low temperatures one has to include the effects of the 
-replica symmetry breaking. Similar to $[S_2]$, we observe that the $1$-RSB approximation 
-$[{\mathcal I}^{1\textrm{-}RSB}_2]/N$, is in good agreement with the Monte Carlo data 
-for $\beta\lesssim 3$.
+does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition, 
+in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, ${\mathcal I}_2/N$ 
+exhibits a maximum for $\beta\approx 1$. The position of this maximum is not simply 
+related to the paramagnetic-glassy transition. At high temperature $[{\mathcal I}_2]/N$ 
+is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$, whereas at low temperatures 
+one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
+approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$, is in good agreement with the Monte Carlo 
+data for $\beta\lesssim 3$.
 
@@
 the thermodynamic limit. Section~\ref{solution} is concerned with the RS approximation. 
-Precisely, in subsection~\ref{para-section} we focus on the high-temperature 
-region, where this approximation becomes exact. In subsection~\ref{rs-section} we discuss 
-the structure of the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} 
-is devoted to   the $1$-RSB approximation. In section~\ref{mc-results} we check the validity 
-of both the RS and the $1$-RSB results comparing with Monte Carlo simulations for the 
-internal energy. Section~\ref{Renyi-section} and section~\ref{I2-section} discuss the classical R\'enyi 
-entropy and the mutual information, respectively. Finally, we conclude in section~\ref{conclusions}.
+In subsection~\ref{para-section} we focus on the high-temperature region, where this 
+approximation becomes exact. In subsection~\ref{rs-section} we discuss the structure of 
+the RS ansatz in the low-temperature region. Section~\ref{rsb-1-section} is devoted to 
+the $1$-RSB approximation. In section~\ref{mc-results} we check the validity of both the 
+RS and the $1$-RSB results comparing with Monte Carlo simulations for the internal energy. 
+Section~\ref{Renyi-section} and section~\ref{I2-section} discuss the classical R\'enyi 
+entropy and the mutual information, respectively. We conclude in section~\ref{conclusions}.
 
@@
 Interestingly, for critical systems ${\mathcal G}_n$ depends only on the 
-geometry of $A$ and $B$, and it is universal. In particular, for conformally 
-invariant models ${\mathcal G}_n$ can be calculated using standard methods of 
-conformal field theory (CFT), and it allows to numerically 
-extract universal information about the CFT, such as the central 
-charge~\cite{stephan-2014}.
+geometry of $A$ and $B$, and it is universal. For conformally invariant models 
+${\mathcal G}_n$ can be calculated using standard methods of conformal field 
+theory (CFT), and it allows to numerically extract universal information 
+about the CFT, such as the central charge~\cite{stephan-2014}.
 
@@
 $N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
-In each ``sheet'' of the booklet all the sites are divided into two groups $A\equiv\{1,
-\dots, N_A\}$ and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ 
-sites, respectively. The spins living in part $A$ and different sheets are identified, 
-i.e., $\forall i\in A$ one has  
+In each ``sheet'' all the sites are divided into two groups $A\equiv\{1,\dots, N_A\}$ 
+and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ sites, 
+respectively. The spins living in part $A$ and different sheets are identified, i.e., 
+$\forall i\in A$ one has  
 %
@@
 At $\omega=0$ and $\omega=1$ the phase diagram of the S-K model in the 
-thermodynamic limit is well established~\cite{nishimori-book}. In particular, 
-at $\omega=0$ the model exhibits a standard paramagnetic phase in the high 
-temperature region, whereas at low temperatures a glassy phase is present, 
-with replica-symmetry breaking~\cite{nishimori-book}. The two phases are 
-divided by a second order phase transition at $\beta=\beta_c=1$. The phase 
-diagram for $\omega=1$ is the same, apart from the trivial redefinition
-$\beta\to n\beta$. We anticipate here (see section~\ref{rs-section}) that 
-a similar scenario holds for generic $\omega$. Specifically, the glassy 
+thermodynamic limit is well established~\cite{parisi-book,nishimori-book}. 
+At $\omega=0$ it exhibits a standard paramagnetic phase in the high temperature 
+region, whereas at low temperatures a glassy phase is present, with replica-symmetry 
+breaking. The two phases are divided by a second order phase transition at 
+$\beta=\beta_c=1$. The phase diagram for $\omega=1$ is the same, apart from the 
+trivial rescaling $\beta\to n\beta$. We anticipate here (see section~\ref{rs-section}) 
+that a similar scenario holds for generic $\omega$. Specifically, the glassy 
 replica-symmetry-broken phase at low temperatures survives for generic 
-$0<\omega<1$, while at high temperature the model is paramagnetic. The 
-critical point at $\beta=\beta_c(\omega)$, which marks the transition 
-between the two phases, is a nontrivial function of the booklet ratio 
-$\omega$ (see section~\ref{tc-section}).
+$0<\omega<1$, while at high enough temperature the model is paramagnetic. The 
+critical point, which marks the transition between the two phases, is a 
+nontrivial function of the booklet ratio $\omega$ (see section~\ref{tc-section}).
 
@@
 The disorder-averaged free energy $[F(\omega,n,\beta)]$ (cf. 
-Eq.~\eqref{free-energy}) is obtained, using the standard replica 
+Eq.~\eqref{free-energy}) of the model is obtained, using the standard replica 
 trick~\cite{cardy-book}, as  
@@
 % 
-It is natural to expect that for arbitrary $\beta\le\beta_c$, with 
+It is natural to expect that for finite $\beta\le\beta_c$, with 
 $\beta_c$ the critical temperature of the paramagnetic-glassy 
@@
 as in the paramagnetic phase (cf. section~\ref{para-section}), whereas 
-$q_0'-1\propto 1/\beta$, similar to the standard SK model~\cite{nishimori-book}.
+$q_0'-1\propto 1/\beta$.
 
@@
 one obtains a standard Landau theory. Thus, $\beta_c$ is obtained by imposing that the 
-coefficient of the quadratic term $q_0'^2$ changes sign. This leads to the equation 
+coefficient of the quadratic term $q_0'^2$ vanishes. This leads to the equation 
 %
@@
 In this section we go beyond the replica-symmetric approximation, including some 
-of the effects of the replica symmetry breaking. More specifically, 
-here we discuss the one-step replica symmetry breaking (1-RSB) approximation. 
-The overlap tensor $q_{\gamma\gamma'}^{rr'}$ now reads  
+of the effects of the replica symmetry breaking. More specifically, here we discuss 
+the one-step replica symmetry breaking (1-RSB) approximation. The overlap tensor 
+$q_{\gamma\gamma'}^{rr'}$ now reads  
 %
@@
 The effective interaction ${\mathcal L}_{1\textrm{-}RSB}$ (cf. Eq.~\eqref{mf-action}) 
-in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in 
-Eq.~\eqref{mf-action}. This yields  
+in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in Eq.~\eqref{mf-action}. 
+This yields  
 %
@@
 Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
-$\beta$, for $\omega=1/2$. The circles, squares, and triangles 
-are the MC results for different sizes, i.e., number of spins per sheet, $N=32,64,128$. 
-The vertical dotted line is the critical temperature $\beta_c\approx 0.6$ of 
-the paramagnetic-glassy transition (cf. Fig.~\ref{beta_c}). In the high-temperature 
-region finite size effects are small, and already for $N=64$ the MC data are indistinguishable 
-from the thermodynamic limit. Oppositely, stronger scaling corrections are visible in 
-the low-temperature phase at $\beta>\beta_c$. 
-The plus symbols in Fig.~\ref{U-MC} are the numerical extrapolations in the 
-thermodynamic limit. These are obtained by fitting the finite size MC data 
+$\beta$, for $\omega=1/2$. The circles, squares, and triangles are the MC results for 
+different sizes, i.e., number of spins per sheet, $N=32,64,128$. The vertical dotted line 
+is the critical temperature $\beta_c\approx 0.6$ of the paramagnetic-glassy transition 
+(cf. Fig.~\ref{beta_c}). In the high-temperature region finite-size effects are small, 
+and already for $N=64$ the MC data are indistinguishable from the thermodynamic limit 
+result. Oppositely, stronger scaling corrections are visible in the low-temperature phase at 
+$\beta>\beta_c$. The plus symbols in Fig.~\ref{U-MC} are the numerical extrapolations in 
+the thermodynamic limit. These are obtained by fitting the finite size MC data 
 to the ansatz $U/N=u_{\infty}(\omega,\beta)+c/N^{\phi}$, where 
@@
 Notice that already at $\beta\gtrsim 1$, $U_{RS}$ is incompatible with the data. 
-Moreover, these deviations increase upon lowering the temperature. This has to be 
-attributed to the replica symmetry breaking happening in the glassy phase. 
-Finally, since in the limit $\beta\to\infty$ all the physical replicas are in the same state, 
+These deviations increase upon lowering the temperature and  have  to be attributed 
+to the replica symmetry breaking happening in the glassy phase. Finally, since in 
+the limit $\beta\to\infty$ all the physical replicas are in the same state, 
 one should expect that $u_\infty(\omega,\beta)\to n \tilde u_\infty$ (horizontal line in 
@@
 c/N^{\phi}$, with $\phi=2/3$ irrespective of $\omega$. The stars in Fig.~\ref{U-RS} are 
-the critical values $U_c/N$ at the paramagnetic-glassy transition. The lines in Fig.~\ref{U-RS} 
-denote $U_{RS}$ (cf. Eq.~\eqref{U}). 
-Notice that at high temperature, and for generic $n$ and $\omega$, Eq.~\eqref{logZ-ht} and Eq.~\eqref{U-def} 
-give  
+the critical values $U_c/N$ at the paramagnetic-glassy transition, whereas the lines 
+are the analytical results (cf. Eq.~\eqref{U}). Notice that at high temperature, and for 
+generic $n$ and $\omega$, Eq.~\eqref{logZ-ht} and Eq.~\eqref{U-def} give  
 %
@@
 
-However, the RS result is not correct for $\beta>\beta_c$, where the replica symmetry breaking 
-has to be taken into account. This is  more carefully 
-discussed in Fig.~\ref{U-RSB-1}, focusing on the low temperature phase at $1\le\beta\le 2$. 
+However, from Fig.~\ref{U-RS} one has that the RS result is not correct for $\beta>\beta_c$, 
+where the replica symmetry breaking has to be taken into account. This is  more carefully 
+discussed in Fig.~\ref{U-RSB-1}, focusing on the low temperature region at $1\le\beta\le 2$. 
 The plus symbols and the lines are the same as in Fig.~\ref{U-RS}. The circles denote the 
@@
 is in good agreement with the Monte Carlo data, at least up to $\beta\approx 2$.
-This allows us to conclude that, although the 1-RSB ansatz (cf. Eq.~\eqref{q-rsb1}) 
-is not correct for $\beta\to\infty$, it captures some of the effects 
-of the replica symmetry breaking.
 
@@
 
-We now turn to discuss the behavior of the disorder-averaged classical R\'enyi entropies 
+We now turn to discuss the behavior of the classical R\'enyi entropies 
 (cf. Eq.~\eqref{renyi}). Here we restrict ourselves to the second R\'enyi 
@@
 to calculate $[S_2]$ are provided in Appendix~\ref{mc-method}. The different panels 
-correspond to the booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all panels the 
-triangles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins per sheet. 
-Clearly, finite size effects are present, which increase upon lowering 
+correspond to the booklet ratios $\omega=3/4,1/2,1/4$ (see Fig.~\ref{cartoon}). In all the 
+panels the triangles, squares, and rhombi correspond to booklets with $N=32,64,128$ spins 
+per sheet. Clearly, finite size effects are present, which increase upon lowering 
 the temperature, as expected. In order to obtain $[S_2]/N$ in the thermodynamic limit 
@@
 
-The dash-dotted line denotes the analytical result $[S_2^{RS}]$ obtained within the RS 
-approximation (see section~\ref{rs-section}). More precisely, $[S_2^{RS}]/N$ is obtained 
+The dash-dotted line in the Figure denotes the analytical result $[S_2^{RS}]$ obtained within 
+the RS approximation (see section~\ref{rs-section}). More precisely, $[S_2^{RS}]/N$ is obtained 
 from Eq.~\eqref{renyi} and the expression for the free energy $[F_{RS}]$ (cf. Eq.~\eqref{rs-F}). 
@@
 Similar to $[S_2]$, the mutual information exhibits the volume law $[{\mathcal I}_2]
-\propto N$. This is in contrast with local models, where $[{\mathcal I}_n]$ for any 
-$n$ by construction obeys an area law at all temperatures. Here we consider the 
+\propto N$. This is in contrast with local models, where $[{\mathcal I}_n]$, for any 
+$n$, by construction obeys an area law at all temperatures. Here we consider the 
 mutual information per spin $[{\mathcal I}_2]/N$.
@@
 are Monte Carlo data for $N=32,64,128$. In the high-temperature region $[{\mathcal I}_2]$ 
-exhibits a vanishing behavior. Moreover, finite size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
+exhibits a vanishing behavior. Moreover, finite-size effects are ``small''. Using Eq.~\eqref{logZ-ht} 
 it is straightforward to derive the high-temperature behavior of $[{\mathcal I}_n]$ as  
@@
 %
-Interestingly, $[{\mathcal I}_2]/N$ increases upon lowering the temperature 
-up to $\beta\approx 1$, where it exhibits a maximum. The height of this maximum 
-decreases as a function of $\omega$. We numerically observe that its position 
-is not simply related to the paramagnetic-glassy transition. Furthermore, the 
-data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. This is 
-in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ exhibits a 
+$[{\mathcal I}_2]/N$ increases upon lowering the temperature up to $\beta\approx 1$, where 
+it exhibits a maximum. The height of this maximum decreases as a function of $\omega$. 
+One should stress that its position is not simply related to the paramagnetic-glassy transition. 
+Furthermore, the data for $[{\mathcal I}_2]/N$ at different system sizes do not exhibit any crossing. 
+This is in sharp contrast with local models~\cite{jaconis-2013}, where ${\mathcal I}_n/L$ exhibits a 
 crossing at a second order phase transition. The dash-dotted line in Fig.~\ref{I2-MC} is the 
@@
 Different symbols now correspond to different aspect ratios $\omega$. Remarkably, the RS 
-approximation (dash-dotted lines) is 
-in good agreement with the extrapolations up to $\beta\lesssim 1.5$, whereas deviations 
-occur at lower temperatures (not shown in the figure). 
+approximation (dash-dotted lines) is in good agreement with the extrapolations up to $\beta\lesssim 1.5$, 
+whereas deviations occur at lower temperatures (not shown in the figure). 
 For $\omega=1/8$, the numerical results exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
@@
 ${\mathcal I}_n$ in the Sherrington-Kirkpatrick (S-K) model, which is the paradigm model 
-of mean-field spin glasses. We focused on the quenched 
-averages $[S_n]$ and $[{\mathcal I}_n]$, with the brackets $[\cdot]$ denoting the average 
-over different disorder realizations. Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ 
-were obtained from suitable combinations of the partition functions of the S-K model on the 
-$n$-sheets booklet (cf. Fig.~\ref{cartoon}). This is constructed by ``gluing'' together 
-$n$ independent replicas (``sheets'') of the model. On each replica the spins are 
-divided into two groups $A$ and $B$, containing $N_A$ and $N_B$ spins respectively. The 
-spins in part $A$ of the different sheets are identified. Due to the mean-field nature of 
-the model, physical quantities depend on the bipartition only through the aspect ratio 
-$\omega\equiv N_A/N$.
+of mean-field spin glasses. We focused on the quenched averages $[S_n]$ and $[{\mathcal I}_n]$. 
+Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ were obtained from suitable combinations 
+of the partition functions of the S-K model on the $n$-sheets booklet (cf. Fig.~\ref{cartoon}). 
+This is constructed by ``gluing'' together $n$ independent replicas (``sheets'') of the model. 
+On each replica the spins are divided into two groups $A$ and $B$, containing $N_A$ and $N_B$ 
+spins respectively. The spins in part $A$ of the different sheets are identified. Due to the 
+mean-field nature of the model, physical quantities depend on the bipartition only through the 
+aspect ratio $\omega\equiv N_A/N$.
 
@@
 We first investigated the phase diagram of the S-K model on the $2$-sheets booklet as a 
-function of $\omega$ and the inverse temperature $\beta$. We considered the situation 
+function of $\omega$, and the inverse temperature $\beta$. We considered the situation 
 without external magnetic field ($h=0$ in Eq.~\eqref{SK-intro}). For any $\omega$, in the 
@@
 a standard paramagnetic one at high temperature. The two phases are divided 
-by a phase transition, as in the S-K model on the plane. Interestingly, the critical 
-temperature exhibits a non-trivial dependence on $\omega$ that we determined analytically. 
-We fully characterized the high-temperature phase of the model using the replica-symmetric 
-(RS) approximation. Specifically, we provided the exact analytical expression for the 
-disorder-averaged free energy $[F_{para}(\omega,n,\beta)]$  (cf. Eq.~\eqref{ht-logZ}) in 
-the thermodynamic limit. On the other hand, we observed that in the glassy phase the 
-replica symmetry has to be broken, similar to the standard S-K model. To take into account 
-the effects of the replica symmetry breaking we used a generalization of the Parisi 
-ansatz~\cite{parisi-1980}, i.e., breaking the replica symmetry in successive 
-steps. We restricted ourselves to the one-step replica symmetry breaking ($1$-RSB),   
-providing the exact expression for the disorder-averaged free energy $F_{1\textrm{-}RSB}
-(\omega,n,\beta)$ (cf. Eq.~\eqref{RSB-1-logZ}).
-
-Finally, we compared our analytical results with Monte Carlo simulations, focusing on the 
-internal energy per spin $U(\omega,n,\beta)/N$. In the high-temperature region, where the 
-replica symmetry is not broken, we observed perfect agreement with the replica-symmetric 
-result $U_{RS}/N$, for any $\omega$. In the glassy phase at low temperature, we found 
-significant deviations from $U_{RS}$ already at $\beta\approx 1$. On the other hand,  
-the one-step replica-symmetry-broken approximation $U_{1\textrm{-}RSB}/N$ matched the 
-Monte Carlo data for $\beta\lesssim 3$.
+by a phase transition, as in the S-K model on the plane. The critical temperature exhibits 
+a non-trivial dependence on $\omega$ that we determined analytically. We fully characterized 
+the high-temperature phase of the model using the replica-symmetric (RS) ansatz. Specifically, 
+we provided the exact analytical expression for the disorder-averaged free energy 
+$[F_{para}(\omega,n,\beta)]$  (cf. Eq.~\eqref{ht-logZ}) in the thermodynamic limit. In the 
+glassy phase the replica symmetry has to be broken, similar to the standard S-K model. To take 
+into account the effects of the replica symmetry breaking we used a generalization of the 
+Parisi ansatz~\cite{parisi-1980}, i.e., breaking the replica symmetry in successive steps. 
+We restricted ourselves to the one-step replica symmetry breaking ($1$-RSB), providing the 
+exact expression for the disorder-averaged free energy $F_{1\textrm{-}RSB}(\omega,n,\beta)$ 
+(cf. Eq.~\eqref{RSB-1-logZ}).
+
+We compared our analytical results with Monte Carlo simulations, focusing on the internal 
+energy per spin $U(\omega,n,\beta)/N$. In the high-temperature region, where the replica 
+symmetry is not broken, the Monte Carlo data are in perfect agreement with the replica-symmetric 
+result $U_{RS}/N$, for any $\omega$. In the glassy phase at low temperature, significant 
+deviations from $U_{RS}$ can be observed already at $\beta\approx 1$. On the other hand, 
+the one-step replica-symmetry-broken approximation $U_{1\textrm{-}RSB}/N$ accurately matches 
+the Monte Carlo data for $\beta\lesssim 3$.
 
 Finally, we discussed the behavior of $[S_2]$ and $[{\mathcal I}_2]$. Due to the mean-field 
-nature of the S-K model we observed the volume laws $[S_2]\propto N$ and 
-$[{\mathcal I}_2]\propto N$, for any $\beta$. We considered the densities 
-$[S_2]/N$ and $[{\mathcal I}_2]/N$. Using the replica-symmetric (RS) and the one-step 
-replica symmetry breaking ($1$-RSB) approximations we provided analytical results for 
-both $[S_2]/N$ and $[{\mathcal I}_2]/N$. We observed that at high temperature the 
+nature of the S-K model one has the volume laws $[S_2]\propto N$ and $[{\mathcal I}_2]\propto N$, 
+for any $\beta$. We considered the densities $[S_2]/N$ and $[{\mathcal I}_2]/N$. Using the 
+replica-symmetric (RS) and the one-step replica symmetry breaking ($1$-RSB) approximations we 
+provided analytical results for both $[S_2]/N$ and $[{\mathcal I}_2]/N$. At high temperature the 
 RS result fully agrees with the Monte Carlo simulations, whereas deviations occur in the 
 glassy phase, signalling the replica symmetry breaking. Similar to the internal energy, 
-we found that the $1$-RSB approximation fully matches the Monte Carlo data for $\beta\approx 3$.
-Interestingly, we numerically observed that at the critical point ${\mathcal I}_2/N$ 
-does not show any crossing for different system sizes, in contrast with local 
-models~\cite{jaconis-2013}.
+the $1$-RSB approximation fully matches the Monte Carlo data for $\beta\approx 3$.
+Interestingly, at the critical point ${\mathcal I}_2/N$ does not show any crossing for 
+different system sizes, in contrast with local models~\cite{jaconis-2013}.
 
@@
 results taking into account the full breaking of the replica symmetry, i.e., going beyond 
-the one-step replica symmetry breaking approximation. This would allow us to reach a conclusion 
-on the correctness of the replica symmetry breaking scheme that we used. Moreover, it 
-would be interesting to discuss the finite size-corrections to the saddle 
-point approximation. An interesting direction would be to investigate whether the 
-glassy behavior is reflected in the volume-law corrections to the classical R\'enyi 
-entropies. Finally, it would be interesting to extend our results to {\it quantum} spin 
-systems exhibiting glassy behavior and replica symmetry breaking~\cite{read-1995,
+the one-step replica symmetry breaking approximation. This would allow us to reach a 
+conclusion on the correctness of the replica symmetry breaking scheme that we used. Moreover, 
+it would be interesting to discuss the finite size-corrections to the saddle point 
+approximation. An intriguing direction would be to investigate whether the glassy 
+physics is reflected in the volume-law corrections to the classical R\'enyi entropies 
+and mutual information. Finally, it would be interesting to extend our results to {\it quantum} 
+spin systems exhibiting glassy behavior and replica symmetry breaking~\cite{read-1995,
 andreanov-2012}.
 
+%##########################################################################
 \section{Acknowledgements}
-We would like to thank Pasquale Calabrese for useful discussions. V.A.  acknowledge 
-financial support by the ERC under Starting Grant 279391 EDEQS. 
-[Stephen's grant under Lode?]
-
+We would like to thank Pasquale Calabrese for useful discussions. V.A.  acknowledges  
+financial support from the ERC under Starting Grant 279391 EDEQS. S.I. and L.P. 
+acknowledge support  from the  FP7/ERC Starting Grant No. 306897.
+
+%##########################################################################
 \appendix
@@
 straightforward to generalize the calculation to the case with non zero magnetic 
-field and to the $n$-sheets booklet. Specifically, here we provide the saddle point 
-equations obtained in both the replica-symmetric (RS) (see section~\ref{rs-section}), 
-and the one-step replica symmetry breaking ($1$-RSB) approximation (see 
-section~\ref{rsb-1-section}).
+field and to the $n$-sheets booklet. Here we provide the saddle point equations 
+for both the replica-symmetric (RS) (see section~\ref{rs-section}) and the one-step 
+replica symmetry breaking ($1$-RSB) approximations (see section~\ref{rsb-1-section}).
 
@@
 parameters $q_0,q_0'\in\mathbb{R}$ (cf. Eq.~\eqref{rs-ansatz}). The saddle point 
-equations are easily derived from the RS approximation for the free energy $[F_{RS}
+equations are derived from the RS approximation for the free energy $[F_{RS}
 (\omega,n,\beta)]$ (cf. Eq.~\eqref{rs-F}) as $\nabla_{\mathbf{q}}[F_{RS}(\omega,2,
 \beta)]=0$, where $\mathbf{q}\equiv(q_0,q_0')$, and $\nabla_{\mathbf{q}}\equiv
-\partial/\partial\mathbf{q}$. A straightforward calculation gives the two equations 
+\partial/\partial\mathbf{q}$. A straightforward calculation gives 
 %
@@
 
-Here we directly calculate the ratio of partition functions in Eq.~\eqref{renyi-app} using the 
-so-called \emph{ratio trick}. In the ratio trick one splits the subsystem $A$ as $A=\sum_{i}A_i$, 
-where $A_i$ is a sequence of subsystems such that $A_i\subset A_{i+1}$. 
-Then one writes 
+Here we directly measure the ratio of partition functions using the so-called \emph{ratio trick}. In 
+the ratio trick one splits the subsystem $A$ as $A=\sum_{i}A_i$, where $A_i$ is a sequence of subsystems 
+such that $A_i\subset A_{i+1}$. Then one writes 
 %
@@
 \label{sub-choice}
-A_i = 4i,\quad i \in [0,N/4] .
+A_i = 4i,\quad i \in [0,N/4].
 \end{align}
@@
 \begin{align}
-\frac{Z(A_i,n,\beta)}{Z(A_{j},n,\beta)} = \frac{T_{j\rightarrow i}}{T_{i\rightarrow j}}
+\frac{Z(A_i,n,\beta)}{Z(A_{j},n,\beta)} = \frac{T_{j\rightarrow i}}{T_{i\rightarrow j}}, 
 \end{align}
@@
 where $T_{i\rightarrow j}$  is the (Monte Carlo) transition probability from a spin 
-configuration living on the booklet with $A=A_i$ to a spin configuration living on the 
-booklet with $A=A_j$. Notice that spins in region $A$ of different sheets are identified 
-(cf. Eq.~\eqref{book-constraint}). Clearly, if $j<i$ one has $T_{i\rightarrow j}=1$.
+configuration living on the booklet with subregion $A=A_i$ to a spin configuration living 
+on the booklet with $A=A_j$. Notice that spins in region $A$ of different sheets are 
+identified (cf. Eq.~\eqref{book-constraint}). Clearly, if $j<i$ one has $T_{i\rightarrow j}=1$.
 When $j>i$ a naive method to determine $T_{i\rightarrow j}$ would be to simply count the 
@@
 In the following we provide a more efficient scheme to calculate $T_{i\rightarrow j}$.
-
 To summarize, our approach for calculating the ratio of partition functions in 
 Eq.~\eqref{ratio-trick} consists of four steps:
+%
 \begin{enumerate}
@@
 update scheme, such as standard Metropolis or cluster updates
-\item For the spins living in $A_{i+1}-A_i$ calculate 
+\item For the spins living in the set difference $A_{i+1}\setminus A_i$ calculate 
 %
@@
 Here (cf. Eq.~\eqref{sub-choice}) $i$ runs over all the $n2^4$ configurations of the 
-four spins in $A_{i+1}-A_i$, and $E_i$ is the energy associated with configuration $i$. 
+four spins in $A_{i+1}\setminus A_i$, and $E_i$ is the energy associated with 
+the spin configuration $i$. 
 \item Calculate the quantity
+%
 \begin{align}
-W_b = \sum_j e^{-\beta E_j}
+W_b = \sum_j e^{-\beta E_j}.
 \end{align}
-where $j$ runs over all the $2^4$ configurations with the four spins living in $A_{i+1}-
-A_i$ and different sheets are identified.
+%
+As in step $2$, $j$ runs over all the $n2^4$ configurations of the four spins living 
+in $A_{i+1}\setminus A_i$, but the spins living on different sheets are identified.
 \item Calculate the transition probability $T_{i\rightarrow i+1}$ as
@@
 This method is much faster than simply counting configurations as it allows 
-us to integrate over all possible configurations of the spins in $A_{i+1}-A_i$, 
+us to integrate over all possible configurations of the spins in $A_{i+1}\setminus A_i$, 
 treating the remaining ones as a bath that is updated by the regular Monte Carlo update. 
 The computational cost of this procedure grows exponentially with the number of spins 
-in $A_{i+1}-A_i$. 
+in $A_{i+1}\setminus A_i$. 
 In our Monte Carlo simulations we calculate $Z(A_i,n,\beta)/Z(A_{i+1},n,\beta)$ 

### 2015-06-23 sk_model_v15.tex
23/06/2015

@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/I2_extrapolated}
-\caption{ The classical mutual information per spin $[{\mathcal I}_2]/N$ 
- in the SK model on the $2$-sheets booklet with zero magnetic field: 
+\caption{The classical mutual information per spin $[{\mathcal I}_2]/N$ 
+ in the S-K model on the $2$-sheets booklet with zero magnetic field: 
  $[{\mathcal I}_2]/N$ plotted versus $\beta$. The symbols denote the 
@@
 \begin{align}
-T_{i \rightarrow i+1} = \Bigl< \frac{W_b}{W_a} \Bigr>.
+T_{i \rightarrow i+1} = \Bigl< \frac{W_b}{W_a} \Bigr>,
 \end{align}
@@
 %
+where the angular brackets denote the Monte Carlo average. 
 This method is much faster than simply counting configurations as it allows 
@@
 
+%##########################################################################
 \begin{thebibliography}{99}

### 2015-06-24 sk_model_v15.tex
Stephen's edit

@@
 paradigm model of mean-field spin glasses. 
-Using classical Monte Carlo simulations and analytical tools we first investigate the 
+Using classical Monte Carlo simulations and analytical tools we investigate the 
 S-K model on the $n$-sheets booklet.
@@
 glassy phase at low temperature, whereas at high temperature the model exhibits 
-paramagnetic behavior. The temperature of the paramagnetic-glassy transition depends 
+paramagnetic behavior, consistent with the regular S-K model. The temperature 
+of the paramagnetic-glassy transition depends 
 non-trivially on the geometry of the booklet. At high-temperatures we provide the exact 
-solution of the model exploiting the replica symmetry. This is the permutation symmetry 
+solution of the model by exploiting the replica symmetry. This is the permutation symmetry 
 among the fictitious replicas that are used to perform disorder averages (via the replica 
 trick). In the glassy phase the replica symmetry has to be broken. Using a generalization 
-of the Parisi solution, we provide analytical results for $S_n$ and ${\mathcal I}_n$, 
+of the Parisi solution, we provide analytical results for $S_n$, ${\mathcal I}_n$, 
 and for standard thermodynamic quantities. Both $S_n$ and ${\mathcal I}_n$ exhibit a 
@@
 of the model, which are introduced to perform disorder averages (via the so-called 
-\emph{replica trick}~\cite{cardy-book}). Finally, although the applicability of the S-K 
+\emph{replica trick}~\cite{cardy-book}, not to be confused with the replica trick used in calculating the R\'enyi entanglement entropies). Finally, although the applicability of the S-K 
 model to describe realistic spin glasses is still highly debated~\cite{yucesoy-2012,
@@
 an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
-definition). This consists of $n$ independent and identical replicas (the 
+definition) using another \emph{replica trick}\cite{nakagawa-2009,buividovich-2008}. This consists of $n$ independent and identical replicas (the 
 booklet ``sheets'') of the model. These \emph{physical} replicas are different 
@@
 %
-Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by interpreting $p_{i_A}$ as 
-the probability of finding part $A$ in the \emph{quantum} configuration $i_A$. For $n=1$ 
-Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
+Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems 
+by replacing the sum over the probabilities of each state in region $A$ with the trace over the 
+reduced density matrix for region $A$.
+For $n=1$ Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
 stephan-2014-a}. From $S_n(A)$, one defines the classical mutual information 
@@
 \propto\ell$, with $\ell$ the length of the boundary between $A$ and $B$. Remarkably, 
-for different $\ell$, the ratio ${\mathcal I}_n/\ell$ exhibits a crossing at a second 
+for different $\ell$, the ratio ${\mathcal I}_n/\ell$ has been shown to exhibit a crossing at a second 
 order phase transition~\cite{jaconis-2013}, implying that it can be used as a diagnostic 
@@
  As a consequence, the effective temperature in part $A$ is $n\beta$. 
- $Z(A,n,\beta)$ denotes the partition function of the S-K model on 
+ $Z(\omega,n,\beta)$ denotes the partition function of the S-K model on 
  the booklet. 
@@
 breaking ($1$-RSB) result $[S_2^{1\textrm{-}RSB}]/N$ is in full agreement with the Monte Carlo 
-data for $\beta\lesssim 3$, confirming what is observed for the internal energy.
+data for $\beta\lesssim 3$, consistent with what is observed for the internal energy.
 
@@
 does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition, 
-in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, ${\mathcal I}_2/N$ 
+in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, $[{\mathcal I}_2]/N$ 
 exhibits a maximum for $\beta\approx 1$. The position of this maximum is not simply 
@@
 one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
-approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$, is in good agreement with the Monte Carlo 
+approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ is in good agreement with the Monte Carlo 
 data for $\beta\lesssim 3$.
@@
 i.e., $n$ disconnected sheets, one has $Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with 
-$Z(\beta,\{J\})$ the partition function of the S-K model on the plane. On the other hand, 
+$Z(\beta,\{J\})$ the partition function of the S-K model on the plane (i.e. the original S-K model). On the other hand, 
 for $\omega=1$ it is $Z(1,n,\beta,\{J\})=Z(n\beta,\{J\})$, i.e., the partition function 
@@
 replicas introduced in Eq.~\eqref{replica-trick}, whereas $r$ denote the 
-physical replicas, as in Eq.~\eqref{book-pf}. Clearly, physical and fictitious 
+physical replicas, as in Eq.~\eqref{book-pf}. Again, both the physical and fictitious 
 replicas do not interact. Notice that $Z^{\alpha}(\omega,n,\beta)$ can be 
@@
 $\omega\to 1$. Also, in the zero-temperature limit $\beta\to\infty$ one has 
-that $q_0\to 1$ and $q_0'\to 1$, for any $\omega$. Moreover, a simple calculation 
+that $q_0\to 1$ and $q_0'\to 1$, for any $\omega$. Moreover, expansion 
 yields  
@@
  transition for the S-K model on the $2$-sheets booklet (see Fig.~\ref{cartoon}) 
- with zero magnetic field: $\beta_c$ as a function of the booklet ratio $\omega
+ with zero magnetic field from Eq.~\eqref{tc}: $\beta_c$ as a function of the booklet ratio $\omega
  \equiv N_A/N$. Here $\beta_c$  is obtained from the replica-symmetric (RS) 
@@
  as a function of inverse temperature $\beta$. The plus symbols are the same 
- Monte Carlo data as in Fig.~\ref{U-RS}. The lines denote $U/N$ 
+ extrapolated Monte Carlo data as in Fig.~\ref{U-RS}. The lines denote $U/N$ 
  in the replica-symmetric (RS) approximation (same as in Fig.~\ref{U-RS}). 
@@
 there is no well defined boundary between the two parts $A$ and $B$ of the system 
-(unlike in local spin models). This suggests the volume-law behavior $[S_2]\propto N$ 
-for all temperatures. Thus, it is natural to consider the entropy per spin 
-$[S_2]/N$.
+(unlike in local spin models). With this in mind we assume that we will find
+volume-law behavior $[S_2]\propto N$ for all temperatures, and consider the entropy per spin 
+$[S_2]/N$ as the quantity of interest.
 
@@
 \begin{equation}
-[S^{RS}_2]=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^3).
+\frac{[S^{RS}_2]}{N}=\omega\log(2)-\frac{\beta^2}{4}\omega^2+{\mathcal O}(\beta^3).
 \end{equation}
@@
 $[{\mathcal I}_2]/N$ increases upon lowering the temperature up to $\beta\approx 1$, where 
-it exhibits a maximum. The height of this maximum decreases as a function of $\omega$. 
+it exhibits a maximum.
 One should stress that its position is not simply related to the paramagnetic-glassy transition. 
@@
 Here we directly measure the ratio of partition functions using the so-called \emph{ratio trick}. In 
-the ratio trick one splits the subsystem $A$ as $A=\sum_{i}A_i$, where $A_i$ is a sequence of subsystems 
-such that $A_i\subset A_{i+1}$. Then one writes 
+the ratio trick one splits the subsystem $A$ in a set of subsystems $A_i$ such that $A_i\subset A_{i+1}$ and the largest subsystem in the set is simply $A$ itself. Then one writes 
 %
@@
 Crucially, if the length of $A_i$ increases mildly with $i$, each term in the product 
-in the left hand side of Eq.~\eqref{ratio-trick} can be sampled efficiently in Monte 
+in the right hand side of Eq.~\eqref{ratio-trick} can be sampled efficiently in Monte 
 Carlo~\cite{stephan-2014}. Notice that the same trick has also been used in 
@@
 \begin{align}
-W_a = \sum_i e^{-\beta E_i}.
+W_a = \prod_n \sum_{i_n} e^{-\beta E_{i_n}}.
 \end{align}
 %
-Here (cf. Eq.~\eqref{sub-choice}) $i$ runs over all the $n2^4$ configurations of the 
-four spins in $A_{i+1}\setminus A_i$, and $E_i$ is the energy associated with 
-the spin configuration $i$. 
+Here (cf. Eq.~\eqref{sub-choice}) $i$ runs over all the $2^4$ configurations of the 
+four spins in $A_{i+1}\setminus A_i$ for each of the $n$ sheets, and $E_i$ is the energy associated with 
+the spin configuration $i$ of a single sheet.
 \item Calculate the quantity
@@
 %
-As in step $2$, $j$ runs over all the $n2^4$ configurations of the four spins living 
-in $A_{i+1}\setminus A_i$, but the spins living on different sheets are identified.
+As in step $2$, $j$ runs over all the $2^4$ configurations of the four spins living 
+in $A_{i+1}\setminus A_i$, but since the spins living on different sheets are identified
+there are only $2^4$ configurations in total and the energy $E_j$ is that of all $n$ sheets together.
 \item Calculate the transition probability $T_{i\rightarrow i+1}$ as
@@
 V.~Alba, J.\ Stat.\ Mech.\ (2013) P05013.
+
+\bibitem{nakagawa-2009}
+Y.~Nakagawa, A.~Nakamura, S.~Motoki, and V.~Zakharov (2009), arXiv:0911.2596
+
+\bibitem{buividovich-2008}
+P.~Buividovich and M.~Polikarpov, Nuc.\ Phys.\ B {\bf 802}, 458 (2008)
 

### 2015-06-27 sk_model_v17.tex
revised-27/06/2015

--- 2015-06-24 sk_model_v15.tex
@@
 glassy phase at low temperature, whereas at high temperature the model exhibits 
-paramagnetic behavior, consistent with the regular S-K model. The temperature 
-of the paramagnetic-glassy transition depends 
+paramagnetic behavior, consistent with the regular S-K model. The temperature of the 
+paramagnetic-glassy transition depends 
 non-trivially on the geometry of the booklet. At high-temperatures we provide the exact 
@@
 trick). In the glassy phase the replica symmetry has to be broken. Using a generalization 
-of the Parisi solution, we provide analytical results for $S_n$, ${\mathcal I}_n$, 
+of the Parisi solution, we provide analytical results for $S_n$ and ${\mathcal I}_n$, 
 and for standard thermodynamic quantities. Both $S_n$ and ${\mathcal I}_n$ exhibit a 
 volume law in the whole phase diagram. We fully characterize the behavior of the 
-corresponding densities $S_n/N$ and ${\mathcal I}_n/N$, in the thermodynamic limit. 
+corresponding densities $S_n/N,{\mathcal I}_n/N$, in the thermodynamic limit. 
 Interestingly, at the critical point the mutual information does not exhibit any 
@@
 of the model, which are introduced to perform disorder averages (via the so-called 
-\emph{replica trick}~\cite{cardy-book}, not to be confused with the replica trick used in calculating the R\'enyi entanglement entropies). Finally, although the applicability of the S-K 
-model to describe realistic spin glasses is still highly debated~\cite{yucesoy-2012,
-billoire-2012,yucesoy-2013}, there are recent proposals on how to realize it  
-in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser systems~\cite{
-ghofraniha-2015}.
+\emph{replica trick}~\cite{cardy-book}), not to be confused with the replica trick used 
+in calculating the R\'enyi entanglement entropies (see below). Finally, although the 
+applicability of the S-K model to describe realistic spin glasses is still highly 
+debated~\cite{yucesoy-2012,billoire-2012,yucesoy-2013}, there are recent proposals on 
+how to realize it in cold-atomic gases~\cite{morrison-2008,rotondo-2015}, or in laser 
+systems~\cite{ghofraniha-2015}.
 
@@
 an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
-definition) using another \emph{replica trick}\cite{nakagawa-2009,buividovich-2008}. This consists of $n$ independent and identical replicas (the 
+definition), using another replica trick. This consists of $n$ independent and identical replicas (the 
 booklet ``sheets'') of the model. These \emph{physical} replicas are different 
@@
 %
-Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems 
-by replacing the sum over the probabilities of each state in region $A$ with the trace over the 
-reduced density matrix for region $A$.
-For $n=1$ Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
+Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by replacing 
+the sum over the proababilities of each state in region $A$ with the trace over the reduced 
+density matrix for region $A$. For $n=1$ 
+Eq.~\eqref{renyi-intro} defines the subsystem Shannon entropy~\cite{alcaraz-2013,
 stephan-2014-a}. From $S_n(A)$, one defines the classical mutual information 
@@
 Notice that a similar geometric construction~\cite{guerra-2002} plays an important role in the 
-mathematical proof of the Parisi ansatz.
+mathematical proof of the Parisi ansatz. Moreover, the study of the partition function of 
+critical models on the booklet has attracted considerable attention recently~\cite{fradkin-2006,
+fradkin-2009,hsu-2009,stephan-2009,hsu-2010,oshikawa-2010,stephan-2010,zaletel-2011}.
 
@@
 \left(\frac{N}{2\pi}\right)^{1/2}
-\exp\Big\{-\frac{N}{2}
+\exp\Big\{-\frac{N}{2J^2}
 \Big(J_{ij}-\frac{J_0}{N}\Big)^2\Big\}.
@@
 i.e., $n$ disconnected sheets, one has $Z(0,n,\beta,\{J\})=Z(\beta,\{J\})^n$, with 
-$Z(\beta,\{J\})$ the partition function of the S-K model on the plane (i.e. the original S-K model). On the other hand, 
+$Z(\beta,\{J\})$ the partition function of the S-K model on the plane (i.e., the original 
+S-K model). On the other hand, 
 for $\omega=1$ it is $Z(1,n,\beta,\{J\})=Z(n\beta,\{J\})$, i.e., the partition function 
@@
 replicas introduced in Eq.~\eqref{replica-trick}, whereas $r$ denote the 
-physical replicas, as in Eq.~\eqref{book-pf}. Again, both the physical and fictitious 
-replicas do not interact. Notice that $Z^{\alpha}(\omega,n,\beta)$ can be 
+physical replicas, as in Eq.~\eqref{book-pf}. Again, physical and fictitious 
+replicas do not interact with each other. Notice that $Z^{\alpha}(\omega,n,\beta)$ can be 
 thought of as the partition function of the S-K model on a ``replicated'' 
@@
 rr'})^2\Big)
-+\frac{\beta}{2 J_0}\sum\limits_{\gamma r}(m_\gamma^r)^2. 
++\frac{\beta}{2}\sum\limits_{\gamma r}(m_\gamma^r)^2. 
 \label{Gamma}
@@
 e^{{\mathcal L}}+(1-\omega)\log\tr_B e^{{\mathcal L}}\right)=
-\frac{1}{J_0}m_\gamma^r.
+m_\gamma^r.
 \end{align}
@@
 \rangle_B\\
-& \frac{1}{J_0}m_\gamma^r=\omega\langle S^{(r,\gamma)}
+& m_\gamma^r=\omega\langle S^{(r,\gamma)}
 \rangle_A+(1-\omega)\langle S^{(r,\gamma)}
@@
 $\omega\to 1$. Also, in the zero-temperature limit $\beta\to\infty$ one has 
-that $q_0\to 1$ and $q_0'\to 1$, for any $\omega$. Moreover, expansion 
-yields  
+that $q_0\to 1$ and $q_0'\to 1$, for any $\omega$. Moreover, a simple large $\beta$ 
+expansion yields  
 %
@@
  analytical result $U_{RS}/N$ obtained using the replica-symmetric (RS) approximation. 
- The horizontal dotted line is the exact zero-temperature result $U/N\approx-1.52642$.
+ The horizontal dotted line is the exact zero-temperature result $U/N=2u_{\infty}$, 
+ with $\tilde u_{\infty}\approx-0.76321$ the zero temperature energy density of the 
+ regular S-K model~\cite{parisi-1979,parisi-1983}.
 }
@@
 Fig.~\ref{U-MC}), with $\tilde u_{\infty}=-0.76321...$~\cite{parisi-1979,parisi-1983} the 
-zero-temperature internal energy density of the S-K model on the plane. Surprisingly, 
-this behavior is already observed in the MC data at $\beta\approx 3$, whereas it is not 
-captured correctly by the RS approximation.
+zero-temperature internal energy density of the S-K model on the plane.
 
@@
 
-The behavior of $U/N$ for $\omega\ne1/2$ is investigated in Fig.~\ref{U-RS},
-plotting $U/N$ as a function of $\beta$ and for $\omega=0,1/4,1/2,3/4,1$. The plus symbols 
+The behavior of $U/N$ for different $\omega$ is investigated in Fig.~\ref{U-RS},
+plotting $U/N$ as a function of $\beta$ and for $\omega=0,1/4,3/4,1$. The result for $\omega=1/2$ 
+is shown for comparison. The plus symbols 
 are the MC data extrapolated to the thermodynamic, at fixed $\omega$. Similar to Fig.~\ref{U-RS}, 
@@
 there is no well defined boundary between the two parts $A$ and $B$ of the system 
-(unlike in local spin models). With this in mind we assume that we will find
-volume-law behavior $[S_2]\propto N$ for all temperatures, and consider the entropy per spin 
+(unlike in local spin models). With this in mind we assume that we will find volume law 
+behavior $[S_2]\propto N$, and consider the entropy per spin 
 $[S_2]/N$ as the quantity of interest.
@@
 Here we directly measure the ratio of partition functions using the so-called \emph{ratio trick}. In 
-the ratio trick one splits the subsystem $A$ in a set of subsystems $A_i$ such that $A_i\subset A_{i+1}$ and the largest subsystem in the set is simply $A$ itself. Then one writes 
+the ratio trick one splits the subsystem $A$ in a set of subsystems $A_i$
+such that $A_i\subset A_{i+1}$, and the largest subsystem in the set is simply $A$ itself. Then one writes 
 %
@@
 Crucially, if the length of $A_i$ increases mildly with $i$, each term in the product 
-in the right hand side of Eq.~\eqref{ratio-trick} can be sampled efficiently in Monte 
+in the right-hand side of Eq.~\eqref{ratio-trick} can be sampled efficiently in Monte 
 Carlo~\cite{stephan-2014}. Notice that the same trick has also been used in 
@@
 \begin{align}
-W_a = \prod_n \sum_{i_n} e^{-\beta E_{i_n}}.
+W_a = \prod_n\sum_{i_n} e^{-\beta E_{i_n}}.
 \end{align}
@@
 Here (cf. Eq.~\eqref{sub-choice}) $i$ runs over all the $2^4$ configurations of the 
-four spins in $A_{i+1}\setminus A_i$ for each of the $n$ sheets, and $E_i$ is the energy associated with 
-the spin configuration $i$ of a single sheet.
+four spins in $A_{i+1}\setminus A_i$ for each of the $n$ sheets, and $E_{i_n}$ is 
+the energy associated with the spin configuration $i_n$ on a single sheet. 
 \item Calculate the quantity
@@
 in $A_{i+1}\setminus A_i$, but since the spins living on different sheets are identified 
-there are only $2^4$ configurations in total and the energy $E_j$ is that of all $n$ sheets together.
+there are only $2^4$ configurations in total and the energy $E_i$ is that of all $n$ 
+sheets together.
 \item Calculate the transition probability $T_{i\rightarrow i+1}$ as
@@
 %##########################################################################
+
 \begin{thebibliography}{99}
@@
 
+\bibitem{fradkin-2006}
+E.~Fradkin and J.~E.~Moore, Phys.\ Rev.\ Lett.\ {\bf 97}, 050404 (2006).
+
+\bibitem{fradkin-2009}
+E.~Fradkin, J.\ Phys.\  A {\bf 42}, 504011 (2009).
+
+\bibitem{hsu-2009}
+B.~Hsu, M.~Mulligan, E.~Fradkin, and E.-A.~Kim, Phys.\ Rev.\ B {\bf 79}, 115421 (2009).
+
+\bibitem{stephan-2009}
+J-M~St\'ephan, S.~Furukawa, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 80}, 
+184421 (2009).
+
+\bibitem{hsu-2010}
+B.~Hsu and E.~Fradkin, J.\ Stat.\ Mech.\  (2010) P09004.
+
+\bibitem{oshikawa-2010}
+M.~Oshikawa, arXiv:1007.3739 (2010).
+
+\bibitem{stephan-2010}
+J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 82}, 125455 
+(2010);
+
+\bibitem{zaletel-2011}
+M.~P.~Zaletel, J.~H.~Bardarson, and J.~E.~Moore, Phys.\ Rev.\ Lett.\ {\bf 107}, 
+020402 (2011).
+
 \bibitem{almeida-1978}
 J.~R.~L.~de Almeida and D.~J.~Thouless, J.\ Phys.\ A {\bf 11}, 983 (1978).
+
+\bibitem{parisi-1983}
+G.~Parisi, Phys.\ Rev.\ Lett\ {\bf 50}, 1946 (1983).
 
@@
 
-\bibitem{parisi-1983}
-G.~Parisi, Phys.\ Rev.\ Lett\ {\bf 50}, 1946 (1983).
-
 \bibitem{read-1995}
@@
 
-\bibitem{nakagawa-2009}
-Y.~Nakagawa, A.~Nakamura, S.~Motoki, and V.~Zakharov (2009), arXiv:0911.2596
-
-\bibitem{buividovich-2008}
-P.~Buividovich and M.~Polikarpov, Nuc.\ Phys.\ B {\bf 802}, 458 (2008)
-
-%\bibitem{katzgraber-2003}
-
-%H.~G.~Katzgraber and I.~A.~Campbell,
-
-%Phys.\ Rev.\ B {\bf 68}, 180402R (2003).
-
 \end{thebibliography}
 
+%Unused bibitems
+
+%\bibitem{stephan-2011}
+%J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 84}, 
+%195128 (2011).
 %Unused bibitems
@@
 %
-%\bibitem{parisi-1980-a}
-%G.~Parisi, J.\ Phys.\ A\ {\bf 13}, 1887 (1980). 
 %\bibitem{huse-1987}
@@
 %J.~Wilms, M.~Troyer, and F.~Verstraete, J.\ Stat.\ Mech.\ (2011) P10011.
-%\bibitem{zaletel-2011}
-%M.~P.~Zaletel, J.~H.~Bardarson, and J.~E.~Moore, Phys.\ Rev.\ Lett.\ {\bf 107}, 
-%020402 (2011).
-%\bibitem{huse-1987-a}
-%D.~A.~Huse and D.~S.~Fisher, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L1005 (1987).
-%\bibitem{fisher-1988}
-%D.~S.~Fisher and D.~A.Huse, Phys.\ Rev. B {\bf 38}, 386 (1988).
-%\bibitem{parisi-1980-b}
-%G.~Parisi, J.\ Phys.\ A\ {\bf 13}, L115 (1980). 
-%\bibitem{fisher-1986}
-%D.~S.~Fisher and D.~A.~Huse, Phys.\ Rev.\ Lett.\ {\bf 56} 1601 (1986).
-%\bibitem{palassini-2000}
-%M.~Palassini and A.~P.~Young, Phys.\ Rev.\ Lett.\  {\bf 85}, 3017 (2000).
-%\bibitem{stephan-2010}
-%J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 82}, 125455 
-%(2010); 
-%\bibitem{stephan-2011}
-%J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 84}, 
-%195128 (2011).
-%\bibitem{stephan-2009}
-%J-M~St\'ephan, S.~Furukawa, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B, {\bf 80}, 
-%184421 (2009)
-%\bibitem{krzakala-2000}
-%F.~Krzakala and O.~C.~Martin, Phys.\ Rev.\ Lett.\ {\bf 85}, 3013 (2000).
 \end{document}

### 2015-06-29 sk_model_v17.tex
revised-28/06/2015

@@
 (n-1)q_0^2-2q_0\Big)\\
-+\int Dz\left\{\frac{\omega}{m_1}\log\int Dz'\Big\{\int Dz''
++\int Dz\left\{\frac{1-\omega}{m_1}\log\int Dz'\Big\{\int Dz''
 H_{1\textrm{-}RSB}^n(z,z',z'')\Big\}^{m_1}
-+\frac{1-\omega}{m_1}
++\frac{\omega}{m_1}
 \log\int Dz'\Big\{\int Dz''
@@
 We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
-with zero external magnetic field. We focus on the internal energy $U(\omega,n,
+with zero external magnetic field. The data are obtained from parallel tempering  
+Monte Carlo simulations~\cite{hukushima-1996}. In the parallel tempering simulations 
+$N_{\textrm{rep}}$ identical copies of the system are simulated. Each copy is at a different temperature 
+in the range $T_{\textrm{max}}-T_{\textrm{min}}$. The standard Metropolis sweeps at 
+each temperature are supplemented with parallel tempering moves, which allow 
+to exchange the spin configurations of replicas with neighboring temperatures. 
+In our simulations we choose $T_{\textrm{min}}=...$ and $T_{\textrm{max}}=...$. 
+Each Monte Carlo sweep consists of $...$ Metropolis steps and $...$ parallel 
+tempering moves. For each disorder realization we perform $...$ sweeps for $L=...$. 
+The disorder average is performed over $...$ different disorder realizations.
+
+We focus on the internal energy $U(\omega,n,
 \beta)$ 
@@
 
+\bibitem{hukushima-1996}
+K.~Hukushima and K.~Nemoto, J.\ Phys.\ Soc.\ Jpn.\ {\bf 65}, 1604 (1996).
+
 \bibitem{billoire-2007}

### 2015-06-29 sk_model_v17.tex

--- 2015-06-27 sk_model_v17.tex
@@
 We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
-with zero external magnetic field. We focus on the internal energy $U(\omega,n,
+with zero external magnetic field. The data are obtained from parallel tempering  
+Monte Carlo simulations~\cite{hukushima-1996}. In the parallel tempering simulations 
+$N_{\textrm{rep}}$ identical disorder realizations of the system are simulated. Each copy is at 
+a different temperature in the range $\beta_{\textrm{min}}-\beta_{\textrm{max}}$. 
+The standard Metropolis sweeps at 
+each temperature are supplemented with parallel tempering moves, which allow 
+the exchange the spin configurations between replicas with neighboring temperatures. 
+In our simulations we choose $\beta_{\textrm{min}}=0.25$ and $\beta_{\textrm{max}}=2.5$, with 46 temperatures
+chosen in total with equal spacing in $\beta$.
+Each Monte Carlo sweep consists of $N$ single spin updates and $45$ parallel 
+tempering moves. For each disorder realization we perform $10^5$ sweeps. 
+The disorder average is performed over $128$ different disorder realizations.
+
+We focus on the internal energy $U(\omega,n,
 \beta)$ 

### 2015-06-30 sk_model_v17.tex
revised-29/06/2015
revised-30/06/2015

@@
 of the model, which are introduced to perform disorder averages (via the so-called 
-\emph{replica trick}~\cite{cardy-book}), not to be confused with the replica trick used 
-in calculating the R\'enyi entanglement entropies (see below). Finally, although the 
+\emph{replica trick}~\cite{cardy-book}, not to be confused with the replica trick used 
+in calculating the R\'enyi entanglement entropies). Finally, although the 
 applicability of the S-K model to describe realistic spin glasses is still highly 
@@
 The resulting $\beta_c$ is plotted in Fig.~\ref{beta_c} as a function of $\omega$.
+
+%##########################################################################
+\section{The one-step replica-symmetry-breaking (1-RSB) approximation}
+\label{rsb-1-section}
+
+In this section we go beyond the replica-symmetric approximation, including some 
+of the effects of the replica symmetry breaking. More specifically, here we discuss 
+the one-step replica symmetry breaking (1-RSB) approximation. The overlap tensor 
+$q_{\gamma\gamma'}^{rr'}$ now reads  
+%
+\begin{equation}
+\label{q-rsb1}
+q_{\gamma\gamma'}^{rr'}=(1-q_0)\delta_{\gamma,\gamma'}\delta_{r,r'} +
+q_0\delta_{\gamma,\gamma'}+(1-\delta_{\gamma,\gamma'})q', 
+\end{equation}
+%
+which is formally equivalent to the RS ansatz in Eq.~\eqref{rs-ansatz}, apart from 
+the trivial redefinition $q_0'\to q'$. However, in contrast with Eq.~\eqref{rs-ansatz}, 
+where $q_0'\in\mathbb{R}$ is a number, here $q'$ is a matrix. Inspired by the Parisi 
+scheme for the standard S-K model~\cite{parisi-1979}, we choose 
+%
+\begin{equation}
+q'=\left\{
+\begin{array}{cc}
+q_1' & \textrm{if}\, \lfloor\gamma/m_1\rfloor=\lfloor\gamma'/m_1\rfloor\\\\
+q_0' & \textrm{otherwise}\\
+\end{array}
+\right.
+\label{q-rsb1a}
+\end{equation}
+%
+where $q_0',q_1'\in{\mathbb R}$, $m_1\in{\mathbb N}$, and $\lfloor\cdot\rfloor$ 
+denotes the floor function. Notice that the off-diagonal elements of $q'$ (i.e., for 
+$\gamma\ne\gamma'$) do not depend on $r,r'$, meaning that, although the permutation 
+symmetry between the fictitious replicas is broken, the symmetry among the physical ones 
+is preserved. The choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block-diagonal 
+structure for $q'$: the matrix elements of the $m_1\times m_1$ diagonal blocks of $q'$ 
+are set to $q_1'$, whereas all the off-diagonal elements are set to $q_0'$. As for the 
+replica-symmetric ansatz in Eq.~\eqref{rs-ansatz}, we do not have any rigorous argument 
+to justify Eq.~\eqref{q-rsb1a} (see section~\eqref{mc-results}, however, for numerical 
+results).
+
+The effective interaction ${\mathcal L}_{1\textrm{-}RSB}$ (cf. Eq.~\eqref{mf-action}) 
+in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in Eq.~\eqref{mf-action}. 
+This yields  
+%
+\begin{multline}
+{\mathcal L}_{1\textrm{-}RSB}/\beta^2=-\frac{q_0}{2}n\alpha
+-\frac{q_1'-q_0}{2}\sum\limits_{\sigma=1}^{\alpha/m_1}
+\sum\limits_{\gamma\in B_\sigma}\Big(\sum_r S^{(r,\gamma)}\Big)^2\\
++\frac{q_0'}{2}\Big(\sum\limits_{\gamma,r}
+S^{(r,\gamma)}\Big)^2-
+\frac{q_0'-q_1'}{2}\sum\limits_{\sigma=1}^{\alpha/m_1}
+\Big(\sum\limits_{\gamma\in B_\sigma,r}S^{(r,\gamma)}\Big)^2,
+\label{blocks}
+\end{multline}
+%
+where we defined $B_\sigma\equiv[\sigma m_1,(\sigma+1)m_1)$ with $\sigma\in\mathbb{N}$.
 
@@
 
-%##########################################################################
-\section{The one-step replica-symmetry-breaking (1-RSB) approximation}
-\label{rsb-1-section}
-
-In this section we go beyond the replica-symmetric approximation, including some 
-of the effects of the replica symmetry breaking. More specifically, here we discuss 
-the one-step replica symmetry breaking (1-RSB) approximation. The overlap tensor 
-$q_{\gamma\gamma'}^{rr'}$ now reads  
-%
-\begin{equation}
-\label{q-rsb1}
-q_{\gamma\gamma'}^{rr'}=(1-q_0)\delta_{\gamma,\gamma'}\delta_{r,r'} +
-q_0\delta_{\gamma,\gamma'}+(1-\delta_{\gamma,\gamma'})q', 
-\end{equation}
-%
-which is formally equivalent to the RS ansatz in Eq.~\eqref{rs-ansatz}, apart from 
-the trivial redefinition $q_0'\to q'$. However, in contrast with Eq.~\eqref{rs-ansatz}, 
-where $q_0'\in\mathbb{R}$ is a number, here $q'$ is a matrix. Inspired by the Parisi 
-scheme for the standard S-K model~\cite{parisi-1979}, we choose 
-%
-\begin{equation}
-q'=\left\{
-\begin{array}{cc}
-q_1' & \textrm{if}\, \lfloor\gamma/m_1\rfloor=\lfloor\gamma'/m_1\rfloor\\\\
-q_0' & \textrm{otherwise}\\
-\end{array}
-\right.
-\label{q-rsb1a}
-\end{equation}
-%
-where $q_0',q_1'\in{\mathbb R}$, $m_1\in{\mathbb N}$, and $\lfloor\cdot\rfloor$ 
-denotes the floor function. Notice that the off-diagonal elements of $q'$ (i.e., for 
-$\gamma\ne\gamma'$) do not depend on $r,r'$, meaning that, although the permutation 
-symmetry between the fictitious replicas is broken, the symmetry among the physical ones 
-is preserved. The choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block-diagonal 
-structure for $q'$: the matrix elements of the $m_1\times m_1$ diagonal blocks of $q'$ 
-are set to $q_1'$, whereas all the off-diagonal elements are set to $q_0'$. As for the 
-replica-symmetric ansatz in Eq.~\eqref{rs-ansatz}, we do not have any rigorous argument 
-to justify Eq.~\eqref{q-rsb1a} (see section~\eqref{mc-results}, however, for numerical 
-results).
-
-The effective interaction ${\mathcal L}_{1\textrm{-}RSB}$ (cf. Eq.~\eqref{mf-action}) 
-in the replica space is obtained by substituting Eq.~\eqref{q-rsb1} in Eq.~\eqref{mf-action}. 
-This yields  
-%
-\begin{multline}
-{\mathcal L}_{1\textrm{-}RSB}/\beta^2=-\frac{q_0}{2}n\alpha
--\frac{q_1'-q_0}{2}\sum\limits_{\sigma=1}^{\alpha/m_1}
-\sum\limits_{\gamma\in B_\sigma}\Big(\sum_r S^{(r,\gamma)}\Big)^2\\
-+\frac{q_0'}{2}\Big(\sum\limits_{\gamma,r}
-S^{(r,\gamma)}\Big)^2-
-\frac{q_0'-q_1'}{2}\sum\limits_{\sigma=1}^{\alpha/m_1}
-\Big(\sum\limits_{\gamma\in B_\sigma,r}S^{(r,\gamma)}\Big)^2,
-\label{blocks}
-\end{multline}
-%
-where we defined $B_\sigma\equiv[\sigma m_1,(\sigma+1)m_1)$ with $\sigma\in\mathbb{N}$. 
 It is convenient to introduce the Hubbard-Stratonovich variables $z,z_\sigma,z_{\sigma,\gamma}$ 
@@
 We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
-with zero external magnetic field. The data are obtained from parallel tempering  
+with zero external magnetic field. The data we present are obtained from parallel tempering  
 Monte Carlo simulations~\cite{hukushima-1996}. In the parallel tempering simulations 
@@
 each temperature are supplemented with parallel tempering moves, which allow 
-the exchange the spin configurations between replicas with neighboring temperatures. 
-In our simulations we choose $\beta_{\textrm{min}}=0.25$ and $\beta_{\textrm{max}}=2.5$, with 46 temperatures
-chosen in total with equal spacing in $\beta$.
-Each Monte Carlo sweep consists of $N$ single spin updates and $45$ parallel 
-tempering moves. For each disorder realization we perform $10^5$ sweeps. 
+to exchange the spin configurations between replicas with neighboring temperatures. 
+In our simulations we choose the interval with $\beta_{\textrm{min}}=0.25$ and 
+$\beta_{\textrm{max}}=2.5$, with $46$ temperatures corresponding to equally spaced 
+values of $\beta$. Each Monte Carlo sweep consists of $N$ single spin updates and $45$ 
+parallel tempering moves. For each disorder realization we perform $10^5$ sweeps. 
 The disorder average is performed over $128$ different disorder realizations.

### 2015-07-03 sk_model_v18.tex
revised-3/07/2015

--- 2015-06-30 sk_model_v17.tex
@@
 and for standard thermodynamic quantities. Both $S_n$ and ${\mathcal I}_n$ exhibit a 
-volume law in the whole phase diagram. We fully characterize the behavior of the 
+volume law in the whole phase diagram. We characterize the behavior of the 
 corresponding densities $S_n/N,{\mathcal I}_n/N$, in the thermodynamic limit. 
@@
 Arguably, \emph{spin glasses} represent one of the most prototypical examples
-of exotic behavior induced by disorder.
+of interesting behavior induced by disorder.
 While at any finite temperature disorder can prevent the 
@@
 of the model, which are introduced to perform disorder averages (via the so-called 
-\emph{replica trick}~\cite{cardy-book}, not to be confused with the replica trick used 
-in calculating the R\'enyi entanglement entropies). Finally, although the 
+\emph{replica trick}~\cite{cardy-book}. Finally, although the 
 applicability of the S-K model to describe realistic spin glasses is still highly 
@@
 an \emph{ad hoc} defined ``booklet'' geometry (see section~\ref{booklet} for its 
-definition), using another replica trick. This consists of $n$ independent and identical replicas (the 
-booklet ``sheets'') of the model. These \emph{physical} replicas are different 
-from the \emph{fictitious} ones used to perform the disorder average. Each sheet is 
+definition). This consists of $n$ independent and identical copies (the 
+booklet ``sheets'') of the model. These \emph{physical} copies are different 
+from the \emph{fictitious} replicas used to perform the disorder average. Each sheet is 
 divided into two parts $A$ and $B$, containing $N_A$ and $N_B$ spins, respectively. 
@@
 \begin{equation}
+\label{MI}
 {\mathcal I}_n(A,B)\equiv S_n(A)+S_n(B)-S_n(A\cup B). 
@@
 temperature exhibits a non trivial dependence on $\omega$ that we are able to determine 
-analytically. In the high-temperature region the permutation symmetry among the replicas, 
-both the physical and the fictitious ones, is preserved. This allows us to provide an exact 
+analytically. In the high-temperature region the permutation symmetry among both the replicas  
+and the physical sheets  is preserved. This allows us to provide an exact 
 analytic expression for the free energy of the model and several derived quantities, such as 
@@
 related to the paramagnetic-glassy transition. At high temperature $[{\mathcal I}_2]/N$ 
-is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$, whereas at low temperatures 
+is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$. Deviations from the RS result, 
+if present, are $\lesssim 10^{-3}$. On the other hand, at low temperatures 
 one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
@@
 fradkin-2009,hsu-2009,stephan-2009,hsu-2010,oshikawa-2010,stephan-2010,zaletel-2011}.
-
-Clearly, one has $S_n(A)\equiv1/(n-1)\log(F(A,n,\beta))-n\log(F(\beta))$, where $F(A,n,\beta)
+Clearly, one has $S_n(A)\equiv1/(n-1)(\log(F(A,n,\beta))-n\log(F(\beta)))$, where $F(A,n,\beta)
 \equiv\log(Z(A,n\beta))$ and $F(\beta)\equiv\log(Z(\beta))$ are related (apart from a factor 
-$\beta$) to the free energy of the model on the booklet and on the plane, respectively.
-The mutual information ${\mathcal I}_n(A,B,\beta)$ is defined~\cite{jaconis-2013,stephan-2014} 
-as 
-%
-\begin{equation}
-\label{MI}
-{\mathcal I}_n(A,B,\beta)\equiv\frac{1}{1-n}\log\Big(
-\frac{Z(A,n,\beta)Z(B,n,\beta)}{Z^n(\beta)Z(n\beta)}
-\Big),
-\end{equation}
-%
-where $Z(B,n,\beta)$ is obtained from $Z(A,n,\beta)$ by replacing $A$ with $B$. 
-Notice that the disorder-averaged mutual information $[{\mathcal I}_n]$ and the R\'enyi 
-entropy $[S_n]$ are directly related to the so-called quenched-averaged free energy 
-$[F(A,n,\beta)]$, which is the main quantity of interest in disordered systems~\cite{cardy-book}.
-
+$-1/\beta$) to the free energy of the model on the booklet and on the plane, respectively.
+
+The mutual information ${\mathcal I}_n(A,B,\beta)$ is obtained in terms of the booklet 
+partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}. Notice that the disorder-averaged 
+mutual information $[{\mathcal I}_n]$ and the R\'enyi entropy $[S_n]$ are directly related to 
+the so-called quenched-averaged free energy $[F(A,n,\beta)]$, which is the main quantity of 
+interest in disordered systems~\cite{cardy-book}. 
 For clean (i.e., without disorder) \emph{local} spin models ${\mathcal I}_n$ 
@@
 each sheet, $J_{ij}$ is the interaction strength, and $h$ is an external 
-magnetic field. Here we choose $h=0$. The total number of spins in the booklet 
-is $nN$. The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
+magnetic field. The total number of spins in the booklet is $nN$. 
+The first sum inside the brackets in Eq.~\eqref{SK-ham} is over all the 
 $N(N-1)/2$ pairs of spins in each sheet. Spins on different sheets do not interact. 
@@
 The mean and the variance of $P(\{J_{ij}\})$ are given as $[J_{ij}]=J_0/N$ 
-and $[(J_{ij}-[J_{ij}])^2]=J^2/N$, respectively. The square brackets $[\cdot]$ denote 
+and $[(J_{ij}-[J_{ij}])^2]=J^2/N$, respectively. Here we set $J=1$. The square brackets $[\cdot]$ denote 
 the average over different realizations of $J_{ij}$. Here we restrict ourselves to 
@@
 replicas introduced in Eq.~\eqref{replica-trick}, whereas $r$ denote the 
-physical replicas, as in Eq.~\eqref{book-pf}. Again, physical and fictitious 
-replicas do not interact with each other. Notice that $Z^{\alpha}(\omega,n,\beta)$ can be 
-thought of as the partition function of the S-K model on a ``replicated'' 
-booklet.
+physical copies, i.e., the booklet sheets, as in Eq.~\eqref{book-pf}. Again, 
+spins on different sheets or different replicas do not interact with each other. 
+Notice that $Z^{\alpha}(\omega,n,\beta)$ can be thought of as the partition 
+function of the S-K model on a ``replicated'' booklet.
 
@@
 %
-In contrast with Eq.~\eqref{rep-Z}, physical and unphysical replicas are 
-now coupled by a four-spin interaction. It is convenient to introduce the  
+In contrast with Eq.~\eqref{rep-Z}, both different sheets and different replicas 
+are now coupled by a four-spin interaction. It is convenient to introduce the  
 Hubbard-Stratonovich variables $q_{\gamma\gamma'}^{rr'}$ and $m_\gamma^r$. 
@@
 {\mathcal K}(\{q,m\})\equiv 
-\frac{\beta^2}{2}\Big(\sum\limits_{\gamma<\gamma'}\sum
+\frac{\beta^2}{2J_0}\Big(\sum\limits_{\gamma<\gamma'}\sum
 \limits_{r,r'} (q_{\gamma\gamma'}^{rr'})^2
@@
 rr'})^2\Big)
-+\frac{\beta}{2}\sum\limits_{\gamma r}(m_\gamma^r)^2. 
++\frac{\beta}{2J_0}\sum\limits_{\gamma r}(m_\gamma^r)^2. 
 \label{Gamma}
@@
 of freedom living in parts $A$ and $B$ of the booklet.
-The subscript $A$ in $\tr_A$ is to stress that spins living in different physical 
-replicas (i.e., for $r\ne r'$ in Eq.~\eqref{mf-action}) are identified (due 
+The subscript $A$ in $\tr_A$ is to stress that spins living in different  
+sheets (i.e., for $r\ne r'$ in Eq.~\eqref{mf-action}) are identified (due 
 to the booklet constraint in Eq.~\eqref{book-constraint}), whereas they have 
@@
 e^{{\mathcal L}}+(1-\omega)\log\tr_B e^{{\mathcal L}}\right)=
-m_\gamma^r.
+J_0^{-1}m_\gamma^r.
 \end{align}
@@
 \rangle_B\\
-& m_\gamma^r=\omega\langle S^{(r,\gamma)}
+& J_0^{-1}m_\gamma^r=\omega\langle S^{(r,\gamma)}
 \rangle_A+(1-\omega)\langle S^{(r,\gamma)}
@@
 to determine the critical temperature of the paramagnetic-glassy transition. 
+For simplicity, here and in the following sections we restrict ourselves to zero 
+magnetic field ($h=0$ in Eq.~\eqref{SK-ham}), and to $J_0=0$ in 
+Eq.~\eqref{quenched-distr}.
 
@@
 \caption{
- The S-K model on the $2$-sheets booklet with zero magnetic field in the 
+ The S-K model on the $2$-sheets booklet in the 
  paramagnetic phase: the solution $q_0$ of the saddle point 
@@
 %
-Remarkably, $q_{\gamma\gamma'}^{rr'}$ becomes diagonal in both the 
-indices $\gamma,\gamma'$ and $r,r'$, i.e., the physical and fictitious 
+Notice that $q_{\gamma\gamma'}^{rr'}$ is diagonal in both the 
+indices $\gamma,\gamma'$ and $r,r'$, i.e., the sheet and the  
 replica spaces. Using Eq.~\eqref{Z-ac} and Eq.~\eqref{replica-trick}, 
@@
 \caption{\label{RSB0-saddle}
- The S-K model on the $2$-sheets booklet with zero magnetic field. The 
+ The S-K model on the $2$-sheets booklet. The 
  overlap tensor in the replica-symmetric (RS) approximation (see Eq.~\eqref{rs-ansatz}): 
@@
 $\forall\gamma\ne\gamma'$ and $\forall r,r'$. Clearly, $q_{\gamma\gamma'}^{rr'}$ is 
-symmetric in both the physical and fictitious replica spaces. We do not have any 
+invariant under permutations of both the booklet sheets and the replicas. We do not have any 
 rigorous argument to justify the ansatz~\eqref{rs-ansatz}, besides its simplicity. 
@@
  transition for the S-K model on the $2$-sheets booklet (see Fig.~\ref{cartoon}) 
- with zero magnetic field from Eq.~\eqref{tc}: $\beta_c$ as a function of the booklet ratio $\omega
+ from Eq.~\eqref{tc}: $\beta_c$ as a function of the booklet ratio $\omega
  \equiv N_A/N$. Here $\beta_c$  is obtained from the replica-symmetric (RS) 
@@
 $\gamma\ne\gamma'$) do not depend on $r,r'$, meaning that, although the permutation 
-symmetry between the fictitious replicas is broken, the symmetry among the physical ones 
+symmetry between the replicas is broken, the symmetry among the booklet sheets  
 is preserved. The choice in Eq.~\eqref{q-rsb1a} corresponds to a simple block-diagonal 
@@
 \caption{
- The S-K model on the $2$-sheets booklet with zero magnetic field and 
- booklet ratio $\omega=1/2$ (see Fig.~\ref{cartoon}): The internal energy 
+ The S-K model on the $2$-sheets booklet with aspect ratio $\omega=1/2$ 
+ (see Fig.~\ref{cartoon}): The internal energy 
  per spin $U/N$ as a function of the inverse temperature $\beta$. The triangles, 
@@
 point equations~\eqref{RSB-1-saddle-a}\eqref{RSB-1-saddle-b}\eqref{RSB-1-saddle-c}
-\eqref{RSB-1-saddle-d}. One should remark that, although formally $m_1$ is an 
+\eqref{RSB-1-saddle-d}. One should remark that, although $m_1$ is by defintion an 
 integer, one obtains $m_1\in\mathbb{R}$ from the saddle point equations. 
@@
 the replica-symmetric (RS) approximation (see section~\ref{rs-section}). 
-Using Eq.~\eqref{rs-F} and Eq~\eqref{U-def}, $U_{RS}$  is obtained as   
+Using Eq.~\eqref{rs-F} and Eq.~\eqref{U-def}, $U_{RS}$  is obtained as   
 %
@@
 to the replica symmetry breaking happening in the glassy phase. Finally, since in 
-the limit $\beta\to\infty$ all the physical replicas are in the same state, 
+the limit $\beta\to\infty$ all the sheets  are in the same state, 
 one should expect that $u_\infty(\omega,\beta)\to n \tilde u_\infty$ (horizontal line in 
@@
 \caption{
- The S-K model on the 2-sheets booklet and zero magnetic field: 
+ The S-K model on the 2-sheets booklet: 
  The internal energy per spin $U/N$ in the thermodynamic limit. 
@@
 \caption{
- The S-K model on the 2-sheets booklet with zero magnetic field: 
+ The S-K model on the 2-sheets booklet: 
  The internal energy per spin $U/N$ in the thermodynamic limit plotted 
@@
 \caption{ The classical disorder-averaged R\'enyi entropy per spin $[S_2(\omega)]/N$  
- in the S-K model on the $2$-sheets booklet with zero magnetic field: 
+ in the S-K model on the $2$-sheets booklet: 
  $[S_2(\omega)]/N$ as a function of the inverse temperature $\beta$. The different panels 
@@
 \caption{The classical disorder-averaged mutual information per spin $[{\mathcal I}_2]/N$ 
- in the S-K model on the $2$-sheets booklet with zero magnetic field: 
+ in the S-K model on the $2$-sheets booklet: 
  $[{\mathcal I}_2]/N$ versus the inverse temperature $\beta$. The 
@@
 analytical result obtained using the replica symmetric (RS) approximation (see 
-section~\ref{rs-section}). Formally, this is obtained using Eq~\eqref{MI} and Eq.~\eqref{rs-F}, 
+section~\ref{rs-section}). Formally, this is obtained using Eq.~\eqref{MI} and Eq.~\eqref{rs-F}, 
 and it is in perfect agreement with the MC data in the whole paramagnetic phase.
@@
 \begin{equation}
-\frac{[{\mathcal I}_2]}{N}=a+\frac{b}{N^{\phi''}},
-\end{equation}
-%
-where we fix $\phi''=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}.  
+\frac{[{\mathcal I}_2]}{N}=a+\frac{b}{N^{\phi}},
+\end{equation}
+%
+where we fix $\phi=2/3$. The results of the fits are shown in Fig.~\ref{I2-extrapolated}.  
 Different symbols now correspond to different aspect ratios $\omega$. Remarkably, the RS 
-approximation (dash-dotted lines) is in good agreement with the extrapolations up to $\beta\lesssim 1.5$, 
-whereas deviations occur at lower temperatures (not shown in the figure). 
-For $\omega=1/8$, the numerical results exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
-These deviations have to be attributed to the physics of the replica symmetry breaking. 
+approximation (dash-dotted lines) is in good agreement with the extrapolations for $\beta\lesssim 0.6$. 
+We should stress that in the region $0.6\lesssim\beta\lesssim 1$, i.e., near the peak, due to the large 
+error bars it is difficult to reach a conclusion on the validity of the RS approximation. 
+In particular, the data exhibit a systematic shift of the mutual information 
+peak towards lower temperatures. Much larger system sizes would be needed to clarify this 
+issue. The effect of the replica symmetry breaking, however, 
+should be negligible. For instance, at $\beta=0.6$ for $\omega=1/2$ one can estimate that 
+$|[{\mathcal I}_2^{RS}]-[{\mathcal I}_2^{1\textrm{-}RSB}]|/N\sim 2\cdot 10^{-5}$. Finally, clear deviations 
+from the RS result occur at lower temperatures. For instance, for $\omega=1/8$, the numerical results 
+exhibit deviations from the RS result already at $\beta\gtrsim 1$. 
+These deviations, however, have to be attributed to the physics of the replica symmetry breaking. 
 The full rhombi in Fig.~\ref{I2-extrapolated} denote the one-step replica symmetry breaking result 
@@
 \caption{The classical mutual information per spin $[{\mathcal I}_2]/N$ 
- in the S-K model on the $2$-sheets booklet with zero magnetic field: 
+ in the S-K model on the $2$-sheets booklet: 
  $[{\mathcal I}_2]/N$ plotted versus $\beta$. The symbols denote the 
@@
 the $1$-RSB approximation fully matches the Monte Carlo data for $\beta\approx 3$.
-Interestingly, at the critical point ${\mathcal I}_2/N$ does not show any crossing for 
+Interestingly, at the critical point $[{\mathcal I}_2]/N$ does not show any crossing for 
 different system sizes, in contrast with local models~\cite{jaconis-2013}.
@@
 to generate an importance sampled spin configuration. This can be done with any 
-update scheme, such as standard Metropolis or cluster updates
+update scheme, such as standard Metropolis or cluster updates. 
 \item For the spins living in the set difference $A_{i+1}\setminus A_i$ calculate 
@@
 V.~Alba, J.\ Stat.\ Mech.\ (2013) P05013. 
-
 \end{thebibliography}
 
-%Unused bibitems
-
-%\bibitem{stephan-2011}
-%J-M~St\'ephan, G.~Misguich, and V.~Pasquier, Phys.\ Rev.\ B {\bf 84}, 
-%195128 (2011).
-%Unused bibitems
-
-%\bibitem{newman-1996}
-%C.~Newman and D.~L.~Stein, Phys.\ Rev.\ Lett.\ {\bf 76}, 515 (1996).
-%\bibitem{wilms-2012}
-%J.~Wilms, J.~Vidal, F.~Verstraete,and S.~Dusuel, J.\ Stat.\ Mech.\ (2012)P01023. 
-%
-%\bibitem{huse-1987}
-%D.~S.~Fisher and D.~A.Huse, J.\ Phys.\ A:\ Math.\ Gen.\ {\bf 20} L997 (1987).
-%\bibitem{wilms-2011}
-%J.~Wilms, M.~Troyer, and F.~Verstraete, J.\ Stat.\ Mech.\ (2011) P10011.
 \end{document}

### 2015-07-04 sk_model_v18.tex
revised-4/07/2015

@@
 the temperature, as expected. In order to obtain $[S_2]/N$ in the thermodynamic limit 
-we fit the data to the ansatz $[S_2]/N=s_2(\omega)+c'(\omega)/N^{\phi'}$, where 
+we fit the data to the ansatz $[S_2]/N=s_2(\omega)+c'(\omega)/N^{\phi}$, where 
 $s_2(\omega)$ is the entropy per spin in the thermodynamic limit, $c'$ a constant, and 
-$\phi'$ the exponent of the finite-size corrections. The plus symbols in Fig.~\ref{Renyi-MC} 
-are the results of the fits. We should mention that the fits give $\phi'\approx 2/3$, 
+$\phi$ the exponent of the finite-size corrections. The plus symbols in Fig.~\ref{Renyi-MC} 
+are the results of the fits. We should mention that the fits give $\phi\approx 2/3$, 
 which is the exponent of the scaling corrections of the free energy in the standard 

### 2015-07-15 sk_model_v18.tex
Small typo corrections

@@
 of the model, which are introduced to perform disorder averages (via the so-called 
-\emph{replica trick}~\cite{cardy-book}. Finally, although the 
+\emph{replica trick}~\cite{cardy-book}). Finally, although the 
 applicability of the S-K model to describe realistic spin glasses is still highly 
@@
 Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by replacing 
-the sum over the proababilities of each state in region $A$ with the trace over the reduced 
+the sum over the probabilities of each state in region $A$ with the trace over the reduced 
 density matrix for region $A$. For $n=1$ 

### 2015-12-10 prb_resub/referee_response/response.txt
rev-10/11/2015

Dear Editors,

=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
RESPONSE TO THE FIRST REFEREE 
=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=

REFEREE:
-------
	This paper deals with the study of entropies in classical spin models.
	The focus is on the Sherrington-Kirkpatrick model, a simple model that
	exhibits spin glass physics. Both analytical and numerical results are
	presented, and compared.

	Overall I found the paper interesting, and clearly written. Such
	classical entropies had only been studied in nearest neighbor spin
	models, so this is a useful addition to the existing literature.

RESPONSE:
========
	We thank the referee for considering our work interesting and 
	clearly written.

REFEREE:
-------

	There is one issue that needs to be addressed I think. In part II the
	classical Renyi entropy is defined by Eq. (5), and this is what is
	studied in the rest of the paper. It is not clear to me which is the
	underlying probability distribution, i.e it is not clear to me that
	this equals Eq. (2), because of the long-range interactions. This
	point needs to be clarified, as using the term Renyi entropy would be
	a slight abuse of terminology, and the reader should be made aware of
	that.

RESPONSE:
========

	We apologise for not being very clear about the equivalence between (5) 
	and (2). Eq. (5) is equivalent to Eq. (2) even with the long range 
	interactions. This is now clarified in the first paragraph in sec II. 
	Notice that the only physical effect of long range interactions is that 
	there is no area law in contrast with local models, as it is discussed 
	extensively in the manuscript.

REFEREE:
-------

	I also have a couple of minor remarks and suggestions, which I list
	below:

	1) In the long introduction, several values of \beta are mentioned. It
	might be helpful to recall the values of $\beta_c(w)$.

RESPONSE:
========

	In order to meet the suggestion of the second referee we moved the summary of 
	results in the conclusions. Therefore, in the new version of the manuscript 
	the referee suggestion is implemented in the conclusions. First, we should 
	clarify that $\beta$ always refers to the explicit temperature in a single 
	replica, and never to the *effective* temperature on the booklet. We thank 
	the referee for noticing that in the introduction we do not mention  explicitly 
	the values of the critical temperature for the model on the booklet. We now 
	mention explicitly that the critical temperature is a decreasing function of 
	the booklet aspect ratio $\omega$ and that $\beta_c=1,1/2$ for $\omega=0,1$. 
	Notice that that all the  values of beta that we mention in the summary of 
	the results (\beta=1,\beta=3) correspond to the low-temperature phase of the 
	model on the booklet.

REFEREE:
-------

	2) Maybe at the $\forall i \in A$ also in equation (8) ?

RESPONSE:
========

	We thank the referee for noticing that. We moved the $\forall i...$  
	in equation (8).

3) Before (40), the sentence "..., one obtains a standard Landau
theory" reads awkwardly.

RESPONSE:
========

	We removed the sentence in question.

REFEREE:
-------
	4) Could the authors comment somewhere on the Monte Carlo statistical
	errors when they are not shown?
	This is: 
	-Fig 8 (hidden behind some of the points, so you could say smaller than 
	point size in caption).
	-Fig 9 (same as 8)
	In the other figures the errors bars are fairly clear, but Fig 5 might be 
	non-obvious at first glance

RESPONSE:
========

	We thank the referee for the useful comment. In the captions of Fig 5, Fig 8, 
	and Fig 9 we now mention explicitly that the error bars are smaller than the 
	symbol size.

=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
RESPONSE TO THE SECOND REFEREE 
=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=

REFEREE:
-------

	In the manuscript BG13275, the authors study the Reny entropy and
	mutual information in the Sherrington-Kirkpatrick model. Using the
	replica method, the authors constructed the replica-symmetric solution
	and 1-step replica-symmetry-breaking solutions. They are solved
	numerically and are compared with the results of the Monte Carlo
	simulations. It was shown that the one-step RSB solution is enough to
	find a good agreement with the Monte Carlo result. The aspect-ratio
	and temperature dependences of the entropy and mutual information are
	analyzed in detail to see the scaling in terms of the system size and
	the critical properties.

RESPONSE:
========

	We thank the referee for the accurate summary of our results.

REFEREE:
-------

	The manuscript is written very clearly and the analytical calculations
	as well as numerical ones look reliable. The authors followed the
	standard procedure of the replica analysis and several ansatz such as
	(28) look reasonable.

RESPONSE:
========

	We thank the referee for finding our paper well written and our analysis 
	reliable.

REFEREE:
-------

	Although the analysis looks quite reasonable, the authors do not
	discuss the results thoroughly nor their physical meaning. Therefore,
	I can recommend the publication if the authors clarify following
	several questions.

	(1). What is the significance to treat infinite-range models in the
	problem of mutual information? As the authors mentioned in the
	manuscript, there is no notion of space and locality in infinite-range
	models. It is not clear for me to consider the booklet geometry in
	such systems. It would be helpful if the authors answer this simple
	question in the manuscript.

RESPONSE:
========

	We thank the referee for the opportunity to clarify this point. The 
	definition of the mutual information is based on formula (2) in the 
	manuscript. Formula (2) is the standard definition of the classical 
	Renyi entropy, which in the limit $n\to 1$ become the Shannon entropy. 
	Formula (2) and the Shannon entropy can be used in systems that do not 
	have the notion of space and locality. The two subsystems A and B 
	appearing in (2) can be interpreted as two complementary groups of 
	spins, without any need for an underlying spatial bipartition. Thus, 
	the quantities that we address in our study, e.g., the mutual information, 
	are well-grounded from an information theoretical point of view. This 
	is now stressed in the introduction below formula (2) with the sentence

		" For local spin models the bipartition correspond to a spatial 
		separation between the spins. However, the definition~\eqref{renyi-intro} 
		can be used  in models with no notion of space, where it quantifies 
		the correlation between two groups of spins rathen than two spatial 
		regions."

	Moreover, (2) can be interpreted as ratios of partition functions defined 
	on the booklet. This is an exact correspondence, and it is not related to 
	any notion of locality. To clarify this point we now show explicitly the 
	equivalence between the booklet construction and (2) in the beginning of 
	section 2. From the derivation it is clear that the booklet construction 
	is meaningful also in mean-field models.

	Besides its meaning from the information theory point of view, from the 
	physics perspective the mutual information provides a lot of information 
	about critical systems without disorder. One of the most striking example is 
	provided by the results in Ref. [29] in the manuscript. We believe that it is 
	a natural and interesting question to study the mutual information in 
	disordered systems, especially in presence of glassy physics.

	(i) For instance, an interesting physics question per se it is to understand 
	what are the fingerprints, if any, of glassy physics in the mutual 
	information or in information-based quantities in general.

	(ii) A related question is whether 
	information motivated quantities could provide alternative good criticality 
	witnesses for glassy transitions. To this purpose we should stress that 
	even in the simple S-K while it is relatively easy to determine numerically 
	the critical point of the paramagnetic-glassy transition using standard 
	tools from critical phenomena, such as the Binder cumulant. In presence 
	of a transverse magnetic field the transition persists but the critical 
	point changes as a function of the field strength (Almeida-Thouless line). 
	In presence of a field it is however much more demanding, as it is shown 
	numerically for instance in

		M. Picco, F. Ritort, and M. Sales, Eur. Phys. J. B 19, 565 (2001)

	Even more difficult it is to clarify whether there is an Almeida-Thouless 
	line in short-range disordered spin models.

	Our work, although for the S-K model, provides the first results in this 
	direction. Concerning (i) for the S-K model a related question is about 
	the effect of the replica symmetry breaking on information motivated 
	quantities. We clarified that while in the low-temperature phase of the 
	model the replica symmetry breaking is reflected in the mutual information.

	As correctly observed by the referee the 1RSB approximation is enough to 
	obtain good agreement with the Monte Carlo simulations. However, we should 
	stress that this is not true at arbitrarily low temperatures, as 
	at some point the effects of the higher order replica symmetry breaking 
	should become visible.

	Concerning (ii)  our work shows that for mean-field spin glasses the 
	mutual information does not show any crossing for different system sizes 
	at the critical point. This implies that the muutual information as defined 
	in the manuscript cannot be used as a good indicator of glassy phase 
	transitions.

	One interesting question would be whether this "failure" is due to the 
	non locality of the model or to the presence of disorder. This could be 
	investigated in disordered models exhibiting a glassy transition. This 
	can be done only numerically as there is no exactly solvable model with 
	spin glass transition and local interactions. Moreover, one should consider 
	a three dimensional model. In fact, to our knowledge there are no glassy 
	transitions at finite temperature in disordered spin models. This certainly 
	goes beyond the scope of the present work.

	Another possibility, as observed by the referee, it is that one has to 
	focus on the subleading corrections to the mutual information in order 
	to obtain a clear signature of the glassy transition. In general, subleading 
	corrections to the entropies have been investigated a lot in the literature 
	in the context of topolocical phases of matter, systems breaking continuous 
	symmetries and bipartitions with sharp corners.

	Figure 9 in our work provides some hints in this direction. Clearly the scaling 
	corrections are dramatically different in the paramagnetic and in the glassy 
	phase, decaying much more slowly in the latter. We regret we did not stress 
	enough this point in the manuscript. We now added the sentence in the introduction

		"We numerically observede that while in the paramagnetic phase the 
		scaling correction to the muatual information decay as 1/L, a much 
		slower decay as 1/L^2/3 is observed in the glassy phase."

	The study of these scaling corrections, although possible using the same 
	techniques employed for the regular S-K model, it is demanding as it requires 
	using the corrections to the saddle point treatment presented in section II.

REFEREE:
-------

	Is there any other work treating the booklet geometry in mean field 
	systems? For example, what is obtained for the simple, pure Ising model 
	with infinite-range interaction?

RESPONSE:
========

	The only study we are aware of is in

		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P01023 (2012)

	In this work the authors investigate the mutual information in the Lipkin-Meshkov-Glick 
	(LMG) model. In particular, they provide results for the case with zero magnetic field, 
	where the model becomes equivalent to a classical infinite-range Ising model. However, 
	the authors investigate the standard mutual information which is obtained from the 
	full reduced density matrix of the subsystem A.

	In contrast with our results the authors find that the mutual information is finite 
	away from the critical point and diverges logarithmically at the critical point.

	In our case this logarithmic correction might be subleading to the volume law.

	TO BE COMPLETED

	About the maximum

		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P010011 (2011)

REFEREE:
-------
	(2). The definition of the mutual information in the present case is
	not clear for me. Please describe how to define and calculate S(B) and
	S(A or B) in the SK model.

RESPONSE:
========

	We thank the referee for this useful comment. 
	Eq. (2), and later Eq. (5) via the replica trick, are both quite explicit. 
	Combined with Eq. (4) this precisely described the mutual information in 
	the SK model. The non-locality of the interactions does 
	not affect the definition compared with the usual one for local models. 
	The definition of region A is however less obvious, and in the case of 
	this work, we simply take it as an arbitrary set of points, rather than 
	one that is spatially connected. As it is clear from the manuscript 
	the best way to calculate the mutual information is using (4) calculating 
	the three different contributions S(A) S(B) and S(AUB) separately. These 
	correspond to ratios of partition functions on the booklet with different 
	aspect ratio omega. As this was not clearly stated in the manuscript we now 
	have written it explicitly in section 2

		"The mutual information ${\mathcal I}_n(A,B,\beta)$ is obtained in terms of the booklet 
		partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}. 
		%%%
		Clearly, $S_n(B)$ (cf. Eq.~\eqref{MI}) is obtained from~\eqref{renyi} and exchanging 
		$A$ and $B$. Notice also that in~\eqref{renyi}  $Z(A\cup B,n,\beta)\equiv Z(n\beta)$ 
		is the partition function of the model on the booklet with all the $n$ sheets identified, 
		equivalently on a single sheet but at temperature $n\beta$."

	From the numerical point of view, the strategy to evaluate the ratios of partition 
	functions in (5) is outlined Appendix B.

REFEREE:
-------

	(3). The authors summarized that the entropy is proportional to the
	system size by using the numerical analysis. Since the entropy is
	calculated from the logarithm of the partition function, the result
	looks trivial for me. As far as I understand, the subleading term is
	important to find the boundary law behavior in the local (non
	mean-field) models. (The leading term is canceled out by the
	definition of the mutual information). Do the authors consider that
	the subleading term is not important in the present system? I expect
	that some universal properties exist in the subleading terms.

RESPONSE:
========

	We agree that in general the leading term is proportional to the 
	system size is an obvious result. In the manuscript we report 
	the entropy only as a sanity check of our calculations.  We also 
	agree that it is likerly that the subleading terms contain 
	more universal information. We thank the referee for raising this 
	point. Although the calculation of the subleading corrections to 
	the entropy and the mutual information is possible in principle, 
	it requires going beyond the saddle point approximation described 
	in section III C. This should be straightforward in the paramagnetic 
	phase although it would require a considerable amount of work in 
	below the critical point. Notice that the same problem is 
	challenging in the regular SK model. We think that this goes 
	beyond the scope of the paper and it is suitable for future work.

	PUT REFERENCE TO PAPERS STUDYING FINITE SIZE IN SK

REFEREE:
-------

	(4). The authors study the aspect-ratio dependence of the result
	closely. It is clearly understood that the limits omega=0 and 1
	reduces to the standard results. This means that we can find a result
	interpolating their limits in the present problem. I do not expect any
	interesting behavior between the limits. What did the authors expect
	as the result and what do the authors consider the obtained results
	interesting, other than the crossing behavior?

RESPONSE:
========

	We agree that omega=0 and 1 are trivial results, at least in terms of 
	the standard SK model, and that one would expect that the results between 
	these two points should vary smoothly, and this is reflected in the data. 
	What was not obvious was the form of the interpolation between these two 
	points. The same statement of the referee would apply to local models.  
	However, as it is clear from Ref [29], in that case the shape function of the mutual 
	information contains universal behavior if the parent model is critical and 
	described by a conformal field theory. In our study we investigate the 
	shape function in a non-trivial disordered model. Notice that this functions 
	have been also investigated in clean (withoud disorder) mean field models 
	in 
		O. Cohen, V. Rittenberg, T. Sadhu J Phys A 48 055002 (2015)

		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P01023 (2012)

	In that respect, 
	we believe it was worth examining the aspect ratio behavior in the SK model. 
	The difference of course is that since the gluing procedure is a bulk effect, 
	the entire system may go through a phase transition as a function of omega, 
	rather than being able to view the system as two parts in contact with each 
	other where one part is critical. In this light, it might be some non-constant 
	temperature cut in (omega,beta) that shows the most interesting behavior.

REFEREE:
-------

	(5). This comment is related to the previous one (4). Strictly
	speaking, I do not see any surprising behavior in the result. What is
	the significance of the present study? Did the authors find anything
	on the information properties of the SK model?

RESPONSE:
========

	The non surprising result would have been if 1-RSB would have reproduced the results 
	of the Monte Carlo simulation. The fact that 2-RSB was necessary shows the non-trivial 
	nature of the transition in the replicated geometry, and represents an expanded set of 
	assumptions compared to the base model. The procedure for handling disorder, usually done 
	via integration over fictitious replicas, in the context of the replica trick, where one 
	has physical replicas, is non-trivial, but grounding such theoretical calculations with 
	numerics is necessary. In this respect, we see the SK model with the replica trick as a 
	base case for studying replica models  in glassy systems, in the same way that the SK 
	model itself is a prototype for understanding standard glassy systems.

REFEREE:
-------

	(6). The authors only focused on the result at n=2. It would be
	interesting if the authors mention the n-dependence of the result.
	Especially, the limit n=1 would give a nontrivial result and is
	interesting. I expect that it wouldn't be difficult to analyze the
	replica symmetric solution.

RESPONSE:
========

	TO BE DONE.

REFEREE:
-------

	(7). Although the manuscript is written very clearly, it is somewhat
	too long. For example, the authors summarized the results in the
	introduction, and they are described again in the final section. It is
	not necessary to summarize the results in the introduction.

RESPONSE:
========

	We would like to thank the referee for this useful comment. We now 
	summarize the main results of the paper in the conclusions.

REFEREE:
-------
	(8). J_{ij} should be inserted in Eq.(10).

RESPONSE:
========

	We thank the referee for spotting this. We restored the missing J_{ij} in 
	Eq. (10).

REFEREE:
-------

	(9). I am not sure whether this manuscript is suitable to PRB. I would
	think that PRE is more appropriate.

RESPONSE:
========

	Argue that similar paper appeared in PRB.

In conclusion, the manuscript will be taken into consideration for
publication if the authors clarify the physical significance of the
analysis. And, I recommend the authors to reconsider the journals to
submit the manuscript.

### 2015-12-10 sk_model_v19.tex
rev-10/11/2015

--- 2015-07-04 sk_model_v18.tex
@@
 %
+%%%
+For local spin models the bipartition correspond to a spatial separation 
+between the spins. However, the definition~\eqref{renyi-intro} can be used  
+in models with no notion of space, where it quantifies the correlation between two 
+groups of spins rathen than two spatial regions.  
+%%%
 Notice that Eq.~\eqref{renyi-intro} can also be used for quantum systems by replacing 
@@
 For any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, which is divided 
-by the standard paramagnetic one at high temperatures by a phase transition. The critical 
-temperature exhibits a non trivial dependence on $\omega$ that we are able to determine 
-analytically. In the high-temperature region the permutation symmetry among both the replicas  
+by the standard paramagnetic one at high temperatures by a phase transition. 
+%%%
+The critical 
+inverse temperature $\beta_c$ exhibits a non trivial decreasing behavior as a function of 
+$\omega$ that we are able to determine analytically. Moreover, one has $\beta_c=1$ 
+and $\beta_c=1/2$ for $\omega=0$ and $\omega=1$, respectively. 
+%%%
+In the high-temperature region the permutation symmetry among both the replicas  
 and the physical sheets  is preserved. This allows us to provide an exact 
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/cartoon}
+%\includegraphics*[width=0.93\linewidth]{./cartoon}
 \caption{ The booklet geometry considered in this work. (a) The single sheet 
@@
 Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
-the classical R\'enyi entropy $S_n(A)$ is defined as~\cite{jaconis-2013,stephan-2014} 
+The probability $p_i$ of a given spin configuration $i\in{\mathcal C}$, with ${\mathcal 
+C}$ being the set of all possible configurations, is given by the Boltzmann weight 
+$p_i=e^{-\beta E(i)}/Z$, with $E(i)$ the associated energy. In presence of a 
+bipartition (see Fig.~\ref{cartoon} (a)) the probability of a spin configuration 
+$i_A\in{\mathcal C}_A$ is given as 
+$p_{i_A}=\sum_{i_B}e^{-\beta E(i_A,i_B)}/Z$, where the sum is over all possible 
+spin configurations in part $B$. Note that this is valid for generic interactions, 
+i.e., both local and non-local ones. Clearly, one has $p^n_{i_A}\equiv\frac{1}{Z^n}
+\sum_{(i^1_B,\dots,i^n_{B})}e^{-\beta\sum_k E(i_A,i^k_{B})}$. 
+Thus, the classical R\'enyi entropy $S_n(A)$ (Eq.~\eqref{renyi-intro}) can be 
+calculated as~\cite{jaconis-2013,stephan-2014} 
 %
@@
 %
-Here $Z(A,n,\beta)$ is the partition function of the model on the $n$-sheet booklet, 
-whereas $Z(\beta)$ is the partition functions on the plane at inverse temperatures 
-$\beta$. The booklet geometry is illustrated in Fig.~\ref{cartoon}, and consists of 
-$n$ identical copies (``sheets'') of the system. Each sheet is divided into two 
+Here $Z(A,n,\beta)\equiv\sum_{i_A,(i_B^1,\dots,i_B^n)}e^{-\beta\sum_k E(i_A,i^k_{B})}$ 
+can be interpreted as  the partition function of the model on the $n$-sheet booklet (with $k$ 
+labelling its different sheets), whereas $Z(\beta)$ is the partition functions on the plane at 
+inverse temperatures $\beta$. The booklet geometry is illustrated in Fig.~\ref{cartoon}, 
+and consists of $n$ identical copies (``sheets'') of the system. Each sheet is divided into two 
 parts $A$ and $B$ (cf. Fig.~\ref{cartoon} (a)). The spins in part $A$ of the different 
@@
 The mutual information ${\mathcal I}_n(A,B,\beta)$ is obtained in terms of the booklet 
-partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}. Notice that the disorder-averaged 
+partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}. 
+%%%
+Clearly, $S_n(B)$ (cf. Eq.~\eqref{MI}) is obtained from~\eqref{renyi} and exchanging 
+$A$ and $B$. Notice also that in~\eqref{renyi}  $Z(A\cup B,n,\beta)\equiv Z(n\beta)$ 
+is the partition function of the model on the booklet with all the $n$ sheets identified, 
+equivalently on a single sheet but at temperature $n\beta$. 
+%%%
+Notice that the disorder-averaged 
 mutual information $[{\mathcal I}_n]$ and the R\'enyi entropy $[S_n]$ are directly related to 
@@
 and $B\equiv\{N_A+1,\dots,N\}$, containing $N_A$ and $N_B\equiv N-N_A$ sites, 
-respectively. The spins living in part $A$ and different sheets are identified, i.e., 
-$\forall i\in A$ one has  
-%
-\begin{equation}
-S_i^{(r)}=S_{i}^{(r')}\quad\forall\, r,r'. 
+respectively. The spins living in part $A$ and different sheets are identified, i.e. 
+one has  
+%
+\begin{equation}
+S_i^{(r)}=S_{i}^{(r')}\quad\forall\, i\in A,r,r'. 
 \label{book-constraint}
@@
 \includegraphics*[width=0.9\linewidth]{./draft_figs/RSB0_saddle_ht}
+%\includegraphics*[width=0.9\linewidth]{./RSB0_saddle_ht}
 \caption{
@@
 \includegraphics*[width=0.9\linewidth]{./draft_figs/RSB0_saddle}
+%\includegraphics*[width=0.9\linewidth]{./RSB0_saddle}
 \caption{\label{RSB0-saddle}
@@
 \includegraphics*[width=0.9\linewidth]{./draft_figs/betac}
+%\includegraphics*[width=0.9\linewidth]{./betac}
 \caption{
@@
 Near the glassy transition one should expect $q'_0\to0$, whereas $q_0$ 
-should remain finite (see section~\ref{para-section}). By expanding $[F_{RS}(\omega,n,\beta)]$ 
-(cf. Eq~\eqref{rs-F}) for small $q_0'$, and keeping only terms up to ${\mathcal O}((q_0')^2)$, 
-one obtains a standard Landau theory. Thus, $\beta_c$ is obtained by imposing that the 
-coefficient of the quadratic term $q_0'^2$ vanishes. This leads to the equation 
+should remain finite (see section~\ref{para-section}). 
+%%%
+One expands $[F_{RS}(\omega,n,\beta)]$ 
+(cf. Eq~\eqref{rs-F}) for small $q_0'$, keeping only terms up to ${\mathcal O}((q_0')^2)$. 
+Thus, $\beta_c$ is obtained by imposing that the coefficient of the quadratic term $q_0'^2$ 
+vanishes. This leads to the equation 
+%%%
 %
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/U_w05}
+%\includegraphics*[width=0.93\linewidth]{./U_w05}
 \caption{
@@
  squares, and rhombi, denote the Monte Carlo data for a booklet with 
- $N=32,64,128$ spins per sheet. The plus symbols are the extrapolations to the 
+ $N=32,64,128$ spins per sheet. Notice that the Monte Carlo error bars are 
+ often smaller than the symbol sizes. The plus symbols are the extrapolations to the 
  thermodynamic limit $N\to\infty$, at fixed $\omega$. The dash-dotted line is the 
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/U_extrapolated}
+%\includegraphics*[width=0.93\linewidth]{./U_extrapolated}
 \caption{
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/U_extrapolated_v1}
+%\includegraphics*[width=0.93\linewidth]{./U_extrapolated_v1}
 \caption{
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/Renyi_MC_v2}
+%\includegraphics*[width=0.93\linewidth]{./Renyi_MC_v2}
 \caption{ The classical disorder-averaged R\'enyi entropy per spin $[S_2(\omega)]/N$  
@@
  The triangles, squares and rhombi denote the Monte Carlo results for 
- booklets with $N=32,64,128$ spins per sheet. The plus symbols are the numerical 
+ booklets with $N=32,64,128$ spins per sheet. The Monte Carlo error bars are often 
+ smaller than the symbol size. The plus symbols are the numerical 
  extrapolations to the thermodynamic limit. The inset in panel (a) shows 
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/I2_MC_v1}
+%\includegraphics*[width=0.93\linewidth]{./I2_MC_v1}
 \caption{The classical disorder-averaged mutual information per spin $[{\mathcal I}_2]/N$ 
@@
  (see Fig.~\ref{cartoon}). The same scale is used on both axes in all 
- panels. The symbols are the Monte Carlo data 
- for systems with $N=32,64,128$ spins per sheet. The dash-dotted line is 
- the analytical result in the replica-symmetric (RS) approximation.  
+ panels. The symbols are the Monte Carlo data for systems with $N=32,64,128$ 
+ spins per sheet. The Monte Carlo error bars are smaller than the symbol size. 
+ The dash-dotted line is the analytical result in the replica-symmetric (RS) 
+ approximation.  
 }
@@
 \includegraphics*[width=0.93\linewidth]{./draft_figs/I2_extrapolated}
+%\includegraphics*[width=0.93\linewidth]{./I2_extrapolated}
 \caption{The classical mutual information per spin $[{\mathcal I}_2]/N$ 

### 2015-12-10 sk_model_v20.tex
rev-10/11/2015

--- 2015-12-10 sk_model_v19.tex
@@
 \documentclass[twocolumn,superscriptaddress,prb,10pt]{revtex4-1}
-%\usepackage{verbatim}
+\usepackage{verbatim}
 \usepackage{amsmath,amssymb}
@@
 
-We start discussing the thermodynamic phase diagram of the S-K model on the $n$-sheets 
-booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
-For any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, which is divided 
-by the standard paramagnetic one at high temperatures by a phase transition. 
-%%%
-The critical 
-inverse temperature $\beta_c$ exhibits a non trivial decreasing behavior as a function of 
-$\omega$ that we are able to determine analytically. Moreover, one has $\beta_c=1$ 
-and $\beta_c=1/2$ for $\omega=0$ and $\omega=1$, respectively. 
-%%%
-In the high-temperature region the permutation symmetry among both the replicas  
-and the physical sheets  is preserved. This allows us to provide an exact 
-analytic expression for the free energy of the model and several derived quantities, such as 
-the internal energy. We compare our results with Monte Carlo simulations, finding perfect 
-agreement. Oppositely, in the low-temperature phase the replica symmetry is broken. For 
-instance, we numerically observe that the replica-symmetric (RS) result for the internal 
-energy is systematically lower than the Monte Carlo data, as in the standard S-K 
-model~\cite{sherrington-1978-prl,sherrington-1978}. This discrepancy becomes larger upon 
-lowering the temperature.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
@@
 
-Inspired by the Parisi scheme~\cite{parisi-1979}, we devise a systematic way of breaking 
-the replica symmetry in successive steps. In our scheme we break only the symmetry among 
-the fictitious replicas, preserving that among the physical ones. Although this appears 
-natural, we are not able to provide a rigorous proof that this is the correct symmetry 
-breaking pattern. As a consequence, our scheme should be regarded as an approximation, 
-and not as an exact solution. Moreover, we restrict ourselves to the one-level replica 
-symmetry breaking ($1$-RSB). Surprisingly, the $1$-RSB result for the internal energy 
-is in excellent agreement with the Monte Carlo data for  $\beta\lesssim 3$, whereas the 
-RS approximation fails already at $\beta\approx 1$. This suggests that the $1$-RSB ansatz 
-captures correctly some aspects of the replica symmetry breaking.
-
-Clear signatures of the replica symmetry breaking are observed in the behavior of $[S_2]$. 
-First, since $[S_2]$ exhibits the volume law behavior $[S_2]\propto N$, 
-we consider its density $[S_2]/N$. For finite-size systems, and for any $\omega$, $[S_2]/N$ 
-exhibits a maximum at infinite temperature, and it is a decreasing function of the temperature, 
-as expected. Finite-size corrections are negligible at high temperatures, whereas they increase 
-upon lowering the temperature. In the paramagnetic phase we are able to determine the functional 
-form of $[S_2]/N$ in the thermodynamic limit, using the replica-symmetric approximation. This 
-perfectly matches the Monte Carlo data. At low temperatures deviations from the RS result are 
-present, reflecting the replica symmetry breaking. Remarkably, the one-step replica symmetry 
-breaking ($1$-RSB) result $[S_2^{1\textrm{-}RSB}]/N$ is in full agreement with the Monte Carlo 
-data for $\beta\lesssim 3$, consistent with what is observed for the internal energy.
-
-Finally, we consider the R\'enyi mutual information $[{\mathcal I}_2]$. This obeys a volume 
-law for any $\beta$ and $\omega$, in contrast with local spin models, where an area law is 
-observed~\cite{wolf-2008}. The corresponding density $[{\mathcal I}_2]/N$ vanishes in 
-both the infinite-temperature and the zero-temperature limits. Surprisingly, $[{\mathcal I}_2]/N$ 
-does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition, 
-in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, $[{\mathcal I}_2]/N$ 
-exhibits a maximum for $\beta\approx 1$. The position of this maximum is not simply 
-related to the paramagnetic-glassy transition. At high temperature $[{\mathcal I}_2]/N$ 
-is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$. Deviations from the RS result, 
-if present, are $\lesssim 10^{-3}$. On the other hand, at low temperatures 
-one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
-approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ is in good agreement with the Monte Carlo 
-data for $\beta\lesssim 3$.
-
 The Article is organized as follows. In section~\ref{booklet} we introduce the classical 
@@
 \textrm{Tr}'\exp\Big\{\beta\sum\limits_{r}\Big(
-\sum\limits_{i<j}S^{(r)}_i 
+\sum\limits_{i<j}J_{ij}S^{(r)}_i 
 S^{(r)}_j-h\sum\limits_{i=1}^NS^{(r)}_i\Big)\Big\},
@@
 of mean-field spin glasses. We focused on the quenched averages $[S_n]$ and $[{\mathcal I}_n]$. 
-Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ were obtained from suitable combinations 
+Specifically, here $[S_n]$ and $[{\mathcal I}_n]$ are obtained from suitable combinations 
 of the partition functions of the S-K model on the $n$-sheets booklet (cf. Fig.~\ref{cartoon}). 
@@
 
-We first investigated the phase diagram of the S-K model on the $2$-sheets booklet as a 
-function of $\omega$, and the inverse temperature $\beta$. We considered the situation 
-without external magnetic field ($h=0$ in Eq.~\eqref{SK-intro}). For any $\omega$, in the 
-thermodynamic limit, the model exhibits a glassy phase for low enough temperatures and 
-a standard paramagnetic one at high temperature. The two phases are divided 
-by a phase transition, as in the S-K model on the plane. The critical temperature exhibits 
-a non-trivial dependence on $\omega$ that we determined analytically. We fully characterized 
-the high-temperature phase of the model using the replica-symmetric (RS) ansatz. Specifically, 
-we provided the exact analytical expression for the disorder-averaged free energy 
-$[F_{para}(\omega,n,\beta)]$  (cf. Eq.~\eqref{ht-logZ}) in the thermodynamic limit. In the 
-glassy phase the replica symmetry has to be broken, similar to the standard S-K model. To take 
-into account the effects of the replica symmetry breaking we used a generalization of the 
-Parisi ansatz~\cite{parisi-1980}, i.e., breaking the replica symmetry in successive steps. 
-We restricted ourselves to the one-step replica symmetry breaking ($1$-RSB), providing the 
-exact expression for the disorder-averaged free energy $F_{1\textrm{-}RSB}(\omega,n,\beta)$ 
-(cf. Eq.~\eqref{RSB-1-logZ}).
-
-We compared our analytical results with Monte Carlo simulations, focusing on the internal 
-energy per spin $U(\omega,n,\beta)/N$. In the high-temperature region, where the replica 
-symmetry is not broken, the Monte Carlo data are in perfect agreement with the replica-symmetric 
-result $U_{RS}/N$, for any $\omega$. In the glassy phase at low temperature, significant 
-deviations from $U_{RS}$ can be observed already at $\beta\approx 1$. On the other hand, 
-the one-step replica-symmetry-broken approximation $U_{1\textrm{-}RSB}/N$ accurately matches 
-the Monte Carlo data for $\beta\lesssim 3$.
-
-Finally, we discussed the behavior of $[S_2]$ and $[{\mathcal I}_2]$. Due to the mean-field 
-nature of the S-K model one has the volume laws $[S_2]\propto N$ and $[{\mathcal I}_2]\propto N$, 
-for any $\beta$. We considered the densities $[S_2]/N$ and $[{\mathcal I}_2]/N$. Using the 
-replica-symmetric (RS) and the one-step replica symmetry breaking ($1$-RSB) approximations we 
-provided analytical results for both $[S_2]/N$ and $[{\mathcal I}_2]/N$. At high temperature the 
-RS result fully agrees with the Monte Carlo simulations, whereas deviations occur in the 
-glassy phase, signalling the replica symmetry breaking. Similar to the internal energy, 
-the $1$-RSB approximation fully matches the Monte Carlo data for $\beta\approx 3$.
-Interestingly, at the critical point $[{\mathcal I}_2]/N$ does not show any crossing for 
-different system sizes, in contrast with local models~\cite{jaconis-2013}.
+We first discussed the thermodynamic phase diagram of the S-K model on the $n$-sheets 
+booklet, as a function of temperature, and the aspect ratio $\omega$ (cf. Eq.~\eqref{a-ratio}). 
+For any fixed $\omega$ the S-K model exhibits a low-temperature glassy phase, which is divided 
+by the standard paramagnetic one at high temperatures by a phase transition. 
+%%%
+The critical inverse temperature $\beta_c$ exhibits a non trivial decreasing behavior as a 
+function of $\omega$. Moreover, one has $\beta_c=1$ and $\beta_c=1/2$ for $\omega=0$ and 
+$\omega=1$, respectively. 
+%%%
+In the high-temperature region the permutation symmetry among both the replicas  and the physical 
+sheets  is preserved. This allowed us to provide an exact analytic expression for the free 
+energy of the model and several derived quantities, such as the internal energy. 
+We compared our results with Monte Carlo simulations, finding perfect agreement. Oppositely, 
+in the low-temperature phase the replica symmetry is broken. For instance, we numerically 
+observed that the replica-symmetric (RS) result for the internal energy is systematically 
+lower than the Monte Carlo data, as in the standard S-K model~\cite{sherrington-1978-prl,
+sherrington-1978}. This discrepancy becomes larger upon lowering the temperature.
+
+Inspired by the Parisi scheme~\cite{parisi-1979}, we devised a systematic way of breaking 
+the replica symmetry in successive steps. Our scheme breaks only the symmetry among 
+the fictitious replicas, preserving that among the physical ones. Although this appears 
+natural, we were not able to provide a rigorous proof that this is the correct symmetry 
+breaking pattern. As a consequence, our scheme should be regarded as an approximation, 
+and not as an exact solution. Moreover, we restricted ourselves to the one-level replica 
+symmetry breaking ($1$-RSB). Surprisingly, the $1$-RSB result for the internal energy 
+were in excellent agreement with the Monte Carlo data for  $\beta\lesssim 3$, whereas the 
+RS approximation failed already at $\beta\approx 1$. This suggests that the $1$-RSB ansatz 
+captures correctly some aspects of the replica symmetry breaking.
+
+Clear signatures of the replica symmetry breaking can be observed in the behavior of $[S_2]$. 
+First, since $[S_2]$ exhibits the volume law behavior $[S_2]\propto N$, we considered its 
+density $[S_2]/N$. For finite-size systems, and for any $\omega$, $[S_2]/N$ 
+exhibits a maximum at infinite temperature, and it is a decreasing function of the temperature, 
+as expected. Finite-size corrections are negligible at high temperatures, whereas they increase 
+upon lowering the temperature. In the paramagnetic phase we are able to determine the functional 
+form of $[S_2]/N$ in the thermodynamic limit, using the replica-symmetric approximation. This 
+perfectly matched the Monte Carlo data. At low temperatures deviations from the RS result are 
+present, reflecting the replica symmetry breaking. Remarkably, the one-step replica symmetry 
+breaking ($1$-RSB) result $[S_2^{1\textrm{-}RSB}]/N$ fully described the Monte Carlo 
+data for $\beta\lesssim 3$, consistent with what was observed for the internal energy.
+
+Finally, we considered the R\'enyi mutual information $[{\mathcal I}_2]$. This obeys a volume 
+law for any $\beta$ and $\omega$, in contrast with local spin models, where an area law is 
+observed~\cite{wolf-2008}. The corresponding density $[{\mathcal I}_2]/N$ vanishes in 
+both the infinite-temperature and the zero-temperature limits. Surprisingly, $[{\mathcal I}_2]/N$ 
+does not exhibit any crossing for different system sizes at the paramagnetic-glassy transition, 
+in striking contrast with local spin models~\cite{jaconis-2013}. For any $\omega$, $[{\mathcal I}_2]/N$ 
+exhibits a maximum for $\beta\approx 1$. The position of this maximum is not simply 
+related to the paramagnetic-glassy transition. At high temperature $[{\mathcal I}_2]/N$ 
+is described analytically by the RS result $[{\mathcal I}_2]^{RS}/N$. Deviations from the RS result, 
+if present, are $\lesssim 10^{-3}$. On the other hand, at low temperatures 
+one has to include the effects of the replica symmetry breaking. Similar to $[S_2]$, the $1$-RSB 
+approximation $[{\mathcal I}^{1\textrm{-}RSB}_2]/N$ is in good agreement with the Monte Carlo 
+data for $\beta\lesssim 3$.
 
@@
 %##########################################################################
+\section{Mutual information in the infinite-range clean Ising model}
+\label{clean-is}
+
+Here we discuss the R\'enyi entropies and the mutual information in the 
+infinite-range Ising model withoud disorder defined by the hamiltonian 
+%
+\begin{equation}
+\label{is-clean}
+{\mathcal H}=-\frac{J}{N}\sum\limits_{i<j}S_iS_j+h\sum_i S_i.
+\end{equation}
+%
+Here we consider the situation without external magnetic field, i.e., 
+$h=0$ and fix $J=1$.
+
+The calculation of the booklet partition function $Z(\omega,n,\beta)$ is 
+done using the same techniques as in section~\ref{}. The result reads 
+%
+\begin{multline}
+\label{clean-is-Z}
+Z(\omega,n,\beta)=
+\exp\Big(-\frac{\beta}{2}n\Big)\Big(2\pi\frac{\beta}{N}\Big)^{-\frac{n}{2}}
+\int\prod_{\delta}dz_\delta\exp N\Big\{\\
+-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
+-(1-\omega)\log(2\cosh z_\delta)\Big]+\omega\log(2\cosh\sum_\delta z_\delta)
+\Big\}.
+\end{multline}
+%
+Using the saddle point approximation one obtains 
+%
+\begin{multline}
+\label{clean-is-F}
+\log Z(\omega,n,\beta)\approx
+N\Big\{-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
+-(1-\omega)\log(2\cosh z_\delta)\Big]\\
++\omega\log(2\cosh\sum_\delta z_\delta)\Big\}, 
+\end{multline}
+%
+where we neglected subleading contributions $o(N)$. The parameters 
+$\{z_\delta\}_{\delta=1}^n$ are solutions of the saddle point equations 
+%
+\begin{equation}
+\label{clean-is-spe}
+0=z_\delta-\beta(1-\omega)\tanh z_\delta-\beta\omega\tanh\big(\sum_\delta 
+z_\delta\big),\quad \forall\delta.
+\end{equation}
+%
+For $n=2$, Eq.~\eqref{clean-is-spe} become 
+%
+\begin{align}
+0=z_1-\beta(1-\omega)\tanh z_1-\beta\omega\tanh\big(z_1+z_2\big)\\
+0=z_2-\beta(1-\omega)\tanh z_2-\beta\omega\tanh\big(z_1+z_2\big). 
+\end{align}
+%
+The system has the solution $z_1=z_2=0$ for $\beta\le\beta_c=1/(1+\omega)$, 
+and $z_1=z_2\ne 0$ for $\beta>\beta_c$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
+\begin{figure}[t]
+\includegraphics*[width=0.9\linewidth]{./draft_figs/saddle_clean}
+%\includegraphics*[width=0.9\linewidth]{./RSB0_saddle_ht}
+\caption{
+ The S-K model on the $2$-sheets booklet in the 
+ paramagnetic phase: the solution $q_0$ of the saddle point 
+ equation~\eqref{saddle-high-t} plotted as a function of the booklet aspect 
+ ratio $\omega$ and several values of the inverse temperature $\beta=1/T$. 
+ At $\omega=1$ one has $q_0=1,\forall\beta$. In the zero-temperature limit 
+ one has $q_0\to 1,\forall\omega$. The straight line is the infinite 
+ temperature result. 
+}
+\label{saddle_clean}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
+\begin{figure}[t]
+\includegraphics*[width=0.9\linewidth]{./draft_figs/renyi_clean}
+%\includegraphics*[width=0.9\linewidth]{./RSB0_saddle_ht}
+\caption{
+ The S-K model on the $2$-sheets booklet in the 
+ paramagnetic phase: the solution $q_0$ of the saddle point 
+ equation~\eqref{saddle-high-t} plotted as a function of the booklet aspect 
+ ratio $\omega$ and several values of the inverse temperature $\beta=1/T$. 
+ At $\omega=1$ one has $q_0=1,\forall\beta$. In the zero-temperature limit 
+ one has $q_0\to 1,\forall\omega$. The straight line is the infinite 
+ temperature result. 
+}
+\label{saddle_clean}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%##########################################################################
 \section{Monte Carlo method to calculate the classical R\'enyi entropies}

### 2015-12-10 compile.sh

@@ -1,3 +1,3 @@
 #latex sk_model_v15.tex
 #dvipdf sk_model_v15.dvi
-pdflatex sk_model_v18.tex
+pdflatex sk_model_v20.tex

### 2015-12-14 sk_model_v20.tex
15/12/2015

@@
  analytical results in the replica-symmetry (RS) approximation. 
- The circles are the analytical results obtained 
- using the one-step replica symmetry breaking (1-RSB) ansatz.
+ The circles are the analytical results obtained  using the one-step replica 
+ symmetry breaking (1-RSB) ansatz. In panel (c) the dotted line (clean Ising) is the 
+ analytic result for the infinite-range Ising model without disorder. 
 }
@@
 
-Here we discuss the R\'enyi entropies and the mutual information in the 
-infinite-range Ising model withoud disorder defined by the hamiltonian 
+Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
+${\mathcal I}_2$ in the infinite-range Ising model without disorder defined by 
+the hamiltonian 
 %
@@
 %
-Here we consider the situation without external magnetic field, i.e., 
-$h=0$ and fix $J=1$.
-
-The calculation of the booklet partition function $Z(\omega,n,\beta)$ is 
-done using the same techniques as in section~\ref{}. The result reads 
+We consider the situation without external magnetic field, i.e., $h=0$ and 
+fix $J=1$.
+
+%##########################################################################
+\subsection{Saddle point approximation}
+
+The calculation of the booklet partition function $Z(\omega,n,\beta)$ 
+(see section~\ref{booklet}) can be done using the same techniques as in 
+section~\ref{the-model}. The result reads 
 %
@@
 %
-Using the saddle point approximation one obtains 
+Using the saddle point approximation, from~\eqref{clean-is-Z} one obtains 
+$F(\omega,n,\beta)\equiv\log Z(\omega,n,\beta)$ as 
 %
@@
 \label{clean-is-F}
-\log Z(\omega,n,\beta)\approx
+F(\omega,n,\beta)\approx
 N\Big\{-\sum_\delta\Big[\frac{z^2_\delta}{2\beta}
@@
 %
-For $n=2$, Eq.~\eqref{clean-is-spe} become 
+For $n=2$, the system~\eqref{clean-is-spe} becomes 
 %
 \begin{align}
-0=z_1-\beta(1-\omega)\tanh z_1-\beta\omega\tanh\big(z_1+z_2\big)\\
-0=z_2-\beta(1-\omega)\tanh z_2-\beta\omega\tanh\big(z_1+z_2\big). 
+& 0=z_1-\beta(1-\omega)\tanh z_1-\beta\omega\tanh\big(z_1+z_2\big)\\
+& 0=z_2-\beta(1-\omega)\tanh z_2-\beta\omega\tanh\big(z_1+z_2\big). 
 \end{align}
 %
-The system has the solution $z_1=z_2=0$ for $\beta\le\beta_c=1/(1+\omega)$, 
-and $z_1=z_2\ne 0$ for $\beta>\beta_c$.
+The system has the solutions $z_1=z_2=z_s=0$ for $\beta\le\beta_c=1/(1+\omega)$, 
+and $z_1=z_2=z_s\ne 0$ for $\beta>\beta_c$. Note that $\beta_c$ is different 
+in presence of disorder (compare with~\eqref{tc}).
+
+The solution $z_s$ of the saddle point equations~\eqref{clean-is-spe} is shown 
+in Fig.~\ref{saddle_clean} for $\omega=0,1/2,1$. The vertical-dotted line 
+is $\beta_c$ for $\omega=1/2$. Notice that at low temperatures $z_s$ is 
+independent on $\omega$, and one has $z_s\sim\beta$.
 
@@
 \includegraphics*[width=0.9\linewidth]{./draft_figs/saddle_clean}
-%\includegraphics*[width=0.9\linewidth]{./RSB0_saddle_ht}
-\caption{
- The S-K model on the $2$-sheets booklet in the 
- paramagnetic phase: the solution $q_0$ of the saddle point 
- equation~\eqref{saddle-high-t} plotted as a function of the booklet aspect 
- ratio $\omega$ and several values of the inverse temperature $\beta=1/T$. 
- At $\omega=1$ one has $q_0=1,\forall\beta$. In the zero-temperature limit 
- one has $q_0\to 1,\forall\omega$. The straight line is the infinite 
- temperature result. 
+%\includegraphics*[width=0.9\linewidth]{./saddle_clean}
+\caption{ The infinite-range Ising model on the $2$-sheets booklet: saddle point 
+ approximation. The solution $z_s$ of the saddle point equations~\eqref{clean-is-spe} 
+ plotted as a function of the inverse temperature $\beta$ and for booklet aspect 
+ ratio $\omega=0,1/2,1$. The vertical dotted line denotes the critical inverse 
+ temperature for $\omega=1/2$. 
 }
@@
 
+%##########################################################################
+\subsection{R\'enyi entropy and mutual information: saddle point results}
+
+It is straightforward to obtain the R\'enyi entropies $S_n=(F(\omega=0,n,\beta)-
+F(\omega,n,\beta))/(n-1)$ using~\eqref{clean-is-F} and~\eqref{renyi}. 
+Figure~\ref{renyi_clean} plots the entropy density $S_2/N$ versus the inverse 
+temperature $\beta$. $S_2$ exhibits a volume-law behavior $S_2\propto N$ for 
+all values of $\beta$ and $\omega$. The different curves correspond to different 
+booklet aspect ratios $\omega$. Clearly, $S_2$ exhibits the volume-law behavior 
+$S_2\propto N$ at all temperatures. For $\beta\le\beta_c$ one has the flat behavior 
+$S_2=\omega\log(2)$, whereas $S_2$ is vanishing in the low-temperature regime. 
+The full symbol (rhombi) in Figure~\ref{renyi_clean} are exact results for a 
+booklet with $N=400$ spins per sheet (see next section), and are in good 
+agreement with the saddle point approximation results.
+
+The mutual information per spin ${\mathcal I}_2/N$ is reported in 
+Figure~\ref{mi_clean}. The lines are the analytical results for booklet aspect 
+ratios $\omega=1/20,1/4,1/2$, while the full symbols are the exact results for 
+the booklet with $N=400$ spins per sheet. Clearly, ${\mathcal I}_2/N$ is exactly zero 
+in the high-temperature region for $\beta\le1/2$, it exhibits at maximum 
+at $\beta\approx 1$, and it is vanishing in the limit $\beta\to\infty$. 
+Similar to Figure~\ref{reny_clean} the full symbols are exact results for 
+a booklet with $N=400$ spins per sheet.
+
+Notice that similar features are observed for the S-K model (see 
+section~\ref{I2-section}). In particular, one should observe that ${\mathcal I}_2/N$ 
+does not exhibit any crossing at the critical point $\beta_c$. However, the information 
+about critical behavior is encoded in the finite-size corrections of ${\mathcal I}_2/N$ 
+(see next section), which are neglected in the saddle point treatment. 
+Finally, one should also stress that a dramatically different behavior is observed 
+in the mutual information obtained from the von Neumann entropy ${\mathcal I}\equiv 
+\lim_{n\to 1}{\mathcal I}_n$. Specifically, no volume law is present for ${\mathcal I}$, 
+which, instead, exhibits a logarithmic divergence as ${\mathcal I}=1/4\log(N)$ at the 
+critical point $\beta_c=1$ (see Ref.~\onlinecite{wilms-2012}).
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
@@
 \includegraphics*[width=0.9\linewidth]{./draft_figs/renyi_clean}
-%\includegraphics*[width=0.9\linewidth]{./RSB0_saddle_ht}
-\caption{
- The S-K model on the $2$-sheets booklet in the 
- paramagnetic phase: the solution $q_0$ of the saddle point 
- equation~\eqref{saddle-high-t} plotted as a function of the booklet aspect 
- ratio $\omega$ and several values of the inverse temperature $\beta=1/T$. 
- At $\omega=1$ one has $q_0=1,\forall\beta$. In the zero-temperature limit 
- one has $q_0\to 1,\forall\omega$. The straight line is the infinite 
- temperature result. 
+%\includegraphics*[width=0.9\linewidth]{./renyi_clean}
+\caption{ The infinite-range Ising model on the $2$-sheets booklet in the thermodynamic 
+ limit: the classical R\'enyi entropy density $S_2/N$, with $N$ the total number of spins 
+ on a single sheet of the booklet. $S_2/N$ is plotted against the inverse temperature 
+ $\beta$ and for booklet aspect ratio $\omega=1/4,1/2,1$. Note tht at high temperature 
+ $S_2=\omega\log(2)$. The full symbols denote the exact numerical results for a finite 
+ system with $N=400$. 
 }
-\label{saddle_clean}
+\label{renyi_clean}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
+\begin{figure}[t]
+\includegraphics*[width=0.9\linewidth]{./draft_figs/mi_clean}
+%\includegraphics*[width=0.9\linewidth]{./renyi_clean}
+\caption{ The infinite-range Ising model on the $2$-sheets booklet in the thermodynamic 
+ limit: the classical mutual information density ${\mathcal I}_2/N$ plotted against the 
+ inverse temperature $\beta$ and for booklet aspect ratio $\omega=1/4,1/2,1$. Note that  
+ ${\mathcal I}_2=0$ for $\beta\le 1/2$. The full symbols are the the exact numerical 
+ results for a finite system with $N=400$. 
+}
+\label{mi_clean}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%##########################################################################
+\subsection{R\'eny entropy and mutual information: Exact treatment}
+
+For finite number of spins $N$, $S_2$ and ${\mathcal I}_2$ can be calculated 
+exactly using the results obtained in Ref.~\onlinecite{wilms-2012}. The eigenstates 
+of~\eqref{is-clean} are product states. They can be characterized as $|p,i\rangle$, 
+with $p$ the total number of up spins (the remaining $N-p$ being down) and $i$ 
+labelling the $B(N,p)\equiv N!/(p!(N-p)!)$ eigenstates with the same $p$.
+
+The partition function of the model on a single sheet is given as 
+%
+\begin{equation}
+Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{N\beta(\frac{p}{N}-
+\frac{1}{2})^2},
+\end{equation}
+%
+where $\rho\equiv 1/Ze^{-\beta {\mathcal H}}$ is the thermal density matrix. 
+Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
+and $N-N_A$ spins, respectively, the reduced density matrix for $A$ is obtained 
+as~\cite{wilms-2012} 
+%
+\begin{equation}
+\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{N(\beta\frac{p}{N}-
+\frac{1}{2})^2}|p,i\rangle\langle p,i|. 
+\end{equation}
+%
+By performing the trace over part $B$ one obtains 
+%
+\begin{equation}
+\rho_A=\sum\limits_{p_A,i_A}R(p_A)|p_A,i_A\rangle\langle p_A,i_A|,
+\end{equation}
+%
+where $|p_A,i_A\rangle$ form a basis for part $A$ of the system and 
+%
+\begin{equation}
+R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{N\beta
+(\frac{p_A}{N}+\frac{p_B}{N}-\frac{1}{2})^2}.
+\end{equation}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
+\begin{figure}[t]
+\includegraphics*[width=0.9\linewidth]{./draft_figs/sub_leading}
+%\includegraphics*[width=0.9\linewidth]{./renyi_clean}
+\caption{ The infinite-range Ising model on the $2$-sheets booklet: saddle point corrections. 
+ The correction for the mutual information ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ are 
+ plotted against the inverse temperature $\beta$. The data are for a booklet with aspect 
+ ratio $\omega=1/2$. Here ${\mathcal I}_2^{(sp)}$ are the same data as in Figure~\ref{mi_clean} 
+ (dotted line). The vertical lines denote the critical temperatures $\beta_c$ for $\omega=1,
+ 1/2,0$ (from left to right). The horizontal dash-dotted line is $\log(2)$. Note the 
+ (logarithmically) divergent behavior at $\beta_c$. 
+}
+\label{sp_corr}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%e
+\begin{figure}[t]
+\includegraphics*[width=0.9\linewidth]{./draft_figs/clean_log}
+%\includegraphics*[width=0.9\linewidth]{./renyi_clean}
+\caption{ The infinite-range Ising model on the $2$-sheets booklet: 
+ Scaling of the corrections of the mutual information ${\mathcal I}_2$ 
+ at the booklet critical points $\beta_c=1/2,2/3,1$ (see 
+ vertical lines in Figure~\ref{sp_corr}). We plot $|{\mathcal I}_2-
+ {\mathcal I}_2^{(sp)}|$ versus $\log(N)$, with $N$ the number of spins 
+ on one sheet of the booklet. Here ${\mathcal I}_2^{(sp)}$ is the same 
+ as in Figure~\ref{mi_clean} (dotted line).  
+}
+\label{clean_log}
 \end{figure}
@@
 V.~Alba, J.\ Stat.\ Mech.\ (2013) P05013.
+
+\bibitem{wilms-2012}
+J.~Wilms, J.~Vidal, F.~Verstraete, and S.~Dusuel, J.\ Stat.\ Mech.\ (2012) P01023.
+
 \end{thebibliography}

### 2015-12-16 prb_resub/referee_response/response.txt
16/12/2015

@@
 	in equation (8).
+
+REFEREE:
+-------
 
@@
 	on the booklet. This is an exact correspondence, and it is not related to 
-	any notion of locality. To clarify this point we now show explicitly the 
-	equivalence between the booklet construction and (2) in the beginning of 
+	any notion of locality. To clarify this point we now demonstrate explicitly 
+	the equivalence between the booklet construction and (2) in the beginning of 
 	section 2. From the derivation it is clear that the booklet construction 
 	is meaningful also in mean-field models.
+
+	A further direct check is provided in appendix B where we discuss (following 
+	the referee suggestion) the classical Renyi entropy and the mutual information 
+	for the infinite-range clean (i.e., without disorder) Ising model. For instance, 
+	in Figure 12 and Figure 13 the continuous lines are obtained using the booklet 
+	construction, while the symbols (rhombi) are the results using the definition 
+	of the classical Renyi entropy and mutual information (formulas (2) and (4) 
+	in the manuscript). The agreement, apart for finite-size corrections, 
+	confirms the applicability of the booklet construction for infinite-range 
+	models.
 
@@
 
-	The only study we are aware of is in
+	We would like to thank the referee for this very useful comment. The only study we 
+	are aware of is in
 
@@
 	the authors investigate the standard mutual information which is obtained from the 
-	full reduced density matrix of the subsystem A.
+	Shannon entropy, instead of the classical Renyi one.
 
-	In contrast with our results the authors find that the mutual information is finite 
-	away from the critical point and diverges logarithmically at the critical point.
+	In contrast with our results the authors find that the Shannon mutual information is 
+	finite at any temperature except at the critical point where it diverges logarithmically.
 
-	In our case this logarithmic correction might be subleading to the volume law.
+	Motivated by the referee observation and the results of Wilms et al we now discuss 
+	in the new version of the manuscript the Renyi entropy and mutual information in the 
+	clean infinite-range Ising model (in appendix B). We find that, in constrast with the 
+	Shannon mutual information, the Renyi one exhibits a volume law for any temperature, 
+	similar to our result for the S-K model. Moreover, I_2 exhibits intriguing subleading 
+	(i.e., subextensive) contributions. Specifically, we numerically observe that these 
+	corrections are logarithmically divergent with system size N. Moreover, they are 
+	present at three values of the inverse temperature. Their precise behaviors is given 
+	as
 
-	TO BE COMPLETED
+		beta=1/2     ---->  1/4 log(N)
 
-	About the maximum
+		beta=1/(1+w) ---->  1/2 log(N)
+
+		beta=1	     ---->  1/2 log(N)
+
+	Notice that beta=1/(1+w) corresponds to the critical temperature on the 2-sheets 
+	booklet with aspect ratio w.
+
+	These new results raise the question whether similar subleading corrections are 
+	present in the S-K model, as also noticed by the referee. Importantly, it would be 
+	interesting to determine the prefactor of these logarithmic corrections to check 
+	whether they are affected by the disorder. However, one should notice that to 
+	investigate analytically this issue one should go beyond the saddle point 
+	approximation, which at least in the low-temperature regioon requires knowing the 
+	full replica-symmetry-broken solution of the model.
+
+	Another possibility is to focus at beta=1/2 where, in analogy with the clean case, 
+	a logarithmic correction is expected and where the high-temperature replica symmetric 
+	result fully captures the saddle point behavior. The strategy would be to consider the 
+	deviations from the saddle point in the Monte Carlo data. However, we checked that 
+	our numerical results are not precise enough to determine the corrections and further 
+	numerical effort would be needed to clarify this point.
 
@@
 
-	We thank the referee for this useful comment. 
-	Eq. (2), and later Eq. (5) via the replica trick, are both quite explicit. 
-	Combined with Eq. (4) this precisely described the mutual information in 
-	the SK model. The non-locality of the interactions does 
-	not affect the definition compared with the usual one for local models. 
-	The definition of region A is however less obvious, and in the case of 
-	this work, we simply take it as an arbitrary set of points, rather than 
-	one that is spatially connected. As it is clear from the manuscript 
-	the best way to calculate the mutual information is using (4) calculating 
-	the three different contributions S(A) S(B) and S(AUB) separately. These 
-	correspond to ratios of partition functions on the booklet with different 
-	aspect ratio omega. As this was not clearly stated in the manuscript we now 
-	have written it explicitly in section 2
+	We thank the referee for this useful comment. Eq. (2), and later Eq. (5) via the replica 
+	trick, are both quite explicit. Combined with Eq. (4) they give the mutual information in 
+	the SK model. The non-locality of the interactions does not affect the definition compared 
+	with the usual one for local models. The definition of region A is however less obvious, 
+	and in the case of this work, we simply take it as an arbitrary set of points, rather than 
+	one that is spatially connected. As it is clear from the manuscript the best way to calculate 
+	the mutual information is using (4) calculating the three different contributions S(A) S(B) 
+	and S(AUB) separately. These correspond to ratios of partition functions on the booklet with 
+	different aspect ratio w. In particular, S(AUB) is obtained from the ratio Z(w=1)/Z(w=0). 
+	As this was not clearly stated in the manuscript we now have written it explicitly in 
+	section 2
 
@@
 
-	(3). The authors summarized that the entropy is proportional to the
-	system size by using the numerical analysis. Since the entropy is
-	calculated from the logarithm of the partition function, the result
-	looks trivial for me. As far as I understand, the subleading term is
-	important to find the boundary law behavior in the local (non
-	mean-field) models. (The leading term is canceled out by the
-	definition of the mutual information). Do the authors consider that
-	the subleading term is not important in the present system? I expect
-	that some universal properties exist in the subleading terms.
+	(3). The authors summarized that the entropy is proportional to the system size by using the 
+	numerical analysis. Since the entropy is calculated from the logarithm of the partition function, 
+	the result looks trivial for me. As far as I understand, the subleading term is	important to find 
+	the boundary law behavior in the local (non mean-field) models. (The leading term is canceled out 
+	by the definition of the mutual information). Do the authors consider that the subleading term is 
+	not important in the present system? I expect that some universal properties exist in the subleading 
+	terms.
 
@@
 
-	We agree that in general the leading term is proportional to the 
-	system size is an obvious result. In the manuscript we report 
-	the entropy only as a sanity check of our calculations.  We also 
-	agree that it is likerly that the subleading terms contain 
-	more universal information. We thank the referee for raising this 
-	point. Although the calculation of the subleading corrections to 
-	the entropy and the mutual information is possible in principle, 
-	it requires going beyond the saddle point approximation described 
-	in section III C. This should be straightforward in the paramagnetic 
-	phase although it would require a considerable amount of work in 
-	below the critical point. Notice that the same problem is 
-	challenging in the regular SK model. We think that this goes 
+	We agree that in general the leading term is proportional to the system size is an obvious result. 
+	In the manuscript we report the entropy only as a sanity check of our calculations.  We also agree 
+	that it is likely that the subleading terms contain more universal information. We thank the referee 
+	for raising this point. Although the analytical calculation of the subleading corrections to the entropy 
+	and the mutual information is possible in principle, it requires going beyond the saddle point approximation 
+	described in section III C. This should be straightforward in the paramagnetic phase although it would 
+	require a considerable amount of work below the critical point. Notice that the same problem of 
+	calculating saddle point corrections is challenging in the regular SK model. We think that this goes 
 	beyond the scope of the paper and it is suitable for future work.
-
-	PUT REFERENCE TO PAPERS STUDYING FINITE SIZE IN SK
 
@@
 
-	(4). The authors study the aspect-ratio dependence of the result
-	closely. It is clearly understood that the limits omega=0 and 1
-	reduces to the standard results. This means that we can find a result
-	interpolating their limits in the present problem. I do not expect any
-	interesting behavior between the limits. What did the authors expect
-	as the result and what do the authors consider the obtained results
-	interesting, other than the crossing behavior?
+	(4). The authors study the aspect-ratio dependence of the result closely. It is clearly understood that 
+	the limits omega=0 and 1 reduces to the standard results. This means that we can find a result interpolating 
+	their limits in the present problem. I do not expect any interesting behavior between the limits. What 
+	did the authors expect as the result and what do the authors consider the obtained results interesting, 
+	other than the crossing behavior?
 
@@
 
-	We agree that omega=0 and 1 are trivial results, at least in terms of 
-	the standard SK model, and that one would expect that the results between 
-	these two points should vary smoothly, and this is reflected in the data. 
-	What was not obvious was the form of the interpolation between these two 
-	points. The same statement of the referee would apply to local models.  
-	However, as it is clear from Ref [29], in that case the shape function of the mutual 
-	information contains universal behavior if the parent model is critical and 
-	described by a conformal field theory. In our study we investigate the 
-	shape function in a non-trivial disordered model. Notice that this functions 
-	have been also investigated in clean (withoud disorder) mean field models 
-	in 
+	We agree that omega=0 and 1 are trivial results, at least in the standard SK model, and that one would 
+	expect that the results between these two points should vary smoothly, and this is reflected in our data. 
+	However, different aspect ratios omega are needed in the booklet constructions in order to construct the 
+	mutual information. We should also stress that the functional dependence of the mutual information on 
+	omega is not trivial. The same statement of the referee would apply to local models. However, as it is clear 
+	from Ref [29], the shape function of the mutual information contains universal behavior if the 
+	parent model is critical and described by a conformal field theory. In that respect, we believe it was 
+	worth examining the aspect ratio behavior in the SK model. Notice that this functions have been also 
+	investigated in clean (withoud disorder) mean field models in
+
 		O. Cohen, V. Rittenberg, T. Sadhu J Phys A 48 055002 (2015)
@@
 		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P01023 (2012)
-
-	In that respect, 
-	we believe it was worth examining the aspect ratio behavior in the SK model. 
-	The difference of course is that since the gluing procedure is a bulk effect, 
-	the entire system may go through a phase transition as a function of omega, 
-	rather than being able to view the system as two parts in contact with each 
-	other where one part is critical. In this light, it might be some non-constant 
-	temperature cut in (omega,beta) that shows the most interesting behavior.
 
@@
 
-	The non surprising result would have been if 1-RSB would have reproduced the results 
-	of the Monte Carlo simulation. The fact that 2-RSB was necessary shows the non-trivial 
-	nature of the transition in the replicated geometry, and represents an expanded set of 
-	assumptions compared to the base model. The procedure for handling disorder, usually done 
-	via integration over fictitious replicas, in the context of the replica trick, where one 
-	has physical replicas, is non-trivial, but grounding such theoretical calculations with 
-	numerics is necessary. In this respect, we see the SK model with the replica trick as a 
-	base case for studying replica models  in glassy systems, in the same way that the SK 
-	model itself is a prototype for understanding standard glassy systems.
+	From our answer to point 1) it should be clear now that our work is well grounded from the information 
+	point of view as we are studying the standard classical Renyi entropies and mutual information. These 
+	quantities have been shown to contain universal information for instance in local critical models described 
+	a conformal field theory (Ref. [29]). Again, we should stress that their behavior in disordered and glassy systems has 
+	not been investigated in the previous literature. We chose to focus on the SK model which is one of the few 
+	exactly solved models for spin glasses and the base case for understanding glassy behavior, and its solution, 
+	although the model is mean field, exhibits quite complex features.
+
+	We have found that the Renyi entropy S_2 and the mutual information I_2 have a volume law and we provided analytical 
+	results using the saddle point approximation. This can be consired as a zeroth order starting point because, as 
+	correctly observed by the referee and as clear from our results on the clean infinite range Ising model (appendix B), 
+	further interesting information could be contained in the finite-size effects. However, already the saddle point 
+	results for S_2 and I_2 are non trivial since they reflect the replica symmetry breaking pattern of the solution 
+	of the SK model. We should stress that we only provided the 1-RSB approximation for these quantities. The fact that 
+	the 2-RSB is necessary at low temperatures confirms the fact that our results are interesting.
+
+	Our results are essential in order to go beyond the saddle point, studying subextensive correctins in S_2 and I_2. 
+	This is confirmed by the results that we provide in appendix B where we show that already for the clean infinite 
+	range Ising model the mutual information contains logarithmically divergent (with system size) terms which reflect 
+	critical behaviors. Our work raises the important question as to whether such subextensive contributions are present 
+	at glassy transitions. Moreover, a related interesting question is if disorder renormalizes the prefactor of this 
+	logarithmic behavior. Additionally, for the SK model it is interesting to understand whether the replica-symmetry-breaking 
+	mechanism affects this prefactor. Besides being interesting in their own, our results are necessary in order to 
+	understand the subleading  of S_2 and I_2.
 
@@
 
-	(6). The authors only focused on the result at n=2. It would be
-	interesting if the authors mention the n-dependence of the result.
-	Especially, the limit n=1 would give a nontrivial result and is
-	interesting. I expect that it wouldn't be difficult to analyze the
-	replica symmetric solution.
+	(6). The authors only focused on the result at n=2. It would be	interesting if the authors mention the n-dependence of 
+	the result. Especially, the limit n=1 would give a nontrivial result and is interesting. I expect that it wouldn't 
+	be difficult to analyze the replica symmetric solution.
 
@@
 
-	TO BE DONE.
+	We thank the referee for asking about this point. In fact we thought about investigating the analytic continuation 
+	n->1 to obtain the Shannon Renyi entropy and mutual information. The referee question is interesting especially 
+	especially in order to compare with the results for the clean infinite range Ising model obtained in Wilms et al. 
+	It has been shown in fact in ... that the Shannon mutual information is O(1) (i.e., not extensive) at any temperature 
+	except for the critical point at beta=1 whete it diverges logarithmically with system size.
+
+	Following the referee suggestion we now provide results for the analytic continuation n->1. First, one should observe 
+	that in the limit of infinite temperature one has from formula () in our paper that
+
+	   I_n(beta)/N = beta^2 omega(1-omega)n/2    for beta --> 0
+
+	which implies that
+
+	   I_1/N = beta^2 omega(1-omega)/2
+
+	i.e., the Shannon entropy obeys a volume law in the paramagnetic phase. This is in contrast with the result in the 
+	clean Ising reported in Wilms et al and it is apparently an effect of the disorder. This suggests that the subextensive 
+	behavior for I_1 found for the clean system is an effect of fine tuned cancellations that do not happen in presence of 
+	disorder.
+
+	In the paper we now included the saddle point equation in the high-temperature phase (equation (31)).
 
@@
 	We would like to thank the referee for this useful comment. We now 
-	summarize the main results of the paper in the conclusions.
+	summarize the main results of the paper in the conclusions and not in the 
+	introduction, while in the introduction we stress better the physical motivation 
+	and the results of the work.
 

### 2015-12-16 sk_model_v20.tex
16/12/2015

@@
 where $q_0$ is determined by solving the saddle point condition $\partial[F_{para}
-(\omega,n,\beta)]/\partial q_0=0$. For the $2$-sheets booklet (i.e., $n=2$) this is  
+(\omega,n,\beta)]/\partial q_0=0$. The saddle point equation reads 
+%
+\begin{equation}
+\end{equation}
+%
+where we used that 
+%
+\begin{multline}
+\frac{1}{\sqrt{2\pi}}\int Dz\cosh^n(z\sqrt{q_0}\beta)= 
+\frac{1}{2}\Gamma(n,n/2)\\
++\frac{1}{2^{n-1}}\sum\limits_{k=0}^{\frac{n}{2}-1}\frac{\Gamma(n+1)}
+{\Gamma(k+1)\Gamma(n-k+1)}e^{2\beta^2 q_0 \big(\frac{n}{2}-k\big)^2}
+\end{multline}
+%
+For the $2$-sheets booklet (i.e., $n=2$) this is  
 given as   
@@
  The dash-dotted line is the analytical result in the replica-symmetric (RS) 
- approximation.  
+ approximation. In (a) the dotted line is the result for the clean, i.e., without 
+ disorder, infinite-range Ising model. 
 }
@@
 $[S_2^{1\textrm{-}RSB}]/N$ is in excellent agreement with the extrapolated Monte Carlo 
-data for $\beta\lesssim 2$.
+data for $\beta\lesssim 2$. Finally, for comparison we report in panel (c) the analytical 
+result (dotted line) for $S_2/N$ for the infinite-range Ising model without 
+disorder at $\omega=1/4$ (see Appendix~\ref{clean-is}).
 
@@
 and it is in perfect agreement with the MC data in the whole paramagnetic phase.  
+Finally, we should stress that similar qualitative behavior is observed for ${\mathcal I}_2/N$ 
+in the infinite-range Ising model without disorder. The analytical result for ${\mathcal I}_2/N$ 
+at $\omega=1/2$ in the thermodynamic limit is reported in panel (a) (dotted line).
 
@@
 should be negligible. For instance, at $\beta=0.6$ for $\omega=1/2$ one can estimate that 
-$|[{\mathcal I}_2^{RS}]-[{\mathcal I}_2^{1\textrm{-}RSB}]|/N\sim 2\cdot 10^{-5}$. Finally, clear deviations 
+$|[{\mathcal I}_2^{RS}]-[{\mathcal I}_2^{1\textrm{-}RSB}]|/N\sim 2\cdot 10^{-5}$. 
+Moreover, the results for the infinite-range clean Ising (see Appendix~\ref{is-clean}) suggest 
+that logarithmic scaling corrections as $\propto\log(N)/N$ could be present at criticality making 
+the extrapolation to the thermodynamic limit tricky. 
+Finally, clear deviations 
 from the RS result occur at lower temperatures. For instance, for $\omega=1/8$, the numerical results 
@@
 Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
-${\mathcal I}_2$ in the infinite-range Ising model without disorder defined by 
-the hamiltonian 
+${\mathcal I}_2$ in the infinite-range Ising model without disorder, i.e., the 
+Curie-Weiss (CW) model, defined by the hamiltonian 
 %
@@
 We consider the situation without external magnetic field, i.e., $h=0$ and 
-fix $J=1$.
+fix $J=1$. The phase diagram of the model exhibits a paramagnetic phase at 
+high temperature, while at low temperatures there is ferromagnetic order. The 
+two phases are separated by a phase transition at $\beta_c=1$.
+We consider both the situations with finite $N$ as well as the 
+thermodynamic limit. For finite $N$ we provide exact numerical results for 
+$S_2$ and ${\mathcal I}_2$, while we address the thermodynamic limit using 
+the booklet construction and the saddle point approximation.
+
+Similar to the S-K model, we find that the para-ferro transition persists on 
+the booklet, and the critical temperature depends on the booklet ratio 
+$\omega$. The R\'enyi entropy $S_2$ and the mutual information ${\mathcal 
+I}_2$ are extensive, and their densities $S_2/N,{\mathcal I}_2/N$ finite 
+and smooth at any temperature. Notice that this in constrast with what is 
+obtained for the von Neumann mutual information~\cite{wilms-2012} ${\mathcal I}$, 
+which is {\it finite} (i.e., ${\mathcal I}\sim {\mathcal O}(1)$) in the whole phase 
+diagram, except for a logarithmically divergent behavior at the critical 
+point at $\beta_c=1$.
+
+However, information about the phase transition is encoded in the subleading, 
+i.e. $o(N)$, corrections of ${\mathcal I}_2$. Precisely, logarithmically 
+divergent corrections are present at $\beta=1/2,1$ and $\beta=\beta_c(\omega)$, 
+with $\beta_c(\omega)$ the critical temperature of the model on the booklet 
+with aspect ratio $\omega$.
 
@@
 %##########################################################################
-\subsection{R\'eny entropy and mutual information: Exact treatment}
+\subsection{R\'enyi entropy and mutual information: Exact treatment}
 
@@
 
-The partition function of the model on a single sheet is given as 
-%
-\begin{equation}
-Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{N\beta(\frac{p}{N}-
+The partition function of the model is given as 
+%
+\begin{equation}
+Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{2N\beta(\frac{p}{N}-
 \frac{1}{2})^2},
@@
 where $\rho\equiv 1/Ze^{-\beta {\mathcal H}}$ is the thermal density matrix. 
+Similarly, one has 
+%
+\begin{equation}
+\label{rhon}
+Z^n(\beta)\equiv\textrm{Tr}\rho^n=\sum\limits_{p=0}^NB(N,p)e^{2nN\beta(\frac{p}{N}-
+\frac{1}{2})^2}. 
+\end{equation}
+%
 Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
@@
 \begin{equation}
-\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{N(\beta\frac{p}{N}-
+\rho_A\equiv\frac{1}{Z}\textrm{Tr}_B\sum\limits_{p,i}e^{2N\beta(\frac{p}{N}-
 \frac{1}{2})^2}|p,i\rangle\langle p,i|. 
@@
 \begin{equation}
+\label{rhoA}
 \rho_A=\sum\limits_{p_A,i_A}R(p_A)|p_A,i_A\rangle\langle p_A,i_A|,
@@
 \begin{equation}
-R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{N\beta
+R(p_A)\equiv\frac{1}{Z}\sum\limits_{p_B=0}^{N-N_A}B(N-N_A,p_B)e^{2N\beta
 (\frac{p_A}{N}+\frac{p_B}{N}-\frac{1}{2})^2}.
@@
 %
+From~\eqref{rhoA} it is straightforward to obtain 
+%
+\begin{equation}
+\label{trrhoA}
+\textrm{Tr}\rho_A^n=\sum\limits_{p_A=0}^{N_A}B(N_A,p_A)R^n(p_A). 
+\end{equation}
+%
+Similarly, $\textrm{Tr}\rho^n_B$ is obtained from~\eqref{trrhoA} substituting 
+$A\to B$ and $N_A\to N-N_A$, while $\textrm{Tr}\rho^n_{A\cup B}\equiv\textrm{Tr}
+\rho^n$ is given in~\eqref{rhon}. The R\'enyi entropies $S_n$ and the mutual 
+informations ${\mathcal I}_n$ can be numerically constructed numerically 
+using~\eqref{trrhoA}, \eqref{rhon} and the definitions~\eqref{renyi-intro}
+\eqref{MI}. The numerical results for $S_2$ and ${\mathcal I}_2$ for a system with 
+$N=400$ spins are shown in Figure~\ref{renyi_clean} and Figure~\ref{mi_clean}, and 
+are in good agreement with the saddle point results.
+
+Figure~\ref{sp_corr} focuses on the finite-size corrections to the saddle point 
+result for ${\mathcal I}_2$. We plot ${\mathcal I}_2-{\mathcal I}^{(sp)}_2$, with 
+${\mathcal I}_2^{(sp)}$ denoting the saddle point results (see Figure~\ref{mi_clean}), 
+versus $\beta$. We restrict ourselves to the situation with $\omega=N_A/N=1/2$, although 
+similar resutls are expected at different $\omega$. Clearly, ${\mathcal I}_2-
+{\mathcal I}_2^{(sp)}$ is vanishing at high temperature, whereas one has ${\mathcal I}_2-
+{\mathcal I}_2^{(sp)}\to\log(2)$ in the limit $\beta\to\infty$ (horizontal line). 
+Surprisingly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ diverges in the thermodynamic limit 
+for $\beta=1/2,2/3,1$ (vertical lines in the Figure), which are the critical 
+temperatures for the model on a booklet with $\omega=1,1/2,0$.
+
+This divergence is logarithmic with $N$ as confirmed in Figure~\ref{clean_log} plotting 
+$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|$ versus $\log(N)$ for fixed $\beta=1/2,2/3,1$. 
+Interestingly, the precise behavior depends on $\beta$. Specificaly, one has 
+$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/4\log(N)$ for $\beta=1/2$ and 
+$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/2\log(N)$ for $\beta=2/3$ and 
+$\beta=1$. Notice that this is dramatically different for the von Neumann mutual 
+information ${\mathcal I}=\lim_{n\to 1}{\mathcal I}_n$, which exhibits only one 
+divergent peak at $\beta=1$~\cite{wilms-2012}.
 

### 2015-12-18 prb_resub/referee_response/response.txt
18/12/2015

@@
 	n->1 to obtain the Shannon Renyi entropy and mutual information. The referee question is interesting especially 
-	especially in order to compare with the results for the clean infinite range Ising model obtained in Wilms et al. 
+	in order to compare with the results for the clean infinite range Ising model obtained in Wilms et al. 
 	It has been shown in fact in ... that the Shannon mutual information is O(1) (i.e., not extensive) at any temperature 
@@
 
-	Following the referee suggestion we now provide results for the analytic continuation n->1. First, one should observe 
-	that in the limit of infinite temperature one has from formula () in our paper that
+	Following the referee suggestion we now provide results for the analytic continuation n->1. In the new version of 
+	the manuscript in section IV B we discuss the analytic continuation for the paramagnetic replica symmetric case, 
+	although this could be done as well in the replica symmetry broken region of the phase diagram.
 
-	   I_n(beta)/N = beta^2 omega(1-omega)n/2    for beta --> 0
-
-	which implies that
+	From the solution we observe that in the limit of infinite temperature one has
 
@@
 	disorder.
-
-	In the paper we now included the saddle point equation in the high-temperature phase (equation (31)).
 

### 2015-12-20 sk_model_v20.tex
20/12/2015

@@
 tensor $q_{\gamma\gamma'}^{rr'}$ (see section~\ref{replica-sec} for its 
-definition). The generic structure of $q_{\gamma\gamma'}^{rr'}$ 
+definition). In~\ref{shannon} we perform the analytic continuation $n\to 1$, 
+which allows to obtain the Shannon mutual information $[{\mathcal I}_1]$. 
+The generic structure of $q_{\gamma\gamma'}^{rr'}$ 
 within the RS ansatz  is discussed in subsection~\ref{rs-section}. This allows us 
@@
 n\log(2)-\omega(n-1)\log(2)\\+
-\beta^2\Big(\frac{n}{4}-\frac{q_0^2}{4}(n^2-n)
-+\frac{\omega}{2}q_0n^2-q_0n\Big)\\
+\frac{\beta^2}{2}\Big(\frac{n}{2}-\frac{q_0^2}{2}(n^2-n)
++\omega q_0n^2-q_0n\Big)\\
 +(1-\omega)\log\int Dz\cosh^n(z\sqrt{q_0}\beta)
@@
 where $q_0$ is determined by solving the saddle point condition $\partial[F_{para}
-(\omega,n,\beta)]/\partial q_0=0$. The saddle point equation reads 
-%
-\begin{equation}
-\end{equation}
-%
-where we used that 
-%
-\begin{multline}
-\frac{1}{\sqrt{2\pi}}\int Dz\cosh^n(z\sqrt{q_0}\beta)= 
-\frac{1}{2}\Gamma(n,n/2)\\
-+\frac{1}{2^{n-1}}\sum\limits_{k=0}^{\frac{n}{2}-1}\frac{\Gamma(n+1)}
-{\Gamma(k+1)\Gamma(n-k+1)}e^{2\beta^2 q_0 \big(\frac{n}{2}-k\big)^2}
+(\omega,n,\beta)]/\partial q_0=0$. $[F_{para}(\omega,n,\beta)]$ can be written in 
+terms of simple functions using that 
+%
+\begin{multline}
+\frac{1}{\sqrt{2\pi}}\int Dz\cosh^n(z\sqrt{q_0}\beta)=\\
+\frac{1}{2^{n-1}}\sum\limits_{k=0}^{\lfloor n/2\rfloor-1}\frac{\Gamma(n+1)}
+{\Gamma(k+1)\Gamma(n-k+1)}e^{2\beta^2 q_0(n/2-k)^2}\\
++\frac{2^{-2\left\lfloor n/2\right\rfloor}\Gamma(n+1)}{\Gamma(n-\lfloor n/2\rfloor+1)
+\Gamma(\lfloor n/2\rfloor+1)}e^{2\beta^2q_0(n/2-\lfloor n/2\rfloor)^2}, 
+\end{multline}
+%
+where $\Gamma(x)$ denotes the Euler Gamma function. 
+The saddle point equation for $q_0$ reads 
+%
+\begin{multline}
+\label{sp-g}
+0=\beta\big(\omega n-1-q_0(n-1)\big)\\
++(1-\omega)\frac{\int Dz\cosh^{n-1}(z\sqrt{q_0}\beta)\sinh(z\sqrt{q_0}\beta)z}
+{\sqrt{q_0}\int Dz\cosh^n(z\sqrt{q_0}\beta)}. 
 \end{multline}
@@
 ansatz~\eqref{high-t-q} in Eqs.~\eqref{saddle-final}~\eqref{saddle-final-a}. 
-
 Clearly, for two independent copies of the S-K model, i.e., $\omega=0$,  
@@
 to check that  $q_0\approx 1-2(1-\omega)\exp(-2\beta^2)$ for $\beta\to\infty$.
+
+%##########################################################################
+\subsection{The analytic continuation $n\to 1$}
+\label{shannon}
+
+It is interesting to consider the analytic continuation $\lim_{n\to 1} [S_n]$ 
+and $\lim_{n\to 1}[{\mathcal I}_n]$ to obtain the Shannon entropy and mutual 
+information. In the limit $n\to 1$, $F_{para}(\omega,n,\beta)$ (see~\eqref{ht-logZ}) 
+does not depend on $q_0$ and $\omega$,  as expected. This holds for any 
+$\beta$ even including the effects of the replica symmetry breaking. However, 
+the Shannon entropy $S_1(A)$ (and the mutual information ${\mathcal I}_1$ thereof) 
+is non trivial due to the prefactor $1/(1-n)$ in~\eqref{renyi}. In order to 
+obtain $S_1(A)$ one should consider $1/(1-n)[F_{para}(\omega,n,\beta)]$ 
+performing carefully the limit $n\to 1$. The result reads 
+%
+\begin{multline}
+\label{sh-F}
+\frac{[F_{para}(\omega,1,\beta)]}{N(1-n)}=
+\omega\log(2)+
+\frac{\beta^2}{2}\Big(\frac{q_0^2}{2}n
+-\omega q_0(n+1)+q_0\Big)\\
+-(1-\omega)\frac{\int Dz\cosh(z\sqrt{q_0}\beta)
+\log\cosh(z\sqrt{q_0}\beta)}{\int Dz\cosh(z\sqrt{q_0\beta})}. 
+\end{multline}
+%
+The saddle point equation~\eqref{sp-g} for $q_0$ now becomes  
+%
+\begin{multline}
+(\omega-q_0)\exp\big(\beta^2\frac{q_0}{2}\big)
++(1-\omega)\int Dz\Big(\frac{z}{\beta\sqrt{q_0}}\sinh(z\sqrt{q_0}\beta)\\
+-\cosh(z\sqrt{q_0}\beta)\Big)\log\cosh(z\sqrt{q_0}\beta)=0. 
+\end{multline}
+%
+Notice that in the limit $\beta\to 0$ one has $q_0\to\omega$, which implies,   
+using~\eqref{sh-F} and~\eqref{MI}, the volume-law behavior $[{\mathcal I}_1]
+\to\beta^2/2\omega(1-\omega)N$. This in constrast with the clean 
+case~\cite{wilms-2012}, where ${\mathcal I}_1={\mathcal O}(1)$ for any 
+$\beta$ away from the critical point at $\beta_c=1$.
 
@@
 Here we discuss the R\'enyi entropy $S_2$ and the associated mutual information 
-${\mathcal I}_2$ in the infinite-range Ising model without disorder, i.e., the 
-Curie-Weiss (CW) model, defined by the hamiltonian 
+${\mathcal I}_2$ in the infinite-range Ising model without disorder, defined by 
+the hamiltonian 
 %
@@
 $S_2$ and ${\mathcal I}_2$, while we address the thermodynamic limit using 
-the booklet construction and the saddle point approximation.
+the booklet construction (see~\ref{booklet}) and the saddle point 
+approximation.
 
@@
 I}_2$ are extensive, and their densities $S_2/N,{\mathcal I}_2/N$ finite 
-and smooth at any temperature. Notice that this in constrast with what is 
-obtained for the von Neumann mutual information~\cite{wilms-2012} ${\mathcal I}$, 
-which is {\it finite} (i.e., ${\mathcal I}\sim {\mathcal O}(1)$) in the whole phase 
-diagram, except for a logarithmically divergent behavior at the critical 
-point at $\beta_c=1$.
-
-However, information about the phase transition is encoded in the subleading, 
-i.e. $o(N)$, corrections of ${\mathcal I}_2$. Precisely, logarithmically 
-divergent corrections are present at $\beta=1/2,1$ and $\beta=\beta_c(\omega)$, 
-with $\beta_c(\omega)$ the critical temperature of the model on the booklet 
-with aspect ratio $\omega$.
+and smooth at any temperature. Notice that this different for the Shannon 
+mutual information~\cite{wilms-2012} ${\mathcal I}_1$, which is {\it finite} 
+(i.e., ${\mathcal I}_1\sim {\mathcal O}(1)$) in the whole phase diagram, 
+except for a logarithmically divergent behavior (with system size) at the 
+critical point $\beta_c=1$.
+
+Finally, we show that the information about the phase transition is encoded in 
+the subleading, i.e. $o(N)$, corrections of ${\mathcal I}_2$. Precisely, 
+logarithmically divergent contributions are present at $\beta=1/2,1$ and 
+$\beta=\beta_c(\omega)$, with $\beta_c(\omega)$ the critical temperature of the 
+model on the booklet at fixed aspect ratio $\omega$.
 
@@
 
-The calculation of the booklet partition function $Z(\omega,n,\beta)$ 
-(see section~\ref{booklet}) can be done using the same techniques as in 
-section~\ref{the-model}. The result reads 
+We first discuss the thermodynamic limit. The calculation of the booklet partition 
+function $Z(\omega,n,\beta)$ (see section~\ref{booklet}) can be done using the same 
+techniques as in section~\ref{the-model}. The result reads 
 %
@@
 -(1-\omega)\log(2\cosh z_\delta)\Big]+\omega\log(2\cosh\sum_\delta z_\delta)
-\Big\}.
-\end{multline}
-%
-Using the saddle point approximation, from~\eqref{clean-is-Z} one obtains 
-$F(\omega,n,\beta)\equiv\log Z(\omega,n,\beta)$ as 
+\Big\}, 
+\end{multline}
+%
+with $\delta=1,\dots,n$. Using the saddle point approximation, from~\eqref{clean-is-Z} 
+one obtains $F(\omega,n,\beta)\equiv\log Z(\omega,n,\beta)$ as 
 %
@@
 and $z_1=z_2=z_s\ne 0$ for $\beta>\beta_c$. Note that $\beta_c$ is different 
-in presence of disorder (compare with~\eqref{tc}).
+in presence of disorder (see~\eqref{tc}).
 
 The solution $z_s$ of the saddle point equations~\eqref{clean-is-spe} is shown 
-in Fig.~\ref{saddle_clean} for $\omega=0,1/2,1$. The vertical-dotted line 
-is $\beta_c$ for $\omega=1/2$. Notice that at low temperatures $z_s$ is 
-independent on $\omega$, and one has $z_s\sim\beta$.
+in Fig.~\ref{saddle_clean} as a function of $\beta$ for $\omega=0,1/2,1$. 
+The vertical-dotted line is $\beta_c$ for $\omega=1/2$. Notice that at low 
+temperatures $z_s$ is independent on $\omega$, and one has $z_s\sim\beta$.
 
@@
 all values of $\beta$ and $\omega$. The different curves correspond to different 
-booklet aspect ratios $\omega$. Clearly, $S_2$ exhibits the volume-law behavior 
-$S_2\propto N$ at all temperatures. For $\beta\le\beta_c$ one has the flat behavior 
+booklet aspect ratios $\omega$. For $\beta\le\beta_c$ one has the flat behavior 
 $S_2=\omega\log(2)$, whereas $S_2$ is vanishing in the low-temperature regime. 
@@
 at $\beta\approx 1$, and it is vanishing in the limit $\beta\to\infty$.
-Similar to Figure~\ref{reny_clean} the full symbols are exact results for 
-a booklet with $N=400$ spins per sheet.
-
-Notice that similar features are observed for the S-K model (see 
-section~\ref{I2-section}). In particular, one should observe that ${\mathcal I}_2/N$ 
-does not exhibit any crossing at the critical point $\beta_c$. However, the information 
-about critical behavior is encoded in the finite-size corrections of ${\mathcal I}_2/N$ 
-(see next section), which are neglected in the saddle point treatment. 
-Finally, one should also stress that a dramatically different behavior is observed 
-in the mutual information obtained from the von Neumann entropy ${\mathcal I}\equiv 
-\lim_{n\to 1}{\mathcal I}_n$. Specifically, no volume law is present for ${\mathcal I}$, 
-which, instead, exhibits a logarithmic divergence as ${\mathcal I}=1/4\log(N)$ at the 
+
+Finally, one should stress that a dramatically different behavior is observed 
+in the Shannon mutual information ${\mathcal I}_1\equiv \lim_{n\to 1}{\mathcal I}_n$. 
+Specifically, ${\mathcal I}_1$ is finite in the thermodynamic limit, and it only 
+exhibits a logarithmic divergence as ${\mathcal I}=1/4\log(N)$ at the 
 critical point $\beta_c=1$ (see Ref.~\onlinecite{wilms-2012}).
@@
  $\beta$ and for booklet aspect ratio $\omega=1/4,1/2,1$. Note tht at high temperature 
- $S_2=\omega\log(2)$. The full symbols denote the exact numerical results for a finite 
- system with $N=400$. 
+ $S_2=\omega\log(2)$. The lines are obtained using the saddle point approximation, while 
+ the full symbols denote the exact numerical results for a finite system with $N=400$. 
 }
@@
 
-For finite number of spins $N$, $S_2$ and ${\mathcal I}_2$ can be calculated 
-exactly using the results obtained in Ref.~\onlinecite{wilms-2012}. The eigenstates 
+For finite $N$, $S_2$ and ${\mathcal I}_2$ can be calculated exactly using the 
+results obtained in Ref.~\onlinecite{wilms-2012}. The eigenstates 
 of~\eqref{is-clean} are product states. They can be characterized as $|p,i\rangle$, 
-with $p$ the total number of up spins (the remaining $N-p$ being down) and $i$ 
+with $p$ the total number of up spins (the remaining $N-p$ being down spins) and $i$ 
 labelling the $B(N,p)\equiv N!/(p!(N-p)!)$ eigenstates with the same $p$. 
-
-The partition function of the model is given as 
+The partition function of~\eqref{is-clean} is given as 
 %
@@
 Z(\beta)\equiv\textrm{Tr}\rho=\sum\limits_{p=0}^NB(N,p)e^{2N\beta(\frac{p}{N}-
-\frac{1}{2})^2},
-\end{equation}
-%
-where $\rho\equiv 1/Ze^{-\beta {\mathcal H}}$ is the thermal density matrix. 
+\frac{1}{2})^2}.
+\end{equation}
+%
 Similarly, one has 
@@
 \label{rhon}
-Z^n(\beta)\equiv\textrm{Tr}\rho^n=\sum\limits_{p=0}^NB(N,p)e^{2nN\beta(\frac{p}{N}-
+Z^n(\beta)\equiv\textrm{Tr}\sum\limits_{p=0}^NB(N,p)e^{2nN\beta(\frac{p}{N}-
 \frac{1}{2})^2}. 
@@
 %
+The thermal density matrix $\rho$ is defined as $\rho\equiv 1/Ze^{-\beta{\mathcal H}}$. 
 Given a bipartition of the spins into two groups $A$ and $B$ containing $N_A$ 
@@
 $A\to B$ and $N_A\to N-N_A$, while $\textrm{Tr}\rho^n_{A\cup B}\equiv\textrm{Tr}
-\rho^n$ is given in~\eqref{rhon}. The R\'enyi entropies $S_n$ and the mutual 
-informations ${\mathcal I}_n$ can be numerically constructed numerically 
+\rho^n$. The R\'enyi entropies $S_n$ and the mutual 
+informations ${\mathcal I}_n$ can be calculated numerically 
 using~\eqref{trrhoA}, \eqref{rhon} and the definitions~\eqref{renyi-intro}
@@
 $N=400$ spins are shown in Figure~\ref{renyi_clean} and Figure~\ref{mi_clean}, and 
-are in good agreement with the saddle point results.
-
-Figure~\ref{sp_corr} focuses on the finite-size corrections to the saddle point 
-result for ${\mathcal I}_2$. We plot ${\mathcal I}_2-{\mathcal I}^{(sp)}_2$, with 
-${\mathcal I}_2^{(sp)}$ denoting the saddle point results (see Figure~\ref{mi_clean}), 
-versus $\beta$. We restrict ourselves to the situation with $\omega=N_A/N=1/2$, although 
-similar resutls are expected at different $\omega$. Clearly, ${\mathcal I}_2-
-{\mathcal I}_2^{(sp)}$ is vanishing at high temperature, whereas one has ${\mathcal I}_2-
-{\mathcal I}_2^{(sp)}\to\log(2)$ in the limit $\beta\to\infty$ (horizontal line). 
-Surprisingly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ diverges in the thermodynamic limit 
-for $\beta=1/2,2/3,1$ (vertical lines in the Figure), which are the critical 
-temperatures for the model on a booklet with $\omega=1,1/2,0$.
-
-This divergence is logarithmic with $N$ as confirmed in Figure~\ref{clean_log} plotting 
-$|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|$ versus $\log(N)$ for fixed $\beta=1/2,2/3,1$. 
-Interestingly, the precise behavior depends on $\beta$. Specificaly, one has 
+are in good agreement with the results in the thermodynamic limit.
+
+Figure~\ref{sp_corr} focuses on the finite-size subextensive corrections for 
+${\mathcal I}_2$. We plot ${\mathcal I}_2-{\mathcal I}^{(sp)}_2$, with ${\mathcal I}_2^{(sp)}$ 
+denoting the saddle point extensive part of ${\mathcal I}_2$. We restrict ourselves to 
+$\omega=N_A/N=1/2$, although similar results have to be expected at different $\omega$. 
+Clearly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ is vanishing at high temperatures, 
+whereas one has ${\mathcal I}_2-{\mathcal I}_2^{(sp)}\to\log(2)$ in the limit 
+$\beta\to\infty$ (horizontal line). Surprisingly, ${\mathcal I}_2-{\mathcal I}_2^{(sp)}$ 
+diverges in the thermodynamic limit for $\beta=1/2,2/3,1$ (vertical lines in the 
+Figure), which are the critical temperatures for the model on a booklet with 
+$\omega=1,1/2,0$. 
+This divergence is logarithmic as a function of $N$, as confirmed in Figure~\ref{clean_log} 
+plotting $|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|$ versus $\log(N)$ for fixed $\beta=1/2,2/3,1$. 
+Interestingly, the precise behavior depends on $\beta$. One has 
 $|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/4\log(N)$ for $\beta=1/2$ and 
 $|{\mathcal I}_2-{\mathcal I}_2^{(sp)}|\propto 1/2\log(N)$ for $\beta=2/3$ and 
-$\beta=1$. Notice that this is dramatically different for the von Neumann mutual 
+$\beta=1$. Again, this is dramatically different for the von Neumann mutual 
 information ${\mathcal I}=\lim_{n\to 1}{\mathcal I}_n$, which exhibits only one 
-divergent peak at $\beta=1$~\cite{wilms-2012}.
+divergent peak~\cite{wilms-2012} at $\beta=1$.
 

### 2015-12-20 prb_resub/referee_response/response_v1.txt

--- 2015-12-10 prb_resub/referee_response/response.txt
@@
 Dear Editors,
+
+We are submitting a revised version of the manuscript BG13275
+"The classical mutual information in mean-field spin glass models".
+
+We would like to thank the editors for their work and the referees for 
+their useful comments and suggestions.
+
+We remind that the first referee considered our work interesting and clearly 
+written and recommended it for publication in its present form. The second 
+referee cosidered our results reliable and the paper very clearly written.
+However, he expressed some criticisms especially focusing on the physical 
+significance of considering the mutual information and the booklet 
+construction in models with infinite range interactions.
+
+We believe that we thoroughly addressed all the criticisms and suggestions of 
+the referees in the new version of the manuscript.
+
+Moreover, here below we provide a detailed answer to all the criticisms of the 
+referees.
+
+Sincerely,
+
+Vincenzo Alba
+Stephen Inglis 
+Lode Pollet
 
@@
 	We thank the referee for considering our work interesting and 
-	clearly written.
+	clearly written. We also would like to stress that classical entropies 
+	have not been studied yet in disordered spin models, which is another 
+	reason why we believe that our work is interesting.
 
@@
 
-	We apologise for not being very clear about the equivalence between (5) 
+	We apologize for not being very clear about the equivalence between (5) 
 	and (2). Eq. (5) is equivalent to Eq. (2) even with the long range 
@@
 	Notice that the only physical effect of long range interactions is that 
-	there is no area law in contrast with local models, as it is discussed 
+	there is no area law, in contrast with local models, as it is discussed 
 	extensively in the manuscript.
@@
 	In order to meet the suggestion of the second referee we moved the summary of 
-	results in the conclusions. Therefore, in the new version of the manuscript 
+	results to the conclusions. Therefore, in the new version of the manuscript 
 	the referee suggestion is implemented in the conclusions. First, we should 
 	clarify that $\beta$ always refers to the explicit temperature in a single 
-	replica, and never to the *effective* temperature on the booklet. We thank 
-	the referee for noticing that in the introduction we do not mention  explicitly 
-	the values of the critical temperature for the model on the booklet. We now 
-	mention explicitly that the critical temperature is a decreasing function of 
-	the booklet aspect ratio $\omega$ and that $\beta_c=1,1/2$ for $\omega=0,1$. 
-	Notice that that all the  values of beta that we mention in the summary of 
-	the results (\beta=1,\beta=3) correspond to the low-temperature phase of the 
-	model on the booklet.
+	replica, and never to the effective temperature on the booklet. We thank 
+	the referee for noticing that we do not mention  explicitly the values of 
+	the critical temperature for the model on the booklet. We now mention explicitly 
+	that the critical temperature is a decreasing function of the booklet aspect 
+	ratio $\omega$ and that $\beta_c=1,1/2$ for $\omega=0,1$. Notice that  
+	all the  values of beta that we mention in the summary of the results 
+	(\beta=1,\beta=3) correspond to the low-temperature phase of the model on 
+	the booklet.
 
@@
 		can be used  in models with no notion of space, where it quantifies 
-		the correlation between two groups of spins rathen than two spatial 
+		the correlation between two groups of spins rather than two spatial 
 		regions."
 
-	Moreover, (2) can be interpreted as ratios of partition functions defined 
-	on the booklet. This is an exact correspondence, and it is not related to 
-	any notion of locality. To clarify this point we now show explicitly the 
-	equivalence between the booklet construction and (2) in the beginning of 
-	section 2. From the derivation it is clear that the booklet construction 
-	is meaningful also in mean-field models.
+	As for the booklet construction, (2) can be interpreted as ratios of partition 
+	functions defined on the booklet. This is an exact correspondence, and it 
+	is not related to any notion of locality. To clarify this point we now demonstrate 
+	explicitly the equivalence between the booklet construction and (2) in a new paragraph 
+	at the beginning of section 2. From the derivation it is clear that the booklet 
+	construction is meaningful also in mean-field models.
 
-	Besides its meaning from the information theory point of view, from the 
-	physics perspective the mutual information provides a lot of information 
-	about critical systems without disorder. One of the most striking example is 
-	provided by the results in Ref. [29] in the manuscript. We believe that it is 
-	a natural and interesting question to study the mutual information in 
-	disordered systems, especially in presence of glassy physics.
-
-	(i) For instance, an interesting physics question per se it is to understand 
-	what are the fingerprints, if any, of glassy physics in the mutual 
-	information or in information-based quantities in general.
-
-	(ii) A related question is whether 
-	information motivated quantities could provide alternative good criticality 
-	witnesses for glassy transitions. To this purpose we should stress that 
-	even in the simple S-K while it is relatively easy to determine numerically 
-	the critical point of the paramagnetic-glassy transition using standard 
-	tools from critical phenomena, such as the Binder cumulant. In presence 
-	of a transverse magnetic field the transition persists but the critical 
-	point changes as a function of the field strength (Almeida-Thouless line). 
-	In presence of a field it is however much more demanding, as it is shown 
-	numerically for instance in
-
-		M. Picco, F. Ritort, and M. Sales, Eur. Phys. J. B 19, 565 (2001)
-
-	Even more difficult it is to clarify whether there is an Almeida-Thouless 
-	line in short-range disordered spin models.
-
-	Our work, although for the S-K model, provides the first results in this 
-	direction. Concerning (i) for the S-K model a related question is about 
-	the effect of the replica symmetry breaking on information motivated 
-	quantities. We clarified that while in the low-temperature phase of the 
-	model the replica symmetry breaking is reflected in the mutual information.
-
-	As correctly observed by the referee the 1RSB approximation is enough to 
-	obtain good agreement with the Monte Carlo simulations. However, we should 
-	stress that this is not true at arbitrarily low temperatures, as 
-	at some point the effects of the higher order replica symmetry breaking 
-	should become visible.
-
-	Concerning (ii)  our work shows that for mean-field spin glasses the 
-	mutual information does not show any crossing for different system sizes 
-	at the critical point. This implies that the muutual information as defined 
-	in the manuscript cannot be used as a good indicator of glassy phase 
-	transitions.
-
-	One interesting question would be whether this "failure" is due to the 
-	non locality of the model or to the presence of disorder. This could be 
-	investigated in disordered models exhibiting a glassy transition. This 
-	can be done only numerically as there is no exactly solvable model with 
-	spin glass transition and local interactions. Moreover, one should consider 
-	a three dimensional model. In fact, to our knowledge there are no glassy 
-	transitions at finite temperature in disordered spin models. This certainly 
-	goes beyond the scope of the present work.
-
-	Another possibility, as observed by the referee, it is that one has to 
-	focus on the subleading corrections to the mutual information in order 
-	to obtain a clear signature of the glassy transition. In general, subleading 
-	corrections to the entropies have been investigated a lot in the literature 
-	in the context of topolocical phases of matter, systems breaking continuous 
-	symmetries and bipartitions with sharp corners.
-
-	Figure 9 in our work provides some hints in this direction. Clearly the scaling 
-	corrections are dramatically different in the paramagnetic and in the glassy 
-	phase, decaying much more slowly in the latter. We regret we did not stress 
-	enough this point in the manuscript. We now added the sentence in the introduction
-
-		"We numerically observede that while in the paramagnetic phase the 
-		scaling correction to the muatual information decay as 1/L, a much 
-		slower decay as 1/L^2/3 is observed in the glassy phase."
-
-	The study of these scaling corrections, although possible using the same 
-	techniques employed for the regular S-K model, it is demanding as it requires 
-	using the corrections to the saddle point treatment presented in section II.
+	A further direct check is provided in appendix B where we discuss (following 
+	the referee suggestion) the classical Renyi entropy and the mutual information 
+	for the infinite-range clean (i.e., without disorder) Ising model. In Figure 12 
+	and Figure 13 the continuous lines are obtained using the booklet 
+	construction, while the symbols (rhombi) are the results using the definition 
+	of the classical Renyi entropy and mutual information (formulas (2) and (4) 
+	in the manuscript).
 
@@
 	where the model becomes equivalent to a classical infinite-range Ising model. However, 
-	the authors investigate the standard mutual information which is obtained from the 
-	full reduced density matrix of the subsystem A.
+	the authors investigate the Shannon mutual information (i.e., the limit $n\to1$) 
+	instead of the Renyi. This paper is now mentioned in the manuscript (Ref. [46]).
 
-	In contrast with our results the authors find that the mutual information is finite 
-	away from the critical point and diverges logarithmically at the critical point.
+	Motivated by the referee observation and the results of Ref. [46] we now discuss 
+	in the appendix B of the manuscript the Renyi entropy and mutual information in the 
+	clean infinite-range Ising model. We find that, both exhibit a volume law for any 
+	temperature. To compare with the SK model we now include in Figure 8 and 9 the results 
+	in the thermodynamic limit for S_2/N and I_2/N for the clean model.
 
-	In our case this logarithmic correction might be subleading to the volume law.
+	Interestingly, in the clean model I_2 exhibits subleading (i.e., subextensive) 
+	contributions. Specifically, these corrections are logarithmically divergent with 
+	system size N and are present only for three values of the inverse temperature. Their 
+	precise behaviors is given as
 
-	TO BE COMPLETED
+		beta=1/2     ---->  1/4 log(N)
 
-	About the maximum
+		beta=1/(1+w) ---->  1/2 log(N)
 
-		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P010011 (2011)
+		beta=1	     ---->  1/2 log(N)
+
+	Notice that beta=1/(1+w) corresponds to the critical temperature of the model on the 
+	2-sheets booklet with aspect ratio w.
+
+	This is different for the Shannon mutual information (see Ref. [46]), which is finite at 
+	any temperature except at the critical point $beta=1$ where it diverges logarithmically 
+	with system size.
+
+	These new results raise the question whether similar subleading corrections are 
+	present in the S-K model, as also noticed by the referee. It would be 
+	interesting to determine the prefactor of these logarithmic corrections to check 
+	whether they are affected by the disorder. Additionally, for the SK model it is 
+	interesting to understand whether the replica-symmetry-breaking mechanism affects the 
+	prefactor of the subleading logarithmic corrections of the mutual information.
+
+	However, in order to investigate analytically these issues one has to go beyond the saddle 
+	point approximation, which, at least in the low-temperature region, requires knowing the full 
+	replica-symmetry-broken solution of the model.
+
+	Another possibility is to focus at beta=1/2 where a logarithmic correction is expected, 
+	and where the high-temperature replica symmetric result that we provide fully captures 
+	the saddle point behavior. The strategy would be to consider the deviations from the saddle 
+	point in the Monte Carlo data. We checked that, indeed, our numerical results are suggestive 
+	of a logarithmic subleading correction although further numerical effort would be needed 
+	to clarify this point. We will certainly address this issue in future work.
 
@@
 
-	We thank the referee for this useful comment. 
-	Eq. (2), and later Eq. (5) via the replica trick, are both quite explicit. 
-	Combined with Eq. (4) this precisely described the mutual information in 
-	the SK model. The non-locality of the interactions does 
-	not affect the definition compared with the usual one for local models. 
-	The definition of region A is however less obvious, and in the case of 
-	this work, we simply take it as an arbitrary set of points, rather than 
-	one that is spatially connected. As it is clear from the manuscript 
-	the best way to calculate the mutual information is using (4) calculating 
-	the three different contributions S(A) S(B) and S(AUB) separately. These 
-	correspond to ratios of partition functions on the booklet with different 
-	aspect ratio omega. As this was not clearly stated in the manuscript we now 
-	have written it explicitly in section 2
+	We thank the referee for this useful comment. Eq. (2), and later Eq. (5) via the replica 
+	trick, are both quite explicit. Combined with Eq. (4) they give the mutual information in 
+	the SK model. The non-locality of the interactions does not affect the definition compared 
+	with the usual one for local models. The definition of region A is however less obvious, 
+	and in the case of this work, we simply take it as an arbitrary set of points, rather than 
+	one that is spatially connected. As it is clear from the manuscript the best way to calculate 
+	the mutual information is using (4) calculating the three different contributions S(A) S(B) 
+	and S(AUB) separately. They correspond to ratios of partition functions on the 
+	booklet with different omega as
+
+		S_AUB = Z(omega=1)/Z(omega=0),
+
+		S_A = Z(omega)/Z(omega=0)
+
+		S_B = Z(1-\omega)/Z(omega=0)
+
+	In the previous version of the manuscript it was not clearly stated how to obtain S_B and S_AUB. We 
+	now have written it explicitly in section 2
 
 		"The mutual information ${\mathcal I}_n(A,B,\beta)$ is obtained in terms of the booklet 
-		partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}. 
-		%%%
-		Clearly, $S_n(B)$ (cf. Eq.~\eqref{MI}) is obtained from~\eqref{renyi} and exchanging 
-		$A$ and $B$. Notice also that in~\eqref{renyi}  $Z(A\cup B,n,\beta)\equiv Z(n\beta)$ 
-		is the partition function of the model on the booklet with all the $n$ sheets identified, 
-		equivalently on a single sheet but at temperature $n\beta$."
+		partition functions using Eq.~\eqref{renyi} and Eq.~\eqref{MI}, where $S_n(B)$ is 
+		obtained from~\eqref{renyi} by exchanging $A$ and $B$. Notice also that in~\eqref{renyi}  
+		$Z(A\cup B,n,\beta)\equiv Z(n\beta)$ is the partition function of the model on the booklet 
+		with all the $n$ sheets identified, equivalently on a single sheet but at temperature $n\beta$."
 
-	From the numerical point of view, the strategy to evaluate the ratios of partition 
-	functions in (5) is outlined Appendix B.
+	We also added the sentence
+
+		...Here we restrict ourselves to the second R\'enyi entropy $[S_2]$, which is obtained 
+		in terms of the booklet partition functions $Z(\omega,2,\beta)$ (see II) as 
+		$-\log(Z(\omega,2,\beta)/Z(0,2,\beta))$...
+
+	at the beginning of section VII where we first discuss the Monte Carlo data for the classical 
+	Renyi to stress its definition in terms of booklet partition function.
+
+	From the numerical point of view, the strategy to evaluate the ratios of booklet partition 
+	functions is outlined Appendix C.
 
@@
 
-	We agree that in general the leading term is proportional to the 
-	system size is an obvious result. In the manuscript we report 
-	the entropy only as a sanity check of our calculations.  We also 
-	agree that it is likerly that the subleading terms contain 
-	more universal information. We thank the referee for raising this 
-	point. Although the calculation of the subleading corrections to 
-	the entropy and the mutual information is possible in principle, 
-	it requires going beyond the saddle point approximation described 
-	in section III C. This should be straightforward in the paramagnetic 
-	phase although it would require a considerable amount of work in 
-	below the critical point. Notice that the same problem is 
-	challenging in the regular SK model. We think that this goes 
-	beyond the scope of the paper and it is suitable for future work.
-
-	PUT REFERENCE TO PAPERS STUDYING FINITE SIZE IN SK
+	We agree that in general the leading term is proportional to the system size is an obvious result. 
+	In the manuscript we report the entropy only as a sanity check of our calculations.  We also agree 
+	that it is likely that the subleading terms contain more universal information. In fact, as we now 
+	discuss in appendix B this is the case for the regular infinite-range Ising model. We thank the referee 
+	for raising this point. However, although the analytical calculation of the subleading corrections to 
+	the entropy and the mutual information is possible in principle, it requires going beyond the saddle point 
+	approximation described in section III C. This should be easier in the paramagnetic (less interesting) 
+	phase but it would require a considerable amount of work below the critical point. As we also mentioned 
+	in our response to question (2) of the referee, we plan to address this issue in future work.
 
@@
 
-	We agree that omega=0 and 1 are trivial results, at least in terms of 
-	the standard SK model, and that one would expect that the results between 
-	these two points should vary smoothly, and this is reflected in the data. 
-	What was not obvious was the form of the interpolation between these two 
-	points. The same statement of the referee would apply to local models.  
-	However, as it is clear from Ref [29], in that case the shape function of the mutual 
-	information contains universal behavior if the parent model is critical and 
-	described by a conformal field theory. In our study we investigate the 
-	shape function in a non-trivial disordered model. Notice that this functions 
-	have been also investigated in clean (withoud disorder) mean field models 
-	in 
-		O. Cohen, V. Rittenberg, T. Sadhu J Phys A 48 055002 (2015)
-
-		J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P01023 (2012)
-
-	In that respect, 
-	we believe it was worth examining the aspect ratio behavior in the SK model. 
-	The difference of course is that since the gluing procedure is a bulk effect, 
-	the entire system may go through a phase transition as a function of omega, 
-	rather than being able to view the system as two parts in contact with each 
-	other where one part is critical. In this light, it might be some non-constant 
-	temperature cut in (omega,beta) that shows the most interesting behavior.
+	We agree that omega=0 and 1 are trivial results, at least in the standard SK model, and that one would 
+	expect that the results between these two points should vary smoothly, and this is reflected in our data. 
+	However, different aspect ratios omega are needed in the booklet constructions in order to construct the 
+	mutual information, which is the main reason why we present them. We should also stress that the functional 
+	dependence of the mutual information on omega is not trivial. The same statement of the referee would apply 
+	to local models. However, as it is clear from Ref [29], the shape function of the mutual information 
+	contains universal behavior if the parent model is critical and described by a conformal field theory. 
+	In that respect, we believe it was worth examining the aspect ratio behavior in the SK model.
 
@@
 
-	The non surprising result would have been if 1-RSB would have reproduced the results 
-	of the Monte Carlo simulation. The fact that 2-RSB was necessary shows the non-trivial 
-	nature of the transition in the replicated geometry, and represents an expanded set of 
-	assumptions compared to the base model. The procedure for handling disorder, usually done 
-	via integration over fictitious replicas, in the context of the replica trick, where one 
-	has physical replicas, is non-trivial, but grounding such theoretical calculations with 
-	numerics is necessary. In this respect, we see the SK model with the replica trick as a 
-	base case for studying replica models  in glassy systems, in the same way that the SK 
-	model itself is a prototype for understanding standard glassy systems.
+	From our answer to point 1) it should be clear now that our work is well grounded from the information theoretical 
+	point of view as we are studying the standard classical Renyi entropies and mutual information. These 
+	quantities have been shown to contain universal information for instance in local critical models described 
+	a conformal field theory (Ref. [29]). Again, we should stress that their behavior in disordered and glassy 
+	systems has not been investigated in the previous literature. We chose to focus on the SK model which is one of 
+	the few exactly solved models for spin glasses and the base case for understanding glassy behavior. Also its 
+	solution exhibits quite complex features (for instance, replica symmetry breaking). We find already quite 
+	interesting that these complex features are reflected in the leading behavior of the mutual information and 
+	entropy.
+
+	Moreover, our study can be considered a zeroth order starting point because, as correctly observed by the 
+	referee and as it is clear from our results on the clean infinite range Ising model (appendix B), further 
+	interesting information could be contained in the finite-size effects of the mutual information. On the other 
+	hand our study characterizing the extensive part of the mutual information provides the necessary background 
+	for conducting these further studies.
 
@@
 
-	TO BE DONE.
+	We thank the referee for asking about this point. In fact we thought about investigating the analytic continuation 
+	n->1 to obtain the Shannon Renyi entropy and mutual information. This question is interesting especially in order to 
+	compare with the results for the clean infinite range Ising model obtained in Ref. [46],  where it has been shown 
+	that the Shannon mutual information is O(1) (i.e., not extensive) at any temperature except for the critical point at 
+	beta=1 where it diverges logarithmically with system size.
+
+	Following the referee suggestion, we now provide results for the analytic continuation n->1. In the new version of 
+	the manuscript in section IV B we discuss the analytic continuation for the paramagnetic replica symmetric case, 
+	although this could be done as well in the replica symmetry broken region of the phase diagram.
+
+	From the solution we observe that in the limit of infinite temperature one has
+
+	   I_1/N = beta^2 omega(1-omega)/2
+
+	i.e., the Shannon mutual information obeys a volume law. This is in contrast with the result in the clean Ising 
+	reported in Ref. [46]. This suggests that the subextensive behavior for I_1 found for the clean system is an effect 
+	of fine tuned cancellations that do not happen in presence of disorder.
 
@@
 
-	We would like to thank the referee for this useful comment. We now 
-	summarize the main results of the paper in the conclusions.
+	We would like to thank the referee for this useful comment. We now summarize the main results of the paper only in the 
+	conclusions.
 
@@
 
-	(9). I am not sure whether this manuscript is suitable to PRB. I would
-	think that PRE is more appropriate.
+	(9). I am not sure whether this manuscript is suitable to PRB. I would think that PRE is more appropriate.
 
@@
 
-	Argue that similar paper appeared in PRB.
+	We believe that after our detailed answer to the referee points it is clear that our work addresses the issue of how 
+	standard information-theory motivated quantities such as entropies and mutual information are affected by disorder and 
+	glassy criticality. Disordered magnetic systems and glassy phase transitions are traditionally topics of PRB, as 
+	well as (especially in recenty years) entanglement and phase transitions. Therefore we believe that our paper 
+	is appropriate for PRB.
 
-In conclusion, the manuscript will be taken into consideration for
-publication if the authors clarify the physical significance of the
-analysis. And, I recommend the authors to reconsider the journals to
-submit the manuscript.
+=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
+SUMMARY OF MAIN CHANGES IN THE MANUSCRIPT 
+=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=-=
+
+1) Shortened introduction. Now the summary of our main results is in the Conclusions, 
+   as suggested by the second referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+2) Modified the captions of Figure 5,8,9 to meet the suggestions of the first referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+3) Added the results for the entropy and mutual information in the infinite-range 
+   clean Ising model in Figure 8,9.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+4) Added appendix B (with 5 Figures) to discuss the entropy and mutual information 
+   in the clean infinite-range Ising model to meet the suggestions of the second 
+   referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+5) Added subsection VI B to discuss the analytic continuation $n\to 1$, as suggested 
+   by the second referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+6) Added reference [46]
+
+	J. Wilms, J. Vidal, F. Verstraete, S. Dusuel, J. Stat. Mech. P01023 (2012)
+
+   to previous work on the Shannon mutual information in the infinite-range Ising model.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+7) Added
+
+	$\forall i\in A$
+
+   in Eq (8) as suggested by the first referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+8) Removed the sentence
+
+	"..., one obtains a standard Landau theory"
+
+   before Eq (40) in the previous version of the manuscript, as suggested by the first 
+   referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+9) Added the paragraph below formula (3)
+
+	" For local spin models the bipartition correspond to a spatial 
+	separation between the spins. However, the definition~\eqref{renyi-intro} 
+	can be used  in models with no notion of space, where it quantifies 
+	the correlation between two groups of spins rather than two spatial 
+	regions."
+
+   to meet the suggestion of the second referee.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+10) Added the paragraph
+
+	"...Given a generic \emph{classical} spin model at inverse temperature $\beta$, 
+	The probability $p_i$ of a given spin configuration $i\in{\mathcal C}$, with ${\mathcal 
+	C}$ being the set of all possible configurations, is given by the Boltzmann weight 
+	$p_i=e^{-\beta E(i)}/Z$, with $E(i)$ the associated energy. In presence of a 
+	bipartition (see Fig.~\ref{cartoon} (a)) the probability of a spin configuration 
+	$i_A\in{\mathcal C}_A$ is given as 
+	$p_{i_A}=\sum_{i_B}e^{-\beta E(i_A,i_B)}/Z$, where the sum is over all possible 
+	spin configurations in part $B$. Note that this is valid for generic interactions, 
+	i.e., both local and non-local ones. Clearly, one has $p^n_{i_A}\equiv\frac{1}{Z^n}
+	\sum_{(i^1_B,\dots,i^n_{B})}e^{-\beta\sum_k E(i_A,i^k_{B})}$...."
+
+   at the beginning of section II to meet the suggestions of both the referees.

### 2016-01-14 prb_resub/referee_response/response_v1.txt
resub

@@
 written and recommended it for publication in its present form. The second 
-referee cosidered our results reliable and the paper very clearly written.
+referee considered our results reliable and the paper very clearly written.
 However, he expressed some criticisms especially focusing on the physical 
@@
 
-Moreover, here below we provide a detailed answer to all the criticisms of the 
-referees.
+Here below we provide a detailed answer to all the criticisms of the referees.
 
@@
 
-	In the manuscript BG13275, the authors study the Reny entropy and
+	In the manuscript BG13275, the authors study the Renyi entropy and
 	mutual information in the Sherrington-Kirkpatrick model. Using the
@@
 	glassy criticality. Disordered magnetic systems and glassy phase transitions are traditionally topics of PRB, as 
-	well as (especially in recenty years) entanglement and phase transitions. Therefore we believe that our paper 
+	well as (especially in recent years) entanglement and phase transitions. Therefore we believe that our paper 
 	is appropriate for PRB.
